### 2020-09-08 doc/ACCAHA_BP_groups.Rmd
switch to officedown

---
title: "Predicted cardiovascular risk and blood pressure for Americans with diabetes, chronic kidney disease, and \u226565 years of age"
bibliography: refs.bib
csl: jacc.csl
output: 
  officedown::rdocx_document:
    reference_docx: style_manuscript.docx
---

```{r setup, include=FALSE}

knitr::opts_chunk$set(echo = FALSE)

loadd(exams)
loadd(current_analysis)
loadd(inline)
loadd(report)

nhanes_years <- exams %>%
  map_chr(~glue("{.x}-{.x+1}")) %>%
  glue_collapse(sep = ', ', last = ', and ')

rp <- report %>% 
  split(list(.$location, .$object_type))

current_analysis$tbl %<>% 
  mutate(across(where(is.numeric), as.integer))

refer_to <- function(label){
  report$pre_cap[report$reference == label]
}

```

Byron C. Jaeger^1^, Shakia T. Hardy^2^, Paul Muntner^2^, and Paul Whelton^3^

1. Department of Biostatistics, University of Alabama at Birmingham
2. Department of Epidemiology, University of Alabama at Birmingham
3. Department of Epidemiology, Tulane University

\newpage

# INTRODUCTION

_To be written in next draft_

# METHODS

NHANES was designed to assess the health and nutritional status of the non-institutionalized US population and is conducted by the National Center for Health Statistics of the Centers for Disease Control and Prevention.[@nhanes_home] Since 1999-2000, NHANES has been conducted in two-year cycles using a multistage probability sampling design to select participants. Each cycle is independent with different participants recruited. For the current analysis, `r as.english(length(exams))` cycles conducted in `r nhanes_years` were pooled for analysis.[@nhanes_tutorial_weights] The protocols for each NHANES cycle were approved by the National Center for Health Statistics of the Centers for Disease Control and Prevention Institutional Review Board. Written informed consent was obtained from each participant. The University of Alabama at Birmingham Institutional Review Board considered the analysis of NHANES data to be exempt research.

```{r}

# some inline results for the exclusion paragraph below

n_age_40_to_79 <- current_analysis$tbl %>% 
  filter(label == 'Aged 40-79 years') %>% 
  pull(sample_size) %>% 
  table_value()

n_bp_too_low <- current_analysis$tbl %>% 
  filter(str_detect(label, '^3 or more systolic and diastolic')) %>% 
  pull(n_removed) %>% 
  table_value()

n_missing_pcr <- current_analysis$tbl %>% 
  filter(str_detect(label, '^Complete data for variables')) %>% 
  pull(n_removed) %>% 
  table_value()

n_final <- table_value(min(current_analysis$tbl$sample_size))

```

\newline

The current analysis was restricted to adults aged 40 to 79 years of age who complete the NHANES interview and examination (n = `r n_age_40_to_79`). Participants with age <40 or >79 were not included because the ASCVD risk prediction equation recommended by the ACC/AHA BP guideline is not recommended in these age ranges. Participants who did not have three SBP and DBP measurements (n = `r n_bp_too_low`) and those who were missing information on age, race, sex, total and high-density lipoprotein cholesterol, smoking status, or diabetes (n = `r n_missing_pcr`) were excluded. After these exclusions, over the three NHANES cycles, a total of `r n_final` survey participants were included in the analysis (`r refer_to('fig_include_exclude')`).

\newline

## Data collection

Data were collected during an in-home interview and a study visit completed at a mobile examination center. Standardized questionnaires were used to assess survey participants’ age, sex, race/ethnicity, smoking habits, medical history and use of antihypertensive medication, oral glucose lowering medication and insulin. Medical history included questions about whether the participant had been told by a doctor or other health professional that they had a heart attack, coronary heart disease stroke, or heart failure. Blood and urine samples were collected during the medical examination. Of relevance to the current analysis, serum creatinine, serum glucose and glycated hemoglobin (HbA1c) were measured. Diabetes was defined by fasting serum glucose ≥126 mg/dL, non-fasting glucose ≥200 mg/dL, HbA1c ≥6.5%, or self-reported use of insulin or oral glucose lowering medication. Estimated glomerular filtration rate was calculated using the Chronic Kidney Disease Epidemiology Collaboration equation.[@levey2009new] Urinary albumin and creatinine levels were measured and used to calculate the albumin-to-creatinine ratio (ACR). CKD was defined by an estimated glomerular filtration rate <60 ml/min/1.73m^2^ or an ACR ≥30 mg/dL. Ten-year predicted risk for ASCVD was calculated using the pooled cohort risk equations for participants without a history of CVD.[@goff20142013] Participants with a history of CVD were presumed to have 10-year risk for ASCVD ≥10%.

\newline

## Blood pressure measurements

Physicians conducting study examinations followed the same protocol to measure SBP and DBP in each NHANES cycle. After survey participants had rested 5 minutes, their BP was measured by a trained physician using a mercury sphygmomanometer and an appropriately sized cuff. Three BP measurements were obtained at 30 second intervals. The mean of all available measurements was used to define SBP and DBP. Quality control included re-certification of physicians every quarter with retraining if needed. All physicians participated in annual retraining.

\newline

## Definitions of hypertension

Participants not taking antihypertensive medication were grouped into four non-overlapping categories based on the 2017 ACC/AHA BP guideline: Normal BP (SBP <120 mm Hg and DBP <80 mm Hg), elevated BP (SBP between 120 and 129 mm Hg and DBP <80 mm Hg), stage 1 hypertension (SBP between 130 and 139 mm Hg and/or DBP between 80 and 89 mm Hg with SBP <140 mm Hg and DBP <90 mm Hg), stage 2 hypertension (SBP ≥140 mm Hg or DBP ≥90 mm Hg). Participants taking antihypertensive medication were placed in a fifth group.

\newline

## Statistical analysis

Analyses were conducted for the overall population and among participants with diabetes, CKD, ≥65 years of age, and for those with any of these three conditions, separately. Participant characteristics were summarized as mean (standard error) and percentage for continuous and categorical variables, respectively. The percentage of US adults in each of the five BP/antihypertensive medication use categories was computed. The median 10-year predicted risk for ASCVD and the proportion with a predicted risk ≥10% was computed for participants in each of the BP/antihypertensive medication use categories. To assess the extent to which participants with a 10-year predicted ASCVD risk <10% were ‘borderline’ cases (i.e., predicted ASCVD risk of 5% to <10% or 7.5% to <10%), the proportion of participants in this subgroup with predicted risk of 0% to <2.5%, 2.5% to <5.0%, 5.0% to <7.5%, and 7.5% to <10% was estimated. The age-adjusted probability of having a 10-year predicted ASCVD risk ≥10% was estimated using logistic regression. The above analyses were repeated among participants with stage 1 hypertension.

\newline

NHANES sampling weights, which were calculated as the inverse probability of being selected for the survey, were used in all calculations to obtain US nationally representative estimates. The survey design of NHANES was also taken into account. Data analysis was conducted using `r version$version.string`. P-values were two-sided.

\newline

# RESULTS

Among US adults who were 40 to 79 years of age from `r min(exams)` to `r max(exams)+1`, the estimated prevalence (95% confidence interval [CI]) of diabetes and CKD was `r inline$prevDiabetesOverall` and `r inline$prevCkdOverall`, respectively, and the estimated proportion (95% CI) of adults aged ≥65 years was `r inline$prevAge65Overall` (`r refer_to('tab_characteristics')`). Overall, an estimated `r inline$prevS1hOverall` of US adults who were 40 to 79 years of age had stage 1 hypertension (`r refer_to('tab_bpdist')`). Among those with diabetes, CKD, and age ≥65 years, the estimated prevalence (95% CI) of stage 1 hypertension was `r inline$prevS1hDiabetes`, `r inline$prevS1hDiabetes` `r inline$prevS1hCkd`, and `r inline$prevS1hAge65`, respectively. Characteristics of US adults with stage 1 hypertension, overall, and with diabetes, CKD and age ≥65 years are presented in Table S1

\newline

## Predicted 10-year risk for atherosclerotic cardiovascular disease

Among US adults without a history of CVD, the estimated median (25th, 75th percentiles) 10-year predicted risk for ASCVD was `r inline$medianPcrOverall` overall and `r inline$medianPcrDiabetes`, `r inline$medianPcrCkd`, and `r inline$medianPcrAge65` among those with diabetes, CKD, and age ≥65 years, respectively (`r refer_to('tab_risk_overall')`; top panel). Among US adults with stage 1 hypertension and no history of CVD, the estimated median (25th, 75th percentiles) 10-year predicted risk for ASCVD was `r inline$medianPcrS1hOverall`. Within this subgroup of adults with stage 1 hypertension, those with diabetes and CKD had median (25th, 75th percentiles) predicted risks of of `r inline$medianPcrS1hDiabetes` and `r inline$medianPcrS1hCkd`, respectively, while adults aged ≥65 years had a median (25th, 75th percentiles) predicted risk of `r inline$medianPcrS1hAge65`. Among all US adults with stage 1 hypertension, an estimated `r inline$prevHighRiskS1hDiabetes` of those with diabetes, `r inline$prevHighRiskS1hCkd` of those with CKD and `r inline$prevHighRiskS1hAge65` who were ≥65 years of age had a 10-year predicted risk for ASCVD ≥10% or a history of CVD (`r refer_to('tab_risk_overall')`; bottom panel).

\newline

## Distribution of predicted risk in low risk groups

Among US adults with 10-year predicted risk for ASCVD <10% and no history of CVD, an estimated `r inline$propLowRiskOverall` had a 10-year predicted ASCVD risk <5% (`r refer_to('fig_hist_ovrl')`). Also, among this subgroup of adults, `r inline$propLowRiskDiabetes`, `r inline$propLowRiskCkd`, and `r inline$propLowRiskAge65` of those with diabetes, CKD and age ≥65 years had a 10-year predicted ASCVD risk <5% . The distribution of 10-year predicted ASCVD risk among US adults with predicted risk <10% and stage 1 hypertension are presented in `r refer_to('fig_hist_stg1')`. For these US adults, `r inline$propLowRiskS1hDiabetes` of those with diabetes and `r inline$propLowRiskS1hCkd` of those with CKD had a 10-year predicted ASCVD risk <5%,  compared with `r inline$propLowRiskS1hAge65` of those with ≥65 years of age.

\newline

## Age-adjusted analysis

The estimated probability of having a 10-year predicted ASCVD risk ≥10% or a history of CVD increased with older age and was 50% (`r inline$intervalHighRiskOvrlNoComorb`) at `r inline$ageHighRiskOvrlNoComorb` years for US adults without diabetes or CKD (`r refer_to('fig_risk_ovrl')`). For US adults with diabetes and US adults with CKD, the age when estimated probability was ≥50% for having a 10-year predicted ASCVD risk ≥10% or a history of CVD was `r inline$ageHighRiskOvrlDiabetes` and `r inline$ageHighRiskOvrlCkd`, respectively. Among US adults with stage 1 hypertension, the age where estimated probability of having a 10-year predicted ASCVD risk ≥10% or a history of CVD exceeded 50% was `r inline$ageHighRiskS1hNoComorb`, `r inline$ageHighRiskS1hDiabetes`, and `r inline$ageHighRiskS1hCkd` years for US adults without diabetes or CKD, with diabetes, and with CKD, respectively (`r refer_to('fig_risk_stg1')`).

\newline

# DISCUSSION

In the current study, the distribution of 10-year predicted risk for ASCVD was investigated among US adults aged 40 to 79 years from `r min(exams)` to `r max(exams)+1` The 2017 ACC/AHA BP guideline states that the vast majority of adults with diabetes, CKD, or ≥65 years of age have a 10-year predicted risk for ASCVD ≥10% and are recommended the initiation of antihypertensive drug therapy for stage 1 hypertension. However, the current analysis estimates that while `r inline$prevHighRiskDiabetes` of US adults with diabetes have 10-year predicted risk for ASCVD ≥10% or prevalent CVD, only `r inline$prevHighRiskS1hDiabetes` of adults with diabetes and stage 1 hypertension do. Similarly, `r inline$prevHighRiskCkd` of US adults with CKD but only `r inline$prevHighRiskS1hCkd` of US adults with CKD and stage 1 hypertension have 10-year predicted risk for ASCVD ≥10% or prevalent CVD. In contrast, among US adults with ≥65 years of age, `r inline$prevHighRiskAge65` have 10-year predicted risk for ASCVD ≥10% or prevalent CVD and `r inline$prevHighRiskS1hAge65` of US adults with stage 1 hypertension and ≥65 years of age do.

<!-- These results are not consistent the guideline's claim that a vast majority of adults with stage 1 hypertension and diabetes or CKD have 10-year predicted risk for ASCVD ≥10%. However, the guideline's claim regarding 10-year predicted ASCVD risk among adults with ≥65 years of age is consistent with our findings: `r inline$prevHighRiskAge65` of US adults aged ≥65 years and `r inline$prevHighRiskS1hAge65` of US adults aged ≥65 years with stage 1 hypertension have 10-year predicted risk for ASCVD ≥10% or prevalent CVD. -->

\newline

The 2017 ACC/AHA BP guideline recommends initiation of antihypertensive medication based on BP level, 10-year predicted risk for ASCVD, and other conditions including diabetes, CKD, and age ≥65 years. Previous analysis of pooled data from the REasons for Geographic and Racial Differences in Stroke study and the Jackson Heart Study showed that adults with stage 1 hypertension recommended versus not recommended to initiate antihypertensive medication by the 2017 ACC/AHA BP guideline were roughly 5 times more likely to experience stroke or coronary heart disease over 12.2 years of follow-up. Moreover, 87.7% of adults with stage 1 hypertension recommended to initiate treatment by the 2017 ACC/AHA BP guideline had a 10-year predicted risk for ASCVD ≥10%. However, the mean age of adults in this group was 70.2 years, with a standard deviation of 6.9, whereas the current study found the estimated mean (95% CI) age of US adults aged 40 to 79 from 2013 to 2018 was `r inline$meanAgeOverall`. Given that age is one of the most influential predictors in the pooled cohort risk equation, the younger age of adults in the US with stage 1 hypertension recommended to initiate antihypertensive medication by the ACC/AHA BP guidelines likely explains the difference in the distribution of 10-year predicted risk for ASCVD in the current study.

\newline

A prior analysis of NHANES data found that the proportion of adults in the US with SBP >130 mm Hg or DBP >80 mm Hg who are aware of their BP level declined from 2013 to 2018. Coupled with data showing that these adults may be at high risk for incident ASCVD events, it is clear that the pooled cohort risk equations or other CVD risk prediction tools should be used in clinical practice to advance critical healthcare goals such as increasing awareness of hypertension and risk for incident ASCVD. Computing predicted risk for ASCVD in the clinical setting may require additional time if a patient's medical record does not contain recent cholesterol measurements, but the current study suggests it is probably safe to assume US adults with stage 1 hypertension and ≥65 years of age have 10-year predicted risk for ASCVD ≥10%. This assumption is not supported for patients with stage 1 hypertension and diabetes or stage 1 hypertension and CKD, particularly for those aged <55 years. However, for younger adults with diabetes or CKD whose predicted 10-year risk for ASCVD is <10%, antihypertensive treatment may still provide substantial reduction in lifetime risk for ASCVD and prevention of complications associated with diabetes or CKD.

\newline

This study has several limitations. First, NHANES participants completed only one visit and guidelines recommend using the mean BP aggregated over 2 or more visits. Second, the response rate for NHANES has declined form 1999-2000 to 2017-2018. The effect of this decline on the current study is unclear. Third, the use of predicted ASCVD risk rather than observed ASCVD events may have over- or under-estimated ASCVD risk in subgroups where the pooled cohort risk equations are not well-calibrated. The current study also has a number of strengths. First, NHANES data are publicly available and representative of the US population when coupled with the NHANES survey design. Second, a host of software geared to enhance the transparency and reproducibility of scientific manuscripts have been leveraged to make the current analysis entirely reproducible and open source (see first author's publicly available GitHub repository: < _Link not yet active so we won't be scooped_ >).

\newline

In conclusion, the claim that a vast majority of adults with diabetes, CKD, or ≥65 years of age have a 10-year predicted risk for ASCVD ≥10% is not supported by data representative of the US population. Future studies should assess the cost-to-benefit ratio of early treatment for this population.

<!-- MAIN TABLES -->

\newpage

`r rp$main.table$caption[1]` 
`r fp_par(line_spacing = 1)`
`r rp$main.table$object[[1]]`

\newpage

`r rp$main.table$caption[2]` 
`r fp_par(line_spacing = 1)`
`r rp$main.table$object[[2]]`

\newpage

`r rp$main.table$caption[3]` 
`r fp_par(line_spacing = 1)`
`r rp$main.table$object[[3]]`

\newpage

<!-- MAIN FIGURES -->

`r rp$main.figure$caption[1]`
`r fp_par(line_spacing = 1)`

```{r fig.width=6, fig.height = 7, dpi = 300}

rp$main.figure$object[[1]]

```

`r rp$main.figure$legend[1]`
`r fp_par(line_spacing = 1)`

\newpage

`r rp$main.figure$caption[2]`
`r fp_par(line_spacing = 1)`

```{r fig.width=6, fig.height = 7, dpi=300}

rp$main.figure$object[[2]]

```

`r rp$main.figure$legend[2]`
`r fp_par(line_spacing = 1)`

\newpage

__SUPPLEMENT__

<!-- SUPPLEMENTAL TABLES -->

\newpage

`r rp$main.table$caption[3]` 
`r fp_par(line_spacing = 1)`
`r rp$main.table$object[[3]]`

<!-- SUPPLEMENTAL FIGURES -->

\newpage

`r rp$supplement.figure$caption[1]`
`r fp_par(line_spacing = 1)`

```{r out.width='100%'}

knitr::include_graphics('../fig/include_exclude.png')

```

`r rp$supplement.figure$legend[1]`
`r fp_par(line_spacing = 1)`

\newpage

`r rp$supplement.figure$caption[2]`
`r fp_par(line_spacing = 1)`

```{r fig.width=6, fig.height = 7, dpi=300}

rp$supplement.figure$object[[2]]

```

`r rp$supplement.figure$legend[2]`
`r fp_par(line_spacing = 1)`

\newpage

`r rp$supplement.figure$caption[3]`
`r fp_par(line_spacing = 1)`

```{r fig.width=6, fig.height = 7, dpi=300}

rp$supplement.figure$object[[3]]

```

`r rp$supplement.figure$legend[3]`
`r fp_par(line_spacing = 1)`

\newpage

# REFERENCES

### 2020-09-08 R/compile_report.R

@@ -1,33 +1,4 @@
 
-
-
-##' .. content for \description{} (no empty lines) ..
-##'
-##' .. content for \details{} ..
-##'
-##' @title
-##' @param x
-##' @param sep
-##' @param last
-##' @param alphabetical_order
-write_abbrevs <- function(
-  x,
-  sep = '; ',
-  last = '; ',
-  alphabetical_order = TRUE
-){
-
-  if(alphabetical_order){
-    x_names_alpha <- sort(names(x))
-    x <- x[x_names_alpha]
-  }
-
-  glue("{names(x)} = {x}") %>%
-    glue_collapse(sep = sep, last = last)
-
-}
-
-
 ##' .. content for \description{} (no empty lines) ..
 ##'
 ##' .. content for \details{} ..
@@ -49,7 +20,8 @@ compile_report <- function(exams,
                            fig_hist_ovrl,
                            fig_hist_stg1,
                            fig_risk_ovrl_bnry,
-                           fig_risk_stg1_bnry) {
+                           fig_risk_stg1_bnry,
+                           inline) {
 
   # setup ----
 
@@ -58,7 +30,8 @@ compile_report <- function(exams,
     BP = 'blood pressure',
     CKD = 'chronic kidney disease',
     CVD = 'cardiovascular disease',
-    HDL = 'High density lipoprotein'
+    HDL = 'high density lipoprotein',
+    ASCVD = 'atherosclerotic cardiovascular disease'
   )
 
   fts <- c(
@@ -76,15 +49,15 @@ compile_report <- function(exams,
 
   tbls_main <- tbls_supp <- tibble(
     object = list(),
-    caption = NA_character_
+    caption = NA_character_,
+    reference = NA_character_
   )
 
   figs_main <- figs_supp <- tibble(
     object = list(),
     caption = character(),
     legend = character(),
-    width = numeric(),
-    height = numeric()
+    reference = NA_character_
   )
 
   nhanes_years <-  exams %>%
@@ -114,7 +87,6 @@ compile_report <- function(exams,
 
   ftr_prisk_defn <- as_paragraph('Predicted risk for cardiovascular disease was computed using the Pooled Cohort Risk equations, based on the guideline by American College of Cardiology / American Heart Association, 2013')
 
-
   # sample sizes for table column headers -----------------------------------
 
   analysis <- current_analysis$data
@@ -126,7 +98,7 @@ compile_report <- function(exams,
     age_gt65     = sum(analysis$age_gt65 == "yes"),
[…]

### 2020-09-08 R/make_inline_results.R

@@ -1,0 +1,457 @@
+##' .. content for \description{} (no empty lines) ..
+##'
+##' .. content for \details{} ..
+##'
+##' @title
+##' @param design_overall
+##' @param design_s1hyp
+##' @return
+##' @author bcjaeger
+##' @export
+make_inline_results <- function(design_overall,
+                                design_s1hyp,
+                                risk_models) {
+
+
+  # rspec <- round_spec() %>%
+  #   round_using_magnitude(digits = c(2,1,1),
+  #                         breaks = c(1,10,Inf)) %>%
+  #   default_rounder_set()
+
+  # accompanying table 1 ----
+
+  prevDiabetesOverall <- svyciprop(~ diabetes, design_overall) %>%
+    tidy_svy(mult_by = 100) %>%
+    transmute(string = table_glue("{est}% ({lwr}, {upr})")) %>%
+    pull(string)
+
+  prevCkdOverall <- svyciprop(~ ckd, design_overall) %>%
+    tidy_svy(mult_by = 100) %>%
+    transmute(string = table_glue("{est}% ({lwr}, {upr})")) %>%
+    pull(string)
+
+  prevAge65Overall <- svyciprop(~ age_gt65, design_overall) %>%
+    tidy_svy(mult_by = 100) %>%
+    transmute(string = table_glue("{est}% ({lwr}, {upr})")) %>%
+    pull(string)
+
+  # not currently used in manuscript, but kept around just in case
+  meanAgeOverall <- svymean(~ age, design_overall) %>%
+    tidy_svy(mult_by = 1) %>%
+    transmute(string = table_glue("{est} ({lwr}, {upr})")) %>%
+    pull(string)
+
+  # accompanying table 2 ----
+
+  prevS1hOverall <- svyciprop(
+    formula = ~ I(bp_cat == 'Stage 1 hypertension'),
+    design = design_overall
+  ) %>%
+    tidy_svy(mult_by = 100) %>%
+    transmute(
+      string = table_glue("{est}% (95% CI: {lwr}, {upr})")
+    ) %>%
+    pull(string)
+
+  prevS1hDiabetes <- svyciprop(
+    formula = ~ I(bp_cat == 'Stage 1 hypertension'),
[…]

### 2020-09-08 R/plan.R

@@ -14,7 +14,6 @@
 the_plan <- drake_plan(
 
   exams = c(2013, 2015, 2017),
-  decimals = c(1, 1, 1),
 
   # Demographics ----
   demo = clean_demo(exams),
@@ -94,16 +93,14 @@ the_plan <- drake_plan(
   # Tables ----
 
   tbl1_overall = tabulate_characteristics(design_overall,
-                                          tbl1_variables,
-                                          decimals),
+                                          tbl1_variables),
 
   tbl1_s1hyp = tabulate_characteristics(design_s1hyp,
-                                        tbl1_variables,
-                                        decimals),
+                                        tbl1_variables),
 
-  tbl_bpdist = tabulate_bpdist(design_overall, decimals),
+  tbl_bpdist = tabulate_bpdist(design_overall),
 
-  tbl_risk_overall = tabulate_risk_summary(design_overall, decimals),
+  tbl_risk_overall = tabulate_risk_summary(design_overall),
 
   # Figures ----
 
@@ -115,10 +112,9 @@ the_plan <- drake_plan(
                 "No diabetes or chronic kidney disease" = "#8D4B08FF"),
 
   qts = seq(0.001, 0.999, by = 0.0001),
-  fig_hist_ovrl = visualize_risk_hist(design_overall, qts),
-  fig_hist_stg1 = visualize_risk_hist(design_s1hyp, qts),
+  fig_hist = visualize_risk_hist(design_overall, qts),
 
-  age_breaks = seq(40, 79, by = .01),
+  age_breaks = seq(40, 79, by = .001),
 
   risk_models = estimate_risk(design_overall, age_breaks),
 
@@ -130,9 +126,9 @@ the_plan <- drake_plan(
                                            bp_level = 'stg1',
                                            color_key = color_key),
 
-  # Report ----
+  inline = make_inline_results(design_overall, design_s1hyp, risk_models),
 
-  compile_report(
+  report = compile_report(
     exams,
     current_analysis,
     design_overall,
@@ -141,10 +137,21 @@ the_plan <- drake_plan(
     tbl_bpdist,
     tbl_risk_overall,
     current_analysis$tbl,
-    fig_hist_ovrl$ovrl,
-    fig_hist_stg1$stg1,
+    fig_hist$ovrl,
+    fig_hist$stg1,
     fig_risk_ovrl_bnry,
     fig_risk_stg1_bnry
[…]

### 2020-09-08 R/table_polisher.R

@@ -1,0 +1,19 @@
+##' .. content for \description{} (no empty lines) ..
+##'
+##' .. content for \details{} ..
+##'
+##' @title
+
+##' @return
+##' @author bcjaeger
+##' @export
+table_polisher <- function(ft,
+                           font_size = 11,
+                           font_name = "Calibri"){
+
+  ft %>%
+    font(fontname = font_name, part = 'all') %>%
+    fontsize(size = font_size, part = 'all') %>%
+    height(height = 2, part = 'footer')
+
+}

### 2020-09-08 R/tabulate_bpdist.R

@@ -29,6 +29,6 @@ tabulate_bpdist <- function(design, decimals) {
     filter(level == 'yes' | is.na(level)) %>%
     select(-level) %>%
     group_by(variable) %>%
-    mutate(n = tbl_val(100 * n / sum(n), decimals = decimals))
+    mutate(n = table_value(100 * n / sum(n)))
 
 }

### 2020-09-08 R/tabulate_characteristics.R

@@ -8,7 +8,7 @@
 tabulate_characteristics <- function(design, variables, decimals) {
 
   tb1_ovrl <- variables %>%
-    map(tb1_fun, design = design, decimals = decimals) %>%
+    map(tb1_fun, design = design) %>%
     bind_rows(.id = 'label')
 
   tb1_diab <- variables %>%
@@ -98,7 +98,7 @@ tb1_fun <- function(.x, by = NULL, design, decimals){
 
     init %>%
       mutate(
-        value = tbl_string("{mn} ({se})", decimals = decimals),
+        value = table_glue("{mn} ({se})"),
         ctns = TRUE
       ) %>%
       select(-mn, -se) %>%
@@ -122,7 +122,7 @@ tb1_fun <- function(.x, by = NULL, design, decimals){
     init %>%
       mutate(
         value = n / sum(n),
-        value = tbl_string("{100 * value}", decimals = decimals),
+        value = table_glue("{100 * value}"),
         ctns = FALSE
       ) %>%
       rename_at(.vars = .x, .funs = ~ 'level') %>%

### 2020-09-08 R/tabulate_risk_summary.R

@@ -5,7 +5,7 @@
 ##' @title
 ##' @param design
 ##' @param decimals
-tabulate_risk_summary <- function(design, decimals) {
+tabulate_risk_summary <- function(design) {
 
   add_confint <- function(x){
     cbind(x, confint(x))
@@ -95,8 +95,7 @@ tabulate_risk_summary <- function(design, decimals) {
       variable,
       bp_cat = fct_inorder(bp_cat),
       bp_cat = fct_relevel(bp_cat, 'Overall'),
-      tbv = tbl_string('{100*pcr_highrisk}\n({100*lwr}, {100*upr})',
-                       decimals = decimals)
+      tbv = table_glue('{100*pcr_highrisk}\n({100*lwr}, {100*upr})')
     ) %>%
     arrange(bp_cat) %>%
     pivot_wider(values_from = tbv, names_from = variable)
@@ -173,8 +172,7 @@ tabulate_risk_summary <- function(design, decimals) {
       variable,
       bp_cat = fct_inorder(bp_cat),
       bp_cat = fct_relevel(bp_cat, 'Overall'),
-      tbv = tbl_string('{100*est}\n({100*lwr}, {100*upr})',
-                       decimals = decimals)
+      tbv = table_glue('{100*est}\n({100*lwr}, {100*upr})')
     ) %>%
     arrange(bp_cat) %>%
     pivot_wider(values_from = tbv, names_from = variable))

### 2020-09-08 R/visualize_risk_hist.R

@@ -33,7 +33,7 @@ visualize_risk_hist <- function(design, qts) {
         transmute(
           x = mids,
           perc_val = counts / sum(counts),
-          perc_lab = tbl_string("{100 * perc_val}%", decimals = c(1,1,1))
+          perc_lab = table_glue("{100 * perc_val}%")
         )
     },
     .id = 'panel'

### 2020-09-08 _drake.R

@@ -8,6 +8,13 @@ lapply(list.files("./R", full.names = TRUE), source)
 ## The arguments to drake_config() are basically the same as those to make().
 ## lock_envir allows functions that alter the random seed to be used. The biggest
 ## culprits of this seem to be interactive graphics e.g. plotly and mapdeck.
-drake_config(the_plan,
-             lock_envir = FALSE,
-             seed = 329730)
+drake_config(
+  the_plan,
+  lock_envir = FALSE,
+  seed = 329730,
+  prework = {
+    round_spec() %>%
+      round_using_decimal(digits = 1) %>%
+      default_rounder_set()
+  }
+)

### 2020-09-08 packages.R

@@ -14,7 +14,7 @@ library(survey)
 library(splines)
 library(scales)
 # reporting
-library(tblStrings)
+library(table.glue)
 library(officer)
 library(glue)
 library(flextable)
@@ -22,6 +22,10 @@ library(devEMF)
 library(magick)
 library(paletteer)
 library(patchwork)
+library(rmarkdown)
+library(english)
+library(officer)
+library(officedown)
 
 conflicted::conflict_prefer("roc",       "pROC")
 conflicted::conflict_prefer("filter",    "dplyr")

### 2020-09-11 doc/ACCAHA_BP_groups.Rmd
cutpoints added as targets

@@
 loadd(report)
+loadd(fasted_hrs_lower)
+loadd(fasted_hrs_upper)
+loadd(gluc_cutpoint_fasted)
+loadd(gluc_cutpoint_fed)
+loadd(hba1c_cutpoint)
+loadd(egfr_cutpoint)
+loadd(acr_cutpoint)
 
@@
 Of relevance to the current analysis, serum creatinine, serum glucose and glycated hemoglobin (HbA1c) were measured.
-Diabetes was defined by fasting serum glucose ≥126 mg/dL, non-fasting glucose ≥200 mg/dL, HbA1c ≥6.5%, or self-reported use of insulin or oral glucose lowering medication.
+Diabetes was defined by fasting serum glucose ≥`r gluc_cutpoint_fasted` mg/dL, non-fasting glucose ≥`r gluc_cutpoint_fed` mg/dL, HbA1c ≥`r hba1c_cutpoint`%, or self-reported use of insulin or oral glucose lowering medication.
 Estimated glomerular filtration rate was calculated using the Chronic Kidney Disease Epidemiology Collaboration equation.[@levey2009new] Urinary albumin and creatinine levels were measured and used to calculate the albumin-to-creatinine ratio (ACR).
-CKD was defined by an estimated glomerular filtration rate <60 ml/min/1.73m^2^ or an ACR ≥30 mg/dL.
+CKD was defined by an estimated glomerular filtration rate <`r egfr_cutpoint` ml/min/1.73m^2^ or an ACR ≥`r acr_cutpoint` mg/dL.
 Ten-year predicted risk for ASCVD was calculated using the pooled cohort risk equations for participants without a history of CVD.[@goff20142013] Participants with a history of CVD were presumed to have 10-year risk for ASCVD ≥10%.
@@
 ## Definitions of hypertension
+
+<!-- These are hard coded to discourage messing with guideline recs -->
 
@@
 
-In the current study, the distribution of 10-year predicted risk for ASCVD was investigated among US adults aged 40 to 79 years from `r min(exams)` to `r max(exams)+1` The 2017 ACC/AHA BP guideline states that the vast majority of adults with diabetes, CKD, or ≥65 years of age have a 10-year predicted risk for ASCVD ≥10% and are recommended the initiation of antihypertensive drug therapy for stage 1 hypertension.
+<!-- In the current study, the distribution of 10-year predicted risk for ASCVD was investigated among US adults aged 40 to 79 years from `r min(exams)` to `r max(exams)+1`  -->
+
+The 2017 ACC/AHA BP guideline states that the vast majority of adults with diabetes, CKD, or ≥65 years of age have a 10-year predicted risk for ASCVD ≥10% and are recommended the initiation of antihypertensive drug therapy for stage 1 hypertension.
 However, the current analysis estimates that while `r inline$prevHighRiskDiabetes` of US adults with diabetes have 10-year predicted risk for ASCVD ≥10% or prevalent CVD, only `r inline$prevHighRiskS1hDiabetes` of adults with diabetes and stage 1 hypertension do.
@@
 In contrast, among US adults with ≥65 years of age, `r inline$prevHighRiskAge65` have 10-year predicted risk for ASCVD ≥10% or prevalent CVD and `r inline$prevHighRiskS1hAge65` of US adults with stage 1 hypertension and ≥65 years of age do.
+Among adults whose 10-year predicted risk for ASCVD was <10%, roughly 50% of those with diabetes or CKD had 10-year predicted risk for ASCVD <5%, whereas over 90% of adults aged ≥65 years had 10-year predicted risk for ASCVD between 5% and 10%.
 
@@
 Moreover, 87.7% of adults with stage 1 hypertension recommended to initiate treatment by the 2017 ACC/AHA BP guideline had a 10-year predicted risk for ASCVD ≥10%.
-However, the mean age of adults in this group was 70.2 years, with a standard deviation of 6.9, whereas the current study found the estimated mean (95% CI) age of US adults aged 40 to 79 from 2013 to 2018 was `r inline$meanAgeOverall`.
+However, the mean age of adults in this group was 70.2 years, with a standard deviation of 6.9, whereas the estimated mean (95% CI) age of US adults with stage 1 hypertension in the current analysis was `r inline$meanAgeS1h`.
 Given that age is one of the most influential predictors in the pooled cohort risk equation, the younger age of adults in the US with stage 1 hypertension recommended to initiate antihypertensive medication by the ACC/AHA BP guidelines likely explains the difference in the distribution of 10-year predicted risk for ASCVD in the current study.
@@
 A prior analysis of NHANES data found that the proportion of adults in the US with SBP >130 mm Hg or DBP >80 mm Hg who are aware of their BP level declined from 2013 to 2018.
-Coupled with data showing that these adults may be at high risk for incident ASCVD events, it is clear that the pooled cohort risk equations or other CVD risk prediction tools should be used in clinical practice to advance critical healthcare goals such as increasing awareness of hypertension and risk for incident ASCVD.
+Coupled with data showing that these adults may be at high risk for incident ASCVD, it is clear that the pooled cohort risk equations or other CVD risk prediction tools should be used in clinical practice to advance critical healthcare goals such as increasing awareness of hypertension and controlling BP levels.
 Computing predicted risk for ASCVD in the clinical setting may require additional time if a patient's medical record does not contain recent cholesterol measurements, but the current study suggests it is probably safe to assume US adults with stage 1 hypertension and ≥65 years of age have 10-year predicted risk for ASCVD ≥10%.
@@
 First, NHANES data are publicly available and representative of the US population when coupled with the NHANES survey design.
-Second, a host of software geared to enhance the transparency and reproducibility of scientific manuscripts have been leveraged to make the current analysis entirely reproducible and open source (see first author's publicly available GitHub repository: < _Link not yet active so we won't be scooped_ >).
+Second, a collection of open-source software geared to enhance the transparency and reproducibility of scientific findings were leveraged to make the current analysis entirely reproducible and publicly available (see first author's GitHub repository: < _Link not yet active so we won't be scooped_ >).
+A point of novelty is that anyone with internet access may download this repository of code and reproduce the current manuscript as-is or with different initial parameters, e.g.
+using data from four NHANES cycles rather than three or modifying exclusion criteria.
+When different parameters are used, results in the manuscript will dynamically update.
+A detailed set of instructions for engaging with the project is provided in the repository.
 
@@
 
-`r rp$main.table$caption[3]` 
+`r rp$supplement.table$caption[1]` 
 `r fp_par(line_spacing = 1)`
-`r rp$main.table$object[[3]]`
+`r rp$supplement.table$object[[1]]`
 

### 2020-09-11 R/compile_report.R

@@ -4,12 +4,28 @@
 ##' .. content for \details{} ..
 ##'
 ##' @title
+##'
+##' @param exams
+##' @param current_analysis
 ##' @param tbl1_overall
 ##' @param tbl1_s1hyp
 ##' @param tbl_bpdist
+##' @param design
+##' @param tbl_exclusions
+##' @param fig_hist_ovrl
+##' @param fig_hist_stg1
+##' @param fig_risk_ovrl_bnry
+##' @param fig_risk_stg1_bnry
 ##' @param tbl_risk_overall
-##' @param tbl_risk_40to79
+##'
 compile_report <- function(exams,
+                           fasted_hrs_lower,
+                           fasted_hrs_upper,
+                           gluc_cutpoint_fasted,
+                           gluc_cutpoint_fed,
+                           hba1c_cutpoint,
+                           egfr_cutpoint,
+                           acr_cutpoint,
                            current_analysis,
                            design,
                            tbl1_overall,
@@ -20,8 +36,7 @@ compile_report <- function(exams,
                            fig_hist_ovrl,
                            fig_hist_stg1,
                            fig_risk_ovrl_bnry,
-                           fig_risk_stg1_bnry,
-                           inline) {
+                           fig_risk_stg1_bnry) {
 
   # setup ----
 
@@ -68,10 +83,9 @@ compile_report <- function(exams,
 
   value_note <- as_paragraph("Table values are mean (standard error) or proportion.")
 
-  ftr_ckd <- as_paragraph('Chronic kidney disease is defined by an albumin-to-creatinine ratio \u2265 30 mg/dl or an estimated glomerular filtration rate <60 ml/min/1.73m\u00b2')
+  ftr_ckd <- as_paragraph(glue('Chronic kidney disease is defined by an albumin-to-creatinine ratio \u2265{acr_cutpoint} mg/dl or an estimated glomerular filtration rate <{egfr_cutpoint} ml/min/1.73m\u00b2'))
 
-  ftr_diab <- as_paragraph('Diabetes was defined by fasting serum glucose \u2265 126 mg/dL, non-fasting glucose \u2265 200 mg/dL, HbA1c \u2265 6.5%, or self-reported use of insulin or oral glucose lowering medication.')
-
[…]

### 2020-09-11 R/derive_others.R

@@ -4,14 +4,15 @@
 ##'
 ##' @title
 ##' @param data
-derive_others <- function(data, exams) {
+derive_others <- function(data, exams,
+                          acr_cutpoint=30) {
 
   data %>%
     mutate(
       # pooling weights for pooled analysis
       wts_mec_2yr = wts_mec_2yr / length(exams),
       # chronic kidney disease variables
-      albuminuria = if_else(acr_mgg >= 30, "yes", "no"),
+      albuminuria = if_else(acr_mgg >= acr_cutpoint, "yes", "no"),
       ckd = if_else(albuminuria == "yes" | egfr_low == "yes", "yes", "no"),
       # update categories to align with acc/aha guidelines
       age_group = case_when(
@@ -82,7 +83,6 @@ derive_others <- function(data, exams) {
         "Other Race/ethnicity - Including Multi-Racial" = "Other Race - Including Multi-Racial"
       )
     ) %>%
-    # dropping variables I don't need
     select(
       exam,
       seqn,

### 2020-09-11 R/make_inline_results.R

@@ -13,11 +13,6 @@ make_inline_results <- function(design_overall,
                                 risk_models) {
 
 
-  # rspec <- round_spec() %>%
-  #   round_using_magnitude(digits = c(2,1,1),
-  #                         breaks = c(1,10,Inf)) %>%
-  #   default_rounder_set()
-
   # accompanying table 1 ----
 
   prevDiabetesOverall <- svyciprop(~ diabetes, design_overall) %>%
@@ -35,8 +30,12 @@ make_inline_results <- function(design_overall,
     transmute(string = table_glue("{est}% ({lwr}, {upr})")) %>%
     pull(string)
 
-  # not currently used in manuscript, but kept around just in case
   meanAgeOverall <- svymean(~ age, design_overall) %>%
+    tidy_svy(mult_by = 1) %>%
+    transmute(string = table_glue("{est} ({lwr}, {upr})")) %>%
+    pull(string)
+
+  meanAgeS1h <- svymean(~ age, design_s1hyp) %>%
     tidy_svy(mult_by = 1) %>%
     transmute(string = table_glue("{est} ({lwr}, {upr})")) %>%
     pull(string)
@@ -263,7 +262,7 @@ make_inline_results <- function(design_overall,
   ) %>%
     tidy_svy(mult_by = 100) %>%
     transmute(
-      string = table_glue("{est}% (95% CI {lwr}, {upr})")
+      string = table_glue("{est}% (95% CI: {lwr}, {upr})")
     ) %>%
     pull(string)
 
@@ -273,7 +272,7 @@ make_inline_results <- function(design_overall,
   ) %>%
     tidy_svy(mult_by = 100) %>%
     transmute(
-      string = table_glue("{est}% (95% CI {lwr}, {upr})")
+      string = table_glue("{est}% (95% CI: {lwr}, {upr})")
     ) %>%
     pull(string)
 
@@ -283,7 +282,7 @@ make_inline_results <- function(design_overall,
   ) %>%
     tidy_svy(mult_by = 100) %>%
     transmute(
-      string = table_glue("{est}% (95% CI {lwr}, {upr})")
+      string = table_glue("{est}% (95% CI: {lwr}, {upr})")
     ) %>%
     pull(string)
 
@@ -294,7 +293,7 @@ make_inline_results <- function(design_overall,
   ) %>%
     tidy_svy(mult_by = 100) %>%
     transmute(
[…]

### 2020-09-11 R/plan.R

@@ -58,11 +58,25 @@ the_plan <- drake_plan(
     by = c('exam', 'seqn')
   ),
 
+  fasted_hrs_lower = 8,
+  fasted_hrs_upper = 24,
+  gluc_cutpoint_fasted = 126,
+  gluc_cutpoint_fed = 200,
+  hba1c_cutpoint = 6.5,
+  egfr_cutpoint = 60,
+  acr_cutpoint = 30,
+
   data_derived = data_pooled %>%
-    derive_diabetes() %>%
-    derive_egfrCKDepi() %>%
-    derive_ascvd_risk_pcr(set_miss_to_no = 'diabetes') %>%
-    derive_others(exams = exams),
+    derive_diabetes(
+      fasted_hrs_lower = fasted_hrs_lower,
+      fasted_hrs_upper = fasted_hrs_upper,
+      gluc_cutpoint_fasted = gluc_cutpoint_fasted,
+      gluc_cutpoint_fed = gluc_cutpoint_fed,
+      hba1c_cutpoint = hba1c_cutpoint
+    ) %>%
+    derive_egfrCKDepi(egfr_cutpoint = egfr_cutpoint) %>%
+    derive_ascvd_risk_pcr() %>%
+    derive_others(exams = exams, acr_cutpoint = acr_cutpoint),
 
   current_analysis = include_exclude(data_derived),
 
@@ -130,6 +144,13 @@ the_plan <- drake_plan(
 
   report = compile_report(
     exams,
+    fasted_hrs_lower,
+    fasted_hrs_upper,
+    gluc_cutpoint_fasted,
+    gluc_cutpoint_fed,
+    hba1c_cutpoint,
+    egfr_cutpoint,
+    acr_cutpoint,
     current_analysis,
     design_overall,
     tbl1_overall,

### 2020-09-11 packages.R

@@ -1,31 +1,38 @@
-## library() calls go here
-library(conflicted)
-library(dotenv)
-library(drake)
-# data management
-library(haven)
-library(janitor)
-library(magrittr)
-library(labelled)
-# data analysis
-library(tidyverse)
-library(tidyselect)
-library(survey)
-library(splines)
-library(scales)
-# reporting
-library(table.glue)
-library(officer)
-library(glue)
-library(flextable)
-library(devEMF)
-library(magick)
-library(paletteer)
-library(patchwork)
-library(rmarkdown)
-library(english)
-library(officer)
-library(officedown)
+
+
+if (!require("pacman")) install.packages("pacman")
+
+pacman::p_load(
+  # drake support
+  conflicted,
+  dotenv,
+  drake,
+  # data management
+  haven,
+  janitor,
+  magrittr,
+  labelled,
+  # data analysis
+  tidyverse,
+  tidyselect,
+  survey,
+  splines,
+  scales,
+  # reporting
+  officer,
+  glue,
+  flextable,
+  devEMF,
+  magick,
+  paletteer,
+  patchwork,
+  rmarkdown,
+  english,
+  officer,
+  officedown
+)
+
+pacman::p_load_gh('bcjaeger/table.glue', update = FALSE)
 
 conflicted::conflict_prefer("roc",       "pROC")
 conflicted::conflict_prefer("filter",    "dplyr")

### 2020-09-12 doc/ACCAHA_BP_groups.Rmd
second draft of discussion

@@
 Each cycle is independent with different participants recruited.
-For the current analysis, `r as.english(length(exams))` cycles conducted in `r nhanes_years` were pooled for analysis.[@nhanes_tutorial_weights] The protocols for each NHANES cycle were approved by the National Center for Health Statistics of the Centers for Disease Control and Prevention Institutional Review Board.
+For the current analysis, the `r as.english(length(exams))` cycles conducted in `r nhanes_years` were pooled for analysis.[@nhanes_tutorial_weights] The protocols for each NHANES cycle were approved by the National Center for Health Statistics of the Centers for Disease Control and Prevention Institutional Review Board.
 Written informed consent was obtained from each participant.
@@
 
-\newline
+<br>
 
 The current analysis was restricted to adults aged 40 to 79 years of age who complete the NHANES interview and examination (n = `r n_age_40_to_79`).
-Participants with age <40 or >79 were not included because the ASCVD risk prediction equation recommended by the ACC/AHA BP guideline is not recommended in these age ranges.
-Participants who did not have three SBP and DBP measurements (n = `r n_bp_too_low`) and those who were missing information on age, race, sex, total and high-density lipoprotein cholesterol, smoking status, or diabetes (n = `r n_missing_pcr`) were excluded.
-After these exclusions, over the three NHANES cycles, a total of `r n_final` survey participants were included in the analysis (`r refer_to('fig_include_exclude')`).
+Participants with age <40 or >79 years of age were not included because the Pooled Cohort risk equations are not recommended in these age ranges.[@goff20142013] Participants who did not have three SBP and DBP measurements (n = `r n_bp_too_low`) and those who were missing information on age, race, sex, total and high-density lipoprotein cholesterol, smoking status, diabetes, or CKD status (n = `r n_missing_pcr`) were excluded.
+After these exclusions, over the `r as.english(length(exams))` NHANES cycles, a total of `r n_final` survey participants were included in the analysis (`r refer_to('fig_include_exclude')`).
 
-\newline
+<br>
 
@@
 Data were collected during an in-home interview and a study visit completed at a mobile examination center.
-Standardized questionnaires were used to assess survey participants’ age, sex, race/ethnicity, smoking habits, medical history and use of antihypertensive medication, oral glucose lowering medication and insulin.
-Medical history included questions about whether the participant had been told by a doctor or other health professional that they had a heart attack, coronary heart disease stroke, or heart failure.
+Standardized questionnaires were used to assess participants’ age, sex, race/ethnicity, smoking habits, medical history and use of antihypertensive medication, oral glucose lowering medication and insulin.
+Medical history included questions about whether the participant had been told by a doctor or other health professional that they have had a heart attack, coronary heart disease stroke, or heart failure.
 Blood and urine samples were collected during the medical examination.
@@
 
-\newline
+<br>
 
@@
 
-Physicians conducting study examinations followed the same protocol to measure SBP and DBP in each NHANES cycle.
+The same protocol was followed to measure SBP and DBP in each NHANES cycle.
 After survey participants had rested 5 minutes, their BP was measured by a trained physician using a mercury sphygmomanometer and an appropriately sized cuff.
@@
 
-\newline
+<br>
 
-## Definitions of hypertension
+## Blood pressure categories
 
@@
 Analyses were conducted for the overall population and among participants with diabetes, CKD, ≥65 years of age, and for those with any of these three conditions, separately.
-Participant characteristics were summarized as mean (standard error) and percentage for continuous and categorical variables, respectively.
-The percentage of US adults in each of the five BP/antihypertensive medication use categories was computed.
-The median 10-year predicted risk for ASCVD and the proportion with a predicted risk ≥10% was computed for participants in each of the BP/antihypertensive medication use categories.
-To assess the extent to which participants with a 10-year predicted ASCVD risk <10% were ‘borderline’ cases (i.e., predicted ASCVD risk of 5% to <10% or 7.5% to <10%), the proportion of participants in this subgroup with predicted risk of 0% to <2.5%, 2.5% to <5.0%, 5.0% to <7.5%, and 7.5% to <10% was estimated.
-The age-adjusted probability of having a 10-year predicted ASCVD risk ≥10% was estimated using logistic regression.
+Participant characteristics were summarized as mean with their standard error and percentage for continuous and categorical variables, respectively.
+The percentage of US adults in each of the five BP categories was computed.
+The median 10-year predicted risk for ASCVD and the proportion with a predicted risk ≥10% was computed for participants in each of the BP categories.
+To assess the extent to which participants with a 10-year predicted ASCVD risk <10% were close to the threshold, the proportion of participants in this subgroup with predicted risk of 0% to <2.5%, 2.5% to <5.0%, 5.0% to <7.5%, and 7.5% to <10% was estimated.
+The probability of having a 10-year predicted ASCVD risk ≥10% was estimated for each year of age from 40 to 79 years using logistic regression.
 The above analyses were repeated among participants with stage 1 hypertension.
 
-\newline
+<br>
 
@@
 
-Among US adults who were 40 to 79 years of age from `r min(exams)` to `r max(exams)+1`, the estimated prevalence (95% confidence interval [CI]) of diabetes and CKD was `r inline$prevDiabetesOverall` and `r inline$prevCkdOverall`, respectively, and the estimated proportion (95% CI) of adults aged ≥65 years was `r inline$prevAge65Overall` (`r refer_to('tab_characteristics')`).
+Among US adults who were 40 to 79 years of age in `r min(exams)`-`r max(exams)+1`, the estimated prevalence (95% confidence interval [CI]) of diabetes and CKD was `r inline$prevDiabetesOverall` and `r inline$prevCkdOverall`, respectively, and `r inline$prevAge65Overall` were estimated to be ≥65 years of age (`r refer_to('tab_characteristics')`).
 Overall, an estimated `r inline$prevS1hOverall` of US adults who were 40 to 79 years of age had stage 1 hypertension (`r refer_to('tab_bpdist')`).
-Among those with diabetes, CKD, and age ≥65 years, the estimated prevalence (95% CI) of stage 1 hypertension was `r inline$prevS1hDiabetes`, `r inline$prevS1hDiabetes` `r inline$prevS1hCkd`, and `r inline$prevS1hAge65`, respectively.
-Characteristics of US adults with stage 1 hypertension, overall, and with diabetes, CKD and age ≥65 years are presented in Table S1
+Among those with diabetes, CKD, and age ≥65 years, the estimated prevalence (95% CI) of stage 1 hypertension was `r inline$prevS1hDiabetes`, `r inline$prevS1hCkd`, and `r inline$prevS1hAge65`, respectively.
+Characteristics of US adults 40 to 79 years of age with stage 1 hypertension, overall, and with diabetes, CKD and age ≥65 years are presented in Table S1
 
-\newline
+<br>
 
@@
 
-Among US adults without a history of CVD, the estimated median (25th, 75th percentiles) 10-year predicted risk for ASCVD was `r inline$medianPcrOverall` overall and `r inline$medianPcrDiabetes`, `r inline$medianPcrCkd`, and `r inline$medianPcrAge65` among those with diabetes, CKD, and age ≥65 years, respectively (`r refer_to('tab_risk_overall')`; top panel).
+Among US adults without a history of CVD, the estimated median (25th, 75th percentiles) 10-year predicted risk for ASCVD was `r inline$medianPcrOverall` in the overall population and `r inline$medianPcrDiabetes`, `r inline$medianPcrCkd`, and `r inline$medianPcrAge65` among those with diabetes, CKD, and age ≥65 years, respectively (`r refer_to('tab_risk_overall')`; top panel).
 Among US adults with stage 1 hypertension and no history of CVD, the estimated median (25th, 75th percentiles) 10-year predicted risk for ASCVD was `r inline$medianPcrS1hOverall`.
@@
 Among US adults with 10-year predicted risk for ASCVD <10% and no history of CVD, an estimated `r inline$propLowRiskOverall` had a 10-year predicted ASCVD risk <5% (`r refer_to('fig_hist_ovrl')`).
-Also, among this subgroup of adults, `r inline$propLowRiskDiabetes`, `r inline$propLowRiskCkd`, and `r inline$propLowRiskAge65` of those with diabetes, CKD and age ≥65 years had a 10-year predicted ASCVD risk <5% .
-The distribution of 10-year predicted ASCVD risk among US adults with predicted risk <10% and stage 1 hypertension are presented in `r refer_to('fig_hist_stg1')`.
-For these US adults, `r inline$propLowRiskS1hDiabetes` of those with diabetes and `r inline$propLowRiskS1hCkd` of those with CKD had a 10-year predicted ASCVD risk <5%,  compared with `r inline$propLowRiskS1hAge65` of those with ≥65 years of age.
+Also, among those with 10-year predicted risk for ASCVD <10% and no history of CVD, `r inline$propLowRiskDiabetes`, `r inline$propLowRiskCkd`, and `r inline$propLowRiskAge65` of those with diabetes, CKD and age ≥65 years had a 10-year predicted ASCVD risk <5%.
+Among US adults with predicted risk <10% and stage 1 hypertension, `r inline$propLowRiskS1hDiabetes` of those with diabetes, `r inline$propLowRiskS1hCkd` of those with CKD, and `r inline$propLowRiskS1hAge65` of those with ≥65 years of age had a 10-year predicted ASCVD risk <5% (`r refer_to('fig_hist_stg1')`).
 
-\newline
+<br>
 
-## Age-adjusted analysis
+## Age-specific analysis of 10-year predicted ASCVD risk ≥10% or history of CVD
 
-The estimated probability of having a 10-year predicted ASCVD risk ≥10% or a history of CVD increased with older age and was 50% (`r inline$intervalHighRiskOvrlNoComorb`) at `r inline$ageHighRiskOvrlNoComorb` years for US adults without diabetes or CKD (`r refer_to('fig_risk_ovrl')`).
-For US adults with diabetes and US adults with CKD, the age when estimated probability was ≥50% for having a 10-year predicted ASCVD risk ≥10% or a history of CVD was `r inline$ageHighRiskOvrlDiabetes` and `r inline$ageHighRiskOvrlCkd`, respectively.
-Among US adults with stage 1 hypertension, the age where estimated probability of having a 10-year predicted ASCVD risk ≥10% or a history of CVD exceeded 50% was `r inline$ageHighRiskS1hNoComorb`, `r inline$ageHighRiskS1hDiabetes`, and `r inline$ageHighRiskS1hCkd` years for US adults without diabetes or CKD, with diabetes, and with CKD, respectively (`r refer_to('fig_risk_stg1')`).
+The estimated probability of having a 10-year predicted ASCVD risk ≥10% or a history of CVD increased with older age and the minimum age where estimated probability was ≥50% was `r inline$ageHighRiskOvrlNoComorb` years for US adults without diabetes or CKD (`r refer_to('fig_risk_ovrl')`).
+For US adults with diabetes and with CKD, the age when estimated probability was ≥50% for having a 10-year predicted ASCVD risk ≥10% or a history of CVD was `r inline$ageHighRiskOvrlDiabetes` and `r inline$ageHighRiskOvrlCkd` years, respectively.
+Among US adults with stage 1 hypertension, the minimum age where estimated probability of having a 10-year predicted ASCVD risk ≥10% or history of CVD exceeded 50% was `r inline$ageHighRiskS1hNoComorb`, `r inline$ageHighRiskS1hDiabetes`, and `r inline$ageHighRiskS1hCkd` years for US adults without diabetes or CKD, with diabetes, and with CKD, respectively (`r refer_to('fig_risk_stg1')`).
+Since the median 10-year predicted risk for ASCVD was >10% among adults ≥65 years, a minimal age was not determined for this group.
 
-\newline
+<br>
 
@@
 
-<!-- In the current study, the distribution of 10-year predicted risk for ASCVD was investigated among US adults aged 40 to 79 years from `r min(exams)` to `r max(exams)+1`  -->
-
-The 2017 ACC/AHA BP guideline states that the vast majority of adults with diabetes, CKD, or ≥65 years of age have a 10-year predicted risk for ASCVD ≥10% and are recommended the initiation of antihypertensive drug therapy for stage 1 hypertension.
-However, the current analysis estimates that while `r inline$prevHighRiskDiabetes` of US adults with diabetes have 10-year predicted risk for ASCVD ≥10% or prevalent CVD, only `r inline$prevHighRiskS1hDiabetes` of adults with diabetes and stage 1 hypertension do.
-Similarly, `r inline$prevHighRiskCkd` of US adults with CKD but only `r inline$prevHighRiskS1hCkd` of US adults with CKD and stage 1 hypertension have 10-year predicted risk for ASCVD ≥10% or prevalent CVD.
-In contrast, among US adults with ≥65 years of age, `r inline$prevHighRiskAge65` have 10-year predicted risk for ASCVD ≥10% or prevalent CVD and `r inline$prevHighRiskS1hAge65` of US adults with stage 1 hypertension and ≥65 years of age do.
-Among adults whose 10-year predicted risk for ASCVD was <10%, roughly 50% of those with diabetes or CKD had 10-year predicted risk for ASCVD <5%, whereas over 90% of adults aged ≥65 years had 10-year predicted risk for ASCVD between 5% and 10%.
+In the current study, the distribution of 10-year predicted risk for ASCVD was investigated among US adults aged 40 to 79 years in `r min(exams)`-`r max(exams)+1`.
+Among those with stage 1 hypertension, `r inline$prevHighRiskS1hDiabetes` of US adults with diabetes and `r inline$prevHighRiskS1hCkd` with CKD had 10-year predicted risk for ASCVD ≥10% or prevalent CVD.
+In contrast, a much larger proportion of US adults with ≥65 years and stage 1 hypertension had a 10-year predicted risk for ASCVD ≥10% or prevalent CVD: `r inline$prevHighRiskS1hAge65`.
+Among adults whose 10-year predicted risk for ASCVD was <10%, roughly half of those with diabetes or CKD were not close to the threshold of 10%, whereas over 90% of adults aged ≥65 years had 10-year predicted risk for ASCVD between 5% and 10%.
 
@@
 
-\newline
+<br>
 
-The 2017 ACC/AHA BP guideline recommends initiation of antihypertensive medication based on BP level, 10-year predicted risk for ASCVD, and other conditions including diabetes, CKD, and age ≥65 years.
-Previous analysis of pooled data from the REasons for Geographic and Racial Differences in Stroke study and the Jackson Heart Study showed that adults with stage 1 hypertension recommended versus not recommended to initiate antihypertensive medication by the 2017 ACC/AHA BP guideline were roughly 5 times more likely to experience stroke or coronary heart disease over 12.2 years of follow-up.
-Moreover, 87.7% of adults with stage 1 hypertension recommended to initiate treatment by the 2017 ACC/AHA BP guideline had a 10-year predicted risk for ASCVD ≥10%.
-However, the mean age of adults in this group was 70.2 years, with a standard deviation of 6.9, whereas the estimated mean (95% CI) age of US adults with stage 1 hypertension in the current analysis was `r inline$meanAgeS1h`.
-Given that age is one of the most influential predictors in the pooled cohort risk equation, the younger age of adults in the US with stage 1 hypertension recommended to initiate antihypertensive medication by the ACC/AHA BP guidelines likely explains the difference in the distribution of 10-year predicted risk for ASCVD in the current study.
+The 2017 ACC/AHA BP guideline suggested that the vast majority of adults with diabetes, CKD, or ≥65 years of age have a 10-year predicted risk for ASCVD ≥10%.
+Prior studies suggest adults with diabetes or CKD have high risk for CVD.
+[@coresh2004evidence; @chronic2010association; @grundy1999diabetes] Moreover, adults with diabetes or CKD tend to be older, age is both a strong risk factor for incident ASCVD and a highly influential predictor in the Pooled Cohort risk equations.[@lakatta2002age; @pencina2019quantifying] However, the current study estimates suggest that a high proportion of US adults with diabetes or CKD do not have a high 10-year predicted risk for ASCVD, especially those with stage 1 hypertension.
 
-\newline
+Previous studies have shown that the use of 10-year predicted risk to guide the decision to initiate antihypertensive medication is critical for US adults with stage 1 hypertension in the general population and for those aged ≥60 years.[@colantonio20182017; @jaeger2019cardiovascular] In an analysis of adults aged ≥60 years, those with stage 1 hypertension recommended versus not recommended to initiate antihypertensive medication by the 2017 ACC/AHA BP guideline were roughly 5 times more likely to experience stroke or coronary heart disease over 12.2 years of follow-up, and 87.7% of the adults with stage 1 hypertension recommended to initiate treatment by the 2017 ACC/AHA BP guideline had a 10-year predicted risk for ASCVD ≥10%.
+However, the mean age of adults in this group was 70.2 years, whereas the estimated mean (95% CI) age of US adults, 40 to 79 years of age, with stage 1 hypertension in the current analysis was `r inline$meanAgeS1h` years.
+The younger age of adults in the US compared to adults in observational studies with stage 1 hypertension likely explains the difference in the distribution of 10-year predicted risk for ASCVD found in the current study versus previous studies.
 
-A prior analysis of NHANES data found that the proportion of adults in the US with SBP >130 mm Hg or DBP >80 mm Hg who are aware of their BP level declined from 2013 to 2018.
-Coupled with data showing that these adults may be at high risk for incident ASCVD, it is clear that the pooled cohort risk equations or other CVD risk prediction tools should be used in clinical practice to advance critical healthcare goals such as increasing awareness of hypertension and controlling BP levels.
-Computing predicted risk for ASCVD in the clinical setting may require additional time if a patient's medical record does not contain recent cholesterol measurements, but the current study suggests it is probably safe to assume US adults with stage 1 hypertension and ≥65 years of age have 10-year predicted risk for ASCVD ≥10%.
-This assumption is not supported for patients with stage 1 hypertension and diabetes or stage 1 hypertension and CKD, particularly for those aged <55 years.
-However, for younger adults with diabetes or CKD whose predicted 10-year risk for ASCVD is <10%, antihypertensive treatment may still provide substantial reduction in lifetime risk for ASCVD and prevention of complications associated with diabetes or CKD.
+While the current study found that 10-year predicted risk for ASCVD is low among US adults with diabetes or CKD in younger age groups, their lifetime CVD risk may be high.[@lloyd2006prediction; @hippisley2010derivation] For younger adults with diabetes or CKD, antihypertensive medication may provide substantial reduction in lifetime risk for ASCVD and prevention of complications associated with diabetes or CKD.
+In the current analysis, adults with stage 1 hypertension and diabetes were expected to have 10-year predicted ASCVD risk ≥10% roughly 10 years before their counterparts without diabetes.
+Patient-provider discussions should clarify the difference in 10-year and lifetime CVD risk and allow for early initiation of antihypertensive medication based on patient preference.
+Early initialization of treatment may reduce lifetime CVD burden and reverse trends in worsening BP control rates.(CITE Muntner JAMA)
 
-\newline
+<br>
 
@@
 
-\newline
+<br>
 
-In conclusion, the claim that a vast majority of adults with diabetes, CKD, or ≥65 years of age have a 10-year predicted risk for ASCVD ≥10% is not supported by data representative of the US population.
+In conclusion, a majority but not all US adults aged 40 to 79 years with diabetes, CKD or ≥65 years of age years have 10-year predicted risk for ASCVD ≥10%.
+Among those with stage 1 hypertension, this percentage is lower.
+Most older US adults with diabetes or CKD will have high risk.
+For younger adults with diabetes or CKD and 10-year predicted risk for ASCVD <10%, early initiation of antihypertensive medication may be an important step towards lowering lifetime CVD risk.
 Future studies should assess the cost-to-benefit ratio of early treatment for this population.

### 2020-09-12 R/derive_others.R

@@ -104,6 +104,9 @@ derive_others <- function(data, exams,
       age_group,
       age_40to79,
       age_gt65,
+      acr_mgg,
+      egfr_low,
+      egfr_ckdepi,
       diabetes,
       ckd,
       diabetes_and_ckd,

### 2020-09-12 R/include_exclude.R

@@ -18,7 +18,6 @@ include_exclude <- function(data) {
   n3 <- nrow(e3)
   # 40 - 79 years old
 
-
   e4 <- e3 %>% filter(n_msr_sbp >= 3 & n_msr_dbp >= 3)
   n4 <- nrow(e4)
   # 3+ BP measurements

### 2020-09-18 doc/ACCAHA_BP_groups.Rmd
PM comments and gfr fix

@@
 
-Byron C. Jaeger^1^, Shakia T. Hardy^2^, Paul Muntner^2^, and Paul Whelton^3^
+Byron C. Jaeger^1^, Swati Sakhuja^2^, Shakia T. Hardy^2^, Paul Muntner^2^, and Paul K. Whelton^3^
 
@@
 
-# INTRODUCTION
+In November 2017, the American College of Cardiology and the American Heart Association (ACC/AHA) published a guideline for the prevention, detection, evaluation, and management of high blood pressure (BP) in adults.[@whelton20182017] This guideline recommends using both predicted cardiovascular disease (CVD) risk and BP levels to guide the initiation of antihypertensive medication.
+All adults with systolic BP (SBP) ≥140 mm Hg or diastolic BP (DBP) ≥90 mm Hg, stage 2 hypertension in the guideline, are recommended to initiate antihypertensive medication.
+Additionally, adults with SBP between 130 and 139 mm Hg and/or DBP between 80 and 89 mm Hg, stage 1 hypertension in the guideline, who have high CVD risk are recommended to initiate antihypertensive medication.
+In the guideline, high CVD risk is defined by a history of CVD, a 10-year predicted risk for atherosclerotic CVD (ASCVD) ≥10%, the presence of diabetes mellitus or chronic kidney disease (CKD), and age ≥65 years.
 
-_To be written in next draft_
+<br>
+
+The 2017 ACC/AHA guideline recommends estimating 10-year risk for ASCVD in all adults with hypertension, including those with diabetes, CKD or ≥65 years of age.
+However, the guideline states that the vast majority of adults with diabetes, CKD, or ≥65 years of age can be assumed to have a 10-year ASCVD risk ≥10%.
+The purpose of the current analysis was to estimate the proportion of US adults with diabetes, CKD, or ≥65 years of age, that have high ASCVD risk defined by a 10-year predicted ASCVD risk ≥10% or a history of CVD.
+A secondary objective was to estimate the proportion with high ASCVD risk among adults with diabetes, CKD or ≥65 years of age among those and stage 1 hypertension as the 2017 ACC/AHA BP guideline recommends initiation of antihypertensive medication for all of these adults.
+To accomplish these goals, we analyzed data from `r as.english(length(exams))` cycles of the US National Health and Nutrition Examination Survey (NHANES).
 
@@
 The current analysis was restricted to adults aged 40 to 79 years of age who complete the NHANES interview and examination (n = `r n_age_40_to_79`).
-Participants with age <40 or >79 years of age were not included because the Pooled Cohort risk equations are not recommended in these age ranges.[@goff20142013] Participants who did not have three SBP and DBP measurements (n = `r n_bp_too_low`) and those who were missing information on age, race, sex, total and high-density lipoprotein cholesterol, smoking status, diabetes, or CKD status (n = `r n_missing_pcr`) were excluded.
+Participants <40 or >79 years of age were not included because the Pooled Cohort risk equations are not recommended to be used in these age ranges.[@goff20142013] Participants who did not have three SBP and DBP measurements (n = `r n_bp_too_low`) and those who were missing information on age, race, sex, total and high-density lipoprotein cholesterol, smoking status, diabetes, or CKD status (n = `r n_missing_pcr`) were excluded.
 After these exclusions, over the `r as.english(length(exams))` NHANES cycles, a total of `r n_final` survey participants were included in the analysis (`r refer_to('fig_include_exclude')`).
@@
 CKD was defined by an estimated glomerular filtration rate <`r egfr_cutpoint` ml/min/1.73m^2^ or an ACR ≥`r acr_cutpoint` mg/dL.
-Ten-year predicted risk for ASCVD was calculated using the pooled cohort risk equations for participants without a history of CVD.[@goff20142013] Participants with a history of CVD were presumed to have 10-year risk for ASCVD ≥10%.
+Ten-year predicted risk for ASCVD was calculated using the Pooled Cohort risk equations for participants without a history of CVD.[@goff20142013] High ASCVD risk was defined as a history of CVD or a 10-year predicted ASCVD risk ≥10%.
 
@@
 Participants not taking antihypertensive medication were grouped into four non-overlapping categories based on the 2017 ACC/AHA BP guideline: Normal BP (SBP <120 mm Hg and DBP <80 mm Hg), elevated BP (SBP between 120 and 129 mm Hg and DBP <80 mm Hg), stage 1 hypertension (SBP between 130 and 139 mm Hg and/or DBP between 80 and 89 mm Hg with SBP <140 mm Hg and DBP <90 mm Hg), stage 2 hypertension (SBP ≥140 mm Hg or DBP ≥90 mm Hg).
-Participants taking antihypertensive medication were placed in a fifth group.
+Participants taking antihypertensive medication were placed in a fifth category.
 
@@
 
-Analyses were conducted for the overall population and among participants with diabetes, CKD, ≥65 years of age, and for those with any of these three conditions, separately.
+Analyses were conducted for the overall population and among participants with diabetes, CKD, ≥65 years of age, and for those with any of these three conditions.
 Participant characteristics were summarized as mean with their standard error and percentage for continuous and categorical variables, respectively.
 The percentage of US adults in each of the five BP categories was computed.
-The median 10-year predicted risk for ASCVD and the proportion with a predicted risk ≥10% was computed for participants in each of the BP categories.
-To assess the extent to which participants with a 10-year predicted ASCVD risk <10% were close to the threshold, the proportion of participants in this subgroup with predicted risk of 0% to <2.5%, 2.5% to <5.0%, 5.0% to <7.5%, and 7.5% to <10% was estimated.
-The probability of having a 10-year predicted ASCVD risk ≥10% was estimated for each year of age from 40 to 79 years using logistic regression.
+The median 10-year predicted risk among participants without a history of CVD was estimated overall and among BP categories in addition to the proportion of participants at high ASCVD risk.
+To assess the extent to which participants with a 10-year predicted ASCVD risk <10% were close to the 10% threshold, the proportion of participants in this subgroup with predicted risk of 0% to <2.5%, 2.5% to <5.0%, 5.0% to <7.5%, and 7.5% to <10% was estimated.
+The probability of having high ASCVD risk was estimated for each year of age from 40 to 79 years using logistic regression.
 The above analyses were repeated among participants with stage 1 hypertension.
@@
 
+```{r}
+
+# R version string with fancy date
+R_string <- glue::glue("R version {version$major}.{version$minor}")
+
+date_string <- with(version, paste(year, month, day, sep = '/')) %>% 
+  as.POSIXct() %>% 
+  format("%B %d, %Y")
+
+R_string_fancy <- glue::glue(
+  "{R_string} (released {date_string})"
+)
+
+```
+
 NHANES sampling weights, which were calculated as the inverse probability of being selected for the survey, were used in all calculations to obtain US nationally representative estimates.
 The survey design of NHANES was also taken into account.
-Data analysis was conducted using `r version$version.string`.
 P-values were two-sided.
+Data analysis was conducted using `r R_string_fancy` along with a collection of open-source software packages (e.g., drake, dflow, officedown, and others) geared to enhance the transparency and reproducibility of our findings.[@cite_R; @cite_drake; @cite_tidyverse; @cite_table.glue] The first author's GitHub repository (< _Link not yet active so we won't be scooped_ >) provides code to reproduce the current manuscript as-is or with different initial parameters including exclusion criteria, variable definitions, and number of NHANES exams to pool.
+A detailed set of instructions for engaging with the project is provided in the repository's ReadMe file.
 
@@
 Among US adults who were 40 to 79 years of age in `r min(exams)`-`r max(exams)+1`, the estimated prevalence (95% confidence interval [CI]) of diabetes and CKD was `r inline$prevDiabetesOverall` and `r inline$prevCkdOverall`, respectively, and `r inline$prevAge65Overall` were estimated to be ≥65 years of age (`r refer_to('tab_characteristics')`).
-Overall, an estimated `r inline$prevS1hOverall` of US adults who were 40 to 79 years of age had stage 1 hypertension (`r refer_to('tab_bpdist')`).
+An estimated `r inline$prevS1hOverall` of US adults who were 40 to 79 years of age had stage 1 hypertension (`r refer_to('tab_bpdist')`).
 Among those with diabetes, CKD, and age ≥65 years, the estimated prevalence (95% CI) of stage 1 hypertension was `r inline$prevS1hDiabetes`, `r inline$prevS1hCkd`, and `r inline$prevS1hAge65`, respectively.
-Characteristics of US adults 40 to 79 years of age with stage 1 hypertension, overall, and with diabetes, CKD and age ≥65 years are presented in Table S1
+Characteristics of US adults 40 to 79 years of age with stage 1 hypertension, overall, and among those with diabetes, CKD and age ≥65 years are presented in Table S1
 
@@
 Among US adults without a history of CVD, the estimated median (25th, 75th percentiles) 10-year predicted risk for ASCVD was `r inline$medianPcrOverall` in the overall population and `r inline$medianPcrDiabetes`, `r inline$medianPcrCkd`, and `r inline$medianPcrAge65` among those with diabetes, CKD, and age ≥65 years, respectively (`r refer_to('tab_risk_overall')`; top panel).
-Among US adults with stage 1 hypertension and no history of CVD, the estimated median (25th, 75th percentiles) 10-year predicted risk for ASCVD was `r inline$medianPcrS1hOverall`.
-Within this subgroup of adults with stage 1 hypertension, those with diabetes and CKD had median (25th, 75th percentiles) predicted risks of of `r inline$medianPcrS1hDiabetes` and `r inline$medianPcrS1hCkd`, respectively, while adults aged ≥65 years had a median (25th, 75th percentiles) predicted risk of `r inline$medianPcrS1hAge65`.
-Among all US adults with stage 1 hypertension, an estimated `r inline$prevHighRiskS1hDiabetes` of those with diabetes, `r inline$prevHighRiskS1hCkd` of those with CKD and `r inline$prevHighRiskS1hAge65` who were ≥65 years of age had a 10-year predicted risk for ASCVD ≥10% or a history of CVD (`r refer_to('tab_risk_overall')`; bottom panel).
+Among US adults with stage 1 hypertension without a history of CVD, the estimated median (25th, 75th percentiles) 10-year predicted risk for ASCVD was `r inline$medianPcrS1hOverall`.
+Within this subgroup of adults with stage 1 hypertension, those with diabetes, CKD, and age ≥65 years had median (25th, 75th percentiles) predicted risks of of `r inline$medianPcrS1hDiabetes`, `r inline$medianPcrS1hCkd`, and `r inline$medianPcrS1hAge65` respectively.
+Among all US adults with stage 1 hypertension, an estimated `r inline$prevHighRiskS1hDiabetes` of those with diabetes, `r inline$prevHighRiskS1hCkd` of those with CKD and `r inline$prevHighRiskS1hAge65` who were ≥65 years of age had high ASCVD risk defined by a 10-year predicted risk for ASCVD ≥10% or a history of CVD (`r refer_to('tab_risk_overall')`; bottom panel).
 
@@
 
-Among US adults with 10-year predicted risk for ASCVD <10% and no history of CVD, an estimated `r inline$propLowRiskOverall` had a 10-year predicted ASCVD risk <5% (`r refer_to('fig_hist_ovrl')`).
-Also, among those with 10-year predicted risk for ASCVD <10% and no history of CVD, `r inline$propLowRiskDiabetes`, `r inline$propLowRiskCkd`, and `r inline$propLowRiskAge65` of those with diabetes, CKD and age ≥65 years had a 10-year predicted ASCVD risk <5%.
-Among US adults with predicted risk <10% and stage 1 hypertension, `r inline$propLowRiskS1hDiabetes` of those with diabetes, `r inline$propLowRiskS1hCkd` of those with CKD, and `r inline$propLowRiskS1hAge65` of those with ≥65 years of age had a 10-year predicted ASCVD risk <5% (`r refer_to('fig_hist_stg1')`).
+Among US adults who were not at high risk for ASCVD, an estimated `r inline$propLowRiskOverall` of US adults had 10-year predicted ASCVD risk <5% (`r refer_to('fig_hist_ovrl')`).
+Among those with diabetes, CKD and age ≥65 years, an estimated `r inline$propLowRiskDiabetes`, `r inline$propLowRiskCkd`, and `r inline$propLowRiskAge65` had a 10-year predicted ASCVD risk <5%, respectively.
+Among US adults with stage 1 hypertension who were not at high risk for ASCVD, an estimated `r inline$propLowRiskS1hDiabetes`, `r inline$propLowRiskS1hCkd`, and `r inline$propLowRiskS1hAge65` of those with diabetes, CKD, and ≥65 years of age had a 10-year predicted ASCVD risk <5%, respectively (`r refer_to('fig_hist_stg1')`).
 
@@
 
-The estimated probability of having a 10-year predicted ASCVD risk ≥10% or a history of CVD increased with older age and the minimum age where estimated probability was ≥50% was `r inline$ageHighRiskOvrlNoComorb` years for US adults without diabetes or CKD (`r refer_to('fig_risk_ovrl')`).
-For US adults with diabetes and with CKD, the age when estimated probability was ≥50% for having a 10-year predicted ASCVD risk ≥10% or a history of CVD was `r inline$ageHighRiskOvrlDiabetes` and `r inline$ageHighRiskOvrlCkd` years, respectively.
-Among US adults with stage 1 hypertension, the minimum age where estimated probability of having a 10-year predicted ASCVD risk ≥10% or history of CVD exceeded 50% was `r inline$ageHighRiskS1hNoComorb`, `r inline$ageHighRiskS1hDiabetes`, and `r inline$ageHighRiskS1hCkd` years for US adults without diabetes or CKD, with diabetes, and with CKD, respectively (`r refer_to('fig_risk_stg1')`).
-Since the median 10-year predicted risk for ASCVD was >10% among adults ≥65 years, a minimal age was not determined for this group.
+The estimated probability of having high ASCVD risk increased with older age and exceeded 50% at `r inline$ageHighRiskOvrlNoComorb` years for US adults without diabetes or CKD compared with `r inline$ageHighRiskOvrlDiabetes` and `r inline$ageHighRiskOvrlCkd` years for US adults with diabetes and CKD, respectively (`r refer_to('fig_risk_ovrl')`).
+Among US adults with stage 1 hypertension, the age at which the estimated probability of having high ASCVD risk exceeded 50% was `r inline$ageHighRiskS1hNoComorb`, `r inline$ageHighRiskS1hDiabetes`, and `r inline$ageHighRiskS1hCkd` years for US adults without diabetes or CKD, with diabetes, and with CKD, respectively (`r refer_to('fig_risk_stg1')`).
+The minimum age where the probability of high ASCVD risk exceeded 50% was not determined for adults ≥65 years of age as the probability exceeded 50% at all ages above 65 years.
 
@@
 
-In the current study, the distribution of 10-year predicted risk for ASCVD was investigated among US adults aged 40 to 79 years in `r min(exams)`-`r max(exams)+1`.
-Among those with stage 1 hypertension, `r inline$prevHighRiskS1hDiabetes` of US adults with diabetes and `r inline$prevHighRiskS1hCkd` with CKD had 10-year predicted risk for ASCVD ≥10% or prevalent CVD.
-In contrast, a much larger proportion of US adults with ≥65 years and stage 1 hypertension had a 10-year predicted risk for ASCVD ≥10% or prevalent CVD: `r inline$prevHighRiskS1hAge65`.
-Among adults whose 10-year predicted risk for ASCVD was <10%, roughly half of those with diabetes or CKD were not close to the threshold of 10%, whereas over 90% of adults aged ≥65 years had 10-year predicted risk for ASCVD between 5% and 10%.
-
-<!-- These results are not consistent the guideline's claim that a vast majority of adults with stage 1 hypertension and diabetes or CKD have 10-year predicted risk for ASCVD ≥10%.
-However, the guideline's claim regarding 10-year predicted ASCVD risk among adults with ≥65 years of age is consistent with our findings: `r inline$prevHighRiskAge65` of US adults aged ≥65 years and `r inline$prevHighRiskS1hAge65` of US adults aged ≥65 years with stage 1 hypertension have 10-year predicted risk for ASCVD ≥10% or prevalent CVD.
--->
+In the current study, a majority of US adults with diabetes, CKD or age ≥65 years had a high risk for ASCVD, defined by a 10-year predicted ASCVD risk ≥10% or history of CVD.
+However, a substantial proportion of US adults with stage 1 hypertension and diabetes, CKD, or age ≥65 years did not have high ASCVD risk.
+Among all US adults who were not at high risk for ASCVD, approximately half of those with diabetes or CKD had a 10-year predicted ASCVD risk <5%.
+In contrast, over 80% of adults aged ≥65 years had 10-year predicted risk for ASCVD between 5% and 10%.
+The probability of having high risk was age-dependent with over 50% of those with diabetes who were 55 years of age and older and with CKD who were age 59 years of age and older having high ASCVD risk.
 
@@
 
-The 2017 ACC/AHA BP guideline suggested that the vast majority of adults with diabetes, CKD, or ≥65 years of age have a 10-year predicted risk for ASCVD ≥10%.
-Prior studies suggest adults with diabetes or CKD have high risk for CVD.
-[@coresh2004evidence; @chronic2010association; @grundy1999diabetes] Moreover, adults with diabetes or CKD tend to be older, age is both a strong risk factor for incident ASCVD and a highly influential predictor in the Pooled Cohort risk equations.[@lakatta2002age; @pencina2019quantifying] However, the current study estimates suggest that a high proportion of US adults with diabetes or CKD do not have a high 10-year predicted risk for ASCVD, especially those with stage 1 hypertension.
-
-Previous studies have shown that the use of 10-year predicted risk to guide the decision to initiate antihypertensive medication is critical for US adults with stage 1 hypertension in the general population and for those aged ≥60 years.[@colantonio20182017; @jaeger2019cardiovascular] In an analysis of adults aged ≥60 years, those with stage 1 hypertension recommended versus not recommended to initiate antihypertensive medication by the 2017 ACC/AHA BP guideline were roughly 5 times more likely to experience stroke or coronary heart disease over 12.2 years of follow-up, and 87.7% of the adults with stage 1 hypertension recommended to initiate treatment by the 2017 ACC/AHA BP guideline had a 10-year predicted risk for ASCVD ≥10%.
-However, the mean age of adults in this group was 70.2 years, whereas the estimated mean (95% CI) age of US adults, 40 to 79 years of age, with stage 1 hypertension in the current analysis was `r inline$meanAgeS1h` years.
-The younger age of adults in the US compared to adults in observational studies with stage 1 hypertension likely explains the difference in the distribution of 10-year predicted risk for ASCVD found in the current study versus previous studies.
-
-While the current study found that 10-year predicted risk for ASCVD is low among US adults with diabetes or CKD in younger age groups, their lifetime CVD risk may be high.[@lloyd2006prediction; @hippisley2010derivation] For younger adults with diabetes or CKD, antihypertensive medication may provide substantial reduction in lifetime risk for ASCVD and prevention of complications associated with diabetes or CKD.
-In the current analysis, adults with stage 1 hypertension and diabetes were expected to have 10-year predicted ASCVD risk ≥10% roughly 10 years before their counterparts without diabetes.
-Patient-provider discussions should clarify the difference in 10-year and lifetime CVD risk and allow for early initiation of antihypertensive medication based on patient preference.
-Early initialization of treatment may reduce lifetime CVD burden and reverse trends in worsening BP control rates.(CITE Muntner JAMA)
+Previous studies have shown that the use of predicted ASCVD risk in addition to BP can direct antihypertensive medication to adults likely to receive the largest risk reduction benefit with treatment.[@colantonio20182017; @jaeger2019cardiovascular] In an analysis of the Reasons for Geographic and Racial Differences in Stroke (REGARDS) study, those with stage 1 hypertension recommended versus not recommended to initiate antihypertensive medication by the 2017 ACC/AHA BP guideline were roughly 6 times more likely to experience a CVD event over 8 years of follow-up.
+Although a substantial proportion of US adults with stage 1 hypertension and diabetes, CKD and age ≥ 65 years of age did not have a high ASCVD risk, they were more likely to have high ASCVD risk when compared to the overall US population with stage 1 hypertension.
+This suggests adults with stage 1 hypertension and diabetes, CKD or age ≥ 65 years of age may obtain greater risk reduction versus the overall population by initiating antihypertensive medication.
 
@@
 
-This study has several limitations.
-First, NHANES participants completed only one visit and guidelines recommend using the mean BP aggregated over 2 or more visits.
-Second, the response rate for NHANES has declined form 1999-2000 to 2017-2018.
-The effect of this decline on the current study is unclear.
-Third, the use of predicted ASCVD risk rather than observed ASCVD events may have over- or under-estimated ASCVD risk in subgroups where the pooled cohort risk equations are not well-calibrated.
-The current study also has a number of strengths.
-First, NHANES data are publicly available and representative of the US population when coupled with the NHANES survey design.
-Second, a collection of open-source software geared to enhance the transparency and reproducibility of scientific findings were leveraged to make the current analysis entirely reproducible and publicly available (see first author's GitHub repository: < _Link not yet active so we won't be scooped_ >).
-A point of novelty is that anyone with internet access may download this repository of code and reproduce the current manuscript as-is or with different initial parameters, e.g.
-using data from four NHANES cycles rather than three or modifying exclusion criteria.
-When different parameters are used, results in the manuscript will dynamically update.
-A detailed set of instructions for engaging with the project is provided in the repository.
+It has been suggested that the vast majority of adults with diabetes, CKD, or ≥65 years of age have a 10-year predicted risk for ASCVD ≥10%.
+Diabetes or CKD are each associated with an increased risk for ASCVD events.[@coresh2004evidence; @chronic2010association; @grundy1999diabetes] Moreover, in the current study, the mean age was 4 to 6 years older for US adults with diabetes and CKD versus the overall US population.
+Age is a strong risk factor for incident ASCVD and a strong contributor to 10-year predicted ASCVD risk in the Pooled Cohort risk equations.[@lakatta2002age; @pencina2019quantifying] However, the current study estimates suggest that a high proportion of US adults with diabetes or CKD do not have a high 10-year predicted risk for ASCVD, especially those with stage 1 hypertension.
+Future studies should assess the absolute CVD risk reduction for this population with antihypertensive medication treatment.
 
@@
 
-In conclusion, a majority but not all US adults aged 40 to 79 years with diabetes, CKD or ≥65 years of age years have 10-year predicted risk for ASCVD ≥10%.
-Among those with stage 1 hypertension, this percentage is lower.
-Most older US adults with diabetes or CKD will have high risk.
-For younger adults with diabetes or CKD and 10-year predicted risk for ASCVD <10%, early initiation of antihypertensive medication may be an important step towards lowering lifetime CVD risk.
-Future studies should assess the cost-to-benefit ratio of early treatment for this population.
+Although a majority of older adults with diabetes and CKD had high ASCVD risk while the majority of younger adults did not have high ASCVD risk.
+However, most young adults with diabetes and CKD have a high lifetime CVD risk.[@lloyd2006prediction; @hippisley2010derivation] Prior studies have found that cumulative exposure to high BP is associated with increased CVD risk.[@allen2014blood] Therefore, for younger adults with diabetes or CKD, antihypertensive medication may provide substantial reduction in ASCVD across their life course.
+Patient-provider discussions, including discussions of 10-year and lifetime risk for CVD, and patient preference should be used to guide the decision to initiate antihypertensive medication.
+
+<br>
+
+The current study has a number of strengths.
+The design of NHANES allows its results to be weighted to provide results that are representative of the US population.
+Additionally, NHANES data are collected following a rigorous protocol by trained study staff.
+BP was measured three times following a standardized protocol.
+However, the results of this study should be considered in the context of known and potential limitations.
+NHANES participants completed only one visit and guidelines recommend using the mean BP averaged over 2 or more visits.
+The use of predicted ASCVD risk rather than observed ASCVD events may have over- or under-estimated ASCVD risk in subgroups where the Pooled Cohort risk equations are not well-calibrated.
+
+<br>
+
+In conclusion, a majority of US adults aged 40 to 79 years with diabetes, CKD or ≥65 years of age had 10-year predicted risk for ASCVD ≥10%.
+However, a lower percentage of with stage 1 hypertension and diabetes, CKD or age ≥65 years of age had 10-year predicted risk for ASCVD ≥10%.
+While most older US adults with diabetes or CKD have high risk, a substantial proportion of younger adults with diabetes or CKD have a 10-year predicted risk for ASCVD <10%.
+While prevention of hypertension should be a primary goal, the early initiation of antihypertensive medication may be an important step towards lowering lifetime CVD risk.
 

### 2020-09-18 R/compile_report.R

@@ -85,13 +85,13 @@ compile_report <- function(exams,
 
   ftr_ckd <- as_paragraph(glue('Chronic kidney disease is defined by an albumin-to-creatinine ratio \u2265{acr_cutpoint} mg/dl or an estimated glomerular filtration rate <{egfr_cutpoint} ml/min/1.73m\u00b2'))
 
-  ftr_diab <- as_paragraph('Diabetes was defined by fasting serum glucose \u2265{gluc_cutpoint_fasted} mg/dL, non-fasting glucose \u2265{gluc_cutpoint_fed} mg/dL, HbA1c \u2265{hba1c_cutpoint}%, or self-reported use of insulin or oral glucose lowering medication.')
+  ftr_diab <- as_paragraph(glue('Diabetes was defined by fasting serum glucose \u2265{gluc_cutpoint_fasted} mg/dL, non-fasting glucose \u2265{gluc_cutpoint_fed} mg/dL, HbA1c \u2265{hba1c_cutpoint}%, or self-reported use of insulin or oral glucose lowering medication.'))
 
   bp_cat_guide <- as_paragraph(paste(
-    "Normal blood pressure: systolic/diastolic blood pressure < 120/80 mm Hg;",
-    "Elevated blood pressure: systolic/diastolic blood pressure 120-129/<80 mm Hg;",
-    "Stage 1 hypertension: systolic/diastolic blood pressure 130-139/80-89 mm Hg;",
-    "Stage 2 hypertension: systolic/diastolic blood pressure \u2265 140/90 mm Hg.",
+    "Normal blood pressure: systolic blood pressure < 120 mm Hg and diastolic blood pressure < 80 mm Hg;",
+    "Elevated blood pressure: systolic blood pressure from 120 to 129 mm Hg and diastolic blood pressure < 80 mm Hg;",
+    "Stage 1 hypertension: systolic blood pressure between 130 and 139 mm Hg and/or diastolic blood pressure between 80 and 89 mm Hg with systolic blood pressure <140 mm Hg and diastolic blood pressure <90 mm Hg;",
+    "Stage 2 hypertension: systolic blood pressure \u2265140 mm Hg or diastolic blood pressure \u226590 mm Hg.",
     sep = '\n'
   ))
 
@@ -269,7 +269,7 @@ compile_report <- function(exams,
         group,
         high_risk = 'Proportion (95% confidence interval) with 10-year predicted risk for ASCVD \u226510% or prevalent cardiovascular disease',
[…]

### 2020-09-18 R/derive_egfrCKDepi.R

@@ -19,24 +19,14 @@ derive_egfrCKDepi <- function(data,
 
   data_out <- data %>%
     mutate(
-      # abbreviate the name so equations fit on one line
-      cre = creat_mgdl,
-      aa = race_ethnicity == "Non-Hispanic black",
-      egfr_ckdepi = case_when(
-        aa  & sex=='Female' & cre<=0.7 ~166*((cre/0.7)^(-0.329))*(0.993^(age)),
-        aa  & sex=='Female' & cre >0.7 ~166*((cre/0.7)^(-1.209))*(0.993^(age)),
-        aa  & sex=='Male'   & cre<=0.9 ~163*((cre/0.9)^(-0.411))*(0.993^(age)),
-        aa  & sex=='Male'   & cre >0.9 ~163*((cre/0.9)^(-1.209))*(0.993^(age)),
-        !aa & sex=='Female' & cre<=0.7 ~144*((cre/0.7)^(-0.329))*(0.993^(age)),
-        !aa & sex=='Female' & cre >0.7 ~144*((cre/0.7)^(-1.209))*(0.993^(age)),
-        !aa & sex=='Male'   & cre<=0.9 ~141*((cre/0.9)^(-0.411))*(0.993^(age)),
-        !aa & sex=='Male'   & cre >0.9 ~141*((cre/0.9)^(-1.209))*(0.993^(age))
+      egfr_ckdepi = CKDEpi.creat(
+        age = age,
+        creatinine = creat_mgdl,
+        sex = as.numeric(sex == 'Male'),
+        ethnicity = as.numeric(race_ethnicity == 'Non-Hispanic Black')
       ),
-      egfr_low = if_else(egfr_ckdepi < egfr_cutpoint, "yes", "no"
-      )
-    ) %>%
-    # drop the cre column since it was just made for convenience
-    select(-cre)
+      egfr_low = if_else(egfr_ckdepi < egfr_cutpoint, "yes", "no")
+    )
 
   if(include_variable_labels){
 

### 2020-09-18 R/derive_others.R

@@ -105,6 +105,7 @@ derive_others <- function(data, exams,
       age_40to79,
       age_gt65,
       acr_mgg,
+      creat_mgdl,
       egfr_low,
       egfr_ckdepi,
       diabetes,

### 2020-09-18 R/make_inline_results.R

@@ -17,17 +17,17 @@ make_inline_results <- function(design_overall,
 
   prevDiabetesOverall <- svyciprop(~ diabetes, design_overall) %>%
     tidy_svy(mult_by = 100) %>%
-    transmute(string = table_glue("{est}% ({lwr}, {upr})")) %>%
+    transmute(string = table_glue("{est}% ({lwr}%, {upr}%)")) %>%
     pull(string)
 
   prevCkdOverall <- svyciprop(~ ckd, design_overall) %>%
     tidy_svy(mult_by = 100) %>%
-    transmute(string = table_glue("{est}% ({lwr}, {upr})")) %>%
+    transmute(string = table_glue("{est}% ({lwr}%, {upr}%)")) %>%
     pull(string)
 
   prevAge65Overall <- svyciprop(~ age_gt65, design_overall) %>%
     tidy_svy(mult_by = 100) %>%
-    transmute(string = table_glue("{est}% ({lwr}, {upr})")) %>%
+    transmute(string = table_glue("{est}% ({lwr}%, {upr}%)")) %>%
     pull(string)
 
   meanAgeOverall <- svymean(~ age, design_overall) %>%
@@ -48,7 +48,7 @@ make_inline_results <- function(design_overall,
   ) %>%
     tidy_svy(mult_by = 100) %>%
     transmute(
-      string = table_glue("{est}% (95% CI: {lwr}, {upr})")
+      string = table_glue("{est}% (95% CI: {lwr}%, {upr}%)")
     ) %>%
     pull(string)
 
@@ -58,7 +58,7 @@ make_inline_results <- function(design_overall,
   ) %>%
     tidy_svy(mult_by = 100) %>%
     transmute(
-      string = table_glue("{est}% ({lwr}, {upr})")
+      string = table_glue("{est}% ({lwr}%, {upr}%)")
     ) %>%
     pull(string)
 
@@ -69,7 +69,7 @@ make_inline_results <- function(design_overall,
   ) %>%
     tidy_svy(mult_by = 100) %>%
     transmute(
-      string = table_glue("{est}% ({lwr}, {upr})")
+      string = table_glue("{est}% ({lwr}%, {upr}%)")
     ) %>%
     pull(string)
 
@@ -79,7 +79,7 @@ make_inline_results <- function(design_overall,
   ) %>%
     tidy_svy(mult_by = 100) %>%
     transmute(
[…]

### 2020-09-18 R/plan.R

@@ -78,6 +78,11 @@ the_plan <- drake_plan(
     derive_ascvd_risk_pcr() %>%
     derive_others(exams = exams, acr_cutpoint = acr_cutpoint),
 
+  inclusion_by_exam = split(data_derived, data_derived$exam) %>%
+    map_dfr(~include_exclude(.x)$tbl, .id = 'exam') %>%
+    select(-n_removed) %>%
+    pivot_wider(names_from = exam, values_from = sample_size),
+
   current_analysis = include_exclude(data_derived),
 
   include_tbls = tabulate_inclusion(data_derived),

### 2020-09-18 packages.R

@@ -12,6 +12,7 @@ pacman::p_load(
   janitor,
   magrittr,
   labelled,
+  nephro, # for ckd-epi equations
   # data analysis
   tidyverse,
   tidyselect,

### 2020-09-18 doc/ACCAHA_BP_groups.Rmd
updated manuscript and smart acronyms

@@
 ```{r setup, include=FALSE}
+
+# misc functions for the paper
+
+# refers to tables and figures
+refer_to <- function(label){
+  report$pre_cap[report$reference == label]
+}
+
+# fixes list names with symbols
+clean_list_names <- function(named_list, case){
+
+  new_names <- make_clean_names(string = names(named_list),
+                                case = case)
+
+  names(named_list) <- new_names
+
+  named_list
+
+}
+
+# adds counter to abbreviation key
+add_counter <- function(data, index){
+  data$counter[index] <- data$counter[index] + 1
+  data
+}
 
@@
 
-refer_to <- function(label){
-  report$pre_cap[report$reference == label]
+abbrev_key <- c(
+  `ACC/AHA` = 'American College of Cardiology and the American Heart Association',
+  CI = 'confidence interval',
+  BP = 'blood pressure',
+  SBP = 'systolic BP',
+  DBP = 'diastolic BP',
+  CKD = 'chronic kidney disease',
+  CVD = 'cardiovascular disease',
+  ASCVD = 'atherosclerotic CVD',
+  NHANES = 'National Health and Nutrition Examination Survey',
+  ACR = 'albumin-to-creatinine ratio',
+  HbA1c = 'glycated hemoglobin',
+  eGFR = 'estimated glomerular filtration rate'
+) %>% 
+  enframe(name = 'acronym', value = 'phrase') %>% 
+  mutate(counter = 0)
+
+# create global functions that will refer to abbreviations
+# in abbrev_key. The first use of the function spells out
+# the acronym in full. All uses thereafter just use the
+# acronym.
+
+# this object must be defined in order for the abbrev functions 
+# to dynamically decide whether to use certain acronyms or not.
+# e.g., some journals only want 5 acronyms to be used.
+max_abbrevs <- 9
+
+abbrev_funs <- map(
+  .x = set_names(abbrev_key$acronym, abbrev_key$acronym),
+  .f = ~ {
+    function(left_mark = '(', right_mark = ')'){
+
+      if(!exists('max_abbrevs')) max_abbrevs <- nrow(abbrev_key)
+
+      abbrev_index <- which(abbrev_key$acronym == .x)
+
+      low_priority <- abbrev_index > max_abbrevs
+
+      if(low_priority) return(abbrev_key$phrase[abbrev_index])
+
+      counter <- abbrev_key$counter[abbrev_index]
+
+      if(counter < 1){
+        # modifies abbrev_key in global environment
+        abbrev_key <<- add_counter(abbrev_key, abbrev_index)
+        string <- glue_data(abbrev_key[abbrev_index,], 
+                            "{phrase} {left_mark}{acronym}{right_mark}")
+
+      } else {
+
+        abbrev_key <<- add_counter(abbrev_key, abbrev_index)
+        string <- abbrev_key$acronym[abbrev_index]
+
       }
+
+      string
+
+    }
+  }) %>% 
+  clean_list_names(case = 'screaming_snake') %>% 
+  list2env(envir = globalenv())
 
@@
 
-In November 2017, the American College of Cardiology and the American Heart Association (ACC/AHA) published a guideline for the prevention, detection, evaluation, and management of high blood pressure (BP) in adults.[@whelton20182017] This guideline recommends using both predicted cardiovascular disease (CVD) risk and BP levels to guide the initiation of antihypertensive medication.
-All adults with systolic BP (SBP) ≥140 mm Hg or diastolic BP (DBP) ≥90 mm Hg, stage 2 hypertension in the guideline, are recommended to initiate antihypertensive medication.
-Additionally, adults with SBP between 130 and 139 mm Hg and/or DBP between 80 and 89 mm Hg, stage 1 hypertension in the guideline, who have high CVD risk are recommended to initiate antihypertensive medication.
-In the guideline, high CVD risk is defined by a history of CVD, a 10-year predicted risk for atherosclerotic CVD (ASCVD) ≥10%, the presence of diabetes mellitus or chronic kidney disease (CKD), and age ≥65 years.
+In November 2017, the `r ACC_AHA()` published a guideline for the prevention, detection, evaluation, and management of high `r BP()` in adults.[@whelton20182017] This guideline recommends using both predicted `r CVD()` risk and `r BP()` levels to guide the initiation of antihypertensive medication.
+All adults with `r SBP()` ≥140 mm Hg or `r DBP()` ≥90 mm Hg, stage 2 hypertension in the guideline, are recommended to initiate antihypertensive medication.
+Additionally, adults with `r SBP()` between 130 and 139 mm Hg and/or `r DBP()` between 80 and 89 mm Hg, stage 1 hypertension in the guideline, who have high `r CVD()` risk are recommended to initiate antihypertensive medication.
+In the guideline, high `r CVD()` risk is defined by a history of `r CVD()`, a 10-year predicted risk for `r ASCVD()` ≥10%, prevalent diabetes mellitus, prevalent `r CKD()`, or ≥65 years of age.
 
@@
 
-The 2017 ACC/AHA guideline recommends estimating 10-year risk for ASCVD in all adults with hypertension, including those with diabetes, CKD or ≥65 years of age.
-However, the guideline states that the vast majority of adults with diabetes, CKD, or ≥65 years of age can be assumed to have a 10-year ASCVD risk ≥10%.
-The purpose of the current analysis was to estimate the proportion of US adults with diabetes, CKD, or ≥65 years of age, that have high ASCVD risk defined by a 10-year predicted ASCVD risk ≥10% or a history of CVD.
-A secondary objective was to estimate the proportion with high ASCVD risk among adults with diabetes, CKD or ≥65 years of age among those and stage 1 hypertension as the 2017 ACC/AHA BP guideline recommends initiation of antihypertensive medication for all of these adults.
-To accomplish these goals, we analyzed data from `r as.english(length(exams))` cycles of the US National Health and Nutrition Examination Survey (NHANES).
+The 2017 `r ACC_AHA()` guideline recommends estimating 10-year risk for `r ASCVD()` in all adults with hypertension, including those with diabetes, `r CKD()` or ≥65 years of age.
+However, the guideline states that the vast majority of adults with diabetes, CKD, or ≥65 years of age can be assumed to have a 10-year `r ASCVD()` risk ≥10%.
+The purpose of the current analysis was to estimate the proportion of US adults with diabetes, `r CKD()`, or ≥65 years of age, that have high `r ASCVD()` risk defined by a 10-year predicted `r ASCVD()` risk ≥10% or a history of `r CVD()`.
+A secondary objective was to estimate the proportion with high `r ASCVD()` risk among adults with diabetes, `r CKD()` or ≥65 years of age among those and stage 1 hypertension as the 2017 `r ACC_AHA()` BP guideline recommends initiation of antihypertensive medication for all of these adults.
+To accomplish these goals, we analyzed data from `r english(length(exams))` cycles of the US `r NHANES()`.
+
+<br>
 
@@
 
-NHANES was designed to assess the health and nutritional status of the non-institutionalized US population and is conducted by the National Center for Health Statistics of the Centers for Disease Control and Prevention.[@nhanes_home] Since 1999-2000, NHANES has been conducted in two-year cycles using a multistage probability sampling design to select participants.
+`r NHANES()` was designed to assess the health and nutritional status of the non-institutionalized US population and is conducted by the National Center for Health Statistics of the Centers for Disease Control and Prevention.[@nhanes_home] Since 1999-2000, `r NHANES()` has been conducted in two-year cycles using a multistage probability sampling design to select participants.
 Each cycle is independent with different participants recruited.
-For the current analysis, the `r as.english(length(exams))` cycles conducted in `r nhanes_years` were pooled for analysis.[@nhanes_tutorial_weights] The protocols for each NHANES cycle were approved by the National Center for Health Statistics of the Centers for Disease Control and Prevention Institutional Review Board.
+For the current analysis, the `r english(length(exams))` cycles conducted in `r nhanes_years` were pooled for analysis.[@nhanes_tutorial_weights] The protocols for each `r NHANES()` cycle were approved by the National Center for Health Statistics of the Centers for Disease Control and Prevention Institutional Review Board.
 Written informed consent was obtained from each participant.
-The University of Alabama at Birmingham Institutional Review Board considered the analysis of NHANES data to be exempt research.
+The University of Alabama at Birmingham Institutional Review Board considered the analysis of `r NHANES()` data to be exempt research.
+
+<br>
 
@@
 
-<br>
-
-The current analysis was restricted to adults aged 40 to 79 years of age who complete the NHANES interview and examination (n = `r n_age_40_to_79`).
-Participants <40 or >79 years of age were not included because the Pooled Cohort risk equations are not recommended to be used in these age ranges.[@goff20142013] Participants who did not have three SBP and DBP measurements (n = `r n_bp_too_low`) and those who were missing information on age, race, sex, total and high-density lipoprotein cholesterol, smoking status, diabetes, or CKD status (n = `r n_missing_pcr`) were excluded.
-After these exclusions, over the `r as.english(length(exams))` NHANES cycles, a total of `r n_final` survey participants were included in the analysis (`r refer_to('fig_include_exclude')`).
+The current analysis was restricted to adults aged 40 to 79 years of age who complete the `r NHANES()` interview and examination (n = `r n_age_40_to_79`).
+Participants <40 or >79 years of age were not included because the Pooled Cohort risk equations are not recommended to be used in these age ranges.[@goff20142013] Participants who did not have three `r SBP()` and `r DBP()` measurements (n = `r n_bp_too_low`) and those who were missing information on age, race, sex, total and high-density lipoprotein cholesterol, smoking status, diabetes, or `r CKD()` status (n = `r n_missing_pcr`) were excluded.
+After these exclusions, over the `r english(length(exams))` `r NHANES()` cycles, a total of `r n_final` survey participants were included in the analysis (`r refer_to('fig_include_exclude')`).
 
@@
 Blood and urine samples were collected during the medical examination.
-Of relevance to the current analysis, serum creatinine, serum glucose and glycated hemoglobin (HbA1c) were measured.
-Diabetes was defined by fasting serum glucose ≥`r gluc_cutpoint_fasted` mg/dL, non-fasting glucose ≥`r gluc_cutpoint_fed` mg/dL, HbA1c ≥`r hba1c_cutpoint`%, or self-reported use of insulin or oral glucose lowering medication.
-Estimated glomerular filtration rate was calculated using the Chronic Kidney Disease Epidemiology Collaboration equation.[@levey2009new] Urinary albumin and creatinine levels were measured and used to calculate the albumin-to-creatinine ratio (ACR).
-CKD was defined by an estimated glomerular filtration rate <`r egfr_cutpoint` ml/min/1.73m^2^ or an ACR ≥`r acr_cutpoint` mg/dL.
-Ten-year predicted risk for ASCVD was calculated using the Pooled Cohort risk equations for participants without a history of CVD.[@goff20142013] High ASCVD risk was defined as a history of CVD or a 10-year predicted ASCVD risk ≥10%.
+Of relevance to the current analysis, serum creatinine, serum glucose and `r HB_A1C()` were measured.
+Diabetes was defined by fasting serum glucose ≥`r gluc_cutpoint_fasted` mg/dL, non-fasting glucose ≥`r gluc_cutpoint_fed` mg/dL, `r HB_A1C()` ≥`r hba1c_cutpoint`%, or self-reported use of insulin or oral glucose lowering medication.
+`r capitalize(E_GFR())` was calculated using the Chronic Kidney Disease Epidemiology Collaboration equation.[@levey2009new] Urinary albumin and creatinine levels were measured and used to calculate the `r ACR()`.
+`r CKD()` was defined by an `r E_GFR()` <`r egfr_cutpoint` ml/min/1.73m^2^ or an `r ACR()` ≥`r acr_cutpoint` mg/dL.
+Ten-year predicted risk for `r ASCVD()` was calculated using the Pooled Cohort risk equations for participants without a history of `r CVD()`.[@goff20142013] High `r ASCVD()` risk was defined as a history of `r CVD()` or a 10-year predicted `r ASCVD()` risk ≥10%.
 
@@
 
-The same protocol was followed to measure SBP and DBP in each NHANES cycle.
-After survey participants had rested 5 minutes, their BP was measured by a trained physician using a mercury sphygmomanometer and an appropriately sized cuff.
-Three BP measurements were obtained at 30 second intervals.
-The mean of all available measurements was used to define SBP and DBP.
+The same protocol was followed to measure `r SBP()` and `r DBP()` in each `r NHANES()` cycle.
+After survey participants had rested 5 minutes, their `r BP()` was measured by a trained physician using a mercury sphygmomanometer and an appropriately sized cuff.
+Three `r BP()` measurements were obtained at 30 second intervals.
+The mean of all available measurements was used to define `r SBP()` and `r DBP()`.
 Quality control included re-certification of physicians every quarter with retraining if needed.
@@
 
-Participants not taking antihypertensive medication were grouped into four non-overlapping categories based on the 2017 ACC/AHA BP guideline: Normal BP (SBP <120 mm Hg and DBP <80 mm Hg), elevated BP (SBP between 120 and 129 mm Hg and DBP <80 mm Hg), stage 1 hypertension (SBP between 130 and 139 mm Hg and/or DBP between 80 and 89 mm Hg with SBP <140 mm Hg and DBP <90 mm Hg), stage 2 hypertension (SBP ≥140 mm Hg or DBP ≥90 mm Hg).
+Participants not taking antihypertensive medication were grouped into four non-overlapping categories based on the 2017 `r ACC_AHA()` `r BP()` guideline: Normal `r BP()` (`r SBP()` <120 mm Hg and `r DBP()` <80 mm Hg), elevated `r BP()` (`r SBP()` between 120 and 129 mm Hg and `r DBP()` <80 mm Hg), stage 1 hypertension (`r SBP()` between 130 and 139 mm Hg and/or `r DBP()` between 80 and 89 mm Hg with `r SBP()` <140 mm Hg and `r DBP()` <90 mm Hg), stage 2 hypertension (`r SBP()` ≥140 mm Hg or `r DBP()` ≥90 mm Hg).
 Participants taking antihypertensive medication were placed in a fifth category.
@@
 Participant characteristics were summarized as mean with their standard error and percentage for continuous and categorical variables, respectively.
-The percentage of US adults in each of the five BP categories was computed.
-The median 10-year predicted risk among participants without a history of CVD was estimated overall and among BP categories in addition to the proportion of participants at high ASCVD risk.
-To assess the extent to which participants with a 10-year predicted ASCVD risk <10% were close to the 10% threshold, the proportion of participants in this subgroup with predicted risk of 0% to <2.5%, 2.5% to <5.0%, 5.0% to <7.5%, and 7.5% to <10% was estimated.
-The probability of having high ASCVD risk was estimated for each year of age from 40 to 79 years using logistic regression.
+The percentage of US adults in each of the five `r BP()` categories was computed.
+The median 10-year predicted risk among participants without a history of `r CVD()` was estimated overall and among `r BP()` categories in addition to the proportion of participants at high `r ASCVD()` risk.
+To assess the extent to which participants with a 10-year predicted `r ASCVD()` risk <10% were close to the 10% threshold, the proportion of participants in this subgroup with predicted risk of 0% to <2.5%, 2.5% to <5.0%, 5.0% to <7.5%, and 7.5% to <10% was estimated.
+The probability of having high `r ASCVD()` risk was estimated for each year of age from 40 to 79 years using logistic regression.
 The above analyses were repeated among participants with stage 1 hypertension.
@@
 
-NHANES sampling weights, which were calculated as the inverse probability of being selected for the survey, were used in all calculations to obtain US nationally representative estimates.
-The survey design of NHANES was also taken into account.
+`r NHANES()` sampling weights, which were calculated as the inverse probability of being selected for the survey, were used in all calculations to obtain US nationally representative estimates.
+The survey design of `r NHANES()` was also taken into account.
 P-values were two-sided.
-Data analysis was conducted using `r R_string_fancy` along with a collection of open-source software packages (e.g., drake, dflow, officedown, and others) geared to enhance the transparency and reproducibility of our findings.[@cite_R; @cite_drake; @cite_tidyverse; @cite_table.glue] The first author's GitHub repository (< _Link not yet active so we won't be scooped_ >) provides code to reproduce the current manuscript as-is or with different initial parameters including exclusion criteria, variable definitions, and number of NHANES exams to pool.
+Data analysis was conducted using `r R_string_fancy` along with a collection of open-source software packages (e.g., drake, dflow, officedown, and others) geared to enhance the transparency and reproducibility of our findings.[@cite_R; @cite_drake; @cite_tidyverse; @cite_table.glue] The first author's GitHub repository (< _Link not yet active so we won't be scooped_ >) provides code to reproduce the current manuscript as-is or with different initial parameters including exclusion criteria, variable definitions, and number of `r NHANES()` exams to pool.
 A detailed set of instructions for engaging with the project is provided in the repository's ReadMe file.
@@
 
-Among US adults who were 40 to 79 years of age in `r min(exams)`-`r max(exams)+1`, the estimated prevalence (95% confidence interval [CI]) of diabetes and CKD was `r inline$prevDiabetesOverall` and `r inline$prevCkdOverall`, respectively, and `r inline$prevAge65Overall` were estimated to be ≥65 years of age (`r refer_to('tab_characteristics')`).
+Among US adults who were 40 to 79 years of age in `r min(exams)`-`r max(exams)+1`, the estimated prevalence (95% `r CI(left_mark = '[', right_mark = ']')`) of diabetes and `r CKD()` was `r inline$prevDiabetesOverall` and `r inline$prevCkdOverall`, respectively, and `r inline$prevAge65Overall` were estimated to be ≥65 years of age (`r refer_to('tab_characteristics')`).
 An estimated `r inline$prevS1hOverall` of US adults who were 40 to 79 years of age had stage 1 hypertension (`r refer_to('tab_bpdist')`).
-Among those with diabetes, CKD, and age ≥65 years, the estimated prevalence (95% CI) of stage 1 hypertension was `r inline$prevS1hDiabetes`, `r inline$prevS1hCkd`, and `r inline$prevS1hAge65`, respectively.
-Characteristics of US adults 40 to 79 years of age with stage 1 hypertension, overall, and among those with diabetes, CKD and age ≥65 years are presented in Table S1
+Among those with diabetes, CKD, and age ≥65 years, the estimated prevalence (95% `r CI()` ) of stage 1 hypertension was `r inline$prevS1hDiabetes`, `r inline$prevS1hCkd`, and `r inline$prevS1hAge65`, respectively.
+Characteristics of US adults 40 to 79 years of age with stage 1 hypertension, overall, and among those with diabetes, `r CKD()` and age ≥65 years are presented in Table S1
 
@@
 
-Among US adults without a history of CVD, the estimated median (25th, 75th percentiles) 10-year predicted risk for ASCVD was `r inline$medianPcrOverall` in the overall population and `r inline$medianPcrDiabetes`, `r inline$medianPcrCkd`, and `r inline$medianPcrAge65` among those with diabetes, CKD, and age ≥65 years, respectively (`r refer_to('tab_risk_overall')`; top panel).
-Among US adults with stage 1 hypertension without a history of CVD, the estimated median (25th, 75th percentiles) 10-year predicted risk for ASCVD was `r inline$medianPcrS1hOverall`.
-Within this subgroup of adults with stage 1 hypertension, those with diabetes, CKD, and age ≥65 years had median (25th, 75th percentiles) predicted risks of of `r inline$medianPcrS1hDiabetes`, `r inline$medianPcrS1hCkd`, and `r inline$medianPcrS1hAge65` respectively.
-Among all US adults with stage 1 hypertension, an estimated `r inline$prevHighRiskS1hDiabetes` of those with diabetes, `r inline$prevHighRiskS1hCkd` of those with CKD and `r inline$prevHighRiskS1hAge65` who were ≥65 years of age had high ASCVD risk defined by a 10-year predicted risk for ASCVD ≥10% or a history of CVD (`r refer_to('tab_risk_overall')`; bottom panel).
+Among US adults aged 40 to 49 years without a history of `r CVD()`, the estimated median (25th, 75th percentiles) 10-year predicted risk for `r ASCVD()` was `r inline$medianPcrOverall` in the overall population and `r inline$medianPcrDiabetes`, `r inline$medianPcrCkd`, and `r inline$medianPcrAge65` among those with diabetes, CKD, and age ≥65 years, respectively (`r refer_to('tab_risk_overall')`; top panel).
+Among US adults with stage 1 hypertension without a history of `r CVD()`, the estimated median (25th, 75th percentiles) 10-year predicted risk for `r ASCVD()` was `r inline$medianPcrS1hOverall`.
+Within this subgroup of adults with stage 1 hypertension, those with diabetes, `r CKD()`, and age ≥65 years had median (25th, 75th percentiles) predicted risks of of `r inline$medianPcrS1hDiabetes`, `r inline$medianPcrS1hCkd`, and `r inline$medianPcrS1hAge65` respectively.
+
+<br>
+
+Among US adults aged 40 to 79 years with diabetes, CKD, or age ≥65 years, an estimated `r inline$prevHighRiskDiabetes`, `r inline$prevHighRiskCkd`, and `r inline$prevHighRiskAge65`, had high `r ASCVD()` risk, respectively (`r refer_to('tab_risk_overall')`; bottom panel).
+Among those with stage 1 hypertension, an estimated `r inline$prevHighRiskS1hDiabetes` of those with diabetes, `r inline$prevHighRiskS1hCkd` of those with `r CKD()` and `r inline$prevHighRiskS1hAge65` who were ≥65 years of age had high `r ASCVD()` risk.
 
@@
 
-Among US adults who were not at high risk for ASCVD, an estimated `r inline$propLowRiskOverall` of US adults had 10-year predicted ASCVD risk <5% (`r refer_to('fig_hist_ovrl')`).
-Among those with diabetes, CKD and age ≥65 years, an estimated `r inline$propLowRiskDiabetes`, `r inline$propLowRiskCkd`, and `r inline$propLowRiskAge65` had a 10-year predicted ASCVD risk <5%, respectively.
-Among US adults with stage 1 hypertension who were not at high risk for ASCVD, an estimated `r inline$propLowRiskS1hDiabetes`, `r inline$propLowRiskS1hCkd`, and `r inline$propLowRiskS1hAge65` of those with diabetes, CKD, and ≥65 years of age had a 10-year predicted ASCVD risk <5%, respectively (`r refer_to('fig_hist_stg1')`).
+Among US adults who were not at high risk for `r ASCVD()`, an estimated `r inline$propLowRiskOverall` of US adults had 10-year predicted `r ASCVD()` risk <5% (`r refer_to('fig_hist_ovrl')`).
+Among those with diabetes, `r CKD()` and age ≥65 years, an estimated `r inline$propLowRiskDiabetes`, `r inline$propLowRiskCkd`, and `r inline$propLowRiskAge65` had a 10-year predicted `r ASCVD()` risk <5%, respectively.
+Among US adults with stage 1 hypertension who were not at high risk for `r ASCVD()`, an estimated `r inline$propLowRiskS1hDiabetes`, `r inline$propLowRiskS1hCkd`, and `r inline$propLowRiskS1hAge65` of those with diabetes, CKD, and ≥65 years of age had a 10-year predicted `r ASCVD()` risk <5%, respectively (`r refer_to('fig_hist_stg1')`).
 
@@
 
-## Age-specific analysis of 10-year predicted ASCVD risk ≥10% or history of CVD
+## Age-specific analysis of 10-year predicted `r ASCVD()` risk ≥10% or history of `r CVD()`
 
-The estimated probability of having high ASCVD risk increased with older age and exceeded 50% at `r inline$ageHighRiskOvrlNoComorb` years for US adults without diabetes or CKD compared with `r inline$ageHighRiskOvrlDiabetes` and `r inline$ageHighRiskOvrlCkd` years for US adults with diabetes and CKD, respectively (`r refer_to('fig_risk_ovrl')`).
-Among US adults with stage 1 hypertension, the age at which the estimated probability of having high ASCVD risk exceeded 50% was `r inline$ageHighRiskS1hNoComorb`, `r inline$ageHighRiskS1hDiabetes`, and `r inline$ageHighRiskS1hCkd` years for US adults without diabetes or CKD, with diabetes, and with CKD, respectively (`r refer_to('fig_risk_stg1')`).
-The minimum age where the probability of high ASCVD risk exceeded 50% was not determined for adults ≥65 years of age as the probability exceeded 50% at all ages above 65 years.
+The estimated probability of having high `r ASCVD()` risk increased with older age and exceeded 50% at `r inline$ageHighRiskOvrlNoComorb` years for US adults without diabetes or `r CKD()` compared with `r inline$ageHighRiskOvrlDiabetes` and `r inline$ageHighRiskOvrlCkd` years for US adults with diabetes and CKD, respectively (`r refer_to('fig_risk_ovrl')`).
+Among US adults with stage 1 hypertension, the age at which the estimated probability of having high `r ASCVD()` risk exceeded 50% was `r inline$ageHighRiskS1hNoComorb`, `r inline$ageHighRiskS1hDiabetes`, and `r inline$ageHighRiskS1hCkd` years for US adults without diabetes or CKD, with diabetes, and with CKD, respectively (`r refer_to('fig_risk_stg1')`).
+The minimum age where the probability of high `r ASCVD()` risk exceeded 50% was not determined for adults ≥65 years of age as the probability exceeded 50% at all ages above 65 years.
 
@@
 
-In the current study, a majority of US adults with diabetes, CKD or age ≥65 years had a high risk for ASCVD, defined by a 10-year predicted ASCVD risk ≥10% or history of CVD.
-However, a substantial proportion of US adults with stage 1 hypertension and diabetes, CKD, or age ≥65 years did not have high ASCVD risk.
-Among all US adults who were not at high risk for ASCVD, approximately half of those with diabetes or CKD had a 10-year predicted ASCVD risk <5%.
-In contrast, over 80% of adults aged ≥65 years had 10-year predicted risk for ASCVD between 5% and 10%.
-The probability of having high risk was age-dependent with over 50% of those with diabetes who were 55 years of age and older and with CKD who were age 59 years of age and older having high ASCVD risk.
+In the current study, a majority of US adults with diabetes, `r CKD()` or age ≥65 years had a high risk for `r ASCVD()`, defined by a 10-year predicted `r ASCVD()` risk ≥10% or history of `r CVD()`.
+However, a substantial proportion of US adults with stage 1 hypertension and diabetes, CKD, or age ≥65 years did not have high `r ASCVD()` risk.
+Among all US adults who were not at high risk for `r ASCVD()`, approximately half of those with diabetes or `r CKD()` had a 10-year predicted `r ASCVD()` risk <5%.
+In contrast, over 80% of adults aged ≥65 years had 10-year predicted risk for `r ASCVD()` between 5% and 10%.
+The probability of having high risk was age-dependent with over 50% of those with diabetes who were 55 years of age and older and with `r CKD()` who were age 59 years of age and older having high `r ASCVD()` risk.
 
@@
 
-Previous studies have shown that the use of predicted ASCVD risk in addition to BP can direct antihypertensive medication to adults likely to receive the largest risk reduction benefit with treatment.[@colantonio20182017; @jaeger2019cardiovascular] In an analysis of the Reasons for Geographic and Racial Differences in Stroke (REGARDS) study, those with stage 1 hypertension recommended versus not recommended to initiate antihypertensive medication by the 2017 ACC/AHA BP guideline were roughly 6 times more likely to experience a CVD event over 8 years of follow-up.
-Although a substantial proportion of US adults with stage 1 hypertension and diabetes, CKD and age ≥ 65 years of age did not have a high ASCVD risk, they were more likely to have high ASCVD risk when compared to the overall US population with stage 1 hypertension.
-This suggests adults with stage 1 hypertension and diabetes, CKD or age ≥ 65 years of age may obtain greater risk reduction versus the overall population by initiating antihypertensive medication.
+Among US adults aged 40 to 79 years, the current study estimates that roughly 33% use antihypertensive medication.
+Among US adults aged 40 to 79 years with diabetes, `r CKD()`, or ≥65 years of age, the current study estimates that roughly 50% use antihypertensive medication and relatively few (roughly 10%) have stage 1 hypertension.
+Therefore, the use of 10-year predicted `r ASCVD()` risk to guide treatment only applies to a small percentage of adults with at least one of these conditions.
+Additionally, it is possible that existing 10-year `r ASCVD()` risk prediction models, including the Pooled Cohort risk prediction equations, are not calibrated for prediction of `r ASCVD()` risk among this relatively small group of adults, particularly for those of younger age.
 
@@
 
-It has been suggested that the vast majority of adults with diabetes, CKD, or ≥65 years of age have a 10-year predicted risk for ASCVD ≥10%.
-Diabetes or CKD are each associated with an increased risk for ASCVD events.[@coresh2004evidence; @chronic2010association; @grundy1999diabetes] Moreover, in the current study, the mean age was 4 to 6 years older for US adults with diabetes and CKD versus the overall US population.
-Age is a strong risk factor for incident ASCVD and a strong contributor to 10-year predicted ASCVD risk in the Pooled Cohort risk equations.[@lakatta2002age; @pencina2019quantifying] However, the current study estimates suggest that a high proportion of US adults with diabetes or CKD do not have a high 10-year predicted risk for ASCVD, especially those with stage 1 hypertension.
-Future studies should assess the absolute CVD risk reduction for this population with antihypertensive medication treatment.
+Previous studies have shown that the use of predicted `r ASCVD()` risk in addition to `r BP()` can direct antihypertensive medication to adults likely to receive the largest risk reduction benefit with treatment.[@colantonio20182017; @jaeger2019cardiovascular] In an analysis of the Reasons for Geographic and Racial Differences in Stroke study, those with stage 1 hypertension recommended versus not recommended to initiate antihypertensive medication by the 2017 `r ACC_AHA()` `r BP()` guideline were roughly 6 times more likely to experience a `r CVD()` event over 8 years of follow-up.
+Although a substantial proportion of US adults with stage 1 hypertension and diabetes, CKD, or age ≥65 years of age did not have a high `r ASCVD()` risk, they were more likely to have high `r ASCVD()` risk when compared to the overall US population with stage 1 hypertension.
+This suggests adults with stage 1 hypertension and diabetes, `r CKD()` or age ≥65 years of age may obtain greater risk reduction versus the overall population by initiating antihypertensive medication.
 
@@
 
-Although a majority of older adults with diabetes and CKD had high ASCVD risk while the majority of younger adults did not have high ASCVD risk.
-However, most young adults with diabetes and CKD have a high lifetime CVD risk.[@lloyd2006prediction; @hippisley2010derivation] Prior studies have found that cumulative exposure to high BP is associated with increased CVD risk.[@allen2014blood] Therefore, for younger adults with diabetes or CKD, antihypertensive medication may provide substantial reduction in ASCVD across their life course.
-Patient-provider discussions, including discussions of 10-year and lifetime risk for CVD, and patient preference should be used to guide the decision to initiate antihypertensive medication.
+It has been suggested that the vast majority of adults with diabetes, CKD, or ≥65 years of age have a 10-year predicted risk for `r ASCVD()` ≥10%.
+Diabetes and `r CKD()` are each associated with an increased risk for `r ASCVD()` events.[@coresh2004evidence; @chronic2010association; @grundy1999diabetes] Moreover, in the current study, the mean age was 4 to 6 years older for US adults with diabetes and `r CKD()` versus the overall US population.
+Age is a strong risk factor for incident `r ASCVD()` and a strong contributor to 10-year predicted `r ASCVD()` risk in the Pooled Cohort risk equations.[@lakatta2002age; @pencina2019quantifying] However, the current study estimates suggest that a high proportion of US adults with diabetes or `r CKD()` do not have a high 10-year predicted risk for `r ASCVD()`, especially those with stage 1 hypertension.
+Future studies should assess the absolute `r CVD()` risk reduction for this population with antihypertensive medication treatment.
+
+<br>
+
+Although a majority of older adults with diabetes and `r CKD()` had high `r ASCVD()` risk, the majority of younger adults did not have high `r ASCVD()` risk.
+However, most young adults with diabetes and `r CKD()` have a high lifetime `r CVD()` risk.[@lloyd2006prediction; @hippisley2010derivation] Prior studies have found that cumulative exposure to high `r BP()` is associated with increased `r CVD()` risk.[@allen2014blood] Therefore, for younger adults with diabetes or CKD, antihypertensive medication may provide substantial reduction in `r ASCVD()` across their life course.
+Patient-provider discussions, including discussions of 10-year and lifetime risk for `r CVD()`, and patient preference should be used to guide the decision to initiate antihypertensive medication.
 
@@
 The current study has a number of strengths.
-The design of NHANES allows its results to be weighted to provide results that are representative of the US population.
-Additionally, NHANES data are collected following a rigorous protocol by trained study staff.
-BP was measured three times following a standardized protocol.
+The design of `r NHANES()` allows its results to be weighted to provide results that are representative of the US population.
+Additionally, `r NHANES()` data are collected following a rigorous protocol by trained study staff.
+`r BP()` was measured three times following a standardized protocol.
 However, the results of this study should be considered in the context of known and potential limitations.
-NHANES participants completed only one visit and guidelines recommend using the mean BP averaged over 2 or more visits.
-The use of predicted ASCVD risk rather than observed ASCVD events may have over- or under-estimated ASCVD risk in subgroups where the Pooled Cohort risk equations are not well-calibrated.
+`r NHANES()` participants completed only one visit and guidelines recommend using the mean `r BP()` averaged over 2 or more visits.
+The use of predicted `r ASCVD()` risk rather than observed `r ASCVD()` events may have over- or under-estimated `r ASCVD()` risk in subgroups where the Pooled Cohort risk equations are not well-calibrated.
 
@@
 
-In conclusion, a majority of US adults aged 40 to 79 years with diabetes, CKD or ≥65 years of age had 10-year predicted risk for ASCVD ≥10%.
-However, a lower percentage of with stage 1 hypertension and diabetes, CKD or age ≥65 years of age had 10-year predicted risk for ASCVD ≥10%.
-While most older US adults with diabetes or CKD have high risk, a substantial proportion of younger adults with diabetes or CKD have a 10-year predicted risk for ASCVD <10%.
-While prevention of hypertension should be a primary goal, the early initiation of antihypertensive medication may be an important step towards lowering lifetime CVD risk.
+In conclusion, a majority of US adults aged 40 to 79 years with diabetes, `r CKD()` or ≥65 years of age had 10-year predicted risk for `r ASCVD()` ≥10%.
+However, a lower percentage of with stage 1 hypertension and diabetes, `r CKD()` or age ≥65 years of age had 10-year predicted risk for `r ASCVD()` ≥10%.
+While most older US adults with diabetes or `r CKD()` have high risk, a substantial proportion of younger adults with diabetes or `r CKD()` have a 10-year predicted risk for `r ASCVD()` <10%.
+While prevention of hypertension should be a primary goal, the early initiation of antihypertensive medication may be an important step towards lowering lifetime `r CVD()` risk.
 

### 2020-09-18 R/tabulate_bpdist.R

@@ -29,6 +29,6 @@ tabulate_bpdist <- function(design, decimals) {
     filter(level == 'yes' | is.na(level)) %>%
     select(-level) %>%
     group_by(variable) %>%
-    mutate(n = table_value(100 * n / sum(n)))
+    mutate(n = table_glue("{100 * n / sum(n)}%"))
 
 }

### 2020-09-18 packages.R

@@ -30,7 +30,8 @@ pacman::p_load(
   rmarkdown,
   english,
   officer,
-  officedown
+  officedown,
+  Hmisc
 )
 
 pacman::p_load_gh('bcjaeger/table.glue', update = FALSE)
@@ -39,5 +40,6 @@ conflicted::conflict_prefer("roc",       "pROC")
 conflicted::conflict_prefer("filter",    "dplyr")
 conflicted::conflict_prefer("slice",     "dplyr")
 conflicted::conflict_prefer('summarise', 'dplyr')
+conflicted::conflict_prefer('summarize', 'dplyr')
 conflicted::conflict_prefer("gather",    "tidyr")
 conflicted::conflict_prefer("set_names", "purrr")

### 2020-09-20 doc/ACCAHA_BP_groups.Rmd
cleaning up variable definitions

@@
   BP = 'blood pressure',
+  NHANES = 'National Health and Nutrition Examination Survey',
   SBP = 'systolic BP',
@@
   ASCVD = 'atherosclerotic CVD',
-  NHANES = 'National Health and Nutrition Examination Survey',
   ACR = 'albumin-to-creatinine ratio',
@@
 
-In November 2017, the `r ACC_AHA()` published a guideline for the prevention, detection, evaluation, and management of high `r BP()` in adults.[@whelton20182017] This guideline recommends using both predicted `r CVD()` risk and `r BP()` levels to guide the initiation of antihypertensive medication.
+In November 2017, the `r ACC_AHA()` published a guideline for the prevention, detection, evaluation, and management of high `r BP()` in adults.[@whelton20182017] This guideline recommends using both predicted predicted risk for `r CVD()` and `r BP()` levels to guide the initiation of antihypertensive medication.
 All adults with `r SBP()` ≥140 mm Hg or `r DBP()` ≥90 mm Hg, stage 2 hypertension in the guideline, are recommended to initiate antihypertensive medication.
-Additionally, adults with `r SBP()` between 130 and 139 mm Hg and/or `r DBP()` between 80 and 89 mm Hg, stage 1 hypertension in the guideline, who have high `r CVD()` risk are recommended to initiate antihypertensive medication.
-In the guideline, high `r CVD()` risk is defined by a history of `r CVD()`, a 10-year predicted risk for `r ASCVD()` ≥10%, prevalent diabetes mellitus, prevalent `r CKD()`, or ≥65 years of age.
+Additionally, adults with `r SBP()` between 130 and 139 mm Hg and/or `r DBP()` between 80 and 89 mm Hg, stage 1 hypertension in the guideline, who have prevalent diabetes mellitus, prevalent `r CKD()`, ≥65 years of age, or high `ASCVD()` risk are recommended to initiate antihypertensive medication.
+High `ASCVD()` risk is defined as prevalent `r CVD()` or a 10-year predicted risk for `r ASCVD()` ≥10%
 
@@
 
-The 2017 `r ACC_AHA()` guideline recommends estimating 10-year risk for `r ASCVD()` in all adults with hypertension, including those with diabetes, `r CKD()` or ≥65 years of age.
-However, the guideline states that the vast majority of adults with diabetes, CKD, or ≥65 years of age can be assumed to have a 10-year `r ASCVD()` risk ≥10%.
-The purpose of the current analysis was to estimate the proportion of US adults with diabetes, `r CKD()`, or ≥65 years of age, that have high `r ASCVD()` risk defined by a 10-year predicted `r ASCVD()` risk ≥10% or a history of `r CVD()`.
-A secondary objective was to estimate the proportion with high `r ASCVD()` risk among adults with diabetes, `r CKD()` or ≥65 years of age among those and stage 1 hypertension as the 2017 `r ACC_AHA()` BP guideline recommends initiation of antihypertensive medication for all of these adults.
+The 2017 `r ACC_AHA()` guideline recommends computing 10-year predicted risk for `r ASCVD()` in all adults with hypertension, including those with diabetes, `r CKD()` or ≥65 years of age.
+However, the guideline states that the vast majority of adults with diabetes, CKD, or ≥65 years of age can be assumed to have a 10-year predicted risk for `r ASCVD()` ≥10%.
+The purpose of the current analysis was to estimate the proportion of US adults with diabetes, `r CKD()`, or ≥65 years of age that have high `r ASCVD()` risk (i.e., a 10-year predicted risk for `r ASCVD()` ≥10% or prevalent `r CVD()`).
+A secondary objective was to estimate the proportion with high `r ASCVD()` risk among adults with stage 1 hypertension and diabetes, `r CKD()`, or ≥65 years as the 2017 `r ACC_AHA()` `r BP()` guideline recommends initiation of antihypertensive medication for all of these adults.
 To accomplish these goals, we analyzed data from `r english(length(exams))` cycles of the US `r NHANES()`.
@@
 
-The current analysis was restricted to adults aged 40 to 79 years of age who complete the `r NHANES()` interview and examination (n = `r n_age_40_to_79`).
+The current analysis was restricted to adults aged 40 to 79 years of age who completed the `r NHANES()` interview and examination (n = `r n_age_40_to_79`).
 Participants <40 or >79 years of age were not included because the Pooled Cohort risk equations are not recommended to be used in these age ranges.[@goff20142013] Participants who did not have three `r SBP()` and `r DBP()` measurements (n = `r n_bp_too_low`) and those who were missing information on age, race, sex, total and high-density lipoprotein cholesterol, smoking status, diabetes, or `r CKD()` status (n = `r n_missing_pcr`) were excluded.
@@
 `r CKD()` was defined by an `r E_GFR()` <`r egfr_cutpoint` ml/min/1.73m^2^ or an `r ACR()` ≥`r acr_cutpoint` mg/dL.
-Ten-year predicted risk for `r ASCVD()` was calculated using the Pooled Cohort risk equations for participants without a history of `r CVD()`.[@goff20142013] High `r ASCVD()` risk was defined as a history of `r CVD()` or a 10-year predicted `r ASCVD()` risk ≥10%.
+Predicted 10-year risk for `r ASCVD()` was calculated using the Pooled Cohort risk equations for participants without prevalent `r CVD()`.[@goff20142013] High `r ASCVD()` risk was defined as prevalent `r CVD()` or a 10-year predicted `r ASCVD()` risk ≥10%.
 
@@
 The percentage of US adults in each of the five `r BP()` categories was computed.
-The median 10-year predicted risk among participants without a history of `r CVD()` was estimated overall and among `r BP()` categories in addition to the proportion of participants at high `r ASCVD()` risk.
-To assess the extent to which participants with a 10-year predicted `r ASCVD()` risk <10% were close to the 10% threshold, the proportion of participants in this subgroup with predicted risk of 0% to <2.5%, 2.5% to <5.0%, 5.0% to <7.5%, and 7.5% to <10% was estimated.
+The 25^th^, 50^th^, and 75^th^ percentile of 10-year predicted risk for `r ASCVD()` and the proportion of participants at high `r ASCVD()` risk were estimated for the overall US population and stratified by the 5 `r BP()` categories outlined in the preceding paragraph.
+To assess the extent to which participants with a 10-year predicted risk for `r ASCVD()` <10% were close to the 10% threshold, the proportion of participants in this subgroup with 10-year predicted risk for `r ASCVD()` from 0% to <2.5%, 2.5% to <5.0%, 5.0% to <7.5%, and 7.5% to <10% was estimated.
 The probability of having high `r ASCVD()` risk was estimated for each year of age from 40 to 79 years using logistic regression.
-The above analyses were repeated among participants with stage 1 hypertension.
+Analyses of participant characteristics, the distribution of 10-year predicted risk for `r ASCVD()`, and the probability of having high `r ASCVD()` risk were repeated among participants with stage 1 hypertension.
 
@@
 
-# R version string with fancy date
+# R version string with date spelled out in words
 R_string <- glue::glue("R version {version$major}.{version$minor}")
@@
 
-R_string_fancy <- glue::glue(
-  "{R_string} (released {date_string})"
-)
+R_string_fancy <- glue::glue("{R_string} (released {date_string})")
 
@@
 P-values were two-sided.
-Data analysis was conducted using `r R_string_fancy` along with a collection of open-source software packages (e.g., drake, dflow, officedown, and others) geared to enhance the transparency and reproducibility of our findings.[@cite_R; @cite_drake; @cite_tidyverse; @cite_table.glue] The first author's GitHub repository (< _Link not yet active so we won't be scooped_ >) provides code to reproduce the current manuscript as-is or with different initial parameters including exclusion criteria, variable definitions, and number of `r NHANES()` exams to pool.
-A detailed set of instructions for engaging with the project is provided in the repository's ReadMe file.
+Data analysis was conducted using `r R_string_fancy` along with a collection of open-source software packages (e.g., drake, dflow, officedown, and others).[@cite_R; @cite_drake; @cite_tidyverse; @cite_table.glue] The first author's GitHub repository (< _Link not yet active so we won't be scooped_ >) provides code to reproduce the current manuscript.
 
@@
 
-Among US adults who were 40 to 79 years of age in `r min(exams)`-`r max(exams)+1`, the estimated prevalence (95% `r CI(left_mark = '[', right_mark = ']')`) of diabetes and `r CKD()` was `r inline$prevDiabetesOverall` and `r inline$prevCkdOverall`, respectively, and `r inline$prevAge65Overall` were estimated to be ≥65 years of age (`r refer_to('tab_characteristics')`).
+Among US adults aged 40 to 79 years in `r min(exams)`-`r max(exams)+1`, the estimated prevalence (95% `r CI(left_mark = '[', right_mark = ']')`) of diabetes and `r CKD()` was `r inline$prevDiabetesOverall` and `r inline$prevCkdOverall`, respectively, `r inline$prevAge65Overall` were estimated to be ≥65 years of age, and `r inline$prevAnyOverall` had at least one of these conditions (`r refer_to('tab_characteristics')`).
 An estimated `r inline$prevS1hOverall` of US adults who were 40 to 79 years of age had stage 1 hypertension (`r refer_to('tab_bpdist')`).
-Among those with diabetes, CKD, and age ≥65 years, the estimated prevalence (95% `r CI()` ) of stage 1 hypertension was `r inline$prevS1hDiabetes`, `r inline$prevS1hCkd`, and `r inline$prevS1hAge65`, respectively.
-Characteristics of US adults 40 to 79 years of age with stage 1 hypertension, overall, and among those with diabetes, `r CKD()` and age ≥65 years are presented in Table S1
+Among those with diabetes, CKD, age ≥65 years, and any of these three conditions, the estimated prevalence (95% `r CI()` ) of stage 1 hypertension was `r inline$prevS1hDiabetes`, `r inline$prevS1hCkd`, `r inline$prevS1hAge65`, `r inline$prevS1hAny`, respectively.
+Characteristics of US adults 40 to 79 years of age with stage 1 hypertension, overall and for subgroups defined by diabetes, `r CKD()` and age ≥65 years, are presented in Table S1
 
@@
 
-Among US adults aged 40 to 49 years without a history of `r CVD()`, the estimated median (25th, 75th percentiles) 10-year predicted risk for `r ASCVD()` was `r inline$medianPcrOverall` in the overall population and `r inline$medianPcrDiabetes`, `r inline$medianPcrCkd`, and `r inline$medianPcrAge65` among those with diabetes, CKD, and age ≥65 years, respectively (`r refer_to('tab_risk_overall')`; top panel).
-Among US adults with stage 1 hypertension without a history of `r CVD()`, the estimated median (25th, 75th percentiles) 10-year predicted risk for `r ASCVD()` was `r inline$medianPcrS1hOverall`.
-Within this subgroup of adults with stage 1 hypertension, those with diabetes, `r CKD()`, and age ≥65 years had median (25th, 75th percentiles) predicted risks of of `r inline$medianPcrS1hDiabetes`, `r inline$medianPcrS1hCkd`, and `r inline$medianPcrS1hAge65` respectively.
+Among US adults aged 40 to 79 years without prevalent `r CVD()`, the estimated median (25th, 75th percentiles) 10-year predicted risk for `r ASCVD()` was `r inline$medianPcrOverall` in the overall population and `r inline$medianPcrDiabetes`, `r inline$medianPcrCkd`, `r inline$medianPcrAge65`, `r inline$medianPcrAny` among those with diabetes, CKD, age ≥65 years, and any of these three conditions, respectively (`r refer_to('tab_risk_overall')`; top panel).
+Among those with stage 1 hypertension and without prevalent `r CVD()`, the estimated median (25th, 75th percentiles) 10-year predicted risk for `r ASCVD()` was `r inline$medianPcrS1hOverall` overall and `r inline$medianPcrS1hDiabetes`, `r inline$medianPcrS1hCkd`, `r inline$medianPcrS1hAge65`, `r inline$medianPcrS1hAny` among those with diabetes, CKD, age ≥65 years, and any of these three conditions, respectively.
 
@@
 
-Among US adults aged 40 to 79 years with diabetes, CKD, or age ≥65 years, an estimated `r inline$prevHighRiskDiabetes`, `r inline$prevHighRiskCkd`, and `r inline$prevHighRiskAge65`, had high `r ASCVD()` risk, respectively (`r refer_to('tab_risk_overall')`; bottom panel).
-Among those with stage 1 hypertension, an estimated `r inline$prevHighRiskS1hDiabetes` of those with diabetes, `r inline$prevHighRiskS1hCkd` of those with `r CKD()` and `r inline$prevHighRiskS1hAge65` who were ≥65 years of age had high `r ASCVD()` risk.
+Among US adults aged 40 to 79 years, `r inline$prevHighRiskDiabetes`, `r inline$prevHighRiskCkd`, `r inline$prevHighRiskAge65`, and `r inline$prevHighRiskAny` of those with diabetes, `r CKD()`, age ≥65 years, or any of these conditions had high `r ASCVD()` risk, respectively (`r refer_to('tab_risk_overall')`; bottom panel).
+Among those with stage 1 hypertension, `r inline$prevHighRiskS1hDiabetes`, `r inline$prevHighRiskS1hCkd`, `r inline$prevHighRiskS1hAge65`, and `r inline$prevHighRiskS1hAny` of those with diabetes, `r CKD()`, age ≥65 years, or any of these conditions had high `r ASCVD()` risk, respectively.
 
@@
 
-## Age-specific analysis of 10-year predicted `r ASCVD()` risk ≥10% or history of `r CVD()`
+## Age-specific analysis of 10-year predicted `r ASCVD()` risk ≥10% or prevalent `r CVD()`
 
@@
 
-In the current study, a majority of US adults with diabetes, `r CKD()` or age ≥65 years had a high risk for `r ASCVD()`, defined by a 10-year predicted `r ASCVD()` risk ≥10% or history of `r CVD()`.
+In the current study, a majority of US adults with diabetes, `r CKD()` or age ≥65 years had a high risk for `r ASCVD()`, defined by a 10-year predicted `r ASCVD()` risk ≥10% or prevalent `r CVD()`.
 However, a substantial proportion of US adults with stage 1 hypertension and diabetes, CKD, or age ≥65 years did not have high `r ASCVD()` risk.
@@
 `r rp$supplement.figure$legend[1]`
+BP = blood pressure; NHANES = National Health and Nutrition Examination Survey. 
 `r fp_par(line_spacing = 1)`

### 2020-09-20 R/compile_report.R

@@ -36,7 +36,9 @@ compile_report <- function(exams,
                            fig_hist_ovrl,
                            fig_hist_stg1,
                            fig_risk_ovrl_bnry,
-                           fig_risk_stg1_bnry) {
+                           fig_risk_stg1_bnry,
+                           risk_10yr,
+                           risk_high) {
 
   # setup ----
 
@@ -88,18 +90,18 @@ compile_report <- function(exams,
   ftr_diab <- as_paragraph(glue('Diabetes was defined by fasting serum glucose \u2265{gluc_cutpoint_fasted} mg/dL, non-fasting glucose \u2265{gluc_cutpoint_fed} mg/dL, HbA1c \u2265{hba1c_cutpoint}%, or self-reported use of insulin or oral glucose lowering medication.'))
 
   bp_cat_guide <- as_paragraph(paste(
-    "Normal blood pressure: systolic blood pressure < 120 mm Hg and diastolic blood pressure < 80 mm Hg;",
-    "Elevated blood pressure: systolic blood pressure from 120 to 129 mm Hg and diastolic blood pressure < 80 mm Hg;",
+    "Normal blood pressure: systolic blood pressure <120 mm Hg and diastolic blood pressure <80 mm Hg;",
+    "Elevated blood pressure: systolic blood pressure from 120 to 129 mm Hg and diastolic blood pressure <80 mm Hg;",
     "Stage 1 hypertension: systolic blood pressure between 130 and 139 mm Hg and/or diastolic blood pressure between 80 and 89 mm Hg with systolic blood pressure <140 mm Hg and diastolic blood pressure <90 mm Hg;",
     "Stage 2 hypertension: systolic blood pressure \u2265140 mm Hg or diastolic blood pressure \u226590 mm Hg.",
     sep = '\n'
   ))
 
-  ftr_cvdHx <- as_paragraph('Data from survey participants with prevalent cardiovascular disease were not included for these statistics')
+  ftr_cvdHx <- as_paragraph('High atherosclerotic cardiovascular disease risk was defined by a 10-year predicted risk for atherosclerotic cardiovascular disease \u226510% or prevalent cardiovascular disease')
 
   ftr_cvdHx_defn <- as_paragraph('Prevalent cardiovascular disease was defined by self-report of previous heart failure, coronary heart disease, stroke, or myocardial infarction')
 
[…]

### 2020-09-20 R/make_inline_results.R

@@ -30,6 +30,11 @@ make_inline_results <- function(design_overall,
     transmute(string = table_glue("{est}% ({lwr}%, {upr}%)")) %>%
     pull(string)
 
+  prevAnyOverall <- svyciprop(~ any_ckd_diab_age65, design_overall) %>%
+    tidy_svy(mult_by = 100) %>%
+    transmute(string = table_glue("{est}% ({lwr}%, {upr}%)")) %>%
+    pull(string)
+
   meanAgeOverall <- svymean(~ age, design_overall) %>%
     tidy_svy(mult_by = 1) %>%
     transmute(string = table_glue("{est} ({lwr}, {upr})")) %>%
@@ -76,6 +81,16 @@ make_inline_results <- function(design_overall,
   prevS1hAge65 <- svyciprop(
     formula = ~ I(bp_cat == 'Stage 1 hypertension'),
     design = subset(design_overall, age_gt65 == 'yes')
+  ) %>%
+    tidy_svy(mult_by = 100) %>%
+    transmute(
+      string = table_glue("{est}% ({lwr}%, {upr}%)")
+    ) %>%
+    pull(string)
+
+  prevS1hAny <- svyciprop(
+    formula = ~ I(bp_cat == 'Stage 1 hypertension'),
+    design = subset(design_overall, any_ckd_diab_age65 == 'yes')
   ) %>%
     tidy_svy(mult_by = 100) %>%
     transmute(
@@ -180,67 +195,98 @@ make_inline_results <- function(design_overall,
     transmute(string = table_glue("{est}% ({lwr}%, {upr}%)")) %>%
     pull(string)
 
-
-
-  prevHighRiskDiabetes <- svyciprop(
-    formula = ~ pcr_highrisk,
-    design = subset(design_overall, diabetes == 'yes')
+  medianPcrAny <- svyquantile(
+    x = ~ ascvd_risk_pcr,
+    design = subset(design_overall,
+                    any_ckd_diab_age65 == 'yes' & ever_had_ascvd == 'no'),
+    quantiles = c(0.25, 0.50, 0.75)
   ) %>%
-    tidy_svy(mult_by = 100) %>%
-    transmute(
-      string = table_glue("{est}% (95% CI: {lwr}%, {upr}%)")
-    ) %>%
+    as_tibble() %>%
+    set_names(c('lwr', 'est', 'upr')) %>%
+    mutate_all(~.x * 100) %>%
[…]

### 2020-09-20 R/plan.R

@@ -15,6 +15,10 @@ the_plan <- drake_plan(
 
   exams = c(2013, 2015, 2017),
 
+  # phrases to be used consistently throughout project
+  risk_10yr = '10-year predicted risk for ASCVD',
+  risk_high = 'high ASCVD risk',
+
   # Demographics ----
   demo = clean_demo(exams),
 
@@ -166,7 +170,9 @@ the_plan <- drake_plan(
     fig_hist$ovrl,
     fig_hist$stg1,
     fig_risk_ovrl_bnry,
-    fig_risk_stg1_bnry
+    fig_risk_stg1_bnry,
+    risk_10yr = risk_10yr,
+    risk_high = risk_high
   ),
 
   # Report ----

### 2020-09-20 R/tabulate_risk_summary.R

@@ -7,29 +7,6 @@
 ##' @param decimals
 tabulate_risk_summary <- function(design) {
 
-  add_confint <- function(x){
-    cbind(x, confint(x))
-  }
-
-  standardize_names <- function(df){
-
-    p <- '^diabetes$|^ckd$|^age_gt65$|^any_ckd_diab_age65$|^diabetes_and_ckd$'
-
-    names(df) <- str_replace(names(df), pattern = p, replacement = 'level')
-
-    se_col <- str_detect(names(df), pattern = '^se\\.')
-    lwr_col <- str_detect(names(df), pattern = '^2\\.5')
-    upr_col <- str_detect(names(df), pattern = '^97\\.5')
-
-    if(any(se_col)) names(df)[se_col] <- 'se'
-    if(any(lwr_col)) names(df)[lwr_col] <- 'lwr'
-    if(any(upr_col)) names(df)[upr_col] <- 'upr'
-
-
-    df
-
-  }
-
   design_no_cvdhx <- subset(design, ever_had_ascvd == 'no')
 
   # Proportion at high risk -------------------------------------------------
@@ -182,5 +159,28 @@ tabulate_risk_summary <- function(design) {
     median_risk = md_risk_tbl,
     .id = 'group'
   )
+
+}
+
+add_confint <- function(x){
+  cbind(x, confint(x))
+}
+
+standardize_names <- function(df){
+
+  p <- '^diabetes$|^ckd$|^age_gt65$|^any_ckd_diab_age65$|^diabetes_and_ckd$'
+
+  names(df) <- str_replace(names(df), pattern = p, replacement = 'level')
+
+  se_col <- str_detect(names(df), pattern = '^se\\.')
+  lwr_col <- str_detect(names(df), pattern = '^2\\.5')
+  upr_col <- str_detect(names(df), pattern = '^97\\.5')
+
+  if(any(se_col)) names(df)[se_col] <- 'se'
+  if(any(lwr_col)) names(df)[lwr_col] <- 'lwr'
+  if(any(upr_col)) names(df)[upr_col] <- 'upr'
+
+
+  df
 
 }

### 2020-09-20 R/visualize_risk_hist.R

@@ -5,7 +5,7 @@
 ##' @title
 ##' @param design_overall
 ##' @param qts
-visualize_risk_hist <- function(design, qts) {
+visualize_risk_hist <- function(design, qts, risk_10yr) {
 
   # do not include participants with CVD history
   design <- subset(design, ever_had_ascvd == 'no' & ascvd_risk_pcr <= 0.10)
@@ -48,7 +48,7 @@ visualize_risk_hist <- function(design, qts) {
         "Diabetes" = "diabetes",
         "Chronic kidney disease" = "ckd",
         "Aged 65+ years" = "age",
-        "Any preceding condition" = "any"
+        "Diabetes, chronic kidney disease,\nor aged 65+ years" = "any"
       )
     )
 
@@ -64,13 +64,15 @@ visualize_risk_hist <- function(design, qts) {
         geom_text(vjust = -1) +
         theme_bw() +
         theme(panel.grid = element_blank(),
-              text = element_text(size = 12)) +
+              text = element_text(size = 10, colour = 'black'),
+              axis.text = element_text(size = 10, color = 'black'),
+              strip.text = element_text(size = 10)) +
         scale_x_continuous(labels = percent) +
         scale_y_continuous(labels = percent,
                            limits = c(0,1),
                            breaks = c(0, 0.25, 0.50, 0.75, 1),
                            expand = c(0,0)) +
-        labs(x = 'Predicted 10-year CVD risk, %',
+        labs(x = 'Predicted 10-year risk for atherosclerotic cardiovascular disease, %',
              y = 'Estimated % of US adults*') +
         facet_wrap(~panel, ncol = 2, scales = 'free')
     )

### 2020-09-21 doc/ACCAHA_BP_groups.Rmd
discussion updates based on PM feedback

@@
 # e.g., some journals only want 5 acronyms to be used.
+
 max_abbrevs <- 9
@@
 
-Byron C. Jaeger^1^, Swati Sakhuja^2^, Shakia T. Hardy^2^, Paul Muntner^2^, and Paul K. Whelton^3^
+Byron C. Jaeger^1^, Swati Sakhuja^2^, Shakia T. Hardy^2^, Philip Akinyelure^2^, Josh Bundy^3^, Paul Muntner^2^, and Paul K. Whelton^3^
 
@@
 In November 2017, the `r ACC_AHA()` published a guideline for the prevention, detection, evaluation, and management of high `r BP()` in adults.[@whelton20182017] This guideline recommends using both predicted predicted risk for `r CVD()` and `r BP()` levels to guide the initiation of antihypertensive medication.
-All adults with `r SBP()` ≥140 mm Hg or `r DBP()` ≥90 mm Hg, stage 2 hypertension in the guideline, are recommended to initiate antihypertensive medication.
-Additionally, adults with `r SBP()` between 130 and 139 mm Hg and/or `r DBP()` between 80 and 89 mm Hg, stage 1 hypertension in the guideline, who have prevalent diabetes mellitus, prevalent `r CKD()`, ≥65 years of age, or high `ASCVD()` risk are recommended to initiate antihypertensive medication.
-High `ASCVD()` risk is defined as prevalent `r CVD()` or a 10-year predicted risk for `r ASCVD()` ≥10%
+All adults with `r SBP()` ≥ 140 mm Hg or `r DBP()` ≥ 90 mm Hg, stage 2 hypertension in the guideline, are recommended to initiate antihypertensive medication.
+Additionally, adults with `r SBP()` between 130 and 139 mm Hg and/or `r DBP()` between 80 and 89 mm Hg, stage 1 hypertension in the guideline, who have prevalent diabetes mellitus, prevalent `r CKD()`, age ≥ 65 years, or high `r ASCVD()` risk are recommended to initiate antihypertensive medication.
+High `r ASCVD()` risk is defined as prevalent `r CVD()` or a 10-year predicted risk for `r ASCVD()` ≥ 10%
 
@@
 
-The 2017 `r ACC_AHA()` guideline recommends computing 10-year predicted risk for `r ASCVD()` in all adults with hypertension, including those with diabetes, `r CKD()` or ≥65 years of age.
-However, the guideline states that the vast majority of adults with diabetes, CKD, or ≥65 years of age can be assumed to have a 10-year predicted risk for `r ASCVD()` ≥10%.
-The purpose of the current analysis was to estimate the proportion of US adults with diabetes, `r CKD()`, or ≥65 years of age that have high `r ASCVD()` risk (i.e., a 10-year predicted risk for `r ASCVD()` ≥10% or prevalent `r CVD()`).
-A secondary objective was to estimate the proportion with high `r ASCVD()` risk among adults with stage 1 hypertension and diabetes, `r CKD()`, or ≥65 years as the 2017 `r ACC_AHA()` `r BP()` guideline recommends initiation of antihypertensive medication for all of these adults.
+The 2017 `r ACC_AHA()` guideline recommends computing 10-year predicted risk for `r ASCVD()` in all adults with hypertension to establish a `r BP()` threshold for treatment.[@whelton20182017] However, it has been suggested that the vast majority of adults with diabetes, CKD, or ≥ 65 years of age are likely to have a 10-year predicted risk for `r ASCVD()` ≥ 10%.
+The purpose of the current analysis was to estimate the proportion of US adults with diabetes, `r CKD()`, or ≥ 65 years of age that have high `r ASCVD()` risk (i.e., a 10-year predicted risk for `r ASCVD()` ≥ 10% or prevalent `r CVD()`).
+A secondary objective was to estimate the proportion of adults with stage 1 hypertension and diabetes, `r CKD()`, or age ≥ 65 years who have high `r ASCVD()` risk, as the 2017 `r ACC_AHA()` `r BP()` guideline recommends initiation of antihypertensive medication for these individuals.
 To accomplish these goals, we analyzed data from `r english(length(exams))` cycles of the US `r NHANES()`.
@@
 
-`r NHANES()` was designed to assess the health and nutritional status of the non-institutionalized US population and is conducted by the National Center for Health Statistics of the Centers for Disease Control and Prevention.[@nhanes_home] Since 1999-2000, `r NHANES()` has been conducted in two-year cycles using a multistage probability sampling design to select participants.
+`r NHANES()` was designed to assess the health and nutritional status of the non-institutionalized US population and was conducted by the National Center for Health Statistics of the Centers for Disease Control and Prevention.[@nhanes_home] Since 1999-2000, `r NHANES()` has been conducted in two-year cycles using a multistage probability sampling design to select participants.
 Each cycle is independent with different participants recruited.
@@
 The current analysis was restricted to adults aged 40 to 79 years of age who completed the `r NHANES()` interview and examination (n = `r n_age_40_to_79`).
-Participants <40 or >79 years of age were not included because the Pooled Cohort risk equations are not recommended to be used in these age ranges.[@goff20142013] Participants who did not have three `r SBP()` and `r DBP()` measurements (n = `r n_bp_too_low`) and those who were missing information on age, race, sex, total and high-density lipoprotein cholesterol, smoking status, diabetes, or `r CKD()` status (n = `r n_missing_pcr`) were excluded.
-After these exclusions, over the `r english(length(exams))` `r NHANES()` cycles, a total of `r n_final` survey participants were included in the analysis (`r refer_to('fig_include_exclude')`).
+Participants < 40 or > 79 years of age were not included because the Pooled Cohort risk equations are not recommended to be used in these age ranges.[@goff20142013] Participants who did not have three `r SBP()` and `r DBP()` measurements (n = `r n_bp_too_low`) and those who were missing information on age, race, sex, total and high-density lipoprotein cholesterol, smoking status, diabetes, or `r CKD()` status (n = `r n_missing_pcr`) were excluded.
+After these exclusions, over the `r english(length(exams))` `r NHANES()` cycles, a total of `r n_final` participants were included in the analysis (`r refer_to('fig_include_exclude')`).
 
@@
 Of relevance to the current analysis, serum creatinine, serum glucose and `r HB_A1C()` were measured.
-Diabetes was defined by fasting serum glucose ≥`r gluc_cutpoint_fasted` mg/dL, non-fasting glucose ≥`r gluc_cutpoint_fed` mg/dL, `r HB_A1C()` ≥`r hba1c_cutpoint`%, or self-reported use of insulin or oral glucose lowering medication.
+Diabetes was defined by fasting serum glucose ≥ `r gluc_cutpoint_fasted` mg/dL, non-fasting glucose ≥ `r gluc_cutpoint_fed` mg/dL, `r HB_A1C()` ≥ `r hba1c_cutpoint`%, or self-reported use of insulin or oral glucose lowering medication.
 `r capitalize(E_GFR())` was calculated using the Chronic Kidney Disease Epidemiology Collaboration equation.[@levey2009new] Urinary albumin and creatinine levels were measured and used to calculate the `r ACR()`.
-`r CKD()` was defined by an `r E_GFR()` <`r egfr_cutpoint` ml/min/1.73m^2^ or an `r ACR()` ≥`r acr_cutpoint` mg/dL.
-Predicted 10-year risk for `r ASCVD()` was calculated using the Pooled Cohort risk equations for participants without prevalent `r CVD()`.[@goff20142013] High `r ASCVD()` risk was defined as prevalent `r CVD()` or a 10-year predicted `r ASCVD()` risk ≥10%.
+`r CKD()` was defined by an `r E_GFR()` < `r egfr_cutpoint` ml/min/1.73m^2^ or an `r ACR()` ≥ `r acr_cutpoint` mg/dL.
+Predicted 10-year risk for `r ASCVD()` was calculated using the Pooled Cohort risk equations for participants without prevalent `r CVD()`.[@goff20142013] High `r ASCVD()` risk was defined as prevalent `r CVD()` or a 10-year predicted `r ASCVD()` risk ≥ 10%.
 
@@
 
-Participants not taking antihypertensive medication were grouped into four non-overlapping categories based on the 2017 `r ACC_AHA()` `r BP()` guideline: Normal `r BP()` (`r SBP()` <120 mm Hg and `r DBP()` <80 mm Hg), elevated `r BP()` (`r SBP()` between 120 and 129 mm Hg and `r DBP()` <80 mm Hg), stage 1 hypertension (`r SBP()` between 130 and 139 mm Hg and/or `r DBP()` between 80 and 89 mm Hg with `r SBP()` <140 mm Hg and `r DBP()` <90 mm Hg), stage 2 hypertension (`r SBP()` ≥140 mm Hg or `r DBP()` ≥90 mm Hg).
+Participants not taking antihypertensive medication were grouped into four non-overlapping categories based on the 2017 `r ACC_AHA()` `r BP()` guideline: Normal `r BP()` (`r SBP()` < 120 mm Hg and `r DBP()` < 80 mm Hg), elevated `r BP()` (`r SBP()` between 120 and 129 mm Hg and `r DBP()` < 80 mm Hg), stage 1 hypertension (`r SBP()` between 130 and 139 mm Hg and/or `r DBP()` between 80 and 89 mm Hg with `r SBP()` < 140 mm Hg and `r DBP()` < 90 mm Hg), stage 2 hypertension (`r SBP()` ≥ 140 mm Hg or `r DBP()` ≥ 90 mm Hg).
 Participants taking antihypertensive medication were placed in a fifth category.
@@
 
-Analyses were conducted for the overall population and among participants with diabetes, CKD, ≥65 years of age, and for those with any of these three conditions.
+Analyses were conducted for the overall population and among participants with diabetes, CKD, ≥ 65 years of age, and for those with any of these three conditions.
 Participant characteristics were summarized as mean with their standard error and percentage for continuous and categorical variables, respectively.
 The percentage of US adults in each of the five `r BP()` categories was computed.
-The 25^th^, 50^th^, and 75^th^ percentile of 10-year predicted risk for `r ASCVD()` and the proportion of participants at high `r ASCVD()` risk were estimated for the overall US population and stratified by the 5 `r BP()` categories outlined in the preceding paragraph.
-To assess the extent to which participants with a 10-year predicted risk for `r ASCVD()` <10% were close to the 10% threshold, the proportion of participants in this subgroup with 10-year predicted risk for `r ASCVD()` from 0% to <2.5%, 2.5% to <5.0%, 5.0% to <7.5%, and 7.5% to <10% was estimated.
+The 25^th^, 50^th^, and 75^th^ percentile of 10-year predicted risk for `r ASCVD()` and the proportion of participants with high `r ASCVD()` risk were estimated overall and within each `r BP()` category outlined in the preceding paragraph.
+To assess the extent to which participants with a 10-year predicted risk for `r ASCVD()` < 10% were close to the 10% threshold, the proportion of participants in this subgroup with 10-year predicted risk for `r ASCVD()` from < 2.5%, 2.5% to < 5.0%, 5.0% to < 7.5%, and 7.5% to < 10% was estimated.
 The probability of having high `r ASCVD()` risk was estimated for each year of age from 40 to 79 years using logistic regression.
-Analyses of participant characteristics, the distribution of 10-year predicted risk for `r ASCVD()`, and the probability of having high `r ASCVD()` risk were repeated among participants with stage 1 hypertension.
+Analyses of participant characteristics, distribution of 10-year predicted risk for `r ASCVD()`, and probability of having high `r ASCVD()` risk were replicated among participants with stage 1 hypertension.
 
@@
 
-`r NHANES()` sampling weights, which were calculated as the inverse probability of being selected for the survey, were used in all calculations to obtain US nationally representative estimates.
-The survey design of `r NHANES()` was also taken into account.
+`r NHANES()` sampling weights, which were calculated as the inverse probability of being selected for the survey, were used in all calculations to obtain nationally representative estimates of the non-institutionalized US population.
+The survey design of `r NHANES()` was also taken into account in all calculations.
 P-values were two-sided.
-Data analysis was conducted using `r R_string_fancy` along with a collection of open-source software packages (e.g., drake, dflow, officedown, and others).[@cite_R; @cite_drake; @cite_tidyverse; @cite_table.glue] The first author's GitHub repository (< _Link not yet active so we won't be scooped_ >) provides code to reproduce the current manuscript.
+Data analysis was conducted using `r R_string_fancy` along with a collection of open-source software packages (e.g., drake, dflow, officedown, and others) to enhance the transparency and reproducibility of the current analysis.[@cite_R; @cite_drake; @cite_tidyverse; @cite_table.glue] The first author's GitHub repository (< _Link not yet active so we won't be scooped_ >) provides code to reproduce the current manuscript.
 
@@
 
-Among US adults aged 40 to 79 years in `r min(exams)`-`r max(exams)+1`, the estimated prevalence (95% `r CI(left_mark = '[', right_mark = ']')`) of diabetes and `r CKD()` was `r inline$prevDiabetesOverall` and `r inline$prevCkdOverall`, respectively, `r inline$prevAge65Overall` were estimated to be ≥65 years of age, and `r inline$prevAnyOverall` had at least one of these conditions (`r refer_to('tab_characteristics')`).
+Among US adults aged 40 to 79 years in `r min(exams)`-`r max(exams)+1`, the estimated prevalence (95% `r CI(left_mark = '[', right_mark = ']')`) of diabetes and `r CKD()` was `r inline$prevDiabetesOverall` and `r inline$prevCkdOverall`, respectively, `r inline$prevAge65Overall` were estimated to be ≥ 65 years of age, and `r inline$prevAnyOverall` had at least one of these conditions (`r refer_to('tab_characteristics')`).
 An estimated `r inline$prevS1hOverall` of US adults who were 40 to 79 years of age had stage 1 hypertension (`r refer_to('tab_bpdist')`).
-Among those with diabetes, CKD, age ≥65 years, and any of these three conditions, the estimated prevalence (95% `r CI()` ) of stage 1 hypertension was `r inline$prevS1hDiabetes`, `r inline$prevS1hCkd`, `r inline$prevS1hAge65`, `r inline$prevS1hAny`, respectively.
-Characteristics of US adults 40 to 79 years of age with stage 1 hypertension, overall and for subgroups defined by diabetes, `r CKD()` and age ≥65 years, are presented in Table S1
+Among those with diabetes, CKD, age ≥ 65 years, and any of these three conditions, the estimated prevalence (95% `r CI()` ) of stage 1 hypertension was `r inline$prevS1hDiabetes`, `r inline$prevS1hCkd`, `r inline$prevS1hAge65`, `r inline$prevS1hAny`, respectively.
+Characteristics of US adults 40 to 79 years of age with stage 1 hypertension, overall and for subgroups defined by diabetes, `r CKD()` and age ≥ 65 years, are presented in Table S1
 
@@
 
-Among US adults aged 40 to 79 years without prevalent `r CVD()`, the estimated median (25th, 75th percentiles) 10-year predicted risk for `r ASCVD()` was `r inline$medianPcrOverall` in the overall population and `r inline$medianPcrDiabetes`, `r inline$medianPcrCkd`, `r inline$medianPcrAge65`, `r inline$medianPcrAny` among those with diabetes, CKD, age ≥65 years, and any of these three conditions, respectively (`r refer_to('tab_risk_overall')`; top panel).
-Among those with stage 1 hypertension and without prevalent `r CVD()`, the estimated median (25th, 75th percentiles) 10-year predicted risk for `r ASCVD()` was `r inline$medianPcrS1hOverall` overall and `r inline$medianPcrS1hDiabetes`, `r inline$medianPcrS1hCkd`, `r inline$medianPcrS1hAge65`, `r inline$medianPcrS1hAny` among those with diabetes, CKD, age ≥65 years, and any of these three conditions, respectively.
+Among US adults aged 40 to 79 years without prevalent `r CVD()`, the estimated median (25^th^, 75^th^ percentiles) 10-year predicted risk for `r ASCVD()` was `r inline$medianPcrOverall` overall and `r inline$medianPcrDiabetes`, `r inline$medianPcrCkd`, `r inline$medianPcrAge65`, `r inline$medianPcrAny` among those with diabetes, CKD, age ≥ 65 years, and any of these three conditions, respectively (`r refer_to('tab_risk_overall')`; top panel).
+Among those with stage 1 hypertension, the estimated median (25^th^, 75^th^ percentiles) 10-year predicted risk for `r ASCVD()` was `r inline$medianPcrS1hOverall` overall and `r inline$medianPcrS1hDiabetes`, `r inline$medianPcrS1hCkd`, `r inline$medianPcrS1hAge65`, `r inline$medianPcrS1hAny` among those with diabetes, CKD, age ≥ 65 years, and any of these three conditions, respectively.
 
@@
 
-Among US adults aged 40 to 79 years, `r inline$prevHighRiskDiabetes`, `r inline$prevHighRiskCkd`, `r inline$prevHighRiskAge65`, and `r inline$prevHighRiskAny` of those with diabetes, `r CKD()`, age ≥65 years, or any of these conditions had high `r ASCVD()` risk, respectively (`r refer_to('tab_risk_overall')`; bottom panel).
-Among those with stage 1 hypertension, `r inline$prevHighRiskS1hDiabetes`, `r inline$prevHighRiskS1hCkd`, `r inline$prevHighRiskS1hAge65`, and `r inline$prevHighRiskS1hAny` of those with diabetes, `r CKD()`, age ≥65 years, or any of these conditions had high `r ASCVD()` risk, respectively.
+Among US adults aged 40 to 79 years, the estimated proportion at high ASCVD risk was `r inline$prevHighRiskOverall` overall and `r inline$prevHighRiskDiabetes`, `r inline$prevHighRiskCkd`, `r inline$prevHighRiskAge65`, and `r inline$prevHighRiskAny` for those with diabetes, `r CKD()`, age ≥ 65 years, or any of these three conditions, respectively (`r refer_to('tab_risk_overall')`; bottom panel).
+Among those with stage 1 hypertension, an estimated `r inline$prevHighRiskS1hOverall` had high `r ASCVD()` risk overall and `r inline$prevHighRiskS1hDiabetes`, `r inline$prevHighRiskS1hCkd`, `r inline$prevHighRiskS1hAge65`, and `r inline$prevHighRiskS1hAny` of those with diabetes, `r CKD()`, age ≥ 65 years, or any of these three conditions had high `r ASCVD()` risk, respectively.
 
@@
 
-## Distribution of predicted risk in low risk groups
-
-Among US adults who were not at high risk for `r ASCVD()`, an estimated `r inline$propLowRiskOverall` of US adults had 10-year predicted `r ASCVD()` risk <5% (`r refer_to('fig_hist_ovrl')`).
-Among those with diabetes, `r CKD()` and age ≥65 years, an estimated `r inline$propLowRiskDiabetes`, `r inline$propLowRiskCkd`, and `r inline$propLowRiskAge65` had a 10-year predicted `r ASCVD()` risk <5%, respectively.
-Among US adults with stage 1 hypertension who were not at high risk for `r ASCVD()`, an estimated `r inline$propLowRiskS1hDiabetes`, `r inline$propLowRiskS1hCkd`, and `r inline$propLowRiskS1hAge65` of those with diabetes, CKD, and ≥65 years of age had a 10-year predicted `r ASCVD()` risk <5%, respectively (`r refer_to('fig_hist_stg1')`).
+Among US adults who were not at high risk for `r ASCVD()`, an estimated `r inline$propLowRiskOverall` had 10-year predicted `r ASCVD()` risk < 5% (`r refer_to('fig_hist_ovrl')`).
+Among those not at high risk for `r ASCVD()` with diabetes, `r CKD()` age ≥ 65 years, and any of these three conditions, an estimated `r inline$propLowRiskDiabetes`, `r inline$propLowRiskCkd`, `r inline$propLowRiskAge65`, and `r inline$propLowRiskAny` had a 10-year predicted `r ASCVD()` risk < 5%, respectively.
+Among those not at high risk for `r ASCVD()` and with stage 1 hypertension, an estimated `r inline$propLowRiskS1hOverall` overall and  `r inline$propLowRiskS1hDiabetes`, `r inline$propLowRiskS1hCkd`, and `r inline$propLowRiskS1hAge65` of those with diabetes, CKD, and ≥ 65 years of age had a 10-year predicted `r ASCVD()` risk < 5%, respectively (`r refer_to('fig_hist_stg1')`).
 
@@
 
-## Age-specific analysis of 10-year predicted `r ASCVD()` risk ≥10% or prevalent `r CVD()`
+## Age-specific analysis of high `r ASCVD()` risk
 
-The estimated probability of having high `r ASCVD()` risk increased with older age and exceeded 50% at `r inline$ageHighRiskOvrlNoComorb` years for US adults without diabetes or `r CKD()` compared with `r inline$ageHighRiskOvrlDiabetes` and `r inline$ageHighRiskOvrlCkd` years for US adults with diabetes and CKD, respectively (`r refer_to('fig_risk_ovrl')`).
+The estimated probability of having high `r ASCVD()` risk increased with older age and exceeded 50% at `r inline$ageHighRiskOvrlNoComorb` years for US adults without diabetes or `r CKD()`, compared with `r inline$ageHighRiskOvrlDiabetes` and `r inline$ageHighRiskOvrlCkd` years for US adults with diabetes and CKD, respectively (`r refer_to('fig_risk_ovrl')`).
 Among US adults with stage 1 hypertension, the age at which the estimated probability of having high `r ASCVD()` risk exceeded 50% was `r inline$ageHighRiskS1hNoComorb`, `r inline$ageHighRiskS1hDiabetes`, and `r inline$ageHighRiskS1hCkd` years for US adults without diabetes or CKD, with diabetes, and with CKD, respectively (`r refer_to('fig_risk_stg1')`).
-The minimum age where the probability of high `r ASCVD()` risk exceeded 50% was not determined for adults ≥65 years of age as the probability exceeded 50% at all ages above 65 years.
+The minimum age where the probability of high `r ASCVD()` risk exceeded 50% was not determined for adults ≥ 65 years of age as the probability exceeded 50% at all ages above 65 years.
 
@@
 
-In the current study, a majority of US adults with diabetes, `r CKD()` or age ≥65 years had a high risk for `r ASCVD()`, defined by a 10-year predicted `r ASCVD()` risk ≥10% or prevalent `r CVD()`.
-However, a substantial proportion of US adults with stage 1 hypertension and diabetes, CKD, or age ≥65 years did not have high `r ASCVD()` risk.
-Among all US adults who were not at high risk for `r ASCVD()`, approximately half of those with diabetes or `r CKD()` had a 10-year predicted `r ASCVD()` risk <5%.
-In contrast, over 80% of adults aged ≥65 years had 10-year predicted risk for `r ASCVD()` between 5% and 10%.
-The probability of having high risk was age-dependent with over 50% of those with diabetes who were 55 years of age and older and with `r CKD()` who were age 59 years of age and older having high `r ASCVD()` risk.
+In the current study, a majority of US adults with diabetes, `r CKD()` age ≥ 65 years, and any of these three conditions had a high risk for `r ASCVD()`, defined by a 10-year predicted `r ASCVD()` risk ≥ 10% or prevalent `r CVD()`.
+However, a substantial proportion of US adults with stage 1 hypertension and diabetes, CKD, age ≥ 65 years, and any of these three conditions did not have high `r ASCVD()` risk.
+It was estimated that approximately half of US adults aged 40 to 79 years with diabetes or `r CKD()` who were not at high `r ASCVD()` risk had a 10-year predicted `r ASCVD()` risk < 5%.
+In contrast, over 80% of adults aged ≥ 65 years not at high `ASCVD()` risk had 10-year predicted risk for `r ASCVD()` between 5% and 10%.
+The probability of having high `r ASCVD()` risk was age-dependent with over 50% of those with diabetes and `CKD()` aged ≥`r inline$ageHighRiskOvrlDiabetes`  and ≥`r inline$ageHighRiskOvrlCkd` years, respectively, expected to have high `r ASCVD()` risk.
 
@@
 
-Among US adults aged 40 to 79 years, the current study estimates that roughly 33% use antihypertensive medication.
-Among US adults aged 40 to 79 years with diabetes, `r CKD()`, or ≥65 years of age, the current study estimates that roughly 50% use antihypertensive medication and relatively few (roughly 10%) have stage 1 hypertension.
-Therefore, the use of 10-year predicted `r ASCVD()` risk to guide treatment only applies to a small percentage of adults with at least one of these conditions.
-Additionally, it is possible that existing 10-year `r ASCVD()` risk prediction models, including the Pooled Cohort risk prediction equations, are not calibrated for prediction of `r ASCVD()` risk among this relatively small group of adults, particularly for those of younger age.
+The current study estimates that roughly 33% of US adults aged 40 to 79 years take antihypertensive medication, including half of those with diabetes, CKD, or ≥ 65 years of age.
+Among those with diabetes, `r CKD()`, or age ≥ 65 years, only about 10% had stage 1 hypertension.
+The 2017 `r ACC_AHA()` `r BP()` guideline recommends all of these adults initiate antihypertensive medication, but the current study estimates that a substantial proportion of them do not have high `r ASCVD()` risk.
+Therefore, computing 10-year predicted `r ASCVD()` risk may be especially informative for adults with stage 1 hypertension and diabetes, `r CKD()`, or ≥ 65 years of age and may also help facilitate patient provider interactions where a `r BP()` treatment goal is discussed.
 
@@
 
-Previous studies have shown that the use of predicted `r ASCVD()` risk in addition to `r BP()` can direct antihypertensive medication to adults likely to receive the largest risk reduction benefit with treatment.[@colantonio20182017; @jaeger2019cardiovascular] In an analysis of the Reasons for Geographic and Racial Differences in Stroke study, those with stage 1 hypertension recommended versus not recommended to initiate antihypertensive medication by the 2017 `r ACC_AHA()` `r BP()` guideline were roughly 6 times more likely to experience a `r CVD()` event over 8 years of follow-up.
-Although a substantial proportion of US adults with stage 1 hypertension and diabetes, CKD, or age ≥65 years of age did not have a high `r ASCVD()` risk, they were more likely to have high `r ASCVD()` risk when compared to the overall US population with stage 1 hypertension.
-This suggests adults with stage 1 hypertension and diabetes, `r CKD()` or age ≥65 years of age may obtain greater risk reduction versus the overall population by initiating antihypertensive medication.
+Previous studies have shown that the use of predicted `r ASCVD()` risk in addition to `r BP()`, as recommended by the 2017 `r ACC_AHA()` `r BP()` guideline, can direct antihypertensive medication to adults likely to receive the largest risk reduction benefit with treatment.[@colantonio20182017; @jaeger2019cardiovascular] In an analysis of the Reasons for Geographic and Racial Differences in Stroke study, those with stage 1 hypertension recommended versus not recommended to initiate antihypertensive medication by the 2017 `r ACC_AHA()` `r BP()` guideline were roughly 6 times more likely to experience a `r CVD()` event over 8 years of follow-up.
+Although a substantial proportion of US adults with stage 1 hypertension and diabetes, `r CKD()`, or ≥ 65 years of age did not have a high `r ASCVD()` risk in the current study, they were more likely to have high `r ASCVD()` risk compared to the overall US population with stage 1 hypertension.
 
@@
 
-It has been suggested that the vast majority of adults with diabetes, CKD, or ≥65 years of age have a 10-year predicted risk for `r ASCVD()` ≥10%.
-Diabetes and `r CKD()` are each associated with an increased risk for `r ASCVD()` events.[@coresh2004evidence; @chronic2010association; @grundy1999diabetes] Moreover, in the current study, the mean age was 4 to 6 years older for US adults with diabetes and `r CKD()` versus the overall US population.
-Age is a strong risk factor for incident `r ASCVD()` and a strong contributor to 10-year predicted `r ASCVD()` risk in the Pooled Cohort risk equations.[@lakatta2002age; @pencina2019quantifying] However, the current study estimates suggest that a high proportion of US adults with diabetes or `r CKD()` do not have a high 10-year predicted risk for `r ASCVD()`, especially those with stage 1 hypertension.
-Future studies should assess the absolute `r CVD()` risk reduction for this population with antihypertensive medication treatment.
+Previous randomized trials and meta-analyses have investigated whether lower `r BP()` treatment goals reduce incident `r CVD()` risk in patients with diabetes, `r CKD()`, or ≥ 65 years of age.
+the Systolic Blood Pressure Intervention Trial, which compared the `r SBP()` treatment target of < 120 mm Hg to < 140 mm Hg among older adults (mean age of 68 years) without diabetes, found lower rates of incident fatal and nonfatal major `r CVD()` events among those with the lower `r SBP()` target.
+A randomized trial of patients with diabetes and baseline `r SBP()` < 140 mm hg and `r DBP()` < 80 mm Hg found lower risk of stroke among participants with more intense `r BP()` treatment goals.[@schrier2002effects] A systematic review and meta-analysis of 123 studies with 613,815 participants found strong support for lowering `r SBP()` to less than 130 mm Hg and providing antihypertensive medication to adults with diabetes, CKD, and various other comorbidities.[@ettehad2016blood] This suggests adults with stage 1 hypertension and diabetes, `r CKD()` or ≥ 65 years of age may obtain greater risk reduction versus the overall population by initiating antihypertensive medication.
 
@@
 
-Although a majority of older adults with diabetes and `r CKD()` had high `r ASCVD()` risk, the majority of younger adults did not have high `r ASCVD()` risk.
-However, most young adults with diabetes and `r CKD()` have a high lifetime `r CVD()` risk.[@lloyd2006prediction; @hippisley2010derivation] Prior studies have found that cumulative exposure to high `r BP()` is associated with increased `r CVD()` risk.[@allen2014blood] Therefore, for younger adults with diabetes or CKD, antihypertensive medication may provide substantial reduction in `r ASCVD()` across their life course.
-Patient-provider discussions, including discussions of 10-year and lifetime risk for `r CVD()`, and patient preference should be used to guide the decision to initiate antihypertensive medication.
+It has been suggested that the vast majority of adults with diabetes, CKD, or ≥ 65 years of age have a 10-year predicted risk for `r ASCVD()` ≥ 10%.[@whelton20182017] Previous research has shown that diabetes, `r CKD()`, and advanced age are each associated with an increased risk for `r ASCVD()` events.[@coresh2004evidence; @chronic2010association; @grundy1999diabetes; @lakatta2002age].
+Although the current study suggests that a high proportion of US adults with stage 1 hypertension and diabetes or `r CKD()` do not have high 10-year predicted risk for `r ASCVD()`, others have previously shown that adults with diabetes and `r CKD()` have a high lifetime `r CVD()` risk.[@lloyd2006prediction; @hippisley2010derivation] Age-adjusted estimates from the current study echo these findings and suggests that adults with diabetes and `r CKD()` develop high `r ASCVD()` risk at a younger age than adults without these conditions.
+Prior studies have also found that cumulative exposure to high `r BP()` is associated with increased `r CVD()` risk.[@allen2014blood] Therefore, for younger adults with diabetes or `r CKD()`, antihypertensive medication may provide substantial reduction in `r ASCVD()` across their life course.
+predicted 10-year risk for `r ASCVD()` should be computed for all patients, as the `r ACC_AHA()` `r BP()` guideline suggests, and lifetime `r CVD()` risk should be taken into account for younger patients with diabetes or `r CKD()`.
+Taken together, these risk assessment techniques can inform patients and help guide the decision to initiate antihypertensive medication.
 
@@
 `r NHANES()` participants completed only one visit and guidelines recommend using the mean `r BP()` averaged over 2 or more visits.
-The use of predicted `r ASCVD()` risk rather than observed `r ASCVD()` events may have over- or under-estimated `r ASCVD()` risk in subgroups where the Pooled Cohort risk equations are not well-calibrated.
+Additionally, only one measurement of serum creatinine and urine albuminuria were available, which may have resulted in mis-classification of CKD status A total of `r table_value(sum(current_analysis$data$bp_cat == 'Stage 1 hypertension'))` participants had stage 1 hypertension, and some subgroups of this population based on diabetes, `r CKD()`, and ≥ 65 years of age were small.
 
@@
 
-In conclusion, a majority of US adults aged 40 to 79 years with diabetes, `r CKD()` or ≥65 years of age had 10-year predicted risk for `r ASCVD()` ≥10%.
-However, a lower percentage of with stage 1 hypertension and diabetes, `r CKD()` or age ≥65 years of age had 10-year predicted risk for `r ASCVD()` ≥10%.
-While most older US adults with diabetes or `r CKD()` have high risk, a substantial proportion of younger adults with diabetes or `r CKD()` have a 10-year predicted risk for `r ASCVD()` <10%.
+In conclusion, a majority of US adults aged 40 to 79 years with diabetes, `r CKD()` or ≥ 65 years of age had 10-year predicted risk for `r ASCVD()` ≥ 10%.
+However, a lower percentage of with stage 1 hypertension and diabetes, `r CKD()` or age ≥ 65 years of age had 10-year predicted risk for `r ASCVD()` ≥ 10%.
+While most older US adults with diabetes or `r CKD()` have high risk, a substantial proportion of younger adults with diabetes or `r CKD()` have a 10-year predicted risk for `r ASCVD()` < 10%.
 While prevention of hypertension should be a primary goal, the early initiation of antihypertensive medication may be an important step towards lowering lifetime `r CVD()` risk.

### 2020-09-21 R/compile_report.R

@@ -85,19 +85,19 @@ compile_report <- function(exams,
 
   value_note <- as_paragraph("Table values are mean (standard error) or proportion.")
 
-  ftr_ckd <- as_paragraph(glue('Chronic kidney disease is defined by an albumin-to-creatinine ratio \u2265{acr_cutpoint} mg/dl or an estimated glomerular filtration rate <{egfr_cutpoint} ml/min/1.73m\u00b2'))
+  ftr_ckd <- as_paragraph(glue('Chronic kidney disease is defined by an albumin-to-creatinine ratio \u2265 {acr_cutpoint} mg/dl or an estimated glomerular filtration rate < {egfr_cutpoint} ml/min/1.73m\u00b2'))
 
-  ftr_diab <- as_paragraph(glue('Diabetes was defined by fasting serum glucose \u2265{gluc_cutpoint_fasted} mg/dL, non-fasting glucose \u2265{gluc_cutpoint_fed} mg/dL, HbA1c \u2265{hba1c_cutpoint}%, or self-reported use of insulin or oral glucose lowering medication.'))
+  ftr_diab <- as_paragraph(glue('Diabetes was defined by fasting serum glucose \u2265 {gluc_cutpoint_fasted} mg/dL, non-fasting glucose \u2265 {gluc_cutpoint_fed} mg/dL, HbA1c \u2265 {hba1c_cutpoint}%, or self-reported use of insulin or oral glucose lowering medication.'))
 
   bp_cat_guide <- as_paragraph(paste(
-    "Normal blood pressure: systolic blood pressure <120 mm Hg and diastolic blood pressure <80 mm Hg;",
-    "Elevated blood pressure: systolic blood pressure from 120 to 129 mm Hg and diastolic blood pressure <80 mm Hg;",
-    "Stage 1 hypertension: systolic blood pressure between 130 and 139 mm Hg and/or diastolic blood pressure between 80 and 89 mm Hg with systolic blood pressure <140 mm Hg and diastolic blood pressure <90 mm Hg;",
-    "Stage 2 hypertension: systolic blood pressure \u2265140 mm Hg or diastolic blood pressure \u226590 mm Hg.",
+    "Normal blood pressure: systolic blood pressure < 120 mm Hg and diastolic blood pressure < 80 mm Hg;",
+    "Elevated blood pressure: systolic blood pressure from 120 to 129 mm Hg and diastolic blood pressure < 80 mm Hg;",
[…]

### 2020-09-21 R/make_inline_results.R

@@ -220,6 +220,7 @@ make_inline_results <- function(design_overall,
     pull(string)
 
   prevHighRisk <- list(
+    overall.bp_cat = ~ bp_cat,
     diabetes.overall = ~ diabetes,
     diabetes.bp_cat = ~ diabetes + bp_cat,
     ckd.overall = ~ ckd,
@@ -250,6 +251,20 @@ make_inline_results <- function(design_overall,
       inline = table_glue('{100*pcr_highrisk} (95% CI: {100*lwr}, {100*upr})')
     ) %>%
     arrange(bp_cat)
+
+  prevHighRiskOverall <- svyciprop(~ pcr_highrisk, design_overall) %>%
+    cbind(confint(.)) %>%
+    as_tibble() %>%
+    set_names(c('est', 'lwr', 'upr')) %>%
+    mutate(across(everything(), ~.x * 100)) %>%
+    mutate(inline = table_glue('{est} (95% CI: {lwr}, {upr})')) %>%
+    pull(inline)
+
+  prevHighRiskS1hOverall <- prevHighRisk %>%
+    filter(variable == 'overall.bp_cat',
+           bp_cat == 'Stage 1 hypertension') %>%
+    pull(inline)
+
 
   prevHighRiskDiabetes <- prevHighRisk %>%
     filter(variable == 'diabetes.overall') %>%
@@ -325,6 +340,16 @@ make_inline_results <- function(design_overall,
   propLowRiskAge65 <- svyciprop(
     formula = ~ ascvd_risk_pcr < 0.05,
     design = subset(design_low_risk, age_gt65 == 'yes')
+  ) %>%
+    tidy_svy(mult_by = 100) %>%
+    transmute(
+      string = table_glue("{est}% (95% CI: {lwr}%, {upr}%)")
+    ) %>%
+    pull(string)
+
+  propLowRiskS1hOverall <- svyciprop(
+    formula = ~ ascvd_risk_pcr < 0.05,
+    design = subset(design_low_risk, bp_cat == 'Stage 1 hypertension')
   ) %>%
     tidy_svy(mult_by = 100) %>%
     transmute(
@@ -456,10 +481,12 @@ make_inline_results <- function(design_overall,
     medianPcrS1hDiabetes = medianPcrS1hDiabetes,
     medianPcrS1hOverall  = medianPcrS1hOverall,
     medianPcrS1hAny      = medianPcrS1hAny,
[…]

### 2020-09-23 doc/ACCAHA_BP_groups.Rmd
cleaning manuscript for consistency

@@
 
-In November 2017, the `r ACC_AHA()` published a guideline for the prevention, detection, evaluation, and management of high `r BP()` in adults.[@whelton20182017] This guideline recommends using both predicted predicted risk for `r CVD()` and `r BP()` levels to guide the initiation of antihypertensive medication.
+In November 2017, the `r ACC_AHA()` published a guideline for the prevention, detection, evaluation, and management of high `r BP()` in adults.[@whelton20182017] This guideline recommends using both predicted risk for `r CVD()` and `r BP()` levels to guide the initiation of antihypertensive medication.
 All adults with `r SBP()` ≥ 140 mm Hg or `r DBP()` ≥ 90 mm Hg, stage 2 hypertension in the guideline, are recommended to initiate antihypertensive medication.
@@
 
-Analyses were conducted for the overall population and among participants with diabetes, CKD, ≥ 65 years of age, and for those with any of these three conditions.
+Analyses were conducted for the overall population and among participants with diabetes, CKD, ≥ 65 years of age, and for those with at least one of these three conditions.
 Participant characteristics were summarized as mean with their standard error and percentage for continuous and categorical variables, respectively.
-The percentage of US adults in each of the five `r BP()` categories was computed.
-The 25^th^, 50^th^, and 75^th^ percentile of 10-year predicted risk for `r ASCVD()` and the proportion of participants with high `r ASCVD()` risk were estimated overall and within each `r BP()` category outlined in the preceding paragraph.
+The percentage of US adults in each of the five `r BP()` categories (defined in the preceding paragraph) was computed.
+The 25^th^, 50^th^, and 75^th^ percentile of 10-year predicted risk for `r ASCVD()` and the proportion of participants with high `r ASCVD()` risk were estimated overall and within each `r BP()` category.
 To assess the extent to which participants with a 10-year predicted risk for `r ASCVD()` < 10% were close to the 10% threshold, the proportion of participants in this subgroup with 10-year predicted risk for `r ASCVD()` from < 2.5%, 2.5% to < 5.0%, 5.0% to < 7.5%, and 7.5% to < 10% was estimated.
@@
 P-values were two-sided.
-Data analysis was conducted using `r R_string_fancy` along with a collection of open-source software packages (e.g., drake, dflow, officedown, and others) to enhance the transparency and reproducibility of the current analysis.[@cite_R; @cite_drake; @cite_tidyverse; @cite_table.glue] The first author's GitHub repository (< _Link not yet active so we won't be scooped_ >) provides code to reproduce the current manuscript.
+Data analysis was conducted using `r R_string_fancy` along with a collection of open-source software packages.[@cite_R; @cite_drake; @cite_tidyverse; @cite_table.glue] The first author's GitHub repository (< _Link not yet active so we won't be scooped_ >) provides code to reproduce the current manuscript.
 
@@
 
-Among US adults aged 40 to 79 years in `r min(exams)`-`r max(exams)+1`, the estimated prevalence (95% `r CI(left_mark = '[', right_mark = ']')`) of diabetes and `r CKD()` was `r inline$prevDiabetesOverall` and `r inline$prevCkdOverall`, respectively, `r inline$prevAge65Overall` were estimated to be ≥ 65 years of age, and `r inline$prevAnyOverall` had at least one of these conditions (`r refer_to('tab_characteristics')`).
-An estimated `r inline$prevS1hOverall` of US adults who were 40 to 79 years of age had stage 1 hypertension (`r refer_to('tab_bpdist')`).
-Among those with diabetes, CKD, age ≥ 65 years, and any of these three conditions, the estimated prevalence (95% `r CI()` ) of stage 1 hypertension was `r inline$prevS1hDiabetes`, `r inline$prevS1hCkd`, `r inline$prevS1hAge65`, `r inline$prevS1hAny`, respectively.
-Characteristics of US adults 40 to 79 years of age with stage 1 hypertension, overall and for subgroups defined by diabetes, `r CKD()` and age ≥ 65 years, are presented in Table S1
+Among US adults aged 40 to 79 years in `r min(exams)`-`r max(exams)+1`, the estimated prevalence (95% `r CI(left_mark = '[', right_mark = ']')`) of diabetes and `r CKD()` was `r inline$prevDiabetesOverall` and `r inline$prevCkdOverall`, respectively, `r inline$prevAge65Overall` were estimated to have ≥ 65 years of age, and `r inline$prevAnyOverall` had at least one of these conditions (`r refer_to('tab_characteristics')`).
+An estimated `r inline$prevS1hOverall` of US adults 40 to 79 years of age had stage 1 hypertension (`r refer_to('tab_bpdist')`).
+Among those with diabetes, CKD, age ≥ 65 years, and any of these three conditions, the estimated prevalence (95% `r CI()`) of stage 1 hypertension was `r inline$prevS1hDiabetes`, `r inline$prevS1hCkd`, `r inline$prevS1hAge65`, `r inline$prevS1hAny`, respectively.
+Characteristics of US adults 40 to 79 years of age with stage 1 hypertension, overall and for subgroups defined by diabetes, `r CKD()` and age ≥ 65 years, are presented in Table S1.
 
@@
 
-Among US adults aged 40 to 79 years, the estimated proportion at high ASCVD risk was `r inline$prevHighRiskOverall` overall and `r inline$prevHighRiskDiabetes`, `r inline$prevHighRiskCkd`, `r inline$prevHighRiskAge65`, and `r inline$prevHighRiskAny` for those with diabetes, `r CKD()`, age ≥ 65 years, or any of these three conditions, respectively (`r refer_to('tab_risk_overall')`; bottom panel).
+Among US adults aged 40 to 79 years, the estimated percentage (95% `r CI()`) at high ASCVD risk was `r inline$prevHighRiskOverall` overall and `r inline$prevHighRiskDiabetes`, `r inline$prevHighRiskCkd`, `r inline$prevHighRiskAge65`, and `r inline$prevHighRiskAny` for those with diabetes, `r CKD()`, age ≥ 65 years, or any of these three conditions, respectively (`r refer_to('tab_risk_overall')`; bottom panel).
 Among those with stage 1 hypertension, an estimated `r inline$prevHighRiskS1hOverall` had high `r ASCVD()` risk overall and `r inline$prevHighRiskS1hDiabetes`, `r inline$prevHighRiskS1hCkd`, `r inline$prevHighRiskS1hAge65`, and `r inline$prevHighRiskS1hAny` of those with diabetes, `r CKD()`, age ≥ 65 years, or any of these three conditions had high `r ASCVD()` risk, respectively.
@@
 
-Among US adults who were not at high risk for `r ASCVD()`, an estimated `r inline$propLowRiskOverall` had 10-year predicted `r ASCVD()` risk < 5% (`r refer_to('fig_hist_ovrl')`).
+Among US adults aged 40 to 79 years who were not at high risk for `r ASCVD()`, an estimated `r inline$propLowRiskOverall` had 10-year predicted `r ASCVD()` risk < 5% (`r refer_to('fig_hist_ovrl')`).
 Among those not at high risk for `r ASCVD()` with diabetes, `r CKD()` age ≥ 65 years, and any of these three conditions, an estimated `r inline$propLowRiskDiabetes`, `r inline$propLowRiskCkd`, `r inline$propLowRiskAge65`, and `r inline$propLowRiskAny` had a 10-year predicted `r ASCVD()` risk < 5%, respectively.
@@
 
-The estimated probability of having high `r ASCVD()` risk increased with older age and exceeded 50% at `r inline$ageHighRiskOvrlNoComorb` years for US adults without diabetes or `r CKD()`, compared with `r inline$ageHighRiskOvrlDiabetes` and `r inline$ageHighRiskOvrlCkd` years for US adults with diabetes and CKD, respectively (`r refer_to('fig_risk_ovrl')`).
+The estimated probability of having high `r ASCVD()` risk increased with older age and exceeded 50% at `r inline$ageHighRiskOvrlNoComorb` years for US adults without diabetes or `r CKD()`, compared with `r inline$ageHighRiskOvrlDiabetes` years for US adults with diabetes and `r inline$ageHighRiskOvrlCkd` years for US adults with CKD (`r refer_to('fig_risk_ovrl')`).
 Among US adults with stage 1 hypertension, the age at which the estimated probability of having high `r ASCVD()` risk exceeded 50% was `r inline$ageHighRiskS1hNoComorb`, `r inline$ageHighRiskS1hDiabetes`, and `r inline$ageHighRiskS1hCkd` years for US adults without diabetes or CKD, with diabetes, and with CKD, respectively (`r refer_to('fig_risk_stg1')`).
@@
 
-In the current study, a majority of US adults with diabetes, `r CKD()` age ≥ 65 years, and any of these three conditions had a high risk for `r ASCVD()`, defined by a 10-year predicted `r ASCVD()` risk ≥ 10% or prevalent `r CVD()`.
-However, a substantial proportion of US adults with stage 1 hypertension and diabetes, CKD, age ≥ 65 years, and any of these three conditions did not have high `r ASCVD()` risk.
-It was estimated that approximately half of US adults aged 40 to 79 years with diabetes or `r CKD()` who were not at high `r ASCVD()` risk had a 10-year predicted `r ASCVD()` risk < 5%.
-In contrast, over 80% of adults aged ≥ 65 years not at high `ASCVD()` risk had 10-year predicted risk for `r ASCVD()` between 5% and 10%.
-The probability of having high `r ASCVD()` risk was age-dependent with over 50% of those with diabetes and `CKD()` aged ≥`r inline$ageHighRiskOvrlDiabetes`  and ≥`r inline$ageHighRiskOvrlCkd` years, respectively, expected to have high `r ASCVD()` risk.
+In the current study, a majority of US adults aged 40 to 79 years with diabetes, `r CKD()`, age ≥ 65 years, and any of these three conditions had a high risk for `r ASCVD()`, defined by a 10-year predicted `r ASCVD()` risk ≥ 10% or prevalent `r CVD()`.
+Among those with stage 1 hypertension and ≥ 65 years of age, a substantial proportion were at high `r ASCVD()` risk.
+However, a substantial proportion of US adults with stage 1 hypertension and diabetes or CKD did not have high `r ASCVD()` risk.
+Among US adults with diabetes or CKD who were not at high `r ASCVD()` risk, approximately half had a 10-year predicted `r ASCVD()` risk < 5%.
+In contrast, over 80% of US adults aged ≥ 65 years not at high `r ASCVD()` risk had 10-year predicted risk for `r ASCVD()` between 5% and 10%.
+The probability of having high `r ASCVD()` risk was age-dependent with over 50% of those with diabetes, `r CKD()`, and with neither of these conditions expected to have high `r ASCVD()` risk at ≥ `r inline$ageHighRiskOvrlDiabetes`, ≥ `r inline$ageHighRiskOvrlCkd`, and ≥ `r inline$ageHighRiskOvrlNoComorb` years of age, respectively.
 
@@
 Among those with diabetes, `r CKD()`, or age ≥ 65 years, only about 10% had stage 1 hypertension.
-The 2017 `r ACC_AHA()` `r BP()` guideline recommends all of these adults initiate antihypertensive medication, but the current study estimates that a substantial proportion of them do not have high `r ASCVD()` risk.
-Therefore, computing 10-year predicted `r ASCVD()` risk may be especially informative for adults with stage 1 hypertension and diabetes, `r CKD()`, or ≥ 65 years of age and may also help facilitate patient provider interactions where a `r BP()` treatment goal is discussed.
+The 2017 `r ACC_AHA()` `r BP()` guideline recommends all of these adults initiate antihypertensive medication and also recommends computing 10-year predicted `r ASCVD()` risk to establish the `r BP()` threshold for treatment.[@whelton20182017] The heterogeneous distribution of 10-year predicted `r ASCVD()` among those with stage 1 hypertension and diabetes, `r CKD()`, or age ≥ 65 years emphasizes the importance of these two recommendations from the guideline.
+Prior studies have shown the 2017 `r ACC_AHA()` `r BP()` guideline directs antihypertensive medication to those most likely to receive the largest risk reduction benefit,[@colantonio20182017; @jaeger2019cardiovascular] and computing 10-year predicted risk for `r ASCVD()` can both inform patients and facilitate patient provider discussions on a `r BP()` threshold for treatment.
 
@@
 
-Previous studies have shown that the use of predicted `r ASCVD()` risk in addition to `r BP()`, as recommended by the 2017 `r ACC_AHA()` `r BP()` guideline, can direct antihypertensive medication to adults likely to receive the largest risk reduction benefit with treatment.[@colantonio20182017; @jaeger2019cardiovascular] In an analysis of the Reasons for Geographic and Racial Differences in Stroke study, those with stage 1 hypertension recommended versus not recommended to initiate antihypertensive medication by the 2017 `r ACC_AHA()` `r BP()` guideline were roughly 6 times more likely to experience a `r CVD()` event over 8 years of follow-up.
-Although a substantial proportion of US adults with stage 1 hypertension and diabetes, `r CKD()`, or ≥ 65 years of age did not have a high `r ASCVD()` risk in the current study, they were more likely to have high `r ASCVD()` risk compared to the overall US population with stage 1 hypertension.
+Previous studies have shown that the use of predicted `r ASCVD()` risk in addition to `r BP()`, as recommended by the 2017 `r ACC_AHA()` `r BP()` guideline, can direct antihypertensive medication to adults likely to receive the largest risk reduction benefit with treatment.[@colantonio20182017] In an analysis of the Reasons for Geographic and Racial Differences in Stroke study, those with stage 1 hypertension recommended versus not recommended to initiate antihypertensive medication by the 2017 `r ACC_AHA()` `r BP()` guideline were roughly 6 times more likely to experience a `r CVD()` event over 8 years of follow-up.
+Although a substantial proportion of US adults with stage 1 hypertension and diabetes, `r CKD()`, or ≥ 65 years of age did not have a high `r ASCVD()` risk in the current study, they were more likely to have high `r ASCVD()` risk compared to the overall US population with stage 1 hypertension, and may therefore still benefit from initiating antihypertensive medication.
 
@@
 Previous randomized trials and meta-analyses have investigated whether lower `r BP()` treatment goals reduce incident `r CVD()` risk in patients with diabetes, `r CKD()`, or ≥ 65 years of age.
-the Systolic Blood Pressure Intervention Trial, which compared the `r SBP()` treatment target of < 120 mm Hg to < 140 mm Hg among older adults (mean age of 68 years) without diabetes, found lower rates of incident fatal and nonfatal major `r CVD()` events among those with the lower `r SBP()` target.
-A randomized trial of patients with diabetes and baseline `r SBP()` < 140 mm hg and `r DBP()` < 80 mm Hg found lower risk of stroke among participants with more intense `r BP()` treatment goals.[@schrier2002effects] A systematic review and meta-analysis of 123 studies with 613,815 participants found strong support for lowering `r SBP()` to less than 130 mm Hg and providing antihypertensive medication to adults with diabetes, CKD, and various other comorbidities.[@ettehad2016blood] This suggests adults with stage 1 hypertension and diabetes, `r CKD()` or ≥ 65 years of age may obtain greater risk reduction versus the overall population by initiating antihypertensive medication.
+the Systolic Blood Pressure Intervention Trial, which compared the `r SBP()` treatment target of < 120 mm Hg to < 140 mm Hg among older (mean age of 68 years) adults without diabetes, found lower rates of incident fatal and nonfatal major `r CVD()` events among those with the lower `r SBP()` target.[@sprint2015randomized] A randomized trial of patients with diabetes and baseline `r SBP()` < 140 mm hg and `r DBP()` < 80 mm Hg found lower risk of stroke among participants with more intense `r BP()` treatment goals.[@schrier2002effects] A systematic review and meta-analysis of 123 studies with 613,815 participants found strong support for lowering `r SBP()` to less than 130 mm Hg and providing antihypertensive medication to adults with diabetes, CKD, and various other comorbidities.[@ettehad2016blood] This suggests adults with stage 1 hypertension and diabetes, `r CKD()` or ≥ 65 years of age may obtain greater risk reduction versus the overall population by initiating antihypertensive medication.
 
@@
 It has been suggested that the vast majority of adults with diabetes, CKD, or ≥ 65 years of age have a 10-year predicted risk for `r ASCVD()` ≥ 10%.[@whelton20182017] Previous research has shown that diabetes, `r CKD()`, and advanced age are each associated with an increased risk for `r ASCVD()` events.[@coresh2004evidence; @chronic2010association; @grundy1999diabetes; @lakatta2002age].
-Although the current study suggests that a high proportion of US adults with stage 1 hypertension and diabetes or `r CKD()` do not have high 10-year predicted risk for `r ASCVD()`, others have previously shown that adults with diabetes and `r CKD()` have a high lifetime `r CVD()` risk.[@lloyd2006prediction; @hippisley2010derivation] Age-adjusted estimates from the current study echo these findings and suggests that adults with diabetes and `r CKD()` develop high `r ASCVD()` risk at a younger age than adults without these conditions.
-Prior studies have also found that cumulative exposure to high `r BP()` is associated with increased `r CVD()` risk.[@allen2014blood] Therefore, for younger adults with diabetes or `r CKD()`, antihypertensive medication may provide substantial reduction in `r ASCVD()` across their life course.
-predicted 10-year risk for `r ASCVD()` should be computed for all patients, as the `r ACC_AHA()` `r BP()` guideline suggests, and lifetime `r CVD()` risk should be taken into account for younger patients with diabetes or `r CKD()`.
+Although the current study suggests that a high proportion of US adults with stage 1 hypertension and diabetes or `r CKD()` do not have 10-year predicted risk for `r ASCVD()` ≥ 10%, others have previously shown that adults with diabetes or `r CKD()` have a high lifetime `r CVD()` risk.[@lloyd2006prediction; @hippisley2010derivation] Age-adjusted estimates for the probability of high `r ASCVD()` risk from the current study echo these findings and suggests that adults with diabetes or `r CKD()` develop high `r ASCVD()` risk at a younger age than adults without these conditions.
+Prior studies have also found that cumulative exposure to high `r BP()` is associated with increased `r CVD()` risk.[@allen2014blood] Therefore, for younger adults with diabetes or `r CKD()`, early initiation of antihypertensive medication may be an important step towards lowering lifetime `r CVD()` risk.
+Predicted 10-year risk for `r ASCVD()` should be computed for all adults with hypertension, as the 2017 `r ACC_AHA()` `r BP()` guideline recommends, and lifetime `r CVD()` risk should also be taken into account for younger adults with diabetes or `r CKD()`.
 Taken together, these risk assessment techniques can inform patients and help guide the decision to initiate antihypertensive medication.
@@
 `r NHANES()` participants completed only one visit and guidelines recommend using the mean `r BP()` averaged over 2 or more visits.
-Additionally, only one measurement of serum creatinine and urine albuminuria were available, which may have resulted in mis-classification of CKD status A total of `r table_value(sum(current_analysis$data$bp_cat == 'Stage 1 hypertension'))` participants had stage 1 hypertension, and some subgroups of this population based on diabetes, `r CKD()`, and ≥ 65 years of age were small.
+Additionally, since only one measurement of serum creatinine and urine albuminuria were available, `r CKD()` status may have been mis-classified in some adults.
+A total of `r table_value(sum(current_analysis$data$bp_cat == 'Stage 1 hypertension'))` participants had stage 1 hypertension, and some subgroups of this population based on diabetes, `r CKD()`, and ≥ 65 years of age were small.
 
@@
 In conclusion, a majority of US adults aged 40 to 79 years with diabetes, `r CKD()` or ≥ 65 years of age had 10-year predicted risk for `r ASCVD()` ≥ 10%.
-However, a lower percentage of with stage 1 hypertension and diabetes, `r CKD()` or age ≥ 65 years of age had 10-year predicted risk for `r ASCVD()` ≥ 10%.
-While most older US adults with diabetes or `r CKD()` have high risk, a substantial proportion of younger adults with diabetes or `r CKD()` have a 10-year predicted risk for `r ASCVD()` < 10%.
-While prevention of hypertension should be a primary goal, the early initiation of antihypertensive medication may be an important step towards lowering lifetime `r CVD()` risk.
+However, a lower percentage of those with stage 1 hypertension and diabetes, `r CKD()` or ≥ 65 years of age had 10-year predicted risk for `r ASCVD()` ≥ 10%.
+While most older US adults with diabetes or `r CKD()` had high `r ASCVD()` risk, a substantial proportion of younger adults with diabetes or `r CKD()` did not.
+Results from the current study support computing 10-year predicted `r ASCVD()` risk for all adults with hypertension, as recommended by the 2017 `r ACC_AHA()` `r BP()` guideline.
 

### 2020-09-23 R/make_inline_results.R

@@ -248,7 +248,8 @@ make_inline_results <- function(design_overall,
       variable,
       bp_cat = replace(bp_cat, is.na(bp_cat), "overall"),
       bp_cat = fct_inorder(bp_cat),
-      inline = table_glue('{100*pcr_highrisk} (95% CI: {100*lwr}, {100*upr})')
+      across(c(pcr_highrisk, lwr, upr), ~.x * 100),
+      inline = table_glue('{pcr_highrisk}% ({lwr}%, {upr}%)')
     ) %>%
     arrange(bp_cat)
 
@@ -257,7 +258,7 @@ make_inline_results <- function(design_overall,
     as_tibble() %>%
     set_names(c('est', 'lwr', 'upr')) %>%
     mutate(across(everything(), ~.x * 100)) %>%
-    mutate(inline = table_glue('{est} (95% CI: {lwr}, {upr})')) %>%
+    mutate(inline = table_glue('{est}% ({lwr}%, {upr}%)')) %>%
     pull(inline)
 
   prevHighRiskS1hOverall <- prevHighRisk %>%
@@ -347,6 +348,16 @@ make_inline_results <- function(design_overall,
     ) %>%
     pull(string)
 
+  propLowRiskAny <- svyciprop(
+    formula = ~ ascvd_risk_pcr < 0.05,
+    design = subset(design_low_risk, any_ckd_diab_age65 == 'yes')
+  ) %>%
+    tidy_svy(mult_by = 100) %>%
+    transmute(
+      string = table_glue("{est}% (95% CI: {lwr}%, {upr}%)")
+    ) %>%
+    pull(string)
+
   propLowRiskS1hOverall <- svyciprop(
     formula = ~ ascvd_risk_pcr < 0.05,
     design = subset(design_low_risk, bp_cat == 'Stage 1 hypertension')
@@ -382,6 +393,17 @@ make_inline_results <- function(design_overall,
   propLowRiskS1hAge65 <- svyciprop(
     formula = ~ ascvd_risk_pcr < 0.05,
     design = subset(design_low_risk, age_gt65 == 'yes' &
+                      bp_cat == 'Stage 1 hypertension')
+  ) %>%
+    tidy_svy(mult_by = 100) %>%
+    transmute(
+      string = table_glue("{est}% (95% CI: {lwr}%, {upr}%)")
+    ) %>%
+    pull(string)
+
+  propLowRiskS1hAny <- svyciprop(
[…]

### 2020-09-23 doc/ACCAHA_BP_groups.Rmd
abstract added

@@
 
+# ABSTRACT
+
+_Note: Maximum word count is 250_
+
+__Background:__ The 2017 American College of Cardiology / American Heart Association blood pressure (BP) guideline recommends predicting 10-year atherosclerotic cardiovascular disease (ASCVD) risk for adults with hypertension to establish a BP treatment threshold.
+It has been suggested that most adults with diabetes, chronic kidney disease (CKD), and age≥65 years have 10-year predicted ASCVD risk≥10%.
+
+__Objectives:__ In subgroups of US adults defined by diabetes, CKD, and age≥65 years, determine whether the majority have high ASCVD risk (i.e., 10-year predicted ASCVD risk≥10% or prevalent CVD), and estimate age-adjusted probability of high ASCVD risk.
+
+__Methods:__ Adults aged 40-79 years from the 2013-2018 National Health and Nutrition Examination Survey were included.
+Age-adjusted probability of high ASCVD risk was estimated using logistic regression.
+Analyses were conducted overall and among those with stage 1 hypertension.
+
+__Results:__ Among US adults overall (with stage 1 hypertension), an estimated 72.5% (55.0%), 64.5% (36.7%), 83.9% (72.6%), and 69.1% (54.4%) had high ASCVD risk in subgroups with diabetes, CKD, age≥65 years, and any of these conditions, respectively.
+Probability of high ASCVD risk exceeded 50% in subgroups with diabetes, CKD, and neither diabetes nor CKD at age 54, 59, and 65 years, respectively.
+
+__Conclusions:__ While the majority of US adults with diabetes, CKD, or age≥65 years had high ASCVD risk, a substantial proportion with stage 1 hypertension did not.
+Predicted 10-year ASCVD risk is heterogeneous among adults with stage 1 hypertension and diabetes or CKD, and should be computed for all adults with hypertension to establish appropriate BP treatment thresholds.
+
+\newpage
+# 
 In November 2017, the `r ACC_AHA()` published a guideline for the prevention, detection, evaluation, and management of high `r BP()` in adults.[@whelton20182017] This guideline recommends using both predicted risk for `r CVD()` and `r BP()` levels to guide the initiation of antihypertensive medication.

### 2020-09-24 doc/ACCAHA_BP_groups.Rmd
first draft sent to co-authors

--- 2020-09-23 doc/ACCAHA_BP_groups.Rmd
@@
 abbrev_key <- c(
+  CVD = 'cardiovascular disease',
+  ASCVD = 'atherosclerotic CVD',
   `ACC/AHA` = 'American College of Cardiology and the American Heart Association',
-  CI = 'confidence interval',
   BP = 'blood pressure',
-  NHANES = 'National Health and Nutrition Examination Survey',
   SBP = 'systolic BP',
@@
   CKD = 'chronic kidney disease',
-  CVD = 'cardiovascular disease',
-  ASCVD = 'atherosclerotic CVD',
+  NHANES = 'National Health and Nutrition Examination Survey',
+  CI = 'confidence interval',
   ACR = 'albumin-to-creatinine ratio',
@@
 
+<br>
+
+Total word count: __FILL THIS IN__
+
 Byron C. Jaeger^1^, Swati Sakhuja^2^, Shakia T. Hardy^2^, Philip Akinyelure^2^, Josh Bundy^3^, Paul Muntner^2^, and Paul K. Whelton^3^
@@
 
+__Funding:__ Information on grants, contracts, and other forms of financial support. _Please add your data if needed_
+
+__Disclosures:__ State each author's disclosures (or lack thereof). This must include the full disclosure of any relationship with industry. _Please add your statement below_
+
+BCJ has nothing to disclose.
+
+__Address for correspondence:__
+Byron C. Jaeger
+University of Alabama at Birmingham
+327M Ryals Public Health Building
+1665 University Blvd
+Birmingham, Alabama 35294-0022
+
+__Acknowledgments:__ to be drafted in next version.
+
 \newpage
+
+# ABSTRACT
+
+_Note: Maximum word count is 250_
+
+__Background:__ The 2017 American College of Cardiology/American Heart Association blood pressure (BP) guideline recommends predicting 10-year atherosclerotic cardiovascular disease (ASCVD) risk for adults with hypertension to establish a BP treatment threshold.
+However, it has been suggested that most adults with diabetes, chronic kidney disease (CKD), and age≥65 years have 10-year predicted ASCVD risk≥10%.
+
+__Objectives:__ In subgroups of US adults defined by diabetes, CKD, and age≥65 years, determine whether the majority have high ASCVD risk (i.e., 10-year predicted ASCVD risk≥10% or prevalent CVD), and estimate age-adjusted probability of high ASCVD risk.
+
+__Methods:__ Adults aged 40-79 years from the 2013-2018 National Health and Nutrition Examination Survey were included.
+Age-adjusted probability of high ASCVD risk was estimated using logistic regression.
+Analyses were conducted overall and among those with stage 1 hypertension.
+
+__Results:__ Among US adults overall (with stage 1 hypertension), an estimated 72.5% (55.0%), 64.5% (36.7%), 83.9% (72.6%), and 69.1% (54.4%) had high ASCVD risk in subgroups with diabetes, CKD, age≥65 years, and any of these conditions, respectively.
+Probability of high ASCVD risk exceeded 50% in subgroups with diabetes, CKD, and neither diabetes nor CKD at age 54 (55), 59 (65), and 65 (65) years, respectively.
+
+__Conclusions:__ While the majority of US adults with diabetes, CKD, or age≥65 years had high ASCVD risk, many with stage 1 hypertension did not.
+Predicted 10-year ASCVD risk is heterogeneous among adults with stage 1 hypertension and diabetes or CKD, and should be computed for all adults with hypertension to establish appropriate BP treatment thresholds.
+
+__Key words__: Atherosclerotic cardiovascular disease, blood pressure, diabetes, chronic kidney disease, risk prediction
+
+\newpage
+
+# ABBREVIATIONS
+
+```{r, results='asis'}
+
+abbrev_key %>% 
+  slice(1:max_abbrevs) %>%
+  select(-counter) %>% 
+  mutate(phrase = str_replace(phrase, 'BP', 'blood pressure'),
+         phrase = str_replace(phrase, 'CVD', 'cardiovascular disease')) %>% 
+  glue_data("{acronym} = {phrase}") %>% 
+  glue_collapse(sep = '\n\n\n')
+
+```
+
+\newpage
+
+# CONDENSED ABSTRACT
+
+_Note: No more than 100 words, stressing clinical implications_
+
+The 2017 American College of Cardiology/American Heart Association blood pressure (BP) guideline recommends predicting 10-year atherosclerotic cardiovascular disease (ASCVD) risk for adults with hypertension to establish BP treatment thresholds.
+However, it has been suggested that most adults with diabetes, chronic kidney disease, and age≥65 years have 10-year predicted ASCVD risk≥10%.
+Nationally representative data show many US adults with stage 1 hypertension and diabetes or chronic kidney disease do not have 10-year predicted ASCVD risk≥10% or prevalent CVD.
+Predicted 10-year ASCVD risk is heterogeneous among adults with stage 1 hypertension and should be computed to establish appropriate BP treatment thresholds.
+
+# Central Illustration:
+
+_To be determined_
+
+# Clinical Perspectives:
+
+_To be drafted in next version_
+
+\newpage
+
+# INTRODUCTION
 
@@
 The 2017 `r ACC_AHA()` guideline recommends computing 10-year predicted risk for `r ASCVD()` in all adults with hypertension to establish a `r BP()` threshold for treatment.[@whelton20182017] However, it has been suggested that the vast majority of adults with diabetes, CKD, or ≥ 65 years of age are likely to have a 10-year predicted risk for `r ASCVD()` ≥ 10%.
-The purpose of the current analysis was to estimate the proportion of US adults with diabetes, `r CKD()`, or ≥ 65 years of age that have high `r ASCVD()` risk (i.e., a 10-year predicted risk for `r ASCVD()` ≥ 10% or prevalent `r CVD()`).
-A secondary objective was to estimate the proportion of adults with stage 1 hypertension and diabetes, `r CKD()`, or age ≥ 65 years who have high `r ASCVD()` risk, as the 2017 `r ACC_AHA()` `r BP()` guideline recommends initiation of antihypertensive medication for these individuals.
+The purpose of the current analysis was to estimate the proportion of US adults with diabetes, `r CKD()`, or ≥ 65 years of age that have high `r ASCVD()` risk (i.e., a 10-year predicted risk for `r ASCVD()` ≥ 10% or prevalent `r CVD()`) and estimate the age-adjusted probability of high `r ASCVD()` risk in these groups.
+Analyses were replicated among adults with stage 1 hypertension since the 2017 `r ACC_AHA()` `r BP()` guideline recommends initiation of antihypertensive medication for adults with stage 1 hypertension and diabetes, `r CKD()`, or age ≥ 65 years, and initiation may involve determining a BP treatment threshold.
 To accomplish these goals, we analyzed data from `r english(length(exams))` cycles of the US `r NHANES()`.
@@
 Medical history included questions about whether the participant had been told by a doctor or other health professional that they have had a heart attack, coronary heart disease stroke, or heart failure.
+Prevalent `r CVD()` was defined as answering 'yes' to at least one of these questions.
+
+<br>
+
 Blood and urine samples were collected during the medical examination.
@@
 Diabetes was defined by fasting serum glucose ≥ `r gluc_cutpoint_fasted` mg/dL, non-fasting glucose ≥ `r gluc_cutpoint_fed` mg/dL, `r HB_A1C()` ≥ `r hba1c_cutpoint`%, or self-reported use of insulin or oral glucose lowering medication.
-`r capitalize(E_GFR())` was calculated using the Chronic Kidney Disease Epidemiology Collaboration equation.[@levey2009new] Urinary albumin and creatinine levels were measured and used to calculate the `r ACR()`.
+`r capitalize(E_GFR())` was calculated using the Chronic Kidney Disease Epidemiology Collaboration equation.[@levey2009new; @cite_nephro] Urinary albumin and creatinine levels were measured and used to calculate the `r ACR()`.
 `r CKD()` was defined by an `r E_GFR()` < `r egfr_cutpoint` ml/min/1.73m^2^ or an `r ACR()` ≥ `r acr_cutpoint` mg/dL.
@@
 P-values were two-sided.
-Data analysis was conducted using `r R_string_fancy` along with a collection of open-source software packages.[@cite_R; @cite_drake; @cite_tidyverse; @cite_table.glue] The first author's GitHub repository (< _Link not yet active so we won't be scooped_ >) provides code to reproduce the current manuscript.
+Data analysis was conducted using `r R_string_fancy` along with a collection of open-source software packages.[@cite_R; @cite_drake; @cite_tidyverse; @cite_table.glue] The first author's GitHub repository (< _Link not yet active so we won't be scooped_ >) provides code to reproduce the current study, allowing for different initial parameters.
 
@@
 Among US adults aged 40 to 79 years in `r min(exams)`-`r max(exams)+1`, the estimated prevalence (95% `r CI(left_mark = '[', right_mark = ']')`) of diabetes and `r CKD()` was `r inline$prevDiabetesOverall` and `r inline$prevCkdOverall`, respectively, `r inline$prevAge65Overall` were estimated to have ≥ 65 years of age, and `r inline$prevAnyOverall` had at least one of these conditions (`r refer_to('tab_characteristics')`).
-An estimated `r inline$prevS1hOverall` of US adults 40 to 79 years of age had stage 1 hypertension (`r refer_to('tab_bpdist')`).
-Among those with diabetes, CKD, age ≥ 65 years, and any of these three conditions, the estimated prevalence (95% `r CI()`) of stage 1 hypertension was `r inline$prevS1hDiabetes`, `r inline$prevS1hCkd`, `r inline$prevS1hAge65`, `r inline$prevS1hAny`, respectively.
+The estimated prevalence (95% `r CI()`) of stage 1 hypertension was `r inline$prevS1hOverall` overall and `r inline$prevS1hDiabetes`, `r inline$prevS1hCkd`, `r inline$prevS1hAge65`, and `r inline$prevS1hAny` among those with diabetes, CKD, age ≥ 65 years, and at least one of these conditions, respectively (`r refer_to('tab_bpdist')`).
 Characteristics of US adults 40 to 79 years of age with stage 1 hypertension, overall and for subgroups defined by diabetes, `r CKD()` and age ≥ 65 years, are presented in Table S1.
@@
 
-Among US adults aged 40 to 79 years without prevalent `r CVD()`, the estimated median (25^th^, 75^th^ percentiles) 10-year predicted risk for `r ASCVD()` was `r inline$medianPcrOverall` overall and `r inline$medianPcrDiabetes`, `r inline$medianPcrCkd`, `r inline$medianPcrAge65`, `r inline$medianPcrAny` among those with diabetes, CKD, age ≥ 65 years, and any of these three conditions, respectively (`r refer_to('tab_risk_overall')`; top panel).
-Among those with stage 1 hypertension, the estimated median (25^th^, 75^th^ percentiles) 10-year predicted risk for `r ASCVD()` was `r inline$medianPcrS1hOverall` overall and `r inline$medianPcrS1hDiabetes`, `r inline$medianPcrS1hCkd`, `r inline$medianPcrS1hAge65`, `r inline$medianPcrS1hAny` among those with diabetes, CKD, age ≥ 65 years, and any of these three conditions, respectively.
+Among US adults aged 40 to 79 years without prevalent `r CVD()`, the estimated median (25^th^, 75^th^ percentiles) 10-year predicted risk for `r ASCVD()` was `r inline$medianPcrOverall` overall and `r inline$medianPcrDiabetes`, `r inline$medianPcrCkd`, `r inline$medianPcrAge65`, `r inline$medianPcrAny` among those with diabetes, CKD, age ≥ 65 years, and any of these conditions, respectively (`r refer_to('tab_risk_overall')`; top panel).
+Among those with stage 1 hypertension, the estimated median (25^th^, 75^th^ percentiles) 10-year predicted risk for `r ASCVD()` was `r inline$medianPcrS1hOverall` overall and `r inline$medianPcrS1hDiabetes`, `r inline$medianPcrS1hCkd`, `r inline$medianPcrS1hAge65`, `r inline$medianPcrS1hAny` for those with diabetes, CKD, age ≥ 65 years, and any of these conditions, respectively.
 
@@
 
-Among US adults aged 40 to 79 years, the estimated percentage (95% `r CI()`) at high ASCVD risk was `r inline$prevHighRiskOverall` overall and `r inline$prevHighRiskDiabetes`, `r inline$prevHighRiskCkd`, `r inline$prevHighRiskAge65`, and `r inline$prevHighRiskAny` for those with diabetes, `r CKD()`, age ≥ 65 years, or any of these three conditions, respectively (`r refer_to('tab_risk_overall')`; bottom panel).
-Among those with stage 1 hypertension, an estimated `r inline$prevHighRiskS1hOverall` had high `r ASCVD()` risk overall and `r inline$prevHighRiskS1hDiabetes`, `r inline$prevHighRiskS1hCkd`, `r inline$prevHighRiskS1hAge65`, and `r inline$prevHighRiskS1hAny` of those with diabetes, `r CKD()`, age ≥ 65 years, or any of these three conditions had high `r ASCVD()` risk, respectively.
+Among US adults aged 40 to 79 years, the estimated percentage (95% `r CI()`) at high ASCVD risk was `r inline$prevHighRiskOverall` overall and `r inline$prevHighRiskDiabetes`, `r inline$prevHighRiskCkd`, `r inline$prevHighRiskAge65`, and `r inline$prevHighRiskAny` for those with diabetes, `r CKD()`, age ≥ 65 years, or any of these conditions, respectively (`r refer_to('tab_risk_overall')`; bottom panel).
+Among those with stage 1 hypertension, the estimated percentage (95% `r CI()`) at high `r ASCVD()` risk was `r inline$prevHighRiskS1hOverall` overall and `r inline$prevHighRiskS1hDiabetes`, `r inline$prevHighRiskS1hCkd`, `r inline$prevHighRiskS1hAge65`, and `r inline$prevHighRiskS1hAny` for those with diabetes, `r CKD()`, age ≥ 65 years, or any of these conditions, respectively.
 
@@
 Among US adults aged 40 to 79 years who were not at high risk for `r ASCVD()`, an estimated `r inline$propLowRiskOverall` had 10-year predicted `r ASCVD()` risk < 5% (`r refer_to('fig_hist_ovrl')`).
-Among those not at high risk for `r ASCVD()` with diabetes, `r CKD()` age ≥ 65 years, and any of these three conditions, an estimated `r inline$propLowRiskDiabetes`, `r inline$propLowRiskCkd`, `r inline$propLowRiskAge65`, and `r inline$propLowRiskAny` had a 10-year predicted `r ASCVD()` risk < 5%, respectively.
+Among those not at high risk for `r ASCVD()` with diabetes, `r CKD()`, age ≥ 65 years, and any of these conditions, an estimated `r inline$propLowRiskDiabetes`, `r inline$propLowRiskCkd`, `r inline$propLowRiskAge65`, and `r inline$propLowRiskAny` had a 10-year predicted `r ASCVD()` risk < 5%, respectively.
 Among those not at high risk for `r ASCVD()` and with stage 1 hypertension, an estimated `r inline$propLowRiskS1hOverall` overall and  `r inline$propLowRiskS1hDiabetes`, `r inline$propLowRiskS1hCkd`, and `r inline$propLowRiskS1hAge65` of those with diabetes, CKD, and ≥ 65 years of age had a 10-year predicted `r ASCVD()` risk < 5%, respectively (`r refer_to('fig_hist_stg1')`).
@@
 
-In the current study, a majority of US adults aged 40 to 79 years with diabetes, `r CKD()`, age ≥ 65 years, and any of these three conditions had a high risk for `r ASCVD()`, defined by a 10-year predicted `r ASCVD()` risk ≥ 10% or prevalent `r CVD()`.
+In the current study, a majority of US adults aged 40 to 79 years with diabetes, `r CKD()`, age ≥ 65 years, and any of these conditions had a high risk for `r ASCVD()`, defined by a 10-year predicted `r ASCVD()` risk ≥ 10% or prevalent `r CVD()`.
 Among those with stage 1 hypertension and ≥ 65 years of age, a substantial proportion were at high `r ASCVD()` risk.
@@
 
-The current study estimates that roughly 33% of US adults aged 40 to 79 years take antihypertensive medication, including half of those with diabetes, CKD, or ≥ 65 years of age.
-Among those with diabetes, `r CKD()`, or age ≥ 65 years, only about 10% had stage 1 hypertension.
-The 2017 `r ACC_AHA()` `r BP()` guideline recommends all of these adults initiate antihypertensive medication and also recommends computing 10-year predicted `r ASCVD()` risk to establish the `r BP()` threshold for treatment.[@whelton20182017] The heterogeneous distribution of 10-year predicted `r ASCVD()` among those with stage 1 hypertension and diabetes, `r CKD()`, or age ≥ 65 years emphasizes the importance of these two recommendations from the guideline.
-Prior studies have shown the 2017 `r ACC_AHA()` `r BP()` guideline directs antihypertensive medication to those most likely to receive the largest risk reduction benefit,[@colantonio20182017; @jaeger2019cardiovascular] and computing 10-year predicted risk for `r ASCVD()` can both inform patients and facilitate patient provider discussions on a `r BP()` threshold for treatment.
+The current study estimates that roughly one third of US adults aged 40 to 79 years take antihypertensive medication, including one half of those with diabetes, CKD, or ≥ 65 years of age.
+Among those with diabetes, `r CKD()`, or age ≥ 65 years, about 10% had stage 1 hypertension.
+The heterogeneous distribution of 10-year predicted `r ASCVD()` among those with stage 1 hypertension and diabetes, `r CKD()`, or age ≥ 65 years emphasizes the importance of the 2017 `r ACC_AHA()` `r BP()` guideline's recommendation to compute 10-year predicted `r ASCVD()` risk for all adults with hypertension.[@whelton20182017] Computing 10-year predicted `r ASCVD()` risk can inform patients recommended to initiate antihypertensive medication and later facilitate patient provider discussions on a `r BP()` threshold for treatment.
 
@@
 
-Previous studies have shown that the use of predicted `r ASCVD()` risk in addition to `r BP()`, as recommended by the 2017 `r ACC_AHA()` `r BP()` guideline, can direct antihypertensive medication to adults likely to receive the largest risk reduction benefit with treatment.[@colantonio20182017] In an analysis of the Reasons for Geographic and Racial Differences in Stroke study, those with stage 1 hypertension recommended versus not recommended to initiate antihypertensive medication by the 2017 `r ACC_AHA()` `r BP()` guideline were roughly 6 times more likely to experience a `r CVD()` event over 8 years of follow-up.
+Previous studies have shown that the use of predicted `r ASCVD()` risk in addition to `r BP()`, as recommended by the 2017 `r ACC_AHA()` `r BP()` guideline, can direct antihypertensive medication to adults likely to receive the largest risk reduction benefit with treatment.[@colantonio20182017; @jaeger2019cardiovascular] In an analysis of the Reasons for Geographic and Racial Differences in Stroke study, those with stage 1 hypertension recommended versus not recommended to initiate antihypertensive medication by the 2017 `r ACC_AHA()` `r BP()` guideline were roughly 6 times more likely to experience a `r CVD()` event over 8 years of follow-up.
 Although a substantial proportion of US adults with stage 1 hypertension and diabetes, `r CKD()`, or ≥ 65 years of age did not have a high `r ASCVD()` risk in the current study, they were more likely to have high `r ASCVD()` risk compared to the overall US population with stage 1 hypertension, and may therefore still benefit from initiating antihypertensive medication.
@@
 
-In conclusion, a majority of US adults aged 40 to 79 years with diabetes, `r CKD()` or ≥ 65 years of age had 10-year predicted risk for `r ASCVD()` ≥ 10%.
-However, a lower percentage of those with stage 1 hypertension and diabetes, `r CKD()` or ≥ 65 years of age had 10-year predicted risk for `r ASCVD()` ≥ 10%.
-While most older US adults with diabetes or `r CKD()` had high `r ASCVD()` risk, a substantial proportion of younger adults with diabetes or `r CKD()` did not.
+# CONCLUSIONS
+
+While the majority of US adults with diabetes, `r CKD()`, or age≥65 years had high `r ASCVD()` risk, many with stage 1 hypertension did not.
+Most older US adults with diabetes or `r CKD()` had high `r ASCVD()` risk, but a substantial proportion of younger adults with diabetes or `r CKD()` did not.
 Results from the current study support computing 10-year predicted `r ASCVD()` risk for all adults with hypertension, as recommended by the 2017 `r ACC_AHA()` `r BP()` guideline.

### 2020-09-24 R/make_inline_results.R

@@ -53,7 +53,7 @@ make_inline_results <- function(design_overall,
   ) %>%
     tidy_svy(mult_by = 100) %>%
     transmute(
-      string = table_glue("{est}% (95% CI: {lwr}%, {upr}%)")
+      string = table_glue("{est}% ({lwr}%, {upr}%)")
     ) %>%
     pull(string)
 

### 2020-10-19 doc/ACCAHA_BP_groups.Rmd
draft 2 complete

@@
 ---
-title: "Predicted cardiovascular risk and blood pressure for Americans with diabetes, chronic kidney disease, and \u226565 years of age"
+title: "Predicted cardiovascular risk for US adults with diabetes, chronic kidney disease, and \u2265 65 years of age"
 bibliography: refs.bib
@@
   officedown::rdocx_document:
-    reference_docx: style_manuscript.docx
+    reference_docx: style_manuscript_times_new_roman.docx
 ---
@@
 
-loadd(exams)
-loadd(current_analysis)
-loadd(inline)
-loadd(report)
-loadd(fasted_hrs_lower)
-loadd(fasted_hrs_upper)
-loadd(gluc_cutpoint_fasted)
-loadd(gluc_cutpoint_fed)
-loadd(hba1c_cutpoint)
-loadd(egfr_cutpoint)
-loadd(acr_cutpoint)
+loadd(exams,
+      current_analysis,
+      inline,
+      report,
+      fasted_hrs_lower,
+      fasted_hrs_upper,
+      gluc_cutpoint_fasted,
+      gluc_cutpoint_fed,
+      hba1c_cutpoint,
+      egfr_cutpoint,
+      acr_cutpoint,
+      fig_central_illustration)
 
@@
 
-Total word count: __FILL THIS IN__
+<!-- The word count includes text from introduction through the conclusion, references, and figure legends.  -->
 
-Byron C. Jaeger^1^, Swati Sakhuja^2^, Shakia T. Hardy^2^, Philip Akinyelure^2^, Josh Bundy^3^, Paul Muntner^2^, and Paul K. Whelton^3^
+<!-- 3,609 / 5000 max -->
+
+Total word count: ~3,700 / 5,000
+
+Byron C. Jaeger, PhD^1^, Swati Sakhuja, MS?^2^, Shakia T. Hardy, PhD^2^, Oluwasegun P. Akinyelure, MD, MPH^2^, Joshua D. Bundy, PhD, MPH^3^, Paul Muntner, PhD^2^, and Paul K. Whelton, MD, MSc^3^
 
@@
 
+Drs Muntner and Jaeger receive support through grant R01HL144773 from the National Heart, Lung, and Blood Institute and grant 15SFRN2390002 from the American Heart Association.
+
+Dr. Hardy receives support through R01HL139716 from the National Heart, Lung, and Blood Institute.
+
+Dr. Whelton was supported by a Centers for Research Excellence grant from the National Institute of General Medical Sciences (P20GM109036)
+
 __Disclosures:__ State each author's disclosures (or lack thereof). This must include the full disclosure of any relationship with industry. _Please add your statement below_
@@
 BCJ has nothing to disclose. 
+OPA has nothing to disclose. 
+JDB has nothing to disclose.
+STH has nothing to disclose.
+PKW has nothing to disclose.
 
@@
 
-__Acknowledgments:__ to be drafted in next version.
+__Acknowledgments:__ None.
 
@@
 
-__Background:__ The 2017 American College of Cardiology/American Heart Association blood pressure (BP) guideline recommends predicting 10-year atherosclerotic cardiovascular disease (ASCVD) risk for adults with hypertension to establish a BP treatment threshold.
-However, it has been suggested that most adults with diabetes, chronic kidney disease (CKD), and age≥65 years have 10-year predicted ASCVD risk≥10%.
+__Background:__ The 2017 American College of Cardiology/American Heart Association blood pressure (BP) guideline recommends using 10-year predicted atherosclerotic cardiovascular disease (ASCVD) risk to guide decisions to initiate antihypertensive medication.
 
-__Objectives:__ In subgroups of US adults defined by diabetes, CKD, and age≥65 years, determine whether the majority have high ASCVD risk (i.e., 10-year predicted ASCVD risk≥10% or prevalent CVD), and estimate age-adjusted probability of high ASCVD risk.
+__Objectives:__ Determine if the majority of US adults in subgroups defined by diabetes, chronic kidney disease (CKD), and age ≥65 years have high ASCVD risk (i.e., 10-year predicted ASCVD risk ≥10% or clinical CVD), and estimate the age-adjusted probability of high ASCVD risk.
 
-__Methods:__ Adults aged 40-79 years from the 2013-2018 National Health and Nutrition Examination Survey were included.
-Age-adjusted probability of high ASCVD risk was estimated using logistic regression.
-Analyses were conducted overall and among those with stage 1 hypertension.
+__Methods:__ Adults aged 40-79 years from the National Health and Nutrition Examination Survey `r min(exams)`-`r max(exams)+1` were included (n=`r table_value(nrow(current_analysis$data))`).
+We predicted 10-year ASCVD risk using the Pooled Cohort risk equations and clinical CVD was self-reported.
+Analyses were conducted overall and among those with stage 1 hypertension, defined by systolic BP of 130-139 mmHg or diastolic BP of 80-89 mm Hg.
 
-__Results:__ Among US adults overall (with stage 1 hypertension), an estimated 72.5% (55.0%), 64.5% (36.7%), 83.9% (72.6%), and 69.1% (54.4%) had high ASCVD risk in subgroups with diabetes, CKD, age≥65 years, and any of these conditions, respectively.
-Probability of high ASCVD risk exceeded 50% in subgroups with diabetes, CKD, and neither diabetes nor CKD at age 54 (55), 59 (65), and 65 (65) years, respectively.
+__Results:__ Among US adults, an estimated `r no_ci(inline$prevHighRiskDiabetes)`, `r no_ci(inline$prevHighRiskCkd)`, and `r no_ci(inline$prevHighRiskAge65)` of those with diabetes, CKD, and age ≥65 years had high ASCVD risk, respectively.
+Among US adults with stage 1 hypertension, an estimated `r no_ci(inline$prevHighRiskS1hDiabetes)`, `r no_ci(inline$prevHighRiskS1hCkd)`, and `r no_ci(inline$prevHighRiskS1hAge65)` of those with diabetes, CKD, and age ≥65 years had high ASCVD risk, respectively.
+The probability of having high ASCVD risk increased with age and exceeded 50% for US adults with diabetes and CKD at ages `r inline$ageHighRiskOvrlDiabetes` and `r inline$ageHighRiskOvrlCkd` years, respectively.
+For those with stage 1 hypertension, these ages were `r inline$ageHighRiskS1hDiabetes` and `r inline$ageHighRiskS1hCkd`, respectively.
 
-__Conclusions:__ While the majority of US adults with diabetes, CKD, or age≥65 years had high ASCVD risk, many with stage 1 hypertension did not.
-Predicted 10-year ASCVD risk is heterogeneous among adults with stage 1 hypertension and diabetes or CKD, and should be computed for all adults with hypertension to establish appropriate BP treatment thresholds.
+__Conclusions:__ Most US adults with diabetes, CKD, or age ≥65 years had high ASCVD risk. However, many with stage 1 hypertension did not.
 
@@
 
-The 2017 American College of Cardiology/American Heart Association blood pressure (BP) guideline recommends predicting 10-year atherosclerotic cardiovascular disease (ASCVD) risk for adults with hypertension to establish BP treatment thresholds.
-However, it has been suggested that most adults with diabetes, chronic kidney disease, and age≥65 years have 10-year predicted ASCVD risk≥10%.
-Nationally representative data show many US adults with stage 1 hypertension and diabetes or chronic kidney disease do not have 10-year predicted ASCVD risk≥10% or prevalent CVD.
-Predicted 10-year ASCVD risk is heterogeneous among adults with stage 1 hypertension and should be computed to establish appropriate BP treatment thresholds.
+The 2017 American College of Cardiology/American Heart Association blood pressure (BP) guideline recommends using atherosclerotic cardiovascular disease (ASCVD) risk to guide decisions to initiate antihypertensive medication.
+Using National Health and Nutrition Examination Survey `r min(exams)`-`r max(exams)+1` data, it was estimated that `r no_ci(inline$prevHighRiskS1hDiabetes)`, `r no_ci(inline$prevHighRiskS1hCkd)`, and `r no_ci(inline$prevHighRiskS1hAge65)` of US adults with stage 1 hypertension and diabetes, chronic kidney disease and age ≥65 years had high ASCVD risk defined by 10-year predicted ASCVD risk ≥10% or clinical CVD.
+Predicted 10-year ASCVD risk should be calculated for all adults with stage 1 hypertension and without clinical CVD as many are not at high risk for ASCVD.
 
-# Central Illustration:
+\newpage
 
-_To be determined_
+# Central Illustration
+
+Distribution of US adults by blood pressure and antihypertensive medication use categories.
+In text, the proportion of adults with stage 1 hypertension at high atherosclerotic cardiovascular disease risk in subgroups defined by diabetes, chronic kidney disease and age ≥ 65 years.
+`r fp_par(line_spacing = 1)`
+
+<br>
+
+```{r fig.width=7, fig.height = 4, dpi = 300}
+
+fig_central_illustration
+
+```
+
+High atherosclerotic cardiovascular disease risk was defined by a 10-year predicted risk for atherosclerotic cardiovascular disease ≥ 10% or clinical cardiovascular disease.
+`r fp_par(line_spacing = 1)`
+
+ASCVD = atherosclerotic cardiovascular disease; CKD = chronic kidney disease
+
+\newpage
 
@@
 
-_To be drafted in next version_
+__Competency in Medical Knowledge:__ The 2017 American College of Cardiology/American Heart Association blood pressure guideline recommends using both blood pressure and atherosclerotic cardiovascular disease (ASCVD) risk to guide decisions to initiate antihypertensive medication.
+
+__Competency in Patient Care:__ The guideline recommends computing 10-year predicted ASCVD risk for all adults with hypertension who do not have clinical CVD.
+
+__Translational Outlook:__ Predicted 10-year ASCVD risk should be computed for all adults with stage 1 hypertension and without clinical CVD as many are not at high risk for ASCVD.
 
@@
 
-In November 2017, the `r ACC_AHA()` published a guideline for the prevention, detection, evaluation, and management of high `r BP()` in adults.[@whelton20182017] This guideline recommends using both predicted risk for `r CVD()` and `r BP()` levels to guide the initiation of antihypertensive medication.
-All adults with `r SBP()` ≥ 140 mm Hg or `r DBP()` ≥ 90 mm Hg, stage 2 hypertension in the guideline, are recommended to initiate antihypertensive medication.
-Additionally, adults with `r SBP()` between 130 and 139 mm Hg and/or `r DBP()` between 80 and 89 mm Hg, stage 1 hypertension in the guideline, who have prevalent diabetes mellitus, prevalent `r CKD()`, age ≥ 65 years, or high `r ASCVD()` risk are recommended to initiate antihypertensive medication.
-High `r ASCVD()` risk is defined as prevalent `r CVD()` or a 10-year predicted risk for `r ASCVD()` ≥ 10%
+In November 2017, the `r ACC_AHA()` published a guideline for the prevention, detection, evaluation, and management of high `r BP()` in adults [@whelton20182017].
+This guideline recommends using both `r BP()` levels and predicted risk for `r CVD()` to guide the initiation of antihypertensive medication in addition to nonpharmacological therapy.
+All adults with an average `r SBP()` ≥ 140 mm Hg or `r DBP()` ≥ 90 mm Hg, stage 2 hypertension in the guideline, are recommended to initiate antihypertensive medication.
+Adults with `r SBP()` between 130 and 139 mm Hg and/or `r DBP()` between 80 and 89 mm Hg, stage 1 hypertension in the guideline, with high `r CVD()` risk are recommended to initiate antihypertensive medication.
+High `r CVD()` risk was defined by the presence of clinical `r CVD()` or a 10-year predicted risk for `r ASCVD()` ≥ 10% [@goff20142013].
+Additionally, adults with with stage 1 hypertension and diabetes mellitus, `r CKD()`, or ≥ 65 years of age are considered to have high CVD risk by the guideline and are recommended to initiate antihypertensive medication.
+This recommendation, written in Sections 9.3, 9.6, and 10.3 of the guideline, was based on the assumption that the vast majority of adults with diabetes, `r CKD()`, or ≥ 65 years of age are likely to have a 10-year predicted `r ASCVD()` risk ≥ 10% [@whelton20182017].
 
@@
 
-The 2017 `r ACC_AHA()` guideline recommends computing 10-year predicted risk for `r ASCVD()` in all adults with hypertension to establish a `r BP()` threshold for treatment.[@whelton20182017] However, it has been suggested that the vast majority of adults with diabetes, CKD, or ≥ 65 years of age are likely to have a 10-year predicted risk for `r ASCVD()` ≥ 10%.
-The purpose of the current analysis was to estimate the proportion of US adults with diabetes, `r CKD()`, or ≥ 65 years of age that have high `r ASCVD()` risk (i.e., a 10-year predicted risk for `r ASCVD()` ≥ 10% or prevalent `r CVD()`) and estimate the age-adjusted probability of high `r ASCVD()` risk in these groups.
-Analyses were replicated among adults with stage 1 hypertension since the 2017 `r ACC_AHA()` `r BP()` guideline recommends initiation of antihypertensive medication for adults with stage 1 hypertension and diabetes, `r CKD()`, or age ≥ 65 years, and initiation may involve determining a BP treatment threshold.
-To accomplish these goals, we analyzed data from `r english(length(exams))` cycles of the US `r NHANES()`.
+The goal of the current analysis was to estimate the proportion of US adults with diabetes, `r CKD()`, or ≥ 65 years of age that have high `r ASCVD()` risk (defined by 10-year predicted risk for `r ASCVD()` ≥ 10% or clinical `r CVD()`).
+This analysis was conducted for all US adults and among those with stage 1 hypertension.
+To accomplish this goal, we analyzed data from `r english(length(exams))` cycles of the US `r NHANES()`.
 
@@
 
-`r NHANES()` was designed to assess the health and nutritional status of the non-institutionalized US population and was conducted by the National Center for Health Statistics of the Centers for Disease Control and Prevention.[@nhanes_home] Since 1999-2000, `r NHANES()` has been conducted in two-year cycles using a multistage probability sampling design to select participants.
+`r NHANES()` was designed to assess the health and nutritional status of the non-institutionalized US population and was conducted by the National Center for Health Statistics of the Centers for Disease Control and Prevention [@nhanes_home].
+Since 1999-2000, `r NHANES()` has been conducted in two-year cycles using a multistage probability sampling design to select participants.
 Each cycle is independent with different participants recruited.
-For the current analysis, the `r english(length(exams))` cycles conducted in `r nhanes_years` were pooled for analysis.[@nhanes_tutorial_weights] The protocols for each `r NHANES()` cycle were approved by the National Center for Health Statistics of the Centers for Disease Control and Prevention Institutional Review Board.
+For the current analysis, the `r english(length(exams))` cycles conducted in `r nhanes_years` were combined [@nhanes_tutorial_weights].
 Written informed consent was obtained from each participant.
@@
 The current analysis was restricted to adults aged 40 to 79 years of age who completed the `r NHANES()` interview and examination (n = `r n_age_40_to_79`).
-Participants < 40 or > 79 years of age were not included because the Pooled Cohort risk equations are not recommended to be used in these age ranges.[@goff20142013] Participants who did not have three `r SBP()` and `r DBP()` measurements (n = `r n_bp_too_low`) and those who were missing information on age, race, sex, total and high-density lipoprotein cholesterol, smoking status, diabetes, or `r CKD()` status (n = `r n_missing_pcr`) were excluded.
-After these exclusions, over the `r english(length(exams))` `r NHANES()` cycles, a total of `r n_final` participants were included in the analysis (`r refer_to('fig_include_exclude')`).
+Participants < 40 or > 79 years of age were not included because use of the Pooled Cohort risk equations is not recommended to be used in these age ranges [@goff20142013].
+Participants who did not have three `r SBP()` and `r DBP()` measurements (n = `r n_bp_too_low`) and those who were missing information on age, race, sex, total and high-density lipoprotein cholesterol, smoking status, diabetes, or `r CKD()` status (n = `r n_missing_pcr`) were excluded.
+After these exclusions, a total of `r n_final` participants were included in the analysis (`r refer_to('fig_include_exclude')`).
 
@@
 Data were collected during an in-home interview and a study visit completed at a mobile examination center.
-Standardized questionnaires were used to assess participants’ age, sex, race/ethnicity, smoking habits, medical history and use of antihypertensive medication, oral glucose lowering medication and insulin.
-Medical history included questions about whether the participant had been told by a doctor or other health professional that they have had a heart attack, coronary heart disease stroke, or heart failure.
-Prevalent `r CVD()` was defined as answering 'yes' to at least one of these questions.
+Standardized questionnaires were used to assess participants’ age, sex, race/ethnicity, smoking habits, medical history, use of antihypertensive medication, oral glucose lowering medication, and insulin.
+The medical history assessment included questions about whether the participant had been told by a doctor or other health professional that they had a heart attack, coronary heart disease stroke, or heart failure.
+Clinical `r CVD()` was defined as answering yes to at least one of these questions.
 
@@
 Blood and urine samples were collected during the medical examination.
-Of relevance to the current analysis, serum creatinine, serum glucose and `r HB_A1C()` were measured.
-Diabetes was defined by fasting serum glucose ≥ `r gluc_cutpoint_fasted` mg/dL, non-fasting glucose ≥ `r gluc_cutpoint_fed` mg/dL, `r HB_A1C()` ≥ `r hba1c_cutpoint`%, or self-reported use of insulin or oral glucose lowering medication.
-`r capitalize(E_GFR())` was calculated using the Chronic Kidney Disease Epidemiology Collaboration equation.[@levey2009new; @cite_nephro] Urinary albumin and creatinine levels were measured and used to calculate the `r ACR()`.
-`r CKD()` was defined by an `r E_GFR()` < `r egfr_cutpoint` ml/min/1.73m^2^ or an `r ACR()` ≥ `r acr_cutpoint` mg/dL.
-Predicted 10-year risk for `r ASCVD()` was calculated using the Pooled Cohort risk equations for participants without prevalent `r CVD()`.[@goff20142013] High `r ASCVD()` risk was defined as prevalent `r CVD()` or a 10-year predicted `r ASCVD()` risk ≥ 10%.
+Serum creatinine, serum glucose and `r HB_A1C()` were measured using standard methods.
+Diabetes was defined by fasting plasma glucose ≥ `r gluc_cutpoint_fasted` mg/dL (≥ `r gluc_cutpoint_fed` mg/dL for those who were not fasting), `r HB_A1C()` ≥ `r hba1c_cutpoint`%, or self-reported use of insulin or oral glucose lowering medication.
+`r capitalize(E_GFR())` was calculated using the `r CKD()` Epidemiology Collaboration equation [@levey2009new; @cite_nephro].
+Urinary albumin and creatinine levels were measured and used to calculate the `r ACR()`.
+`r CKD()` was defined by an `r E_GFR()` < `r egfr_cutpoint` ml/min/1.73m^2^ or an `r ACR()` ≥ `r acr_cutpoint` mg/g.
+Ten-year predicted `r ASCVD()` risk was calculated using the Pooled Cohort risk equations for participants without clinical `r CVD()` [@goff20142013].
+High `r ASCVD()` risk was defined as clinical `r CVD()` or a 10-year predicted `r ASCVD()` risk ≥ 10%.
 
@@
 Three `r BP()` measurements were obtained at 30 second intervals.
-The mean of all available measurements was used to define `r SBP()` and `r DBP()`.
+The mean of all three measurements was used to define `r SBP()` and `r DBP()`.
 Quality control included re-certification of physicians every quarter with retraining if needed.
@@
 
-## Blood pressure categories
+## Blood pressure and antihypertensive medication use categories
 
@@
 
-Participants not taking antihypertensive medication were grouped into four non-overlapping categories based on the 2017 `r ACC_AHA()` `r BP()` guideline: Normal `r BP()` (`r SBP()` < 120 mm Hg and `r DBP()` < 80 mm Hg), elevated `r BP()` (`r SBP()` between 120 and 129 mm Hg and `r DBP()` < 80 mm Hg), stage 1 hypertension (`r SBP()` between 130 and 139 mm Hg and/or `r DBP()` between 80 and 89 mm Hg with `r SBP()` < 140 mm Hg and `r DBP()` < 90 mm Hg), stage 2 hypertension (`r SBP()` ≥ 140 mm Hg or `r DBP()` ≥ 90 mm Hg).
+Participants not taking antihypertensive medication were grouped into four non-overlapping categories based on the 2017 `r ACC_AHA()` `r BP()` guideline: normal `r BP()` (`r SBP()` < 120 mm Hg and `r DBP()` < 80 mm Hg), elevated `r BP()` (`r SBP()` between 120 and 129 mm Hg and `r DBP()` < 80 mm Hg), stage 1 hypertension (`r SBP()` between 130 and 139 mm Hg or `r DBP()` between 80 and 89 mm Hg with SBP < 140 mm Hg and DBP < 90 mm Hg), stage 2 hypertension (`r SBP()` ≥ 140 mm Hg or `r DBP()` ≥ 90 mm Hg).
 Participants taking antihypertensive medication were placed in a fifth category.
@@
 
-Analyses were conducted for the overall population and among participants with diabetes, CKD, ≥ 65 years of age, and for those with at least one of these three conditions.
-Participant characteristics were summarized as mean with their standard error and percentage for continuous and categorical variables, respectively.
-The percentage of US adults in each of the five `r BP()` categories (defined in the preceding paragraph) was computed.
-The 25^th^, 50^th^, and 75^th^ percentile of 10-year predicted risk for `r ASCVD()` and the proportion of participants with high `r ASCVD()` risk were estimated overall and within each `r BP()` category.
-To assess the extent to which participants with a 10-year predicted risk for `r ASCVD()` < 10% were close to the 10% threshold, the proportion of participants in this subgroup with 10-year predicted risk for `r ASCVD()` from < 2.5%, 2.5% to < 5.0%, 5.0% to < 7.5%, and 7.5% to < 10% was estimated.
+Analyses were conducted for the overall population and among participants with diabetes, CKD, ≥ 65 years of age, and for those with any of these three characteristics.
+Participant characteristics were summarized as mean with its standard error for continuous variables and percentage for categorical variables.
+The percentage of US adults in each of the five categories based on `r BP()` and antihypertensive medication use was computed.
+The 25^th^, 50^th^, and 75^th^ percentile of 10-year predicted `r ASCVD()` risk and the proportion of participants with high `r ASCVD()` risk were estimated for the overall population and within each of the five categories based on `r BP()` and antihypertensive medication use.
+To assess the extent to which participants with a 10-year predicted `r ASCVD()` risk < 10% were close to the 10% threshold, we estimated the distribution of 10-year predicted `r ASCVD()` risk.
 The probability of having high `r ASCVD()` risk was estimated for each year of age from 40 to 79 years using logistic regression.
-Analyses of participant characteristics, distribution of 10-year predicted risk for `r ASCVD()`, and probability of having high `r ASCVD()` risk were replicated among participants with stage 1 hypertension.
+Analyses of participant characteristics, the distribution of 10-year predicted `r ASCVD()` risk, and the probability of having high `r ASCVD()` risk were repeated among participants with stage 1 hypertension.
 
@@
 `r NHANES()` sampling weights, which were calculated as the inverse probability of being selected for the survey, were used in all calculations to obtain nationally representative estimates of the non-institutionalized US population.
-The survey design of `r NHANES()` was also taken into account in all calculations.
 P-values were two-sided.
-Data analysis was conducted using `r R_string_fancy` along with a collection of open-source software packages.[@cite_R; @cite_drake; @cite_tidyverse; @cite_table.glue] The first author's GitHub repository (< _Link not yet active so we won't be scooped_ >) provides code to reproduce the current study, allowing for different initial parameters.
+Data analysis was conducted using `r R_string_fancy` along with a collection of open-source software packages [@cite_R; @cite_drake; @cite_tidyverse; @cite_table.glue].
+The first author's GitHub repository (< _Link not yet active so we won't be scooped_ >) provides code to reproduce the current study.
 
@@
 
-Among US adults aged 40 to 79 years in `r min(exams)`-`r max(exams)+1`, the estimated prevalence (95% `r CI(left_mark = '[', right_mark = ']')`) of diabetes and `r CKD()` was `r inline$prevDiabetesOverall` and `r inline$prevCkdOverall`, respectively, `r inline$prevAge65Overall` were estimated to have ≥ 65 years of age, and `r inline$prevAnyOverall` had at least one of these conditions (`r refer_to('tab_characteristics')`).
+Among US adults aged 40 to 79 years in `r min(exams)`-`r max(exams)+1`, the estimated prevalence (95% `r CI(left_mark = '[', right_mark = ']')`) of diabetes and `r CKD()` was `r inline$prevDiabetesOverall` and `r inline$prevCkdOverall`, respectively, `r inline$prevAge65Overall` were estimated to be ≥ 65 years of age, and `r inline$prevAnyOverall` had diabetes, CKD, or ≥ 65 years of age (`r refer_to('tab_characteristics')`).
 The estimated prevalence (95% `r CI()`) of stage 1 hypertension was `r inline$prevS1hOverall` overall and `r inline$prevS1hDiabetes`, `r inline$prevS1hCkd`, `r inline$prevS1hAge65`, and `r inline$prevS1hAny` among those with diabetes, CKD, age ≥ 65 years, and at least one of these conditions, respectively (`r refer_to('tab_bpdist')`).
@@
 
-## Predicted 10-year risk for atherosclerotic cardiovascular disease
+## Predicted 10-year atherosclerotic cardiovascular disease risk
 
-Among US adults aged 40 to 79 years without prevalent `r CVD()`, the estimated median (25^th^, 75^th^ percentiles) 10-year predicted risk for `r ASCVD()` was `r inline$medianPcrOverall` overall and `r inline$medianPcrDiabetes`, `r inline$medianPcrCkd`, `r inline$medianPcrAge65`, `r inline$medianPcrAny` among those with diabetes, CKD, age ≥ 65 years, and any of these conditions, respectively (`r refer_to('tab_risk_overall')`; top panel).
-Among those with stage 1 hypertension, the estimated median (25^th^, 75^th^ percentiles) 10-year predicted risk for `r ASCVD()` was `r inline$medianPcrS1hOverall` overall and `r inline$medianPcrS1hDiabetes`, `r inline$medianPcrS1hCkd`, `r inline$medianPcrS1hAge65`, `r inline$medianPcrS1hAny` for those with diabetes, CKD, age ≥ 65 years, and any of these conditions, respectively.
+Among US adults aged 40 to 79 years without clinical `r CVD()`, the estimated median (25^th^, 75^th^ percentiles) 10-year predicted `r ASCVD()` risk was `r inline$medianPcrOverall` in the overall population and `r inline$medianPcrDiabetes`, `r inline$medianPcrCkd`, `r inline$medianPcrAge65`, and `r inline$medianPcrAny` among those with diabetes, `r CKD()`, age ≥ 65 years, and any of these conditions, respectively (`r refer_to('tab_risk_overall')`; top panel).
+Among those with stage 1 hypertension, the estimated median (25^th^, 75^th^ percentiles) 10-year predicted `r ASCVD()` risk was `r inline$medianPcrS1hOverall` in the overall population and `r inline$medianPcrS1hDiabetes`, `r inline$medianPcrS1hCkd`, `r inline$medianPcrS1hAge65`, and `r inline$medianPcrS1hAny` for those with diabetes, `r CKD()`, age ≥ 65 years, and any of these conditions, respectively.
 
@@
 
-Among US adults aged 40 to 79 years, the estimated percentage (95% `r CI()`) at high ASCVD risk was `r inline$prevHighRiskOverall` overall and `r inline$prevHighRiskDiabetes`, `r inline$prevHighRiskCkd`, `r inline$prevHighRiskAge65`, and `r inline$prevHighRiskAny` for those with diabetes, `r CKD()`, age ≥ 65 years, or any of these conditions, respectively (`r refer_to('tab_risk_overall')`; bottom panel).
-Among those with stage 1 hypertension, the estimated percentage (95% `r CI()`) at high `r ASCVD()` risk was `r inline$prevHighRiskS1hOverall` overall and `r inline$prevHighRiskS1hDiabetes`, `r inline$prevHighRiskS1hCkd`, `r inline$prevHighRiskS1hAge65`, and `r inline$prevHighRiskS1hAny` for those with diabetes, `r CKD()`, age ≥ 65 years, or any of these conditions, respectively.
+Among US adults aged 40 to 79 years, the estimated percentage (95% `r CI()`) with high `r ASCVD()` risk was `r inline$prevHighRiskOverall` (`r refer_to('tab_risk_overall')`; bottom panel).
+Among sub-groups with diabetes, `r CKD()`, age ≥ 65 years, or any of these conditions, `r inline$prevHighRiskDiabetes`, `r inline$prevHighRiskCkd`, `r inline$prevHighRiskAge65`, and `r inline$prevHighRiskAny` had high `r ASCVD()` risk, respectively .
+Among those with stage 1 hypertension, the estimated percentage (95% `r CI()`) with high `r ASCVD()` risk was `r inline$prevHighRiskS1hOverall` in the overall population and `r inline$prevHighRiskS1hDiabetes`, `r inline$prevHighRiskS1hCkd`, `r inline$prevHighRiskS1hAge65`, and `r inline$prevHighRiskS1hAny` for those with diabetes, `r CKD()`, age ≥ 65 years, or any of these conditions, respectively.
 
@@
 
-Among US adults aged 40 to 79 years who were not at high risk for `r ASCVD()`, an estimated `r inline$propLowRiskOverall` had 10-year predicted `r ASCVD()` risk < 5% (`r refer_to('fig_hist_ovrl')`).
-Among those not at high risk for `r ASCVD()` with diabetes, `r CKD()`, age ≥ 65 years, and any of these conditions, an estimated `r inline$propLowRiskDiabetes`, `r inline$propLowRiskCkd`, `r inline$propLowRiskAge65`, and `r inline$propLowRiskAny` had a 10-year predicted `r ASCVD()` risk < 5%, respectively.
-Among those not at high risk for `r ASCVD()` and with stage 1 hypertension, an estimated `r inline$propLowRiskS1hOverall` overall and  `r inline$propLowRiskS1hDiabetes`, `r inline$propLowRiskS1hCkd`, and `r inline$propLowRiskS1hAge65` of those with diabetes, CKD, and ≥ 65 years of age had a 10-year predicted `r ASCVD()` risk < 5%, respectively (`r refer_to('fig_hist_stg1')`).
+Among US adults aged 40 to 79 years without high `r ASCVD()` risk, an estimated `r inline$propLowRiskOverall` had 10-year predicted `r ASCVD()` risk < 2.5% (`r refer_to('fig_hist_ovrl')`).
+Among subgroups with diabetes, `r CKD()`, age ≥ 65 years, and any of these conditions, an estimated `r inline$propLowRiskDiabetes`, `r inline$propLowRiskCkd`, `r inline$propLowRiskAge65`, and `r inline$propLowRiskAny` had a 10-year predicted `r ASCVD()` risk < 2.5%, respectively.
+Among those with stage 1 hypertension, an estimated `r inline$propLowRiskS1hOverall` had a 10-year predicted `r ASCVD()` risk < 2.5% (`r refer_to('fig_hist_stg1')`).
+Also, `r inline$propLowRiskS1hDiabetes`, `r inline$propLowRiskS1hCkd`, and `r inline$propLowRiskS1hAge65` of those with diabetes, CKD, and ≥ 65 years of age had a 10-year predicted `r ASCVD()` risk < 2.5%, respectively.
 
@@
 
-## Age-specific analysis of high `r ASCVD()` risk
+## Age-specific probability of having high `r ASCVD()` risk
 
@@
 Among US adults with stage 1 hypertension, the age at which the estimated probability of having high `r ASCVD()` risk exceeded 50% was `r inline$ageHighRiskS1hNoComorb`, `r inline$ageHighRiskS1hDiabetes`, and `r inline$ageHighRiskS1hCkd` years for US adults without diabetes or CKD, with diabetes, and with CKD, respectively (`r refer_to('fig_risk_stg1')`).
-The minimum age where the probability of high `r ASCVD()` risk exceeded 50% was not determined for adults ≥ 65 years of age as the probability exceeded 50% at all ages above 65 years.
+The minimum age where the probability of high `r ASCVD()` risk exceeded 50% was not estimated for adults ≥ 65 years of age as the probability exceeded 50% at all ages above 65 years.
 
@@
 
-In the current study, a majority of US adults aged 40 to 79 years with diabetes, `r CKD()`, age ≥ 65 years, and any of these conditions had a high risk for `r ASCVD()`, defined by a 10-year predicted `r ASCVD()` risk ≥ 10% or prevalent `r CVD()`.
-Among those with stage 1 hypertension and ≥ 65 years of age, a substantial proportion were at high `r ASCVD()` risk.
-However, a substantial proportion of US adults with stage 1 hypertension and diabetes or CKD did not have high `r ASCVD()` risk.
-Among US adults with diabetes or CKD who were not at high `r ASCVD()` risk, approximately half had a 10-year predicted `r ASCVD()` risk < 5%.
-In contrast, over 80% of US adults aged ≥ 65 years not at high `r ASCVD()` risk had 10-year predicted risk for `r ASCVD()` between 5% and 10%.
-The probability of having high `r ASCVD()` risk was age-dependent with over 50% of those with diabetes, `r CKD()`, and with neither of these conditions expected to have high `r ASCVD()` risk at ≥ `r inline$ageHighRiskOvrlDiabetes`, ≥ `r inline$ageHighRiskOvrlCkd`, and ≥ `r inline$ageHighRiskOvrlNoComorb` years of age, respectively.
+In the current study, a majority of US adults aged 40 to 79 years with diabetes, `r CKD()`, age ≥ 65 years, and any of these conditions had high `r ASCVD()` risk, defined by a 10-year predicted `r ASCVD()` risk ≥ 10% or clinical CVD.
+Also, the majority of US adults with stage 1 hypertension who were ≥ 65 years of age had high `r ASCVD()` risk.
+However, a substantial proportion of US adults with stage 1 hypertension and diabetes or `r CKD()` did not have high `r ASCVD()` risk.
+Among US adults with `r CKD()` and without high `r ASCVD()` risk, approximately one-third had a 10-year predicted `r ASCVD()` risk < 2.5%.
+In contrast, over 80% of US adults aged ≥ 65 years without high `r ASCVD()` risk had a 10-year predicted `r ASCVD()` risk between 5% and 10%.
+The probability of having high `r ASCVD()` risk was age-dependent with over 50% of US adults with diabetes and `r CKD()` having high `r ASCVD()` risk at ages above `r inline$ageHighRiskOvrlDiabetes` and `r inline$ageHighRiskOvrlCkd` years, respectively.
 
@@
 
-The current study estimates that roughly one third of US adults aged 40 to 79 years take antihypertensive medication, including one half of those with diabetes, CKD, or ≥ 65 years of age.
-Among those with diabetes, `r CKD()`, or age ≥ 65 years, about 10% had stage 1 hypertension.
-The heterogeneous distribution of 10-year predicted `r ASCVD()` among those with stage 1 hypertension and diabetes, `r CKD()`, or age ≥ 65 years emphasizes the importance of the 2017 `r ACC_AHA()` `r BP()` guideline's recommendation to compute 10-year predicted `r ASCVD()` risk for all adults with hypertension.[@whelton20182017] Computing 10-year predicted `r ASCVD()` risk can inform patients recommended to initiate antihypertensive medication and later facilitate patient provider discussions on a `r BP()` threshold for treatment.
+The current study estimates that about 15% of US adults aged 40 to 79 years have stage 1 hypertension.
+The 2017 `r ACC_AHA()` `r BP()` guideline recommends computing 10-year predicted `r ASCVD()` risk for all adults with hypertension who do not have clinical `r CVD()` [@whelton20182017].
+As many adults with stage 1 hypertension and diabetes or `r CKD()` do not have 10-year predicted `r ASCVD()` risk ≥ 10%, computing 10-year predicted `r ASCVD()` risk for adults with stage 1 hypertension can inform recommendations to initiate antihypertensive medication and inform patient-provider discussions on the potential benefits of treatment.
 
@@
 
-Previous studies have shown that the use of predicted `r ASCVD()` risk in addition to `r BP()`, as recommended by the 2017 `r ACC_AHA()` `r BP()` guideline, can direct antihypertensive medication to adults likely to receive the largest risk reduction benefit with treatment.[@colantonio20182017; @jaeger2019cardiovascular] In an analysis of the Reasons for Geographic and Racial Differences in Stroke study, those with stage 1 hypertension recommended versus not recommended to initiate antihypertensive medication by the 2017 `r ACC_AHA()` `r BP()` guideline were roughly 6 times more likely to experience a `r CVD()` event over 8 years of follow-up.
-Although a substantial proportion of US adults with stage 1 hypertension and diabetes, `r CKD()`, or ≥ 65 years of age did not have a high `r ASCVD()` risk in the current study, they were more likely to have high `r ASCVD()` risk compared to the overall US population with stage 1 hypertension, and may therefore still benefit from initiating antihypertensive medication.
+Previous studies have shown that the use of predicted `r ASCVD()` risk in addition to `r BP()` can direct antihypertensive medication to adults likely to receive the largest risk reduction benefit [@colantonio20182017; @jaeger2019cardiovascular, @herrett2019eligibility].
+For example, in an analysis of the Reasons for Geographic and Racial Differences in Stroke study, those with stage 1 hypertension for whom initiation of antihypertensive medication was recommended versus not recommended by the 2017 `r ACC_AHA()` `r BP()` guideline were roughly 6 times more likely to experience a `r CVD()` event over 8 years of follow-up [@colantonio20182017].
+Although a substantial proportion of US adults with stage 1 hypertension and diabetes or `r CKD()` did not have a high `r ASCVD()` risk in the current study, these subgroups were more likely to have high `r ASCVD()` risk compared to the overall US population with stage 1 hypertension, and may therefore still benefit from initiating antihypertensive medication.
 
@@
 
-Previous randomized trials and meta-analyses have investigated whether lower `r BP()` treatment goals reduce incident `r CVD()` risk in patients with diabetes, `r CKD()`, or ≥ 65 years of age.
-the Systolic Blood Pressure Intervention Trial, which compared the `r SBP()` treatment target of < 120 mm Hg to < 140 mm Hg among older (mean age of 68 years) adults without diabetes, found lower rates of incident fatal and nonfatal major `r CVD()` events among those with the lower `r SBP()` target.[@sprint2015randomized] A randomized trial of patients with diabetes and baseline `r SBP()` < 140 mm hg and `r DBP()` < 80 mm Hg found lower risk of stroke among participants with more intense `r BP()` treatment goals.[@schrier2002effects] A systematic review and meta-analysis of 123 studies with 613,815 participants found strong support for lowering `r SBP()` to less than 130 mm Hg and providing antihypertensive medication to adults with diabetes, CKD, and various other comorbidities.[@ettehad2016blood] This suggests adults with stage 1 hypertension and diabetes, `r CKD()` or ≥ 65 years of age may obtain greater risk reduction versus the overall population by initiating antihypertensive medication.
+Previous randomized trials and meta-analyses have investigated whether lower `r BP()` goals reduce incident `r CVD()` risk in patients with diabetes, `r CKD()`, or older age.
+A randomized trial of patients with diabetes and baseline `r SBP()` < 140 mm hg and `r DBP()` < 80 mm Hg found lower risk of stroke among participants with more intense `r BP()` treatment goals [@schrier2002effects].
+The Systolic Blood Pressure Intervention Trial compared an `r SBP()` treatment target of < 120 mm Hg to < 140 mm Hg among older adults (mean age of 68 years) without diabetes.
+Among participants with `r CKD()`, randomization to the lower `r SBP()` target reduced rates of major `r CVD()` events and all-cause death without evidence of effect modifications by `r CKD()` or deleterious effect on `r E_GFR()` or end stage renal disease [@cheung2017effects].
+In the overall population, those randomized to the lower `r SBP()` target experienced lower rates of incident fatal and nonfatal major `r CVD()` events as well as all-cause mortality [@sprint2015randomized].
+A systematic review and meta-analysis of 123 studies with 613,815 participants found strong support for lowering `r SBP()` to < 130 mm Hg and providing antihypertensive medication to adults with diabetes, CKD, and various other comorbidities [@ettehad2016blood].
+Benefits associated with a `r SBP()` treatment goal of < 130 mm Hg have also been identified in several other meta-analyses [@bundy2017systolic; @reboussin2018systematic].
+Collectively, evidence from previous studies suggests that adults with hypertension and diabetes, `r CKD()` or ≥ 65 years of age may experience lower rates of `r CVD()` events by initiating antihypertensive medication with an `r SBP()` treatment goal of < 130 mm Hg versus < 140 mm Hg.
 
@@
 
-It has been suggested that the vast majority of adults with diabetes, CKD, or ≥ 65 years of age have a 10-year predicted risk for `r ASCVD()` ≥ 10%.[@whelton20182017] Previous research has shown that diabetes, `r CKD()`, and advanced age are each associated with an increased risk for `r ASCVD()` events.[@coresh2004evidence; @chronic2010association; @grundy1999diabetes; @lakatta2002age].
-Although the current study suggests that a high proportion of US adults with stage 1 hypertension and diabetes or `r CKD()` do not have 10-year predicted risk for `r ASCVD()` ≥ 10%, others have previously shown that adults with diabetes or `r CKD()` have a high lifetime `r CVD()` risk.[@lloyd2006prediction; @hippisley2010derivation] Age-adjusted estimates for the probability of high `r ASCVD()` risk from the current study echo these findings and suggests that adults with diabetes or `r CKD()` develop high `r ASCVD()` risk at a younger age than adults without these conditions.
-Prior studies have also found that cumulative exposure to high `r BP()` is associated with increased `r CVD()` risk.[@allen2014blood] Therefore, for younger adults with diabetes or `r CKD()`, early initiation of antihypertensive medication may be an important step towards lowering lifetime `r CVD()` risk.
-Predicted 10-year risk for `r ASCVD()` should be computed for all adults with hypertension, as the 2017 `r ACC_AHA()` `r BP()` guideline recommends, and lifetime `r CVD()` risk should also be taken into account for younger adults with diabetes or `r CKD()`.
-Taken together, these risk assessment techniques can inform patients and help guide the decision to initiate antihypertensive medication.
+It has been suggested that the vast majority of adults with diabetes, CKD, or ≥ 65 years of age have a 10-year predicted `r ASCVD()` risk ≥ 10% [@whelton20182017].
+Previous research has shown that diabetes, `r CKD()`, and older age are each associated with an increased risk for `r ASCVD()` events [@coresh2004evidence; @chronic2010association; @grundy1999diabetes; @lakatta2002age].
+Although the current study suggests that a high proportion of US adults with stage 1 hypertension and diabetes or `r CKD()` do not have a 10-year predicted `r ASCVD()` risk ≥ 10%, diabetes and `r CKD()` are associated with a high lifetime `r CVD()` risk [@lloyd2006prediction; @hippisley2010derivation].
+Age-specific estimates in the current study suggest that US adults with diabetes or `r CKD()` develop high `r ASCVD()` risk at a younger age than their counterparts without these conditions.
+Prior studies have also found that cumulative exposure to high `r BP()` is associated with increased `r CVD()` risk [@allen2014blood].
+Therefore, for younger adults with diabetes or `r CKD()`, early initiation of antihypertensive medication may be an important step towards lowering lifetime `r CVD()` risk.
+Estimating lifetime CVD risk may be useful when discussing the initiation of antihypertensive medication among young and middle-aged adults with diabetes or CKD.
 
@@
 `r NHANES()` participants completed only one visit and guidelines recommend using the mean `r BP()` averaged over 2 or more visits.
+In addition, the `r ACC_AHA()` `r BP()` guideline recommends confirmation of office hypertension by measurement of out-of-office `r BP()`s.
 Additionally, since only one measurement of serum creatinine and urine albuminuria were available, `r CKD()` status may have been mis-classified in some adults.
@@
 
-While the majority of US adults with diabetes, `r CKD()`, or age≥65 years had high `r ASCVD()` risk, many with stage 1 hypertension did not.
-Most older US adults with diabetes or `r CKD()` had high `r ASCVD()` risk, but a substantial proportion of younger adults with diabetes or `r CKD()` did not.
+While the majority of US adults with diabetes, `r CKD()`, or age ≥ 65 years had high `r ASCVD()` risk, many with stage 1 hypertension and diabetes or `r CKD()` did not.
 Results from the current study support computing 10-year predicted `r ASCVD()` risk for all adults with hypertension, as recommended by the 2017 `r ACC_AHA()` `r BP()` guideline.
@@
 `r rp$supplement.figure$legend[1]`
-BP = blood pressure; NHANES = National Health and Nutrition Examination Survey. 
+BP = blood pressure; CKD = chronic kidney disease; NHANES = National Health and Nutrition Examination Survey. 
 `r fp_par(line_spacing = 1)`

### 2020-10-19 R/clean_exam_bp.R

@@ -57,7 +57,6 @@ clean_exam_bp <- function(
   # Some participants have zero BP values. taking their mean results in
   # NaN (not a number). I set these NaN values to missing.
 
-
   data_cleaned_bp <- select(
     data_all,
     exam,

### 2020-10-19 R/compile_report.R

@@ -87,19 +87,19 @@ compile_report <- function(exams,
 
   ftr_ckd <- as_paragraph(glue('Chronic kidney disease is defined by an albumin-to-creatinine ratio \u2265 {acr_cutpoint} mg/dl or an estimated glomerular filtration rate < {egfr_cutpoint} ml/min/1.73m\u00b2'))
 
-  ftr_diab <- as_paragraph(glue('Diabetes was defined by fasting serum glucose \u2265 {gluc_cutpoint_fasted} mg/dL, non-fasting glucose \u2265 {gluc_cutpoint_fed} mg/dL, HbA1c \u2265 {hba1c_cutpoint}%, or self-reported use of insulin or oral glucose lowering medication.'))
+  ftr_diab <- as_paragraph(glue('Diabetes was defined by fasting serum glucose \u2265 {gluc_cutpoint_fasted} mg/dL, non-fasting glucose \u2265 {gluc_cutpoint_fed} mg/dL, glycated hemoglobin (HbA1c) \u2265 {hba1c_cutpoint}%, or self-reported use of insulin or oral glucose lowering medication.'))
 
   bp_cat_guide <- as_paragraph(paste(
     "Normal blood pressure: systolic blood pressure < 120 mm Hg and diastolic blood pressure < 80 mm Hg;",
     "Elevated blood pressure: systolic blood pressure from 120 to 129 mm Hg and diastolic blood pressure < 80 mm Hg;",
-    "Stage 1 hypertension: systolic blood pressure between 130 and 139 mm Hg and/or diastolic blood pressure between 80 and 89 mm Hg with systolic blood pressure < 140 mm Hg and diastolic blood pressure < 90 mm Hg;",
+    "Stage 1 hypertension: systolic blood pressure between 130 and 139 mm Hg or diastolic blood pressure between 80 and 89 mm Hg;",
     "Stage 2 hypertension: systolic blood pressure \u2265 140 mm Hg or diastolic blood pressure \u2265 90 mm Hg.",
     sep = '\n'
   ))
 
-  ftr_cvdHx <- as_paragraph('High atherosclerotic cardiovascular disease risk was defined by a 10-year predicted risk for atherosclerotic cardiovascular disease \u2265 10% or prevalent cardiovascular disease')
[…]

### 2020-10-19 R/estimate_risk.R

@@ -72,12 +72,12 @@ pcr_model_bnry <- function(.variable, .design, age_breaks){
 
   if(.variable == 'Overall'){
 
-    mdl_f <- pcr_gteq_10 ~ age
+    mdl_f <- pcr_highrisk ~ age
 
   } else {
 
     mdl_f <- as.formula(
-      glue("pcr_gteq_10 ~ age * {.variable}")
+      glue("pcr_highrisk ~ age * {.variable}")
     )
 
     data_grid[[.variable]] <- 'yes'

### 2020-10-19 R/make_inline_results.R

@@ -309,7 +309,7 @@ make_inline_results <- function(design_overall,
   design_low_risk <- subset(design_overall, pcr_highrisk == 'no')
 
   propLowRiskOverall <- svyciprop(
-    formula = ~ ascvd_risk_pcr < 0.05,
+    formula = ~ ascvd_risk_pcr < 0.025,
     design = design_low_risk
   ) %>%
     tidy_svy(mult_by = 100) %>%
@@ -319,7 +319,7 @@ make_inline_results <- function(design_overall,
     pull(string)
 
   propLowRiskDiabetes <- svyciprop(
-    formula = ~ ascvd_risk_pcr < 0.05,
+    formula = ~ ascvd_risk_pcr < 0.025,
     design = subset(design_low_risk, diabetes == 'yes')
   ) %>%
     tidy_svy(mult_by = 100) %>%
@@ -329,7 +329,7 @@ make_inline_results <- function(design_overall,
     pull(string)
 
   propLowRiskCkd <- svyciprop(
-    formula = ~ ascvd_risk_pcr < 0.05,
+    formula = ~ ascvd_risk_pcr < 0.025,
     design = subset(design_low_risk, ckd == 'yes')
   ) %>%
     tidy_svy(mult_by = 100) %>%
@@ -339,7 +339,7 @@ make_inline_results <- function(design_overall,
     pull(string)
 
   propLowRiskAge65 <- svyciprop(
-    formula = ~ ascvd_risk_pcr < 0.05,
+    formula = ~ ascvd_risk_pcr < 0.025,
     design = subset(design_low_risk, age_gt65 == 'yes')
   ) %>%
     tidy_svy(mult_by = 100) %>%
@@ -349,7 +349,7 @@ make_inline_results <- function(design_overall,
     pull(string)
 
   propLowRiskAny <- svyciprop(
-    formula = ~ ascvd_risk_pcr < 0.05,
+    formula = ~ ascvd_risk_pcr < 0.025,
     design = subset(design_low_risk, any_ckd_diab_age65 == 'yes')
   ) %>%
     tidy_svy(mult_by = 100) %>%
@@ -359,7 +359,7 @@ make_inline_results <- function(design_overall,
     pull(string)
 
   propLowRiskS1hOverall <- svyciprop(
-    formula = ~ ascvd_risk_pcr < 0.05,
+    formula = ~ ascvd_risk_pcr < 0.025,
     design = subset(design_low_risk, bp_cat == 'Stage 1 hypertension')
[…]

### 2020-10-19 R/no_ci.R

@@ -1,0 +1,12 @@
+##' .. content for \description{} (no empty lines) ..
+##'
+##' .. content for \details{} ..
+##'
+##' @title
+##' @param x
+##' @return
+##' @export
+
+no_ci <- function(x){
+  stringr::str_remove(x, pattern = ' \\(.+\\)')
+}

### 2020-10-19 R/plan.R

@@ -101,16 +101,17 @@ the_plan <- drake_plan(
     "Age, years" = "age",
     "Gender" = "sex",
     "Race / ethnicity" = "race_ethnicity",
+    "Current smoker" = "smk_current",
     "Total cholesterol, mg/dl" = "chol_total_mgdl",
     "HDL-cholesterol, mg/dl" = "chol_hdl_mgdl",
     "Systolic blood pressure, mm Hg" = "bp_sys_mmhg",
     "Diastolic blood pressure, mm Hg" = "bp_dia_mmhg",
     "Antihypertensive medication use" = "meds_bp",
     "Diabetes" = "diabetes",
-    "Chronic kidney disease" = "ckd",
+    "CKD" = "ckd",
     "Aged 65+ years" = "age_gt65",
-    "Current smoker" = "smk_current",
-    "Prevalent CVD" = "ever_had_ascvd"
+    "Diabetes, chronic kidney disease, or age 65+ years" = 'any_ckd_diab_age65',
+    "Clinical CVD" = "ever_had_ascvd"
   ),
 
   # Tables ----
@@ -135,7 +136,12 @@ the_plan <- drake_plan(
                 "No diabetes or chronic kidney disease" = "#8D4B08FF"),
 
   qts = seq(0.001, 0.999, by = 0.0001),
-  fig_hist = visualize_risk_hist(design_overall, qts),
+
+  fig_text = element_text(family = 'Times',
+                          size = 12,
+                          color = 'black'),
+
+  fig_hist = visualize_risk_hist(design_overall, qts, fig_text),
 
   age_breaks = seq(40, 79, by = .001),
 
@@ -143,13 +149,19 @@ the_plan <- drake_plan(
 
   fig_risk_ovrl_bnry = visualize_risk_bnry(risk_models,
                                            bp_level = 'ovrl',
-                                           color_key = color_key),
+                                           color_key = color_key,
+                                           fig_text = fig_text),
 
   fig_risk_stg1_bnry = visualize_risk_bnry(risk_models,
                                            bp_level = 'stg1',
-                                           color_key = color_key),
+                                           color_key = color_key,
+                                           fig_text = fig_text),
+
 
   inline = make_inline_results(design_overall, design_s1hyp, risk_models),
+
+  fig_central_illustration = visualize_central_illustration(tbl_bpdist,
+                                                            inline),
 
   report = compile_report(
     exams,

### 2020-10-19 R/visualize_central_illustration.R

@@ -1,0 +1,104 @@
+##' .. content for \description{} (no empty lines) ..
+##'
+##' .. content for \details{} ..
+##'
+##' @title
+##' @param inline
+##' @return
+##' @export
+visualize_central_illustration <- function(tbl_bpdist, inline) {
+
+  bar_layer_overall <- tbl_bpdist %>%
+    filter(variable == 'overall') %>%
+    rename(n_chr = n) %>%
+    mutate(
+      n_dbl = as.numeric(str_remove(n_chr, '%')),
+      bp_cat = factor(
+        bp_cat,
+        levels = c(
+          "Taking antihypertensive medication",
+          "Stage 2 hypertension",
+          "Stage 1 hypertension",
+          "Elevated blood pressure",
+          "Normal blood pressure"
+        ),
+        labels = c(
+          "Taking antihyper-\ntensive medication",
+          "Stage 2\nhypertension",
+          "Stage 1\nhypertension",
+          "Elevated\nblood pressure",
+          "Normal\nblood pressure"
+        )
+      )
+    ) %>%
+    arrange(bp_cat)
+
+  text <- data.frame(
+    n_dbl = c(22, 36, 52),
+    bp_cat = 'Stage 1\nhypertension',
+    n_chr = c("diabetes,",
+              "CKD,",
+              "age \u226565yrs:"),
+    prevHighRisk = c(
+      no_ci(inline$prevHighRiskS1hDiabetes),
+      no_ci(inline$prevHighRiskS1hCkd),
+      no_ci(inline$prevHighRiskS1hAge65)
+    )
+  ) %>%
+    unite(n_chr, prevHighRisk,
+          col = 'n_chr',
+          sep = '\n') %>%
+    mutate(n_chr = paste0(n_chr, c(',', ',', '.')))
+
+  text_spanner <- data.frame(
+    n_dbl = 37.5,
+    bp_cat = 'Stage 1\nhypertension',
+    n_chr = c("Percent at high ASCVD risk with")
+  )
+
+  bar_plot <- ggplot(bar_layer_overall) +
+    aes(x = bp_cat, y = n_dbl, fill = bp_cat, label = n_chr) +
+    geom_bar(stat = 'identity', show.legend = FALSE) +
+    theme_bw() +
+    theme(panel.grid = element_blank(),
+          panel.border = element_blank(),
+          axis.text.x = element_blank(),
+          axis.text.y = element_text(size = 12,
+                                     color = 'black',
+                                     family = "serif"),
+          plot.title = element_text(size = 20,
[…]

### 2020-10-19 R/visualize_risk_bnry.R

@@ -11,7 +11,8 @@
 ##'
 visualize_risk_bnry <- function(risk_models,
                                 bp_level,
-                                color_key) {
+                                color_key,
+                                fig_text) {
 
   .design <- risk_models %>%
     filter(bp_cat == bp_level) %>%
@@ -45,7 +46,7 @@ visualize_risk_bnry <- function(risk_models,
         .f = .variable,
         'Diabetes' = 'diabetes',
         'Chronic kidney disease' = 'ckd',
-        'No Diabetes or chronic kidney disease' = 'no_diabetes_or_ckd'
+        'No Diabetes or\nchronic kidney disease' = 'no_diabetes_or_ckd'
       )
     )
 
@@ -62,9 +63,17 @@ visualize_risk_bnry <- function(risk_models,
         .f = .variable,
         'Diabetes' = 'diabetes',
         'Chronic kidney disease' = 'ckd',
-        'No diabetes or chronic kidney disease' = 'no_diabetes_or_ckd'
+        'No diabetes or\nchronic kidney disease' = 'no_diabetes_or_ckd'
       )
     )
+
+  name_to_update <- which(
+    names(color_key) == 'No diabetes or chronic kidney disease'
+  )
+
+  names(color_key)[name_to_update] <-
+    'No diabetes or\nchronic kidney disease'
+
 
   age_quants %<>%
     rename(age2 = age) %>%
@@ -97,8 +106,8 @@ visualize_risk_bnry <- function(risk_models,
   )
 
   ggplot(ggdat) +
-    aes(x = age, y = est, col = .variable) +
-    geom_line() +
+    aes(x = age, y = est, col = .variable, linetype = .variable) +
+    geom_line(size = 1) +
     geom_hline(yintercept = 0.50, col = 'grey', linetype = 2) +
     geom_point(
       data = vertical_lines,
@@ -110,16 +119,17 @@ visualize_risk_bnry <- function(risk_models,
       nudge_x = nudge_x,
       nudge_y = nudge_y,
       show.legend = FALSE,
+      family = 'Times',
       mapping = aes(x = cpoint,
                     y = est,
                     label = paste0(round(cpoint, 0),'*'))
     ) +
-    geom_line(size = 0.9) +
     scale_color_manual(values = color_key[levels(ggdat$.variable)]) +
+    scale_linetype_manual("", values = c(1,2,3)) +
     theme_bw() +
     labs(
       x = 'Age, years',
[…]

### 2020-10-19 R/visualize_risk_hist.R

@@ -5,7 +5,7 @@
 ##' @title
 ##' @param design_overall
 ##' @param qts
-visualize_risk_hist <- function(design, qts, risk_10yr) {
+visualize_risk_hist <- function(design, qts, fig_text) {
 
   # do not include participants with CVD history
   design <- subset(design, ever_had_ascvd == 'no' & ascvd_risk_pcr <= 0.10)
@@ -61,12 +61,12 @@ visualize_risk_hist <- function(design, qts, risk_10yr) {
         aes(x = x, y = perc_val, label = perc_lab) +
         geom_bar(stat = 'identity', fill = 'grey80',
                  color = 'grey80', alpha = 0.50) +
-        geom_text(vjust = -1) +
+        geom_text(vjust = -1, family = 'Times') +
         theme_bw() +
         theme(panel.grid = element_blank(),
-              text = element_text(size = 10, colour = 'black'),
-              axis.text = element_text(size = 10, color = 'black'),
-              strip.text = element_text(size = 10)) +
+              text = fig_text,
+              axis.text = fig_text,
+              legend.text = fig_text) +
         scale_x_continuous(labels = percent) +
         scale_y_continuous(labels = percent,
                            limits = c(0,1),

### 2020-10-19 _drake.R

@@ -13,8 +13,15 @@ drake_config(
   lock_envir = FALSE,
   seed = 329730,
   prework = {
-    round_spec() %>%
-      round_using_decimal(digits = 1) %>%
-      default_rounder_set()
+
+    windowsFonts(Times = 'Times New Roman')
+
+    rspec <- round_spec() %>%
+      round_using_decimal(digits = 1)
+
+    names(rspec) <- paste('table.glue', names(rspec), sep = '.')
+
+    options(rspec)
+
   }
 )

### 2020-10-19 packages.R

@@ -22,6 +22,7 @@ pacman::p_load(
   # reporting
   officer,
   glue,
+  broman,
   flextable,
   devEMF,
   magick,
@@ -43,3 +44,4 @@ conflicted::conflict_prefer('summarise', 'dplyr')
 conflicted::conflict_prefer('summarize', 'dplyr')
 conflicted::conflict_prefer("gather",    "tidyr")
 conflicted::conflict_prefer("set_names", "purrr")
+conflicted::conflict_prefer("make",      "drake")

### 2020-10-29 README.Rmd
second draft feedback incorporated

---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)

loadd(exams,
      current_analysis,
      inline,
      fig_central_illustration)

```

# ACC AHA BP guideline groups

This repository contains all of the code necessary to reproduce the manuscript _Predicted cardiovascular risk for US adults with diabetes, chronic kidney disease, and ≥ 65 years of age_. The abstract and one central illustration for the paper are below.

# ABSTRACT

__Background:__ The 2017 American College of Cardiology/American Heart Association blood pressure (BP) guideline recommends using 10-year predicted atherosclerotic cardiovascular disease (ASCVD) risk to guide decisions to initiate antihypertensive medication.

__Objectives:__ Determine if the majority of US adults in subgroups defined by diabetes, chronic kidney disease (CKD), and age ≥65 years have high ASCVD risk (i.e., 10-year predicted ASCVD risk ≥10% or clinical CVD), and estimate the age-adjusted probability of having high ASCVD risk.

__Methods:__ Adults aged 40-79 years from the National Health and Nutrition Examination Survey `r min(exams)`-`r max(exams)+1` were included (n=`r table_value(nrow(current_analysis$data))`). We predicted 10-year ASCVD risk using the Pooled Cohort risk equations and clinical CVD was self-reported. Analyses were conducted overall and among those with stage 1 hypertension, defined by systolic BP of 130-139 mm Hg or diastolic BP of 80-89 mm Hg.

__Results:__ Among US adults, an estimated `r no_ci(inline$prevHighRiskDiabetes)`, `r no_ci(inline$prevHighRiskCkd)`, and `r no_ci(inline$prevHighRiskAge65)` of those with diabetes, CKD, and age ≥65 years had high ASCVD risk, respectively. Among US adults with stage 1 hypertension, an estimated `r no_ci(inline$prevHighRiskS1hDiabetes)`, `r no_ci(inline$prevHighRiskS1hCkd)`, and `r no_ci(inline$prevHighRiskS1hAge65)` of those with diabetes, CKD, and age ≥65 years had high ASCVD risk, respectively. The probability of having high ASCVD risk increased with age and exceeded 50% for US adults with diabetes and CKD at ages `r inline$ageHighRiskOvrlDiabetes` and `r inline$ageHighRiskOvrlCkd` years, respectively. For those with stage 1 hypertension, these ages were `r inline$ageHighRiskS1hDiabetes` and `r inline$ageHighRiskS1hCkd`, respectively.

__Conclusions:__ Most US adults with diabetes, CKD, or age ≥65 years had high ASCVD risk. However, many with stage 1 hypertension did not.

## Central Illustration

Distribution of US adults by blood pressure and antihypertensive medication use categories. In text, the proportion of adults with stage 1 hypertension at high atherosclerotic cardiovascular disease risk in subgroups defined by diabetes, chronic kidney disease and age ≥ 65 years.

```{r, echo = FALSE}
fig_central_illustration
```

High atherosclerotic cardiovascular disease risk was defined by a 10-year predicted risk for atherosclerotic cardiovascular disease ≥ 10% or clinical cardiovascular disease. Data are from the National Health and Nutrition Examination Survey, `r min(exams)`-`r max(exams)+1`.
`r fp_par(line_spacing = 1)`

# INSTRUCTIONS FOR REPRODUCTION

To reproduce this manuscript, you should first obtain all of the code in this repository. To do this, fork or download its contents. Once the repository is locally available and its contents unzipped, find and open the `ACC AHA BP guideline groups.Rproj` file. This should trigger Rstudio to open the project for you in a local R session.

To reproduce the manuscript as-is, follow the steps below:

1. Open `packages.R` and run all of the code in the file.

    + The `pacman` package must be installed on your machine to run this code

    + Two packages need to be installed from GitHub: `table.glue` and `PooledCohort`. If you asked whether you want to update dependencies - say 'no'. If `pacman` is not able to do this for you, you can use `remotes::install_github('bcjaeger/table.glue)` and `remotes::install_github('bcjaeger/PooledCohort)` to get these packages manually.

    + It may take more than one try to successfully download and/or update the packages and their dependencies. If any installations fail, try restarting your R session and using `install.packages()` to install any packages that are causing issues for `pacman`.

2. This project is built around `drake`, a workflow package. To produce every target in the drake workflow, run `r_make()` in your console.

3. Allow Rstudio to access the internet if prompted, as `r_make()` will be downloading NHANES data from the NHANES website while it produces the manuscript.

4. `r_make()` will build every target, ending with the manuscript and finally the `README.md` file. Simply open the file 'doc/ACCAHA_BP_groups.docx' to see the manuscript you built.

_Note:_ If an error occurs while the project is being made and you have successfully downloaded all of the packages in `packages.R`, please file an issue in this repository.

## Make a different manuscript

_Note:_ Not everything in the paper will update when you change parameters. For example, the exclusion figure was made using InkScape and the paper's central illustration was made using PowerPoint, so they won't update if you change parameters in the `plan.R` file. However, the remaining figures and text are.

These instructions assume you have successfully completed the steps above. If you would like to change some initial parameters for the manuscript, you can do so by following these instructions:

1. Open `R/plan.R`.

2. Notice that `exams = c(2013, 2015, 2017)` is the first argument in `drake_plan()`. Change this to `exams = c(2011, 2013, 2015, 2017)` to include a fourth NHANES exam.

3. Save your changes to the `R/plan.R` file and then run `r_make()` in your console.

4. Enjoy reading your fascinating new paper!

There are a few other parameters that can be changed in `R/plan.R`:

- `fasted_hrs_lower = 8`,
- `fasted_hrs_upper = 24`,
- `gluc_cutpoint_fasted = 126`,
- `gluc_cutpoint_fed = 200`,
- `hba1c_cutpoint = 6.5`,
- `egfr_cutpoint = 60`,
- `acr_cutpoint = 30`

These values define variables, manuscript variable definitions, and table footnotes.

### 2020-10-29 doc/ACCAHA_BP_groups.Rmd
second draft feedback incorporated

@@
 
-Byron C. Jaeger, PhD^1^, Swati Sakhuja, MS?^2^, Shakia T. Hardy, PhD^2^, Oluwasegun P. Akinyelure, MD, MPH^2^, Joshua D. Bundy, PhD, MPH^3^, Paul Muntner, PhD^2^, and Paul K. Whelton, MD, MSc^3^
+Byron C. Jaeger, PhD^1^, Swati Sakhuja, MPH^2^, Shakia T. Hardy, PhD, MPH^2^, Oluwasegun P. Akinyelure, MD, MPH^2^, Joshua D. Bundy, PhD, MPH^3^, Paul Muntner, PhD^2^, and Paul K. Whelton, MD, MSc^3^
 
@@
 
-__Funding:__ Information on grants, contracts, and other forms of financial support. _Please add your data if needed_
+__Funding:__
 
@@
 
-Dr. Whelton was supported by a Centers for Research Excellence grant from the National Institute of General Medical Sciences (P20GM109036)
+Dr. Bundy receives support through K12HD043451 from the Eunice Kennedy Shriver National Institute of Child Health and Human Development.
 
-__Disclosures:__ State each author's disclosures (or lack thereof). This must include the full disclosure of any relationship with industry. _Please add your statement below_
+Dr. Whelton receives support through P20GM109036 from the Centers for Research Excellence grant from the National Institute of General Medical Sciences.
+
+__Disclosures:__
 
 BCJ has nothing to disclose. 
+SS has nothing to disclose.
+STH has nothing to disclose.
 OPA has nothing to disclose. 
 JDB has nothing to disclose.
-STH has nothing to disclose.
+PM received grant funding and consulting fees from Amgen Inc., unrelated to the current manuscript.
 PKW has nothing to disclose.
@@
 __Address for correspondence:__
+
 Byron C. Jaeger
@@
 
-_Note: Maximum word count is 250_
-
 __Background:__ The 2017 American College of Cardiology/American Heart Association blood pressure (BP) guideline recommends using 10-year predicted atherosclerotic cardiovascular disease (ASCVD) risk to guide decisions to initiate antihypertensive medication.
 
-__Objectives:__ Determine if the majority of US adults in subgroups defined by diabetes, chronic kidney disease (CKD), and age ≥65 years have high ASCVD risk (i.e., 10-year predicted ASCVD risk ≥10% or clinical CVD), and estimate the age-adjusted probability of high ASCVD risk.
+__Objectives:__ Determine if the majority of US adults in subgroups defined by diabetes, chronic kidney disease (CKD), and age ≥65 years have high ASCVD risk (i.e., 10-year predicted ASCVD risk ≥10% or clinical CVD), and estimate the age-adjusted probability of having high ASCVD risk.
 
@@
 We predicted 10-year ASCVD risk using the Pooled Cohort risk equations and clinical CVD was self-reported.
-Analyses were conducted overall and among those with stage 1 hypertension, defined by systolic BP of 130-139 mmHg or diastolic BP of 80-89 mm Hg.
+Analyses were conducted overall and among those with stage 1 hypertension, defined by systolic BP of 130-139 mm Hg or diastolic BP of 80-89 mm Hg.
 
@@
 
-_Note: No more than 100 words, stressing clinical implications_
-
 The 2017 American College of Cardiology/American Heart Association blood pressure (BP) guideline recommends using atherosclerotic cardiovascular disease (ASCVD) risk to guide decisions to initiate antihypertensive medication.
@@
 Distribution of US adults by blood pressure and antihypertensive medication use categories.
-In text, the proportion of adults with stage 1 hypertension at high atherosclerotic cardiovascular disease risk in subgroups defined by diabetes, chronic kidney disease and age ≥ 65 years.
+In pie charts, the proportion of adults with stage 1 hypertension at high atherosclerotic cardiovascular disease risk in subgroups defined by diabetes, chronic kidney disease and age ≥ 65 years.
 `r fp_par(line_spacing = 1)`
@@
 
-```{r fig.width=7, fig.height = 4, dpi = 300}
+```{r out.width='100%'}
 
-fig_central_illustration
+knitr::include_graphics("../fig/central_illustration.png")
 
@@
 High atherosclerotic cardiovascular disease risk was defined by a 10-year predicted risk for atherosclerotic cardiovascular disease ≥ 10% or clinical cardiovascular disease.
+Data are from the National Health and Nutrition Examination Survey, `r min(exams)`-`r max(exams)+1`.
 `r fp_par(line_spacing = 1)`
@@
 
-__Translational Outlook:__ Predicted 10-year ASCVD risk should be computed for all adults with stage 1 hypertension and without clinical CVD as many are not at high risk for ASCVD.
+__Translational Outlook:__ Predicted 10-year ASCVD risk should be computed for all adults with stage 1 hypertension and without clinical CVD, as many are not at high risk for ASCVD.
 
@@
 This guideline recommends using both `r BP()` levels and predicted risk for `r CVD()` to guide the initiation of antihypertensive medication in addition to nonpharmacological therapy.
-All adults with an average `r SBP()` ≥ 140 mm Hg or `r DBP()` ≥ 90 mm Hg, stage 2 hypertension in the guideline, are recommended to initiate antihypertensive medication.
-Adults with `r SBP()` between 130 and 139 mm Hg and/or `r DBP()` between 80 and 89 mm Hg, stage 1 hypertension in the guideline, with high `r CVD()` risk are recommended to initiate antihypertensive medication.
-High `r CVD()` risk was defined by the presence of clinical `r CVD()` or a 10-year predicted risk for `r ASCVD()` ≥ 10% [@goff20142013].
-Additionally, adults with with stage 1 hypertension and diabetes mellitus, `r CKD()`, or ≥ 65 years of age are considered to have high CVD risk by the guideline and are recommended to initiate antihypertensive medication.
-This recommendation, written in Sections 9.3, 9.6, and 10.3 of the guideline, was based on the assumption that the vast majority of adults with diabetes, `r CKD()`, or ≥ 65 years of age are likely to have a 10-year predicted `r ASCVD()` risk ≥ 10% [@whelton20182017].
+Initiation of antihypertensive medication is recommended for all adults with a confirmed average `r SBP()` ≥ 140 mm Hg or `r DBP()` ≥ 90 mm Hg, stage 2 hypertension in the guideline.
+Initiation of antihypertensive medication is also recommended for adults with clinical `r CVD()` or a 10-year risk of `r ASCVD()` events ≥ 10% who have a confirmed average `r SBP()` between 130 and 139 mm Hg and/or `r DBP()` between 80 and 89 mm Hg, stage 1 hypertension in the guideline [@goff20142013].
+Additionally, as a matter of practical convenience, adults with stage 1 hypertension and diabetes mellitus, `r CKD()`, or ≥ 65 years of age are considered to have high `r CVD()` risk by the guideline and initiation of antihypertensive medication is recommended.
+This recommendation, written in Sections 9.3, 9.6, and 10.3 of the guideline, was based on the assumption that the vast majority of adults with diabetes, `r CKD()`, or ≥ 65 years of age are likely to have a 10-year predicted `r ASCVD()` risk ≥ 10% and the knowledge that surveys suggest most clinicians, including cardiologists, do not assess `r CVD()` risk using recommended risk prediction tools [@whelton20182017; @shillinglaw2012use].
 
@@
 The current analysis was restricted to adults aged 40 to 79 years of age who completed the `r NHANES()` interview and examination (n = `r n_age_40_to_79`).
-Participants < 40 or > 79 years of age were not included because use of the Pooled Cohort risk equations is not recommended to be used in these age ranges [@goff20142013].
+Participants < 40 or > 79 years of age were not included because use of the Pooled Cohort risk equations is not recommended in these age ranges [@goff20142013].
 Participants who did not have three `r SBP()` and `r DBP()` measurements (n = `r n_bp_too_low`) and those who were missing information on age, race, sex, total and high-density lipoprotein cholesterol, smoking status, diabetes, or `r CKD()` status (n = `r n_missing_pcr`) were excluded.
@@
 Standardized questionnaires were used to assess participants’ age, sex, race/ethnicity, smoking habits, medical history, use of antihypertensive medication, oral glucose lowering medication, and insulin.
-The medical history assessment included questions about whether the participant had been told by a doctor or other health professional that they had a heart attack, coronary heart disease stroke, or heart failure.
+The medical history assessment included questions about whether the participant had been told by a doctor or other health professional that they had a heart attack, coronary heart disease, stroke, or heart failure.
 Clinical `r CVD()` was defined as answering yes to at least one of these questions.
@@
 `r CKD()` was defined by an `r E_GFR()` < `r egfr_cutpoint` ml/min/1.73m^2^ or an `r ACR()` ≥ `r acr_cutpoint` mg/g.
-Ten-year predicted `r ASCVD()` risk was calculated using the Pooled Cohort risk equations for participants without clinical `r CVD()` [@goff20142013].
-High `r ASCVD()` risk was defined as clinical `r CVD()` or a 10-year predicted `r ASCVD()` risk ≥ 10%.
+Ten-year predicted `r ASCVD()` risk was calculated using the Pooled Cohort risk equations for participants without clinical `r CVD()` [@goff20142013; @lloyd2019use].
+High `r ASCVD()` risk was defined as having a 10-year predicted `r ASCVD()` risk ≥ 10% or clinical `r CVD()`.
 
@@
 Among US adults aged 40 to 79 years, the estimated percentage (95% `r CI()`) with high `r ASCVD()` risk was `r inline$prevHighRiskOverall` (`r refer_to('tab_risk_overall')`; bottom panel).
-Among sub-groups with diabetes, `r CKD()`, age ≥ 65 years, or any of these conditions, `r inline$prevHighRiskDiabetes`, `r inline$prevHighRiskCkd`, `r inline$prevHighRiskAge65`, and `r inline$prevHighRiskAny` had high `r ASCVD()` risk, respectively .
+Among sub-groups with diabetes, `r CKD()`, age ≥ 65 years, or any of these conditions, `r inline$prevHighRiskDiabetes`, `r inline$prevHighRiskCkd`, `r inline$prevHighRiskAge65`, and `r inline$prevHighRiskAny` had high `r ASCVD()` risk, respectively.
 Among those with stage 1 hypertension, the estimated percentage (95% `r CI()`) with high `r ASCVD()` risk was `r inline$prevHighRiskS1hOverall` in the overall population and `r inline$prevHighRiskS1hDiabetes`, `r inline$prevHighRiskS1hCkd`, `r inline$prevHighRiskS1hAge65`, and `r inline$prevHighRiskS1hAny` for those with diabetes, `r CKD()`, age ≥ 65 years, or any of these conditions, respectively.
@@
 
-In the current study, a majority of US adults aged 40 to 79 years with diabetes, `r CKD()`, age ≥ 65 years, and any of these conditions had high `r ASCVD()` risk, defined by a 10-year predicted `r ASCVD()` risk ≥ 10% or clinical CVD.
+In the current study, the majority of US adults aged 40 to 79 years with diabetes, `r CKD()`, age ≥ 65 years, and any of these conditions had high `r ASCVD()` risk, defined by a 10-year predicted `r ASCVD()` risk ≥ 10% or clinical CVD.
 Also, the majority of US adults with stage 1 hypertension who were ≥ 65 years of age had high `r ASCVD()` risk.
@@
 Previous randomized trials and meta-analyses have investigated whether lower `r BP()` goals reduce incident `r CVD()` risk in patients with diabetes, `r CKD()`, or older age.
-A randomized trial of patients with diabetes and baseline `r SBP()` < 140 mm hg and `r DBP()` < 80 mm Hg found lower risk of stroke among participants with more intense `r BP()` treatment goals [@schrier2002effects].
+A randomized trial of patients with diabetes and baseline `r SBP()` < 140 mm Hg and `r DBP()` < 90 mm Hg found lower risk of stroke among participants with more intense `r BP()` treatment goals [@schrier2002effects].
 The Systolic Blood Pressure Intervention Trial compared an `r SBP()` treatment target of < 120 mm Hg to < 140 mm Hg among older adults (mean age of 68 years) without diabetes.
@@
 
-It has been suggested that the vast majority of adults with diabetes, CKD, or ≥ 65 years of age have a 10-year predicted `r ASCVD()` risk ≥ 10% [@whelton20182017].
+It has been suggested that most adults with diabetes, CKD, or ≥ 65 years of age have a 10-year predicted `r ASCVD()` risk ≥ 10% [@whelton20182017].
 Previous research has shown that diabetes, `r CKD()`, and older age are each associated with an increased risk for `r ASCVD()` events [@coresh2004evidence; @chronic2010association; @grundy1999diabetes; @lakatta2002age].

### 2020-10-29 R/compile_report.R

@@ -32,6 +32,7 @@ compile_report <- function(exams,
                            tbl1_s1hyp,
                            tbl_bpdist,
                            tbl_risk_overall,
+                           tbl_risk_overall_supp,
                            tbl_exclusions,
                            fig_hist_ovrl,
                            fig_hist_stg1,
@@ -85,7 +86,7 @@ compile_report <- function(exams,
 
   value_note <- as_paragraph("Table values are mean (standard error) or proportion.")
 
-  ftr_ckd <- as_paragraph(glue('Chronic kidney disease is defined by an albumin-to-creatinine ratio \u2265 {acr_cutpoint} mg/dl or an estimated glomerular filtration rate < {egfr_cutpoint} ml/min/1.73m\u00b2'))
+  ftr_ckd <- as_paragraph(glue('Chronic kidney disease is defined by an albumin-to-creatinine ratio \u2265 {acr_cutpoint} mg/g or an estimated glomerular filtration rate < {egfr_cutpoint} ml/min/1.73m\u00b2'))
 
   ftr_diab <- as_paragraph(glue('Diabetes was defined by fasting serum glucose \u2265 {gluc_cutpoint_fasted} mg/dL, non-fasting glucose \u2265 {gluc_cutpoint_fed} mg/dL, glycated hemoglobin (HbA1c) \u2265 {hba1c_cutpoint}%, or self-reported use of insulin or oral glucose lowering medication.'))
 
@@ -102,6 +103,7 @@ compile_report <- function(exams,
   ftr_cvdHx_defn <- as_paragraph('Clinical cardiovascular disease was defined by self-report of previous heart failure, coronary heart disease, stroke, or myocardial infarction')
 
   ftr_prisk_defn <- as_paragraph('Predicted risk for atherosclerotic cardiovascular disease was computed using the Pooled Cohort risk equations, based on the guideline by American College of Cardiology / American Heart Association, 2013')
+  ftr_prisk_defn_supp <- as_paragraph('Predicted risk for atherosclerotic cardiovascular disease was computed using an updated version of the Pooled Cohort risk equations from Yadlowsky et al., 2018')
 
   # sample sizes for table column headers -----------------------------------
 
@@ -262,94 +264,109 @@ compile_report <- function(exams,
 
   # table 3: % with high risk and median ------------------------------
 
-  .tbl_risk_overall <- tbl_risk_overall %>%
[…]

### 2020-10-29 R/derive_ascvd_risk_pcr.R

@@ -43,81 +43,144 @@ derive_ascvd_risk_pcr <- function(data,
       )
     )
 
-  data_out <- data %>%
+  data_out <- suppressWarnings(
     mutate(
-      # baseline survival probability varies by race/sex
-      base_surv = case_when(
-        sex == 'Female' & race_ethnicity == 'Non-Hispanic Black' ~ 0.9533,
-        sex == 'Female' & race_ethnicity != 'Non-Hispanic Black' ~ 0.9665,
-        sex == 'Male'   & race_ethnicity == 'Non-Hispanic Black' ~ 0.8954,
-        sex == 'Male'   & race_ethnicity != 'Non-Hispanic Black' ~ 0.9144,
-        TRUE ~ NA_real_
+      data,
+      ascvd_risk_pcr = predict_10yr_ascvd_risk(
+        age_years = age,
+        race = race_ethnicity,
+        sex = sex,
+        smoke_current = smk_current,
+        chol_total_mgdl = chol_total_mgdl,
+        chol_hdl_mgdl = chol_hdl_mgdl,
+        bp_sys_mmhg = bp_sys_mmhg,
+        bp_meds = meds_bp,
+        diabetes = diabetes,
+        equation_version = "Goff_2013",
+        override_boundary_errors = TRUE,
+        race_levels = list(
+          white = c(
+            "Non-Hispanic White",
+            "Hispanic",
+            "Non-Hispanic Asian",
+            "Mexican American",
+            "Other Hispanic",
+            "Other Race - Including Multi-Racial"
+          ),
+          black = "Non-Hispanic Black"
+        ),
+        sex_levels = list(
+          male = 'Male',
+          female = 'Female'
+        )
       ),
-      # mean log-hazard varies by race/sex
-      mean_coef = case_when(
-        sex == 'Female' & race_ethnicity == 'Non-Hispanic Black' ~ 86.61,
-        sex == 'Female' & race_ethnicity != 'Non-Hispanic Black' ~ -29.18,
-        sex == 'Male'   & race_ethnicity == 'Non-Hispanic Black' ~ 19.54,
-        sex == 'Male'   & race_ethnicity != 'Non-Hispanic Black' ~ 61.18,
-        TRUE ~ NA_real_
-      ),
-      # individual sums taken from Table A of
[…]

### 2020-10-29 R/derive_others.R

@@ -49,11 +49,17 @@ derive_others <- function(data, exams,
       ),
       # categorize pooled cohort risk
       pcr_gteq_10 = if_else(ascvd_risk_pcr >= 0.10, "yes", "no"),
+      pcr_gteq_10_yadlowsky = if_else(ascvd_risk_pcr_yadlowsky >= 0.10,
+                                      true = "yes", false = "no"),
       # set missing values to "no" for history of ASCVD
       ever_had_ascvd = replace(ever_had_ascvd, is.na(ever_had_ascvd), 'no'),
       # set high risk for participants with history of ASCVD
       pcr_highrisk = if_else(
         condition = pcr_gteq_10 == "yes" | ever_had_ascvd == "yes",
+        true = "yes", false = "no"
+      ),
+      pcr_highrisk_yadlowsky = if_else(
+        condition = pcr_gteq_10_yadlowsky == "yes" | ever_had_ascvd == "yes",
         true = "yes", false = "no"
       ),
       race_ethnicity = fct_collapse(
@@ -117,7 +123,9 @@ derive_others <- function(data, exams,
       ever_had_ascvd,
       ascvd_risk_pcr,
       pcr_gteq_10,
+      pcr_gteq_10_yadlowsky,
       pcr_highrisk,
+      pcr_highrisk_yadlowsky
     ) %>%
     mutate_if(is.character, as.factor)
 

### 2020-10-29 R/plan.R

@@ -95,6 +95,16 @@ the_plan <- drake_plan(
                              weights = ~wts_mec_2yr, nest = TRUE,
                              data = current_analysis$data),
 
+  design_overall_supp = svydesign(
+    ids = ~ psu,
+    strata = ~strata,
+    weights = ~wts_mec_2yr,
+    nest = TRUE,
+    data = mutate(current_analysis$data,
+                  pcr_gteq_10 = pcr_gteq_10_yadlowsky,
+                  pcr_highrisk = pcr_highrisk_yadlowsky)
+  ),
+
   design_s1hyp = subset(design_overall, bp_cat == 'Stage 1 hypertension'),
 
   tbl1_variables = c(
@@ -125,6 +135,7 @@ the_plan <- drake_plan(
   tbl_bpdist = tabulate_bpdist(design_overall),
 
   tbl_risk_overall = tabulate_risk_summary(design_overall),
+  tbl_risk_overall_supp = tabulate_risk_summary(design_overall_supp),
 
   # Figures ----
 
@@ -160,7 +171,7 @@ the_plan <- drake_plan(
 
   inline = make_inline_results(design_overall, design_s1hyp, risk_models),
 
-  fig_central_illustration = visualize_central_illustration(tbl_bpdist,
+  fig_central_illustration = visualize_central_illustration(tbl_bpdist$table,
                                                             inline),
 
   report = compile_report(
@@ -174,10 +185,11 @@ the_plan <- drake_plan(
     acr_cutpoint,
     current_analysis,
     design_overall,
-    tbl1_overall,
-    tbl1_s1hyp,
-    tbl_bpdist,
+    tbl1_overall$table,
+    tbl1_s1hyp$table,
+    tbl_bpdist$table,
     tbl_risk_overall,
+    tbl_risk_overall_supp,
     current_analysis$tbl,
     fig_hist$ovrl,
     fig_hist$stg1,
@@ -193,6 +205,13 @@ the_plan <- drake_plan(
     command = {
       rmarkdown::render(knitr_in("doc/ACCAHA_BP_groups.Rmd"))
       file_out("doc/ACCAHA_BP_groups.docx")
+    }
+  ),
+
+  readme = target(
+    command = {
+      rmarkdown::render(knitr_in("README.Rmd"))
+      file_out("README.md")
     }
   )
 

### 2020-10-29 R/tabulate_bpdist.R

@@ -4,7 +4,7 @@
 ##'
 ##' @title
 ##' @param design
-tabulate_bpdist <- function(design, decimals) {
+tabulate_bpdist <- function(design) {
 
   fix_names <- function(.x, first_name = 'bp_cat'){
     if(ncol(.x) == 3){
@@ -14,7 +14,7 @@ tabulate_bpdist <- function(design, decimals) {
     }
   }
 
-  list(
+  tbl_data <- list(
     overall = ~ bp_cat,
     diabetes = ~ bp_cat + diabetes,
     ckd = ~ bp_cat + ckd,
@@ -30,5 +30,12 @@ tabulate_bpdist <- function(design, decimals) {
     select(-level) %>%
     group_by(variable) %>%
     mutate(n = table_glue("{100 * n / sum(n)}%"))
+
+  tbl_inline <- tbl_data %>%
+    as_inline(tbl_variables = c('variable', 'bp_cat'),
+              tbl_value = 'n')
+
+  list(table = tbl_data,
+       inline = tbl_inline)
 
 }

### 2020-10-29 R/tabulate_characteristics.R

@@ -5,7 +5,7 @@
 ##' @title
 ##' @param design
 ##' @param variables
-tabulate_characteristics <- function(design, variables, decimals) {
+tabulate_characteristics <- function(design, variables) {
 
   tb1_ovrl <- variables %>%
     map(tb1_fun, design = design) %>%
@@ -13,35 +13,39 @@ tabulate_characteristics <- function(design, variables, decimals) {
 
   tb1_diab <- variables %>%
     map(.f = tb1_fun,
-        design = subset(design, diabetes == 'yes'),
-        decimals = decimals) %>%
+        design = subset(design, diabetes == 'yes')) %>%
     bind_rows(.id = 'label')
 
   tb1_ckd <- variables %>%
     map(tb1_fun,
-        design = subset(design, ckd == 'yes'),
-        decimals = decimals) %>%
+        design = subset(design, ckd == 'yes')) %>%
     bind_rows(.id = 'label')
-
-  # tb1_diab_and_ckd <- variables %>%
-  #   map(tb1_fun,
-  #       design = subset(design, diabetes_and_ckd == 'yes'),
-  #       decimals = decimals) %>%
-  #   bind_rows(.id = 'label')
 
   tb1_age <- variables %>%
     map(tb1_fun,
-        design = subset(design, age >= 65),
-        decimals = decimals) %>%
+        design = subset(design, age >= 65)) %>%
     bind_rows(.id = 'label')
 
   tb1_any <- variables %>%
     map(tb1_fun,
-        design = subset(design, any_ckd_diab_age65 == "yes"),
-        decimals = decimals) %>%
+        design = subset(design, any_ckd_diab_age65 == "yes")) %>%
     bind_rows(.id = 'label')
 
-  tb1 <- bind_rows(
+  tb1_inline <- bind_rows(
+    overall = tb1_ovrl,
+    diabetes = tb1_diab,
+    ckd = tb1_ckd,
+    age_gt65 = tb1_age,
+    any = tb1_any,
+    .id = 'name'
+  ) %>%
+    mutate(variable = recode(label, !!!variables)) %>%
+    select(name, variable, level, value) %>%
+    as_inline(tbl_variables = c('name', 'variable', 'level'),
+              tbl_value = 'value')
+
+
+  tb1_data <- bind_rows(
     Overall = tb1_ovrl,
     Diabetes = tb1_diab,
     'CKD' = tb1_ckd,
[…]

### 2020-10-29 packages.R

@@ -35,6 +35,7 @@ pacman::p_load(
   Hmisc
 )
 
+pacman::p_load_gh('bcjaeger/PooledCohort', update = FALSE)
 pacman::p_load_gh('bcjaeger/table.glue', update = FALSE)
 
 conflicted::conflict_prefer("roc",       "pROC")

### 2020-10-29 README.Rmd
still prepping for JACC submission

@@
 
-2. This project is built around `drake`, a workflow package. To produce every target in the drake workflow, run `r_make()` in your console.
+2. This project is built around `drake`, a workflow package. To produce every target in the drake workflow, run `drake::r_make()` in your console.
 
-3. Allow Rstudio to access the internet if prompted, as `r_make()` will be downloading NHANES data from the NHANES website while it produces the manuscript.
+3. Allow Rstudio to access the internet if prompted, as `drake::r_make()` will be downloading NHANES data from the NHANES website while it produces the manuscript.
 
-4. `r_make()` will build every target, ending with the manuscript and finally the `README.md` file. Simply open the file 'doc/ACCAHA_BP_groups.docx' to see the manuscript you built.
+4. `drake::r_make()` will build every target, ending with the manuscript and finally the `README.md` file. Simply open the file 'doc/ACCAHA_BP_groups.docx' to see the manuscript you built.
 
@@
 
-3. Save your changes to the `R/plan.R` file and then run `r_make()` in your console.
+3. Save your changes to the `R/plan.R` file and then run `drake::r_make()` in your console.
 

### 2020-10-29 doc/ACCAHA_BP_groups.Rmd
include GH link
still prepping for JACC submission

@@
 
+_Note:_ This illustration is not the same as the central illustration in the paper.
+A different version is used in order to adhere to a publication agreement: "Excluding abstracts, none of the paper's contents have been previously published."
+
 Distribution of US adults by blood pressure and antihypertensive medication use categories.
@@
 Data analysis was conducted using `r R_string_fancy` along with a collection of open-source software packages [@cite_R; @cite_drake; @cite_tidyverse; @cite_table.glue].
-The first author's GitHub repository (< _Link not yet active so we won't be scooped_ >) provides code to reproduce the current study.
+The first author's GitHub repository (https://github.com/bcjaeger/ACC-AHA-BP-guideline-groups) provides code to reproduce the current study.
 

### 2020-10-29 README.Rmd
note on central illustration

@@
 `r fp_par(line_spacing = 1)`
+
+ASCVD = atherosclerotic cardiovascular disease; CKD = chronic kidney disease
+
+_Note:_ This illustration is not the same as the central illustration in the paper.
+A different version is used in order to adhere to a publication agreement: "Excluding abstracts, none of the paper's contents have been previously published."
 

### 2020-10-29 doc/ACCAHA_BP_groups.Rmd
note on central illustration

@@
 
-_Note:_ This illustration is not the same as the central illustration in the paper.
-A different version is used in order to adhere to a publication agreement: "Excluding abstracts, none of the paper's contents have been previously published."
-
 Distribution of US adults by blood pressure and antihypertensive medication use categories.
@@
 
-ASCVD = atherosclerotic cardiovascular disease; CKD = chronic kidney disease
+BP = blood presure; HTN = hypertension
 

### 2021-01-11 doc/ACCAHA_BP_groups.Rmd
updates based on JACC reviewers

@@
 ---
-title: "Predicted cardiovascular risk for US adults with diabetes, chronic kidney disease, and \u2265 65 years of age"
+title: "Predicted cardiovascular risk for US adults with diabetes, chronic kidney disease, and \u2265 65 years of age overall and with stage 1 hypertension"
 bibliography: refs.bib
@@
 
-<!-- The word count includes text from introduction through the conclusion, references, and figure legends.  -->
-
-<!-- 3,609 / 5000 max -->
-
-Total word count: ~3,700 / 5,000
+__Abbreviated title__: Predicted cardiovascular risk for US adults
 
@@
 
+__Total word count including the title page, abstract, text, references, tables, and figures legends__:
+
 \newpage
@@
 __Background:__ The 2017 American College of Cardiology/American Heart Association blood pressure (BP) guideline recommends using 10-year predicted atherosclerotic cardiovascular disease (ASCVD) risk to guide decisions to initiate antihypertensive medication.
+Adults with stage 1 hypertension and diabetes mellitus, chronic kidney disease (CKD), or aged ≥65 years are considered to have high CVD risk by the guideline and initiation of antihypertensive medication is recommended.
+This recommendation is based on the assumption that the vast majority of adults with diabetes, CKD, or aged ≥65 years are likely to have a 10-year predicted ASCVD risk ≥10% and surveys that suggest most clinicians, including cardiologists, do not assess CVD risk using recommended risk prediction tools.
 
-__Objectives:__ Determine if the majority of US adults in subgroups defined by diabetes, chronic kidney disease (CKD), and age ≥65 years have high ASCVD risk (i.e., 10-year predicted ASCVD risk ≥10% or clinical CVD), and estimate the age-adjusted probability of having high ASCVD risk.
-
-__Methods:__ Adults aged 40-79 years from the National Health and Nutrition Examination Survey `r min(exams)`-`r max(exams)+1` were included (n=`r table_value(nrow(current_analysis$data))`).
-We predicted 10-year ASCVD risk using the Pooled Cohort risk equations and clinical CVD was self-reported.
+__Methods:__ We included adults aged 40-79 years from the National Health and Nutrition Examination Survey `r min(exams)`-`r max(exams)+1` (n=`r table_value(nrow(current_analysis$data))`).
+We computed 10-year predicted ASCVD risk using the Pooled Cohort risk equations and clinical CVD was self-reported.
 Analyses were conducted overall and among those with stage 1 hypertension, defined by systolic BP of 130-139 mm Hg or diastolic BP of 80-89 mm Hg.
+In subgroups defined by diabetes, chronic kidney disease (CKD), and age ≥65 years, we estimated the proportion of US adults with high ASCVD risk (i.e., 10-year predicted ASCVD risk ≥10% or clinical CVD) and estimated age-adjusted probability of having high ASCVD risk.
 
@@
 ```
-
-\newpage
-
-# CONDENSED ABSTRACT
-
-The 2017 American College of Cardiology/American Heart Association blood pressure (BP) guideline recommends using atherosclerotic cardiovascular disease (ASCVD) risk to guide decisions to initiate antihypertensive medication.
-Using National Health and Nutrition Examination Survey `r min(exams)`-`r max(exams)+1` data, it was estimated that `r no_ci(inline$prevHighRiskS1hDiabetes)`, `r no_ci(inline$prevHighRiskS1hCkd)`, and `r no_ci(inline$prevHighRiskS1hAge65)` of US adults with stage 1 hypertension and diabetes, chronic kidney disease and age ≥65 years had high ASCVD risk defined by 10-year predicted ASCVD risk ≥10% or clinical CVD.
-Predicted 10-year ASCVD risk should be calculated for all adults with stage 1 hypertension and without clinical CVD as many are not at high risk for ASCVD.
-
-\newpage
-
-# Central Illustration
-
-Distribution of US adults by blood pressure and antihypertensive medication use categories.
-In pie charts, the proportion of adults with stage 1 hypertension at high atherosclerotic cardiovascular disease risk in subgroups defined by diabetes, chronic kidney disease and age ≥ 65 years.
-`r fp_par(line_spacing = 1)`
-
-<br>
-
-```{r out.width='100%'}
-
-knitr::include_graphics("../fig/central_illustration.png")
-
-```
-
-High atherosclerotic cardiovascular disease risk was defined by a 10-year predicted risk for atherosclerotic cardiovascular disease ≥ 10% or clinical cardiovascular disease.
-Data are from the National Health and Nutrition Examination Survey, `r min(exams)`-`r max(exams)+1`.
-`r fp_par(line_spacing = 1)`
-
-BP = blood presure; HTN = hypertension
-
-\newpage
-
-# Clinical Perspectives:
-
-__Competency in Medical Knowledge:__ The 2017 American College of Cardiology/American Heart Association blood pressure guideline recommends using both blood pressure and atherosclerotic cardiovascular disease (ASCVD) risk to guide decisions to initiate antihypertensive medication.
-
-__Competency in Patient Care:__ The guideline recommends computing 10-year predicted ASCVD risk for all adults with hypertension who do not have clinical CVD.
-
-__Translational Outlook:__ Predicted 10-year ASCVD risk should be computed for all adults with stage 1 hypertension and without clinical CVD, as many are not at high risk for ASCVD.
 
@@
 Previous studies have shown that the use of predicted `r ASCVD()` risk in addition to `r BP()` can direct antihypertensive medication to adults likely to receive the largest risk reduction benefit [@colantonio20182017; @jaeger2019cardiovascular, @herrett2019eligibility].
-For example, in an analysis of the Reasons for Geographic and Racial Differences in Stroke study, those with stage 1 hypertension for whom initiation of antihypertensive medication was recommended versus not recommended by the 2017 `r ACC_AHA()` `r BP()` guideline were roughly 6 times more likely to experience a `r CVD()` event over 8 years of follow-up [@colantonio20182017].
+For example, in an analysis of the Reasons for Geographic and Racial Differences in Stroke study, those with stage 1 hypertension for whom initiation of antihypertensive medication __would have been__ recommended versus not recommended by the 2017 `r ACC_AHA()` `r BP()` guideline were roughly 6 times more likely to experience a `r CVD()` event over 8 years of follow-up [@colantonio20182017].
 Although a substantial proportion of US adults with stage 1 hypertension and diabetes or `r CKD()` did not have a high `r ASCVD()` risk in the current study, these subgroups were more likely to have high `r ASCVD()` risk compared to the overall US population with stage 1 hypertension, and may therefore still benefit from initiating antihypertensive medication.
@@
 In the overall population, those randomized to the lower `r SBP()` target experienced lower rates of incident fatal and nonfatal major `r CVD()` events as well as all-cause mortality [@sprint2015randomized].
+__The trial did not examine stage 1 hypertension specifically, but found no evidence of a difference in treatment effect across baseline `r SBP()` groups and estimated a hazard ratio (95% `r CI()`) of 0.77 (0.57 - 1.03) comparing intensive to standard treatment for major `r CVD()` events among participants with `r SBP()` > 132 and < 145 mm Hg__ [@sprint2015randomized].
 A systematic review and meta-analysis of 123 studies with 613,815 participants found strong support for lowering `r SBP()` to < 130 mm Hg and providing antihypertensive medication to adults with diabetes, CKD, and various other comorbidities [@ettehad2016blood].

### 2021-01-14 doc/ACCAHA_BP_groups.Rmd
PW edits

@@
 
-Dr. Whelton receives support through P20GM109036 from the Centers for Research Excellence grant from the National Institute of General Medical Sciences.
+Dr. Whelton receives support through a Centers of Research Excellence grant from the National Institute of General Medical Sciences, P20GM109036.
 
@@
 We computed 10-year predicted ASCVD risk using the Pooled Cohort risk equations and clinical CVD was self-reported.
-Analyses were conducted overall and among those with stage 1 hypertension, defined by systolic BP of 130-139 mm Hg or diastolic BP of 80-89 mm Hg.
+Analyses were conducted overall and among those with stage 1 hypertension, defined by a mean systolic BP of 130-139 mm Hg or diastolic BP of 80-89 mm Hg.
 In subgroups defined by diabetes, chronic kidney disease (CKD), and age ≥65 years, we estimated the proportion of US adults with high ASCVD risk (i.e., 10-year predicted ASCVD risk ≥10% or clinical CVD) and estimated age-adjusted probability of having high ASCVD risk.
@@
 Participants < 40 or > 79 years of age were not included because use of the Pooled Cohort risk equations is not recommended in these age ranges [@goff20142013].
-Participants who did not have three `r SBP()` and `r DBP()` measurements (n = `r n_bp_too_low`) and those who were missing information on age, race, sex, total and high-density lipoprotein cholesterol, smoking status, diabetes, or `r CKD()` status (n = `r n_missing_pcr`) were excluded.
+Participants who did not have three `r SBP()` and `r DBP()` measurements (n = `r n_bp_too_low`) and those who were missing information on age, race, sex, total and high-density lipoprotein cholesterol, smoking status, diabetes, or `r CKD()` status (n = `r n_missing_pcr`) were also excluded.
 After these exclusions, a total of `r n_final` participants were included in the analysis (`r refer_to('fig_include_exclude')`).
@@
 In the overall population, those randomized to the lower `r SBP()` target experienced lower rates of incident fatal and nonfatal major `r CVD()` events as well as all-cause mortality [@sprint2015randomized].
-__The trial did not examine stage 1 hypertension specifically, but found no evidence of a difference in treatment effect across baseline `r SBP()` groups and estimated a hazard ratio (95% `r CI()`) of 0.77 (0.57 - 1.03) comparing intensive to standard treatment for major `r CVD()` events among participants with `r SBP()` > 132 and < 145 mm Hg__ [@sprint2015randomized].
+The trial did not examine stage 1 hypertension specifically, but found no evidence of a difference in treatment effect across baseline `r SBP()` groups and estimated a hazard ratio (95% `r CI()`) of 0.77 (0.57 - 1.03) comparing intensive to standard treatment for major `r CVD()` events among participants with `r SBP()` > 132 and < 145 mm Hg [@sprint2015randomized].
 A systematic review and meta-analysis of 123 studies with 613,815 participants found strong support for lowering `r SBP()` to < 130 mm Hg and providing antihypertensive medication to adults with diabetes, CKD, and various other comorbidities [@ettehad2016blood].

### 2021-03-18 doc/ACCAHA_BP_groups.Rmd
drop abbrev functions

@@
 bibliography: refs.bib
-csl: jacc.csl
+csl: ccqo.csl
 output: 
   officedown::rdocx_document:
-    reference_docx: style_manuscript_times_new_roman.docx
+    reference_docx: style_manuscript_times_new_roman_lines.docx
 ---
@@
 
-__Abbreviated title__: Predicted cardiovascular risk for US adults
-
 Byron C. Jaeger, PhD^1^, Swati Sakhuja, MPH^2^, Shakia T. Hardy, PhD, MPH^2^, Oluwasegun P. Akinyelure, MD, MPH^2^, Joshua D. Bundy, PhD, MPH^3^, Paul Muntner, PhD^2^, and Paul K. Whelton, MD, MSc^3^
@@
 
-__Funding:__
-
-Drs Muntner and Jaeger receive support through grant R01HL144773 from the National Heart, Lung, and Blood Institute and grant 15SFRN2390002 from the American Heart Association.
-
-Dr. Hardy receives support through R01HL139716 from the National Heart, Lung, and Blood Institute.
-
-Dr. Bundy receives support through K12HD043451 from the Eunice Kennedy Shriver National Institute of Child Health and Human Development.
-
-Dr. Whelton receives support through a Centers of Research Excellence grant from the National Institute of General Medical Sciences, P20GM109036.
-
-__Disclosures:__
-
-BCJ has nothing to disclose. 
-SS has nothing to disclose.
-STH has nothing to disclose.
-OPA has nothing to disclose. 
-JDB has nothing to disclose.
-PM received grant funding and consulting fees from Amgen Inc., unrelated to the current manuscript.
-PKW has nothing to disclose.
+__Short title__: Predicted cardiovascular risk for US adults
 
@@
 
-__Acknowledgments:__ None.
-
 __Total word count including the title page, abstract, text, references, tables, and figures legends__:
@@
 Adults with stage 1 hypertension and diabetes mellitus, chronic kidney disease (CKD), or aged ≥65 years are considered to have high CVD risk by the guideline and initiation of antihypertensive medication is recommended.
-This recommendation is based on the assumption that the vast majority of adults with diabetes, CKD, or aged ≥65 years are likely to have a 10-year predicted ASCVD risk ≥10% and surveys that suggest most clinicians, including cardiologists, do not assess CVD risk using recommended risk prediction tools.
+This recommendation assumes that most adults with diabetes, CKD, or aged ≥65 years have 10-year predicted ASCVD risk ≥10%.
 
@@
 
-In November 2017, the `r ACC_AHA()` published a guideline for the prevention, detection, evaluation, and management of high `r BP()` in adults  [@whelton20182017].
-This guideline recommends using both `r BP()` levels and predicted risk for `r CVD()` to guide the initiation of antihypertensive medication in addition to nonpharmacological therapy.
-Initiation of antihypertensive medication is recommended for all adults with a confirmed average `r SBP()` ≥ 140 mm Hg or `r DBP()` ≥ 90 mm Hg, stage 2 hypertension in the guideline.
-Initiation of antihypertensive medication is also recommended for adults with clinical `r CVD()` or a 10-year risk of `r ASCVD()` events ≥ 10% who have a confirmed average `r SBP()` between 130 and 139 mm Hg and/or `r DBP()` between 80 and 89 mm Hg, stage 1 hypertension in the guideline [@goff20142013].
-Additionally, as a matter of practical convenience, adults with stage 1 hypertension and diabetes mellitus, `r CKD()`, or ≥ 65 years of age are considered to have high `r CVD()` risk by the guideline and initiation of antihypertensive medication is recommended.
-This recommendation, written in Sections 9.3, 9.6, and 10.3 of the guideline, was based on the assumption that the vast majority of adults with diabetes, `r CKD()`, or ≥ 65 years of age are likely to have a 10-year predicted `r ASCVD()` risk ≥ 10% and the knowledge that surveys suggest most clinicians, including cardiologists, do not assess `r CVD()` risk using recommended risk prediction tools [@whelton20182017; @shillinglaw2012use].
+In November 2017, the American College of Cardiology and the American Heart Association (ACC/AHA) published a guideline for the prevention, detection, evaluation, and management of high blood pressure (BP) in adults  [@whelton20182017].
+This guideline recommends using both BP levels and predicted risk for cardiovascular disease (CVD) to guide the initiation of antihypertensive medication in addition to nonpharmacological therapy.
+Initiation of antihypertensive medication is recommended for all adults with a confirmed average systolic BP (SBP) ≥ 140 mm Hg or diastolic BP (DBP) ≥ 90 mm Hg, stage 2 hypertension in the guideline.
+Initiation of antihypertensive medication is also recommended for adults with clinical CVD or a 10-year risk of atherosclerotic CVD (ASCVD) events ≥ 10% who have a confirmed average SBP between 130 and 139 mm Hg and/or DBP between 80 and 89 mm Hg, stage 1 hypertension in the guideline [@goff20142013].
+Additionally, as a matter of practical convenience, adults with stage 1 hypertension and diabetes mellitus, chronic kidney disease (CKD), or ≥ 65 years of age are considered to have high CVD risk by the guideline and initiation of antihypertensive medication is recommended.
+This recommendation, written in Sections 9.3, 9.6, and 10.3 of the guideline, was based on the assumption that the vast majority of adults with diabetes, CKD, or ≥ 65 years of age are likely to have a 10-year predicted ASCVD risk ≥ 10% and the knowledge that surveys suggest most clinicians, including cardiologists, do not assess CVD risk using recommended risk prediction tools [@whelton20182017; @shillinglaw2012use].
 
@@
 
-The goal of the current analysis was to estimate the proportion of US adults with diabetes, `r CKD()`, or ≥ 65 years of age that have high `r ASCVD()` risk (defined by 10-year predicted risk for `r ASCVD()` ≥ 10% or clinical `r CVD()`).
+The goal of the current analysis was to estimate the proportion of US adults with diabetes, CKD, or ≥ 65 years of age that have high ASCVD risk (defined by 10-year predicted risk for ASCVD ≥ 10% or clinical CVD).
 This analysis was conducted for all US adults and among those with stage 1 hypertension.
-To accomplish this goal, we analyzed data from `r english(length(exams))` cycles of the US `r NHANES()`.
+To accomplish this goal, we analyzed data from `r english(length(exams))` cycles of the US US National Health and Nutrition Examination Survey (NHANES).
 
@@
 
-`r NHANES()` was designed to assess the health and nutritional status of the non-institutionalized US population and was conducted by the National Center for Health Statistics of the Centers for Disease Control and Prevention [@nhanes_home].
-Since 1999-2000, `r NHANES()` has been conducted in two-year cycles using a multistage probability sampling design to select participants.
+NHANES was designed to assess the health and nutritional status of the non-institutionalized US population and was conducted by the National Center for Health Statistics of the Centers for Disease Control and Prevention [@nhanes_home].
+Since 1999-2000, NHANES has been conducted in two-year cycles using a multistage probability sampling design to select participants.
 Each cycle is independent with different participants recruited.
@@
 Written informed consent was obtained from each participant.
-The University of Alabama at Birmingham Institutional Review Board considered the analysis of `r NHANES()` data to be exempt research.
+The University of Alabama at Birmingham Institutional Review Board considered the analysis of NHANES data to be exempt research.
 
@@
 
-The current analysis was restricted to adults aged 40 to 79 years of age who completed the `r NHANES()` interview and examination (n = `r n_age_40_to_79`).
+The current analysis was restricted to adults aged 40 to 79 years of age who completed the NHANES interview and examination (n = `r n_age_40_to_79`).
 Participants < 40 or > 79 years of age were not included because use of the Pooled Cohort risk equations is not recommended in these age ranges [@goff20142013].
-Participants who did not have three `r SBP()` and `r DBP()` measurements (n = `r n_bp_too_low`) and those who were missing information on age, race, sex, total and high-density lipoprotein cholesterol, smoking status, diabetes, or `r CKD()` status (n = `r n_missing_pcr`) were also excluded.
+Participants who did not have three SBP and DBP measurements (n = `r n_bp_too_low`) and those who were missing information on age, race, sex, total and high-density lipoprotein cholesterol, smoking status, diabetes, or CKD status (n = `r n_missing_pcr`) were also excluded.
 After these exclusions, a total of `r n_final` participants were included in the analysis (`r refer_to('fig_include_exclude')`).
@@
 The medical history assessment included questions about whether the participant had been told by a doctor or other health professional that they had a heart attack, coronary heart disease, stroke, or heart failure.
-Clinical `r CVD()` was defined as answering yes to at least one of these questions.
+Clinical CVD was defined as answering yes to at least one of these questions.
 
@@
 Blood and urine samples were collected during the medical examination.
-Serum creatinine, serum glucose and `r HB_A1C()` were measured using standard methods.
-Diabetes was defined by fasting plasma glucose ≥ `r gluc_cutpoint_fasted` mg/dL (≥ `r gluc_cutpoint_fed` mg/dL for those who were not fasting), `r HB_A1C()` ≥ `r hba1c_cutpoint`%, or self-reported use of insulin or oral glucose lowering medication.
-`r capitalize(E_GFR())` was calculated using the `r CKD()` Epidemiology Collaboration equation [@levey2009new; @cite_nephro].
-Urinary albumin and creatinine levels were measured and used to calculate the `r ACR()`.
-`r CKD()` was defined by an `r E_GFR()` < `r egfr_cutpoint` ml/min/1.73m^2^ or an `r ACR()` ≥ `r acr_cutpoint` mg/g.
-Ten-year predicted `r ASCVD()` risk was calculated using the Pooled Cohort risk equations for participants without clinical `r CVD()` [@goff20142013; @lloyd2019use].
-High `r ASCVD()` risk was defined as having a 10-year predicted `r ASCVD()` risk ≥ 10% or clinical `r CVD()`.
+Serum creatinine, serum glucose and glycated hemoglobin were measured using standard methods.
+Diabetes was defined by fasting plasma glucose ≥ `r gluc_cutpoint_fasted` mg/dL (≥ `r gluc_cutpoint_fed` mg/dL for those who were not fasting), glycated hemoglobin ≥ `r hba1c_cutpoint`%, or self-reported use of insulin or oral glucose lowering medication.
+Estimated glomerular filtration rate was calculated using the CKD Epidemiology Collaboration equation [@levey2009new; @cite_nephro].
+Urinary albumin and creatinine levels were measured and used to calculate the albumin-to-creatinine ratio.
+CKD was defined by an estimated glomerular filtration rate < `r egfr_cutpoint` ml/min/1.73m^2^ or an albumin-to-creatinine ratio ≥ `r acr_cutpoint` mg/g.
+Ten-year predicted ASCVD risk was calculated using the Pooled Cohort risk equations for participants without clinical CVD [@goff20142013; @lloyd2019use].
+High ASCVD risk was defined as having a 10-year predicted ASCVD risk ≥ 10% or clinical CVD.
 
@@
 
-The same protocol was followed to measure `r SBP()` and `r DBP()` in each `r NHANES()` cycle.
-After survey participants had rested 5 minutes, their `r BP()` was measured by a trained physician using a mercury sphygmomanometer and an appropriately sized cuff.
-Three `r BP()` measurements were obtained at 30 second intervals.
-The mean of all three measurements was used to define `r SBP()` and `r DBP()`.
+The same protocol was followed to measure SBP and DBP in each NHANES cycle.
+After survey participants had rested 5 minutes, their BP was measured by a trained physician using a mercury sphygmomanometer and an appropriately sized cuff.
+Three BP measurements were obtained at 30 second intervals.
+The mean of all three measurements was used to define SBP and DBP.
 Quality control included re-certification of physicians every quarter with retraining if needed.
@@
 
-Participants not taking antihypertensive medication were grouped into four non-overlapping categories based on the 2017 `r ACC_AHA()` `r BP()` guideline: normal `r BP()` (`r SBP()` < 120 mm Hg and `r DBP()` < 80 mm Hg), elevated `r BP()` (`r SBP()` between 120 and 129 mm Hg and `r DBP()` < 80 mm Hg), stage 1 hypertension (`r SBP()` between 130 and 139 mm Hg or `r DBP()` between 80 and 89 mm Hg with SBP < 140 mm Hg and DBP < 90 mm Hg), stage 2 hypertension (`r SBP()` ≥ 140 mm Hg or `r DBP()` ≥ 90 mm Hg).
+Participants not taking antihypertensive medication were grouped into four non-overlapping categories based on the 2017 ACC/AHA BP guideline: normal BP (SBP < 120 mm Hg and DBP < 80 mm Hg), elevated BP (SBP between 120 and 129 mm Hg and DBP < 80 mm Hg), stage 1 hypertension (SBP between 130 and 139 mm Hg or DBP between 80 and 89 mm Hg with SBP < 140 mm Hg and DBP < 90 mm Hg), stage 2 hypertension (SBP ≥ 140 mm Hg or DBP ≥ 90 mm Hg).
 Participants taking antihypertensive medication were placed in a fifth category.
@@
 Participant characteristics were summarized as mean with its standard error for continuous variables and percentage for categorical variables.
-The percentage of US adults in each of the five categories based on `r BP()` and antihypertensive medication use was computed.
-The 25^th^, 50^th^, and 75^th^ percentile of 10-year predicted `r ASCVD()` risk and the proportion of participants with high `r ASCVD()` risk were estimated for the overall population and within each of the five categories based on `r BP()` and antihypertensive medication use.
-To assess the extent to which participants with a 10-year predicted `r ASCVD()` risk < 10% were close to the 10% threshold, we estimated the distribution of 10-year predicted `r ASCVD()` risk.
-The probability of having high `r ASCVD()` risk was estimated for each year of age from 40 to 79 years using logistic regression.
-Analyses of participant characteristics, the distribution of 10-year predicted `r ASCVD()` risk, and the probability of having high `r ASCVD()` risk were repeated among participants with stage 1 hypertension.
+The percentage of US adults in each of the five categories based on BP and antihypertensive medication use was computed.
+The 25^th^, 50^th^, and 75^th^ percentile of 10-year predicted ASCVD risk and the proportion of participants with high ASCVD risk were estimated for the overall population and within each of the five categories based on BP and antihypertensive medication use.
+To assess the extent to which participants with a 10-year predicted ASCVD risk < 10% were close to the 10% threshold, we estimated the distribution of 10-year predicted ASCVD risk.
+The probability of having high ASCVD risk was estimated for each year of age from 40 to 79 years using logistic regression.
+Analyses of participant characteristics, the distribution of 10-year predicted ASCVD risk, and the probability of having high ASCVD risk were repeated among participants with stage 1 hypertension.
 
@@
 
-`r NHANES()` sampling weights, which were calculated as the inverse probability of being selected for the survey, were used in all calculations to obtain nationally representative estimates of the non-institutionalized US population.
+NHANES sampling weights, which were calculated as the inverse probability of being selected for the survey, were used in all calculations to obtain nationally representative estimates of the non-institutionalized US population.
 P-values were two-sided.
@@
 
-Among US adults aged 40 to 79 years in `r min(exams)`-`r max(exams)+1`, the estimated prevalence (95% `r CI(left_mark = '[', right_mark = ']')`) of diabetes and `r CKD()` was `r inline$prevDiabetesOverall` and `r inline$prevCkdOverall`, respectively, `r inline$prevAge65Overall` were estimated to be ≥ 65 years of age, and `r inline$prevAnyOverall` had diabetes, CKD, or ≥ 65 years of age (`r refer_to('tab_characteristics')`).
-The estimated prevalence (95% `r CI()`) of stage 1 hypertension was `r inline$prevS1hOverall` overall and `r inline$prevS1hDiabetes`, `r inline$prevS1hCkd`, `r inline$prevS1hAge65`, and `r inline$prevS1hAny` among those with diabetes, CKD, age ≥ 65 years, and at least one of these conditions, respectively (`r refer_to('tab_bpdist')`).
-Characteristics of US adults 40 to 79 years of age with stage 1 hypertension, overall and for subgroups defined by diabetes, `r CKD()` and age ≥ 65 years, are presented in Table S1.
+Among US adults aged 40 to 79 years in `r min(exams)`-`r max(exams)+1`, the estimated prevalence (95% confidence interval [CI]) of diabetes and CKD was `r inline$prevDiabetesOverall` and `r inline$prevCkdOverall`, respectively, `r inline$prevAge65Overall` were estimated to be ≥ 65 years of age, and `r inline$prevAnyOverall` had diabetes, CKD, or ≥ 65 years of age (`r refer_to('tab_characteristics')`).
+The estimated prevalence (95% CI) of stage 1 hypertension was `r inline$prevS1hOverall` overall and `r inline$prevS1hDiabetes`, `r inline$prevS1hCkd`, `r inline$prevS1hAge65`, and `r inline$prevS1hAny` among those with diabetes, CKD, age ≥ 65 years, and at least one of these conditions, respectively (`r refer_to('tab_bpdist')`).
+Characteristics of US adults 40 to 79 years of age with stage 1 hypertension, overall and for subgroups defined by diabetes, CKD and age ≥ 65 years, are presented in Table S1.
 
@@
 
-Among US adults aged 40 to 79 years without clinical `r CVD()`, the estimated median (25^th^, 75^th^ percentiles) 10-year predicted `r ASCVD()` risk was `r inline$medianPcrOverall` in the overall population and `r inline$medianPcrDiabetes`, `r inline$medianPcrCkd`, `r inline$medianPcrAge65`, and `r inline$medianPcrAny` among those with diabetes, `r CKD()`, age ≥ 65 years, and any of these conditions, respectively (`r refer_to('tab_risk_overall')`; top panel).
-Among those with stage 1 hypertension, the estimated median (25^th^, 75^th^ percentiles) 10-year predicted `r ASCVD()` risk was `r inline$medianPcrS1hOverall` in the overall population and `r inline$medianPcrS1hDiabetes`, `r inline$medianPcrS1hCkd`, `r inline$medianPcrS1hAge65`, and `r inline$medianPcrS1hAny` for those with diabetes, `r CKD()`, age ≥ 65 years, and any of these conditions, respectively.
+Among US adults aged 40 to 79 years without clinical CVD, the estimated median (25^th^, 75^th^ percentiles) 10-year predicted ASCVD risk was `r inline$medianPcrOverall` in the overall population and `r inline$medianPcrDiabetes`, `r inline$medianPcrCkd`, `r inline$medianPcrAge65`, and `r inline$medianPcrAny` among those with diabetes, CKD, age ≥ 65 years, and any of these conditions, respectively (`r refer_to('tab_risk_overall')`; top panel).
+Among those with stage 1 hypertension, the estimated median (25^th^, 75^th^ percentiles) 10-year predicted ASCVD risk was `r inline$medianPcrS1hOverall` in the overall population and `r inline$medianPcrS1hDiabetes`, `r inline$medianPcrS1hCkd`, `r inline$medianPcrS1hAge65`, and `r inline$medianPcrS1hAny` for those with diabetes, CKD, age ≥ 65 years, and any of these conditions, respectively.
 
@@
 
-Among US adults aged 40 to 79 years, the estimated percentage (95% `r CI()`) with high `r ASCVD()` risk was `r inline$prevHighRiskOverall` (`r refer_to('tab_risk_overall')`; bottom panel).
-Among sub-groups with diabetes, `r CKD()`, age ≥ 65 years, or any of these conditions, `r inline$prevHighRiskDiabetes`, `r inline$prevHighRiskCkd`, `r inline$prevHighRiskAge65`, and `r inline$prevHighRiskAny` had high `r ASCVD()` risk, respectively.
-Among those with stage 1 hypertension, the estimated percentage (95% `r CI()`) with high `r ASCVD()` risk was `r inline$prevHighRiskS1hOverall` in the overall population and `r inline$prevHighRiskS1hDiabetes`, `r inline$prevHighRiskS1hCkd`, `r inline$prevHighRiskS1hAge65`, and `r inline$prevHighRiskS1hAny` for those with diabetes, `r CKD()`, age ≥ 65 years, or any of these conditions, respectively.
+Among US adults aged 40 to 79 years, the estimated percentage (95% CI) with high ASCVD risk was `r inline$prevHighRiskOverall` (`r refer_to('tab_risk_overall')`; bottom panel).
+Among sub-groups with diabetes, CKD, age ≥ 65 years, or any of these conditions, `r inline$prevHighRiskDiabetes`, `r inline$prevHighRiskCkd`, `r inline$prevHighRiskAge65`, and `r inline$prevHighRiskAny` had high ASCVD risk, respectively.
+Among those with stage 1 hypertension, the estimated percentage (95% CI) with high ASCVD risk was `r inline$prevHighRiskS1hOverall` in the overall population and `r inline$prevHighRiskS1hDiabetes`, `r inline$prevHighRiskS1hCkd`, `r inline$prevHighRiskS1hAge65`, and `r inline$prevHighRiskS1hAny` for those with diabetes, CKD, age ≥ 65 years, or any of these conditions, respectively.
 
@@
 
-Among US adults aged 40 to 79 years without high `r ASCVD()` risk, an estimated `r inline$propLowRiskOverall` had 10-year predicted `r ASCVD()` risk < 2.5% (`r refer_to('fig_hist_ovrl')`).
-Among subgroups with diabetes, `r CKD()`, age ≥ 65 years, and any of these conditions, an estimated `r inline$propLowRiskDiabetes`, `r inline$propLowRiskCkd`, `r inline$propLowRiskAge65`, and `r inline$propLowRiskAny` had a 10-year predicted `r ASCVD()` risk < 2.5%, respectively.
-Among those with stage 1 hypertension, an estimated `r inline$propLowRiskS1hOverall` had a 10-year predicted `r ASCVD()` risk < 2.5% (`r refer_to('fig_hist_stg1')`).
-Also, `r inline$propLowRiskS1hDiabetes`, `r inline$propLowRiskS1hCkd`, and `r inline$propLowRiskS1hAge65` of those with diabetes, CKD, and ≥ 65 years of age had a 10-year predicted `r ASCVD()` risk < 2.5%, respectively.
+Among US adults aged 40 to 79 years without high ASCVD risk, an estimated `r inline$propLowRiskOverall` had 10-year predicted ASCVD risk < 2.5% (`r refer_to('fig_hist_ovrl')`).
+Among subgroups with diabetes, CKD, age ≥ 65 years, and any of these conditions, an estimated `r inline$propLowRiskDiabetes`, `r inline$propLowRiskCkd`, `r inline$propLowRiskAge65`, and `r inline$propLowRiskAny` had a 10-year predicted ASCVD risk < 2.5%, respectively.
+Among those with stage 1 hypertension, an estimated `r inline$propLowRiskS1hOverall` had a 10-year predicted ASCVD risk < 2.5% (`r refer_to('fig_hist_stg1')`).
+Also, `r inline$propLowRiskS1hDiabetes`, `r inline$propLowRiskS1hCkd`, and `r inline$propLowRiskS1hAge65` of those with diabetes, CKD, and ≥ 65 years of age had a 10-year predicted ASCVD risk < 2.5%, respectively.
 
@@
 
-## Age-specific probability of having high `r ASCVD()` risk
+## Age-specific probability of having high ASCVD risk
 
-The estimated probability of having high `r ASCVD()` risk increased with older age and exceeded 50% at `r inline$ageHighRiskOvrlNoComorb` years for US adults without diabetes or `r CKD()`, compared with `r inline$ageHighRiskOvrlDiabetes` years for US adults with diabetes and `r inline$ageHighRiskOvrlCkd` years for US adults with CKD (`r refer_to('fig_risk_ovrl')`).
-Among US adults with stage 1 hypertension, the age at which the estimated probability of having high `r ASCVD()` risk exceeded 50% was `r inline$ageHighRiskS1hNoComorb`, `r inline$ageHighRiskS1hDiabetes`, and `r inline$ageHighRiskS1hCkd` years for US adults without diabetes or CKD, with diabetes, and with CKD, respectively (`r refer_to('fig_risk_stg1')`).
-The minimum age where the probability of high `r ASCVD()` risk exceeded 50% was not estimated for adults ≥ 65 years of age as the probability exceeded 50% at all ages above 65 years.
+The estimated probability of having high ASCVD risk increased with older age and exceeded 50% at `r inline$ageHighRiskOvrlNoComorb` years for US adults without diabetes or CKD, compared with `r inline$ageHighRiskOvrlDiabetes` years for US adults with diabetes and `r inline$ageHighRiskOvrlCkd` years for US adults with CKD (`r refer_to('fig_risk_ovrl')`).
+Among US adults with stage 1 hypertension, the age at which the estimated probability of having high ASCVD risk exceeded 50% was `r inline$ageHighRiskS1hNoComorb`, `r inline$ageHighRiskS1hDiabetes`, and `r inline$ageHighRiskS1hCkd` years for US adults without diabetes or CKD, with diabetes, and with CKD, respectively (`r refer_to('fig_risk_stg1')`).
+The minimum age where the probability of high ASCVD risk exceeded 50% was not estimated for adults ≥ 65 years of age as the probability exceeded 50% at all ages above 65 years.
 
@@
 
-In the current study, the majority of US adults aged 40 to 79 years with diabetes, `r CKD()`, age ≥ 65 years, and any of these conditions had high `r ASCVD()` risk, defined by a 10-year predicted `r ASCVD()` risk ≥ 10% or clinical CVD.
-Also, the majority of US adults with stage 1 hypertension who were ≥ 65 years of age had high `r ASCVD()` risk.
-However, a substantial proportion of US adults with stage 1 hypertension and diabetes or `r CKD()` did not have high `r ASCVD()` risk.
-Among US adults with `r CKD()` and without high `r ASCVD()` risk, approximately one-third had a 10-year predicted `r ASCVD()` risk < 2.5%.
-In contrast, over 80% of US adults aged ≥ 65 years without high `r ASCVD()` risk had a 10-year predicted `r ASCVD()` risk between 5% and 10%.
-The probability of having high `r ASCVD()` risk was age-dependent with over 50% of US adults with diabetes and `r CKD()` having high `r ASCVD()` risk at ages above `r inline$ageHighRiskOvrlDiabetes` and `r inline$ageHighRiskOvrlCkd` years, respectively.
+In the current study, the majority of US adults aged 40 to 79 years with diabetes, CKD, age ≥ 65 years, and any of these conditions had high ASCVD risk, defined by a 10-year predicted ASCVD risk ≥ 10% or clinical CVD.
+Also, the majority of US adults with stage 1 hypertension who were ≥ 65 years of age had high ASCVD risk.
+However, a substantial proportion of US adults with stage 1 hypertension and diabetes or CKD did not have high ASCVD risk.
+Among US adults with CKD and without high ASCVD risk, approximately one-third had a 10-year predicted ASCVD risk < 2.5%.
+In contrast, over 80% of US adults aged ≥ 65 years without high ASCVD risk had a 10-year predicted ASCVD risk between 5% and 10%.
+The probability of having high ASCVD risk was age-dependent with over 50% of US adults with diabetes and CKD having high ASCVD risk at ages above `r inline$ageHighRiskOvrlDiabetes` and `r inline$ageHighRiskOvrlCkd` years, respectively.
 
@@
 The current study estimates that about 15% of US adults aged 40 to 79 years have stage 1 hypertension.
-The 2017 `r ACC_AHA()` `r BP()` guideline recommends computing 10-year predicted `r ASCVD()` risk for all adults with hypertension who do not have clinical `r CVD()` [@whelton20182017].
-As many adults with stage 1 hypertension and diabetes or `r CKD()` do not have 10-year predicted `r ASCVD()` risk ≥ 10%, computing 10-year predicted `r ASCVD()` risk for adults with stage 1 hypertension can inform recommendations to initiate antihypertensive medication and inform patient-provider discussions on the potential benefits of treatment.
+The 2017 ACC/AHA BP guideline recommends computing 10-year predicted ASCVD risk for all adults with hypertension who do not have clinical CVD [@whelton20182017].
+As many adults with stage 1 hypertension and diabetes or CKD do not have 10-year predicted ASCVD risk ≥ 10%, computing 10-year predicted ASCVD risk for adults with stage 1 hypertension can inform recommendations to initiate antihypertensive medication and inform patient-provider discussions on the potential benefits of treatment.
 
@@
 
-Previous studies have shown that the use of predicted `r ASCVD()` risk in addition to `r BP()` can direct antihypertensive medication to adults likely to receive the largest risk reduction benefit [@colantonio20182017; @jaeger2019cardiovascular, @herrett2019eligibility].
-For example, in an analysis of the Reasons for Geographic and Racial Differences in Stroke study, those with stage 1 hypertension for whom initiation of antihypertensive medication __would have been__ recommended versus not recommended by the 2017 `r ACC_AHA()` `r BP()` guideline were roughly 6 times more likely to experience a `r CVD()` event over 8 years of follow-up [@colantonio20182017].
-Although a substantial proportion of US adults with stage 1 hypertension and diabetes or `r CKD()` did not have a high `r ASCVD()` risk in the current study, these subgroups were more likely to have high `r ASCVD()` risk compared to the overall US population with stage 1 hypertension, and may therefore still benefit from initiating antihypertensive medication.
+Previous studies have shown that the use of predicted ASCVD risk in addition to BP can direct antihypertensive medication to adults likely to receive the largest risk reduction benefit [@colantonio20182017; @jaeger2019cardiovascular, @herrett2019eligibility].
+For example, in an analysis of the Reasons for Geographic and Racial Differences in Stroke study, those with stage 1 hypertension for whom initiation of antihypertensive medication __would have been__ recommended versus not recommended by the 2017 ACC/AHA BP guideline were roughly 6 times more likely to experience a CVD event over 8 years of follow-up [@colantonio20182017].
+Although a substantial proportion of US adults with stage 1 hypertension and diabetes or CKD did not have a high ASCVD risk in the current study, these subgroups were more likely to have high ASCVD risk compared to the overall US population with stage 1 hypertension, and may therefore still benefit from initiating antihypertensive medication.
 
@@
 
-Previous randomized trials and meta-analyses have investigated whether lower `r BP()` goals reduce incident `r CVD()` risk in patients with diabetes, `r CKD()`, or older age.
-A randomized trial of patients with diabetes and baseline `r SBP()` < 140 mm Hg and `r DBP()` < 90 mm Hg found lower risk of stroke among participants with more intense `r BP()` treatment goals [@schrier2002effects].
-The Systolic Blood Pressure Intervention Trial compared an `r SBP()` treatment target of < 120 mm Hg to < 140 mm Hg among older adults (mean age of 68 years) without diabetes.
-Among participants with `r CKD()`, randomization to the lower `r SBP()` target reduced rates of major `r CVD()` events and all-cause death without evidence of effect modifications by `r CKD()` or deleterious effect on `r E_GFR()` or end stage renal disease [@cheung2017effects].
-In the overall population, those randomized to the lower `r SBP()` target experienced lower rates of incident fatal and nonfatal major `r CVD()` events as well as all-cause mortality [@sprint2015randomized].
-The trial did not examine stage 1 hypertension specifically, but found no evidence of a difference in treatment effect across baseline `r SBP()` groups and estimated a hazard ratio (95% `r CI()`) of 0.77 (0.57 - 1.03) comparing intensive to standard treatment for major `r CVD()` events among participants with `r SBP()` > 132 and < 145 mm Hg [@sprint2015randomized].
-A systematic review and meta-analysis of 123 studies with 613,815 participants found strong support for lowering `r SBP()` to < 130 mm Hg and providing antihypertensive medication to adults with diabetes, CKD, and various other comorbidities [@ettehad2016blood].
-Benefits associated with a `r SBP()` treatment goal of < 130 mm Hg have also been identified in several other meta-analyses [@bundy2017systolic; @reboussin2018systematic].
-Collectively, evidence from previous studies suggests that adults with hypertension and diabetes, `r CKD()` or ≥ 65 years of age may experience lower rates of `r CVD()` events by initiating antihypertensive medication with an `r SBP()` treatment goal of < 130 mm Hg versus < 140 mm Hg.
+Previous randomized trials and meta-analyses have investigated whether lower BP goals reduce incident CVD risk in patients with diabetes, CKD, or older age.
+A randomized trial of patients with diabetes and baseline SBP < 140 mm Hg and DBP < 90 mm Hg found lower risk of stroke among participants with more intense BP treatment goals [@schrier2002effects].
+The Systolic Blood Pressure Intervention Trial compared an SBP treatment target of < 120 mm Hg to < 140 mm Hg among older adults (mean age of 68 years) without diabetes.
+Among participants with CKD, randomization to the lower SBP target reduced rates of major CVD events and all-cause death without evidence of effect modifications by CKD or deleterious effect on estimated glomerular filtration rate or end stage renal disease [@cheung2017effects].
+In the overall population, those randomized to the lower SBP target experienced lower rates of incident fatal and nonfatal major CVD events as well as all-cause mortality [@sprint2015randomized].
+The trial did not examine stage 1 hypertension specifically, but found no evidence of a difference in treatment effect across baseline SBP groups and estimated a hazard ratio (95% CI) of 0.77 (0.57 - 1.03) comparing intensive to standard treatment for major CVD events among participants with SBP > 132 and < 145 mm Hg [@sprint2015randomized].
+A systematic review and meta-analysis of 123 studies with 613,815 participants found strong support for lowering SBP to < 130 mm Hg and providing antihypertensive medication to adults with diabetes, CKD, and various other comorbidities [@ettehad2016blood].
+Benefits associated with a SBP treatment goal of < 130 mm Hg have also been identified in several other meta-analyses [@bundy2017systolic; @reboussin2018systematic].
+Collectively, evidence from previous studies suggests that adults with hypertension and diabetes, CKD or ≥ 65 years of age may experience lower rates of CVD events by initiating antihypertensive medication with an SBP treatment goal of < 130 mm Hg versus < 140 mm Hg.
 
@@
 
-It has been suggested that most adults with diabetes, CKD, or ≥ 65 years of age have a 10-year predicted `r ASCVD()` risk ≥ 10% [@whelton20182017].
-Previous research has shown that diabetes, `r CKD()`, and older age are each associated with an increased risk for `r ASCVD()` events [@coresh2004evidence; @chronic2010association; @grundy1999diabetes; @lakatta2002age].
-Although the current study suggests that a high proportion of US adults with stage 1 hypertension and diabetes or `r CKD()` do not have a 10-year predicted `r ASCVD()` risk ≥ 10%, diabetes and `r CKD()` are associated with a high lifetime `r CVD()` risk [@lloyd2006prediction; @hippisley2010derivation].
-Age-specific estimates in the current study suggest that US adults with diabetes or `r CKD()` develop high `r ASCVD()` risk at a younger age than their counterparts without these conditions.
-Prior studies have also found that cumulative exposure to high `r BP()` is associated with increased `r CVD()` risk [@allen2014blood].
-Therefore, for younger adults with diabetes or `r CKD()`, early initiation of antihypertensive medication may be an important step towards lowering lifetime `r CVD()` risk.
+It has been suggested that most adults with diabetes, CKD, or ≥ 65 years of age have a 10-year predicted ASCVD risk ≥ 10% [@whelton20182017].
+Previous research has shown that diabetes, CKD, and older age are each associated with an increased risk for ASCVD events [@coresh2004evidence; @chronic2010association; @grundy1999diabetes; @lakatta2002age].
+Although the current study suggests that a high proportion of US adults with stage 1 hypertension and diabetes or CKD do not have a 10-year predicted ASCVD risk ≥ 10%, diabetes and CKD are associated with a high lifetime CVD risk [@lloyd2006prediction; @hippisley2010derivation].
+Age-specific estimates in the current study suggest that US adults with diabetes or CKD develop high ASCVD risk at a younger age than their counterparts without these conditions.
+Prior studies have also found that cumulative exposure to high BP is associated with increased CVD risk [@allen2014blood].
+Therefore, for younger adults with diabetes or CKD, early initiation of antihypertensive medication may be an important step towards lowering lifetime CVD risk.
 Estimating lifetime CVD risk may be useful when discussing the initiation of antihypertensive medication among young and middle-aged adults with diabetes or CKD.
@@
 The current study has a number of strengths.
-The design of `r NHANES()` allows its results to be weighted to provide results that are representative of the US population.
-Additionally, `r NHANES()` data are collected following a rigorous protocol by trained study staff.
-`r BP()` was measured three times following a standardized protocol.
+The design of NHANES allows its results to be weighted to provide results that are representative of the US population.
+Additionally, NHANES data are collected following a rigorous protocol by trained study staff.
+BP was measured three times following a standardized protocol.
 However, the results of this study should be considered in the context of known and potential limitations.
-`r NHANES()` participants completed only one visit and guidelines recommend using the mean `r BP()` averaged over 2 or more visits.
-In addition, the `r ACC_AHA()` `r BP()` guideline recommends confirmation of office hypertension by measurement of out-of-office `r BP()`s.
-Additionally, since only one measurement of serum creatinine and urine albuminuria were available, `r CKD()` status may have been mis-classified in some adults.
-A total of `r table_value(sum(current_analysis$data$bp_cat == 'Stage 1 hypertension'))` participants had stage 1 hypertension, and some subgroups of this population based on diabetes, `r CKD()`, and ≥ 65 years of age were small.
+NHANES participants completed only one visit and guidelines recommend using the mean BP averaged over 2 or more visits.
+In addition, the ACC/AHA BP guideline recommends confirmation of office hypertension by measurement of out-of-office BPs.
+Additionally, since only one measurement of serum creatinine and urine albuminuria were available, CKD status may have been mis-classified in some adults.
+A total of `r table_value(sum(current_analysis$data$bp_cat == 'Stage 1 hypertension'))` participants had stage 1 hypertension, and some subgroups of this population based on diabetes, CKD, and ≥ 65 years of age were small.
 
@@
 
-While the majority of US adults with diabetes, `r CKD()`, or age ≥ 65 years had high `r ASCVD()` risk, many with stage 1 hypertension and diabetes or `r CKD()` did not.
-Results from the current study support computing 10-year predicted `r ASCVD()` risk for all adults with hypertension, as recommended by the 2017 `r ACC_AHA()` `r BP()` guideline.
+While the majority of US adults with diabetes, CKD, or age ≥ 65 years had high ASCVD risk, many with stage 1 hypertension and diabetes or CKD did not.
+Results from the current study support computing 10-year predicted ASCVD risk for all adults with hypertension, as recommended by the 2017 ACC/AHA BP guideline.
 
@@
 
+__Acknowledgments:__ None.
+
+__Sources of Funding:__
+
+Drs Muntner and Jaeger receive support through grant R01HL144773 from the National Heart, Lung, and Blood Institute and grant 15SFRN2390002 from the American Heart Association.
+
+Dr. Hardy receives support through R01HL139716 from the National Heart, Lung, and Blood Institute.
+
+Dr. Bundy receives support through K12HD043451 from the Eunice Kennedy Shriver National Institute of Child Health and Human Development.
+
+Dr. Whelton receives support through a Centers of Research Excellence grant from the National Institute of General Medical Sciences, P20GM109036.
+
+__Disclosures:__
+
+BCJ has nothing to disclose. 
+SS has nothing to disclose.
+STH has nothing to disclose.
+OPA has nothing to disclose. 
+JDB has nothing to disclose.
+PM received grant funding and consulting fees from Amgen Inc., unrelated to the current manuscript.
+PKW has nothing to disclose.
+
+\newpage
+
 # REFERENCES

### 2021-03-18 R/compile_report.R

@@ -363,11 +363,11 @@ compile_report <- function(exams,
     reference = 'tab_risk_overall'
   )
 
-  tbls_supp %<>% add_row(
-    object = list(.tbls_risk$supplement),
-    caption = "Median 10-year predicted risk for atherosclerotic cardiovascular disease using an updated Pooled Cohort risk prediction equation and proportion of US adults with high atherosclerotic cardiovascular disease risk overall and for subgroups defined by diabetes, chronic kidney disease, and \u2265 65 years of age, stratified by blood pressure categories based on the 2017 American College of Cardiology / American Heart Association blood pressure guideline.",
-    reference = 'tab_risk_supplement'
-  )
+  # tbls_supp %<>% add_row(
+  #   object = list(.tbls_risk$supplement),
+  #   caption = "Median 10-year predicted risk for atherosclerotic cardiovascular disease using an updated Pooled Cohort risk prediction equation and proportion of US adults with high atherosclerotic cardiovascular disease risk overall and for subgroups defined by diabetes, chronic kidney disease, and \u2265 65 years of age, stratified by blood pressure categories based on the 2017 American College of Cardiology / American Heart Association blood pressure guideline.",
+  #   reference = 'tab_risk_supplement'
+  # )
 
   # table s1: characteristics for SPs with stage 1 hypertension ----
 

### 2021-03-18 _drake.R

@@ -14,7 +14,8 @@ drake_config(
   seed = 329730,
   prework = {
 
-    windowsFonts(Times = 'Times New Roman')
+    if(Sys.info()['sysname'] == 'Windows')
+      windowsFonts(Times = 'Times New Roman')
 
     rspec <- round_spec() %>%
       round_using_decimal(digits = 1)

### 2021-03-18 packages.R

@@ -46,3 +46,4 @@ conflicted::conflict_prefer('summarize', 'dplyr')
 conflicted::conflict_prefer("gather",    "tidyr")
 conflicted::conflict_prefer("set_names", "purrr")
 conflicted::conflict_prefer("make",      "drake")
+conflicted::conflict_prefer("expand", "tidyr")

### 2021-03-23 doc/ACCAHA_BP_groups.Rmd
seminar update

@@
 csl: ccqo.csl
+always_allow_html: true
 output: 
@@
 ```{r setup, include=FALSE}
-
-# misc functions for the paper
 

### 2021-03-23 doc/seminar/ACCAHA_BP_groups.Rmd
seminar update

---
title: "Predicted cardiovascular risk for adults in the US with diabetes, chronic kidney disease, and ≥ 65 years of age"
subtitle: "A case study in reproducible and agile research"  
author: "Byron C. Jaeger, PhD"
date: 'March 25, 2021'
always_allow_html: true
output:
  xaringan::moon_reader:
    lib_dir: libs
    css: xaringan-themer.css
    nature:
      highlightStyle: github
      highlightLines: true
      countIncrementalSlides: false
---

```{r, include=FALSE, warning=FALSE}

knitr::opts_chunk$set(echo = FALSE,
                      message = FALSE,
                      warning = FALSE)

options(htmltools.dir.version = FALSE)

library(xaringanthemer)

style_duo_accent(
  primary_color = "#006341",
  secondary_color = "#CC8A00",
  inverse_header_color = "#FFFFFF"
)

loadd(exams,
      current_analysis,
      inline,
      report,
      fasted_hrs_lower,
      fasted_hrs_upper,
      gluc_cutpoint_fasted,
      gluc_cutpoint_fed,
      hba1c_cutpoint,
      egfr_cutpoint,
      acr_cutpoint,
      fig_central_illustration,
      fig_hist,
      fig_risk_ovrl_bnry,
      fig_risk_stg1_bnry)

nhanes_years <- exams %>%
  map_chr(~glue("{.x}-{.x+1}")) %>%
  glue_collapse(sep = ', ', last = ', and ')

```

## Overview

__Research__

- The 2017 ACC/AHA Blood Pressure Guideline

- The National Health and Nutrition Examination Survey

- Predicted risk in blood pressure groups

- Conclusions

__Reproducibility__

- What is reproducible research?

- Demo

---
class: inverse, center, middle

# The 2017 ACC/AHA Blood Pressure Guideline

---
layout: true

## 2017 ACC/AHA Blood Pressure Guideline

The 2017 ACC/AHA (American College of Cardiology/American Heart Association) blood pressure guideline<sup>1</sup> recommends using blood pressure levels and 10-year predicted risk for ASCVD<sup>2</sup> (atherosclerotic cardiovascular disease) to guide clinical decisions related to the management and treatment of blood pressure.

<br/>

.footnote[
<sup>1</sup>The 2017 ACC AHA guideline is available [here](https://www.ahajournals.org/doi/pdf/10.1161/HYP.0000000000000065) <br/>
<sup>2</sup> Using the ACC/AHA Pooled Cohort Equations, which are available [here](http://tools.acc.org/ASCVD-Risk-Estimator-Plus/#!/calculate/estimate/)
]

---

__Normal blood pressure__: systolic < 120 mm Hg and diastolic < 80 mm Hg

- Promote optimal lifestyle habits,

- reassess blood pressure in 1 year.

---

__Elevated blood pressure__: systolic 120-129 mm Hg and diastolic < 80 mm Hg

- Recommend nonpharmalogical therapy,

- reassess blood pressure in 3-6 months.

---

<span style="color:orange"><b>Stage 1 hypertension</b></span>: systolic 130-139 mm Hg or diastolic 80-89 mm Hg

- If no clinical CVD and predicted 10-year ASCVD risk < 10%,

    + Recommend nonpharmalogical therapy

    + Reassess blood pressure in 3-6 months

---

<span style="color:orange"><b>Stage 1 hypertension</b></span>: systolic 130-139 mm Hg or diastolic 80-89 mm Hg

- If clinical CVD or predicted 10-year ASCVD risk ≥ 10%,

    + Recommend nonpharmalogical therapy and antihypertensive medication

    + Reassess blood pressure in 1 month

---

<span style="color:red"><b>Stage 2 hypertension</b></span>: systolic ≥ 140 mm Hg or diastolic ≥ 90 mm Hg

- Recommend nonpharmalogical therapy and antihypertensive medication (consider 2 classes)

- Reassess blood pressure in 1 month

---
layout: false

## 2017 ACC/AHA Blood Pressure Guideline

__High ASCVD risk defn__: clinical CVD or __predicted 10-year ASCVD risk ≥ 10%__

As a matter of practical convenience, adults with stage 1 hypertension and

- diabetes mellitus,

- CKD (chronic kidney disease), or

- ≥ 65 years of age

are considered to have high ASCVD risk by the guideline.

This recommendation was based on the assumption that most adults with diabetes, CKD, or ≥ 65 years of age are likely to have a 10-year predicted ASCVD risk ≥ 10% and data from surveys suggesting most clinicians, including cardiologists, do not assess ASCVD risk using recommended risk prediction tools.

.footnote[
<sup>1</sup>See Sections 9.3, 9.6, and 10.3 of  [the guideline](https://www.ahajournals.org/doi/pdf/10.1161/HYP.0000000000000065)
]

---

## The current analysis

__Aims__:

- Estimate the proportion of US adults with diabetes, CKD, or ≥ 65 years of age that have high ASCVD risk (defined by 10-year predicted risk for ASCVD ≥ 10% or clinical CVD).

- Examine these proportions for all US adults and among those with stage 1 hypertension.

To accomplish these aims, we analyzed data from `r english(length(exams))` cycles of NHANES (the National Health and Nutrition Examination Survey).

---
class: inverse, center, middle

# NHANES

---

## NHANES

NHANES was designed to assess the health and nutritional status of the non-institutionalized US population and was conducted by the National Center for Health Statistics of the Centers for Disease Control and Prevention

--

Since 1999-2000, NHANES has been conducted in two-year cycles using a multistage probability sampling design to select participants.

--

Each cycle is independent with different participants recruited.

---

## NHANES; data collection

Data were collected during an in-home interview and a study visit completed at a mobile examination center.

--

Standardized questionnaires were used to assess participants' age, sex, race/ethnicity, smoking habits, medical history, and use of antihypertensive medication.

--

Medical history included questions about whether the participant had been told by a doctor or other health professional that they had a heart attack, coronary heart disease, stroke, or heart failure.

--

__For the current analysis__,

- Clinical CVD was defined as answering yes to ≥1 CVD question.

- Ten-year predicted ASCVD risk was calculated using the Pooled Cohort risk equations for participants without clinical CVD.

- High ASCVD risk was defined as having a 10-year predicted ASCVD risk ≥ 10% or clinical CVD.

---

## NHANES; blood pressure

The same protocol was followed to measure blood pressure in each NHANES cycle.

--

After survey participants had rested 5 minutes, their blood pressure was measured by a trained physician using a mercury sphygmomanometer and an appropriately sized cuff.

--

Three blood pressure measurements were obtained at 30 second intervals. The mean of all three measurements was used to define systolic and diastolic blood pressure.

--

__For the current analysis__, Participants not taking antihypertensive medication were grouped into four non-overlapping categories based on the 2017 ACC/AHA BP guideline: normal blood pressure, elevated blood pressure, stage 1 hypertension, and stage 2 hypertension. Participants taking antihypertensive medication were placed in a fifth category.

---

## NHANES; current analysis

```{r}

# some inline results for the exclusion paragraph below

rspec <- round_spec() %>% 
  round_using_magnitude()

n_age_40_to_79 <- current_analysis$tbl %>% 
  filter(label == 'Aged 40-79 years') %>% 
  pull(sample_size) %>% 
  table_value(rspec = rspec)

n_bp_too_low <- current_analysis$tbl %>% 
  filter(str_detect(label, '^3 or more systolic and diastolic')) %>% 
  pull(n_removed) %>% 
  table_value(rspec = rspec)

n_missing_pcr <- current_analysis$tbl %>% 
  filter(str_detect(label, '^Complete data for variables')) %>% 
  pull(n_removed) %>% 
  table_value(rspec = rspec)

n_final <- table_value(min(current_analysis$tbl$sample_size))

```

For the current analysis, the <span style="color:purple"><b>`r english(length(exams))`</b></span> cycles conducted in <span style="color:purple"><b>`r nhanes_years`</b></span> were combined.

--

Adults aged 40 to 79 years of age who completed the NHANES interview and examination were included (n = <span style="color:purple"><b>`r n_age_40_to_79`</b></span>). Participants < 40 or > 79 years of age were not included because use of the Pooled Cohort risk equations is not recommended in these age ranges.

--

Participants who did not have three systolic and diastolic blood pressure measurements (n = <span style="color:purple"><b>`r n_bp_too_low`</b></span>) and those who were missing information on age, race, sex, total and high-density lipoprotein cholesterol, smoking status, diabetes, or CKD status (n = <span style="color:purple"><b>`r n_missing_pcr`</b></span>) were also excluded.

--

After these exclusions, a total of <span style="color:purple"><b>`r n_final`</b></span> participants were included in the analysis.

---

## NHANES; statistical analysis (highlights)

Step 1. The percentage of participants with high ASCVD risk was estimated overall and among sub-groups defined by diabetes, CKD, and age ≥ 65 years

--

Step 2. The percentage of US adults in each of the five categories based on blood pressure and antihypertensive medication use was computed. Step 1. was also repeated in each of these blood pressure / medication categories.

--

Step 3. To assess the extent to which participants with a 10-year predicted ASCVD risk < 10% were close to the 10% threshold, the distribution of 10-year predicted ASCVD risk between 0 and 10% was visualized using bar plots.

--

Step 4. The probability of having high ASCVD risk was estimated for each year of age from 40 to 79 years using logistic regression

---
class: inverse, center, middle

# Predicted risk in blood pressure groups

---

## Results

Among US adults aged 40-79 years, the estimated percentage (95% CI [confidence interval]) with high ASCVD risk was <span style="color:purple"><b>`r inline$prevHighRiskOverall`</b></span>.

Among sub-groups, the estimated percentage (95% CI) with high ASCVD risk was:

- diabetes: <span style="color:purple"><b>`r inline$prevHighRiskDiabetes`</b></span>.
- CKD: <span style="color:purple"><b>`r inline$prevHighRiskCkd`</b></span>.
- age ≥ 65 years: <span style="color:purple"><b>`r inline$prevHighRiskAge65`</b></span>.
- any of these conditions:  <span style="color:purple"><b>`r inline$prevHighRiskAny`</b></span>.

__Interpretation__ These data support the assumption that most adults with diabetes, CKD, or ≥ 65 years of age are likely to have high ASCVD risk. __However__, this assumption only has clinical relevance for adults with stage 1 hypertension. (Why?)

---

Distribution of blood pressure categories among US adults.

```{r, fig.width=8, fig.height=5, dpi=300}

fig_central_illustration

```

__Interpretation__:  Among US adults with stage 1 hypertension, the proportion with high ASCVD risk and diabetes or CKD was lower than expected.

---

Distribution of 10-year predicted risk for ASCVD among US adults with predicted risk < 10%

```{r, fig.width=8, fig.height=4.9, dpi=300}

fig_hist$fig_2row$ovrl

```

__Interpretation__: Many adults with age 65+ years are close to the 10% threshold, but adults with diabetes or CKD do not show the same pattern.

---

Distribution of 10-year predicted risk for ASCVD among US adults with stage 1 hypertension and predicted risk < 10%

```{r, fig.width=8, fig.height=4.9, dpi=300}

fig_hist$fig_2row$stg1

```

__Interpretation__: A surprising amount of adults with stage 1 hypertension and CKD or diabetes have a 10-year predicted risk for ASCVD < 5%.

---

Estimated probability of high ASCVD risk for US adults with diabetes, with CKD, and without diabetes or CKD.

```{r, fig.width=8, fig.height=4.9, dpi=300}

fig_risk_ovrl_bnry + 
  theme(panel.grid = element_blank(),
        legend.position = c(0.20, 0.85),
        legend.background = element_rect(fill=alpha('white', 0.0)))

```

__Interpretation__: High ASCVD risk probability reaches 50% for adults with CKD or diabetes sooner than adults without these conditions.

---

Estimated probability of high ASCVD risk for US adults with __stage 1 hypertension and__ with diabetes, with CKD, and without diabetes or CKD.

```{r, fig.width=8, fig.height=4.9, dpi=300}

fig_risk_stg1_bnry + 
  theme(panel.grid = element_blank(),
        legend.position = c(0.20, 0.85),
        legend.background = element_rect(fill=alpha('white', 0.0)))

```

__Interpretation__: High ASCVD risk probability reaches 50% for adults __with diabetes__ sooner than adults without diabetes.

---
class:inverse, center, middle

# Conclusions

---

## Conclusions

While the majority of US adults with diabetes, CKD, or age ≥ 65 years had high ASCVD risk, many with stage 1 hypertension and diabetes or CKD did not.

Results from the current study do not support assuming 10-year CVD risk is high for all adults with stage 1 hypertension and CKD or diabetes.

Results from the current study do support computing 10-year predicted ASCVD risk for all adults with hypertension, as recommended by the 2017 ACC/AHA BP guideline.

---
class: inverse, center, middle

# What is reproducible research?

---

## What is reproducible research?

__Definition__: a software platform and set of procedures that permit the reader of a paper to see the entire processing trail from the raw data and code to figures and tables.<sup>1,2</sup>

--

According to a U.S. National Science Foundation subcommittee on replicability in science, “reproducibility refers to the ability of a researcher to duplicate the results of a prior study using the same materials as were used by the original investigator. That is, a second researcher might use the same raw data to build the same analysis files and implement the same statistical analysis in an attempt to yield the same results... Reproducibility is a minimum necessary condition for a finding to be believable and informative.”

.footnote[
<sup>1</sup>Claerbout, Jon F., and Martin Karrenbach. "Electronic documents give reproducible research a new meaning." SEG Technical Program Expanded Abstracts 1992. Society of Exploration Geophysicists, 1992. 601-604.<br/><br/>
<sup>2</sup>Goodman, Steven N., Daniele Fanelli, and John PA Ioannidis. "What does research reproducibility mean?." Science translational medicine 8.341 (2016): 341ps12-341ps12.
]

---

### 2021-03-23 R/plan.R

@@ -148,7 +148,7 @@ the_plan <- drake_plan(
 
   qts = seq(0.001, 0.999, by = 0.0001),
 
-  fig_text = element_text(family = 'Times',
+  fig_text = element_text(#family = 'Times',
                           size = 12,
                           color = 'black'),
 
@@ -191,8 +191,8 @@ the_plan <- drake_plan(
     tbl_risk_overall,
     tbl_risk_overall_supp,
     current_analysis$tbl,
-    fig_hist$ovrl,
-    fig_hist$stg1,
+    fig_hist$fig_3row$ovrl,
+    fig_hist$fig_3row$stg1,
     fig_risk_ovrl_bnry,
     fig_risk_stg1_bnry,
     risk_10yr = risk_10yr,
@@ -205,6 +205,13 @@ the_plan <- drake_plan(
     command = {
       rmarkdown::render(knitr_in("doc/ACCAHA_BP_groups.Rmd"))
       file_out("doc/ACCAHA_BP_groups.docx")
+    }
+  ),
+
+  seminar = target(
+    command = {
+      rmarkdown::render(knitr_in("doc/seminar/ACCAHA_BP_groups.Rmd"))
+      file_out("doc/seminar/ACCAHA_BP_groups.html")
     }
   ),
 

### 2021-03-23 R/visualize_risk_bnry.R

@@ -119,7 +119,7 @@ visualize_risk_bnry <- function(risk_models,
       nudge_x = nudge_x,
       nudge_y = nudge_y,
       show.legend = FALSE,
-      family = 'Times',
+      #family = 'TT Times New Roman',
       mapping = aes(x = cpoint,
                     y = est,
                     label = paste0(round(cpoint, 0),'*'))

### 2021-03-23 R/visualize_risk_hist.R

@@ -54,14 +54,15 @@ visualize_risk_hist <- function(design, qts, fig_text) {
 
   # to make separate figures
 
-  .hist %>%
+  .hist_3row <- .hist %>%
     split(f = .$subpop) %>%
     map(
       ~ ggplot(.x) +
         aes(x = x, y = perc_val, label = perc_lab) +
         geom_bar(stat = 'identity', fill = 'grey80',
                  color = 'grey80', alpha = 0.50) +
-        geom_text(vjust = -1, family = 'Times') +
+        geom_text(vjust = -1) +
+                  #family = 'Times'
         theme_bw() +
         theme(panel.grid = element_blank(),
               text = fig_text,
@@ -78,6 +79,34 @@ visualize_risk_hist <- function(design, qts, fig_text) {
     )
 
 
+  .hist_2row <- .hist %>%
+    filter(!str_detect(panel, ',')) %>%
+    droplevels() %>%
+    split(f = .$subpop) %>%
+    map(
+      ~ ggplot(.x) +
+        aes(x = x, y = perc_val, label = perc_lab) +
+        geom_bar(stat = 'identity', fill = 'grey80',
+                 color = 'grey80', alpha = 0.50) +
+        geom_text(vjust = -1) +
+        #family = 'Times'
+        theme_bw() +
+        theme(panel.grid = element_blank(),
+              text = fig_text,
+              axis.text = fig_text,
+              legend.text = fig_text) +
+        scale_x_continuous(labels = percent) +
+        scale_y_continuous(labels = percent,
+                           limits = c(0,1),
+                           breaks = c(0, 0.25, 0.50, 0.75, 1),
+                           expand = c(0,0)) +
+        labs(x = 'Predicted 10-year risk for atherosclerotic cardiovascular disease, %',
+             y = 'Estimated % of US adults*') +
+        facet_wrap(~panel, ncol = 2, scales = 'free')
+    )
+
+  list(fig_2row = .hist_2row,
+       fig_3row = .hist_3row)
 
   # to make it all go into one figure
   # ggplot(.hist) +

### 2021-03-23 _drake.R

@@ -14,9 +14,6 @@ drake_config(
   seed = 329730,
   prework = {
 
-    if(Sys.info()['sysname'] == 'Windows')
-      windowsFonts(Times = 'Times New Roman')
-
     rspec <- round_spec() %>%
       round_using_decimal(digits = 1)
 

### 2021-03-23 packages.R
packages for seminar

@@ -32,7 +32,10 @@ pacman::p_load(
   english,
   officer,
   officedown,
-  Hmisc
+  Hmisc,
+  xaringan,
+  xaringanthemer,
+  showtext
 )
 
 pacman::p_load_gh('bcjaeger/PooledCohort', update = FALSE)

### 2021-03-24 docs/index.Rmd
getting slides online

--- 2021-03-23 doc/seminar/ACCAHA_BP_groups.Rmd
@@
 - High ASCVD risk was defined as having a 10-year predicted ASCVD risk ≥ 10% or clinical CVD.
+
+---
+
+## NHANES; data collection
+
+Data were collected during an in-home interview and a study visit completed at a mobile examination center.
+
+Blood and urine samples were collected during the medical examination. Serum creatinine, serum glucose and glycated hemoglobin were measured using standard methods.
+
+Estimated glomerular filtration rate was calculated using the CKD Epidemiology Collaboration equation.
+Urinary albumin and creatinine levels were measured and used to calculate the albumin-to-creatinine ratio.
+
+--
+
+__For the current analysis__,
+
+- Diabetes was defined by fasting plasma glucose ≥ <span style="color:purple"><b>`r gluc_cutpoint_fasted`</b></span> mg/dL (≥ <span style="color:purple"><b>`r gluc_cutpoint_fed`</b></span> mg/dL for those who were not fasting), glycated hemoglobin ≥ <span style="color:purple"><b>`r hba1c_cutpoint`</b></span>%, or self-reported use of insulin or oral glucose lowering medication
+
+- CKD was defined by an estimated glomerular filtration rate < <span style="color:purple"><b>`r egfr_cutpoint`</b></span> ml/min/1.73m<sup>2</sup> or an albumin-to-creatinine ratio ≥ <span style="color:purple"><b>`r acr_cutpoint`</b></span> mg/g.
 
@@
 ---
+class: inverse, center, middle
+
+# Demo

### 2021-03-24 R/plan.R

@@ -210,7 +210,7 @@ the_plan <- drake_plan(
 
   seminar = target(
     command = {
-      rmarkdown::render(knitr_in("doc/seminar/ACCAHA_BP_groups.Rmd"))
+      rmarkdown::render(knitr_in("docs/index.Rmd"))
       file_out("doc/seminar/ACCAHA_BP_groups.html")
     }
   ),

### 2021-04-15 docs/index.Rmd
no longer ignore html
add bp figs

@@
 style_duo_accent(
-  primary_color = "#006341",
-  secondary_color = "#CC8A00",
-  inverse_header_color = "#FFFFFF"
+  primary_color = "#1E6B52",
+  secondary_color = "#000000",
+  inverse_header_color = "#CFC580"
 )
@@
 
-__Normal blood pressure__: systolic < 120 mm Hg and diastolic < 80 mm Hg
+<span style="color:green"><b> Normal blood pressure</b></span>: systolic < 120 mm Hg and diastolic < 80 mm Hg
 
@@
 
-__Elevated blood pressure__: systolic 120-129 mm Hg and diastolic < 80 mm Hg
+<span style="color:blue"><b> Elevated blood pressure</b></span>: systolic 120-129 mm Hg and diastolic < 80 mm Hg
 
@@
 layout: false
+
+```{r fig.width=8, fig.height=6, dpi=300}
+
+p1 <- current_analysis$data %>%
+  filter(bp_cat != 'Taking antihypertensive medication') %>%
+  ggplot() +
+  aes(x = bp_sys_mmhg, y = bp_dia_mmhg, col = bp_cat) +
+  geom_point() +
+  scale_color_manual(values = c("olivedrab3",
+                                "darkturquoise",
+                                "orange",
+                                "red")) +
+  theme_bw() +
+  theme(panel.grid.minor = element_blank(),
+        legend.position = 'top') +
+  scale_x_continuous(breaks = c(120, 130, 140)) +
+  scale_y_continuous(breaks = c(80, 90)) +
+  labs(y = 'Diastolic blood pressure, mm Hg',
+       x = 'Systolic blood pressure, mm Hg',
+       color = '') +
+  guides(colour = guide_legend(override.aes = list(size = 8)))
+
+xlimits <- ggplot_build(p1)$layout$panel_scales_x[[1]]$range$range
+ylimits <- ggplot_build(p1)$layout$panel_scales_y[[1]]$range$range
+
+p1
+
+```
+
+---
+
+```{r fig.width=8, fig.height=6, dpi=300}
+
+current_analysis$data %>%
+  filter(bp_cat == 'Stage 1 hypertension') %>%
+  mutate(
+    high_ascvd_risk = if_else(
+      ever_had_ascvd == 'yes' | pcr_highrisk == 'yes',
+      'High ASCVD risk',
+      'Not high risk'
+    )
+  ) %>% 
+  ggplot() +
+  aes(x = bp_sys_mmhg, y = bp_dia_mmhg, col = high_ascvd_risk) +
+  geom_point() +
+  scale_color_manual(values = c("red", "orange")) +
+  theme_bw() +
+  theme(panel.grid.minor = element_blank(),
+        legend.position = 'top') +
+  scale_x_continuous(breaks = c(120, 130, 140), limits = xlimits) +
+  scale_y_continuous(breaks = c(80, 90), limits = ylimits) +
+  labs(y = 'Diastolic blood pressure, mm Hg',
+       x = 'Systolic blood pressure, mm Hg',
+       color = '') +
+  guides(colour = guide_legend(override.aes = list(size = 8)))
+
+```
+
+---
 

### 2021-04-15 R/plan.R

@@ -211,7 +211,7 @@ the_plan <- drake_plan(
   seminar = target(
     command = {
       rmarkdown::render(knitr_in("docs/index.Rmd"))
-      file_out("doc/seminar/ACCAHA_BP_groups.html")
+      file_out("docs/index.html")
     }
   ),
 

### 2021-06-09 doc/ACCAHA_BP_groups.Rmd
add bp figs
dropped reference to sections of ACCAHA GL

@@
 ---
-title: "Predicted cardiovascular risk for US adults with diabetes, chronic kidney disease, and \u2265 65 years of age overall and with stage 1 hypertension"
+title: "Predicted cardiovascular risk for US adults with diabetes, chronic kidney disease, and \u226565 years of age"
 bibliography: refs.bib
-csl: ccqo.csl
+csl: joh.csl
 always_allow_html: true
@@
   officedown::rdocx_document:
-    reference_docx: style_manuscript_times_new_roman_lines.docx
+    reference_docx: style_manuscript_times_new_roman.docx
 ---
@@
 ```{r setup, include=FALSE}
+
+# source("_drake.R")
 
@@
 
-__Short title__: Predicted cardiovascular risk for US adults
+__Short title__: Cardiovascular risk for US adults
 
@@
 
-__Total word count including the title page, abstract, text, references, tables, and figures legends__:
+__Word count (including references, but not tables and legends)__: 3837
+
+__number of tables__: 4 (3 main tables; 1 supplemental table)
+
+__number of figures__: 5 (2 main figures, 3, supplemental figues)
+
+__number of supplementary digital content files__: 0
+
+\newpage
+
+__Sources of Funding:__
+
+Drs Muntner and Jaeger receive support through grant R01HL144773 from the National Heart, Lung, and Blood Institute and grant 15SFRN2390002 from the American Heart Association.
+
+Dr. Hardy receives support through R01HL139716 from the National Heart, Lung, and Blood Institute.
+
+Dr. Bundy receives support through K12HD043451 from the Eunice Kennedy Shriver National Institute of Child Health and Human Development.
+
+Dr. Whelton receives support through a Centers of Research Excellence grant from the National Institute of General Medical Sciences, P20GM109036.
+
+__Disclosures:__
+
+BCJ has nothing to disclose. 
+SS has nothing to disclose.
+STH has nothing to disclose.
+OPA has nothing to disclose. 
+JDB has nothing to disclose.
+PM received grant funding and consulting fees from Amgen Inc., unrelated to the current manuscript.
+PKW has nothing to disclose.
 
@@
 __Background:__ The 2017 American College of Cardiology/American Heart Association blood pressure (BP) guideline recommends using 10-year predicted atherosclerotic cardiovascular disease (ASCVD) risk to guide decisions to initiate antihypertensive medication.
-Adults with stage 1 hypertension and diabetes mellitus, chronic kidney disease (CKD), or aged ≥65 years are considered to have high CVD risk by the guideline and initiation of antihypertensive medication is recommended.
-This recommendation assumes that most adults with diabetes, CKD, or aged ≥65 years have 10-year predicted ASCVD risk ≥10%.
 
 __Methods:__ We included adults aged 40-79 years from the National Health and Nutrition Examination Survey `r min(exams)`-`r max(exams)+1` (n=`r table_value(nrow(current_analysis$data))`).
-We computed 10-year predicted ASCVD risk using the Pooled Cohort risk equations and clinical CVD was self-reported.
+We computed 10-year predicted ASCVD risk using the Pooled Cohort risk equations.
+Clinical CVD was self-reported.
 Analyses were conducted overall and among those with stage 1 hypertension, defined by a mean systolic BP of 130-139 mm Hg or diastolic BP of 80-89 mm Hg.
@@
 __Key words__: Atherosclerotic cardiovascular disease, blood pressure, diabetes, chronic kidney disease, risk prediction
+\newpage
+
+# CONDENSED ABSTRACT
+
+The 2017 American College of Cardiology/American Heart Association blood pressure (BP) guideline recommends using atherosclerotic cardiovascular disease (ASCVD) risk to guide decisions to initiate antihypertensive medication.
+Using National Health and Nutrition Examination Survey `r min(exams)`-`r max(exams)+1` data, it was estimated that `r no_ci(inline$prevHighRiskS1hDiabetes)`, `r no_ci(inline$prevHighRiskS1hCkd)`, and `r no_ci(inline$prevHighRiskS1hAge65)` of US adults with stage 1 hypertension and diabetes, chronic kidney disease and age ≥65 years had high ASCVD risk defined by 10-year predicted ASCVD risk ≥10% or clinical CVD.
+Predicted 10-year ASCVD risk should be calculated for all adults with stage 1 hypertension and without clinical CVD as many are not at high risk for ASCVD.
 
@@
 Additionally, as a matter of practical convenience, adults with stage 1 hypertension and diabetes mellitus, chronic kidney disease (CKD), or ≥ 65 years of age are considered to have high CVD risk by the guideline and initiation of antihypertensive medication is recommended.
-This recommendation, written in Sections 9.3, 9.6, and 10.3 of the guideline, was based on the assumption that the vast majority of adults with diabetes, CKD, or ≥ 65 years of age are likely to have a 10-year predicted ASCVD risk ≥ 10% and the knowledge that surveys suggest most clinicians, including cardiologists, do not assess CVD risk using recommended risk prediction tools [@whelton20182017; @shillinglaw2012use].
+This recommendation was based on the assumption that the vast majority of adults with diabetes, CKD, or ≥ 65 years of age are likely to have a 10-year predicted ASCVD risk ≥ 10% and the knowledge that surveys suggest most clinicians, including cardiologists, do not assess CVD risk using recommended risk prediction tools [@whelton20182017; @shillinglaw2012use].
 
@@
 
-__Sources of Funding:__
-
-Drs Muntner and Jaeger receive support through grant R01HL144773 from the National Heart, Lung, and Blood Institute and grant 15SFRN2390002 from the American Heart Association.
-
-Dr. Hardy receives support through R01HL139716 from the National Heart, Lung, and Blood Institute.
-
-Dr. Bundy receives support through K12HD043451 from the Eunice Kennedy Shriver National Institute of Child Health and Human Development.
-
-Dr. Whelton receives support through a Centers of Research Excellence grant from the National Institute of General Medical Sciences, P20GM109036.
-
-__Disclosures:__
-
-BCJ has nothing to disclose. 
-SS has nothing to disclose.
-STH has nothing to disclose.
-OPA has nothing to disclose. 
-JDB has nothing to disclose.
-PM received grant funding and consulting fees from Amgen Inc., unrelated to the current manuscript.
-PKW has nothing to disclose.
-
 \newpage

### 2021-06-09 doc/JoH submission/reviewer_response/reviewer_response.Rmd
JoH submission; response to review

---
date: "`r Sys.Date()`"
author: "Your Name"
title: "officedown template"
output: 
  officedown::rdocx_document:
    reference_docx: style_manuscript_times_new_roman.docx
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, fig.cap = TRUE)
library(officedown)
library(officer)

fp <- fp_par(
  text.align = "center", 
  padding.bottom = 20, padding.top = 120, 
  border.bottom = fp_border())

ft <- fp_text(shading.color='#EFEFEF', bold = TRUE)

make_revision <- function(text, label){

  file <- glue::glue('doc/JoH submission/reviewer_response/{label}.rds')
  saveRDS(object = text,  file = file)

  paste(text)

}

```

# Reviewer 1

<br>

__Summary__: Authors used the NHANES database to assess the prevalence of elevated 10-year predicted risk according to the ASCVD risk score in various groups of blood pressure. The paper is well-written and provides data supporting the recommendations made by the AHA/ACC Guidelines when to initiate antihypertensive medication.

__Response__: Thank you for your review and helpful feedback. We have responded to each of your comments below and included a list of relevant changes in the revised manuscript.

<br>

__Comment 1__: Introduction, The reference to specific section in the US GL appears superfluous.

__Response__:

<br>

__Comment 2__ Methods, It should be clearly stated that the subgroups were non-exclusive.

__Response__:

<br>

__Comment 3__ Results, It would be interesting to provide data on the number/characteristics of patients who would have received antihypertensive medication according to the ACC/AHA GL (stage 1 hypertension) but have an ASCVD risk score <10% (and would not be treated according to the ESC/ESH GL).

__Response__:

Regarding the parenthetical mention of the ESC/ESH blood pressure guideline, we believe this guideline is highly relevant for clinical practice, but we are unable to determine precisely who would or would not be recommended to initiate treatment in the current study. The ESC/ESH guideline leverages the Systematic COronary Risk Evaluation (SCORE) algorithm to predict 10-year CVD risk. SCORE is derived from European cohort studies and includes risk charts for low and high risk countries. As the United States is not listed as a low or high risk country in the [online calculator for SCORE](https://www.escardio.org/Education/Practice-Tools/CVD-prevention-toolbox/SCORE-Risk-Charts), we do not feel that the SCORE algorithm could be properly applied to our cohort of US adults. Therefore, we have not classified who would or would not be recommended to initiate treatment based on the ESC/ESH guideline in the revised manuscript.

<br>

__Comment 4__ Discussion, Along the lines, please discuss the ESH/ESC GL in this context and what the data adds for the recommendation provided herein.

\newpage

# Reviewer 2

__Summary__: Jaeger et al. estimated the proportion of US adults with diabetes, chronic kidney disease,or ≥ 65 years of age that have high cardiovascular risk. The analysis was conducted for all US adults and among those with stage 1 hypertension. It was based on data from 3 cycles of the US National Health and Nutrition Examination Survey (NHANES).

__Response__: Thank you for your review and helpful feedback. We have responded to each of your comments below and included a list of relevant changes in the revised manuscript.

__Comment 1__: Clinical CVD was self-reported, and the analysis did not take into account target organ damage, which is a strong predictor of cardiovascular risk. It should be identified as a potential limitation of the study.

__Comment 2__: Table 1 presents only total and HDL cholesterol values. However, cardiovascular risk is primarily driven by LDL cholesterol. How many patients were treated with statins ?

__Comment 3__: The current US definition and staging of hypertension are different than in all other countries. This issue should be addressed in the discussion.

__Comment 4__: Table 1: Presentation of heart rate might provide additional insights into differentiation between 4 subgroups.

__Comment 5__: Can you provide the number of drugs in treated patients ?

__Comment 6__: Table S1. Please provide data regarding antihypertensive medication use.

### 2021-06-09 packages.R

@@ -35,11 +35,10 @@ pacman::p_load(
   Hmisc,
   xaringan,
   xaringanthemer,
-  showtext
+  showtext,
+  PooledCohort,
+  table.glue
 )
-
-pacman::p_load_gh('bcjaeger/PooledCohort', update = FALSE)
-pacman::p_load_gh('bcjaeger/table.glue', update = FALSE)
 
 conflicted::conflict_prefer("roc",       "pROC")
 conflicted::conflict_prefer("filter",    "dplyr")

### 2021-06-17 doc/JoH submission/reviewer_response/reviewer_response.Rmd
r2r updated with PW feedback

@@
 date: "`r Sys.Date()`"
-author: "Your Name"
-title: "officedown template"
+title: "Predicted cardiovascular risk for US adults with diabetes, chronic kidney disease, and \u226565 years of age"
+subtitle: "Response to reviewers"
 output: 
@@
 ```{r setup, include=FALSE}
-knitr::opts_chunk$set(echo = TRUE, fig.cap = TRUE)
+
+knitr::opts_chunk$set(echo = FALSE)
+
 library(officedown)
 library(officer)
+library(drake)
+library(tidyverse)
+library(flextable)
+library(table.glue)
+library(glue)
+library(janitor)
+library(survey)
 
-fp <- fp_par(
-  text.align = "center", 
-  padding.bottom = 20, padding.top = 120, 
-  border.bottom = fp_border())
+rspec <- round_spec() %>%
+  round_using_decimal(digits = 1)
 
-ft <- fp_text(shading.color='#EFEFEF', bold = TRUE)
+names(rspec) <- paste('table.glue', names(rspec), sep = '.')
 
-make_revision <- function(text, label){
+options(rspec)
 
-  file <- glue::glue('doc/JoH submission/reviewer_response/{label}.rds')
-  saveRDS(object = text,  file = file)
+R.utils::sourceDirectory('../../R')
 
-  paste(text)
+loadd(tbl1_s1hyp_lowrisk,
+      current_analysis,
+      egfr_cutpoint,
+      acr_cutpoint,
+      gluc_cutpoint_fasted,
+      gluc_cutpoint_fed,
+      hba1c_cutpoint,
+      perc_assumed_highrisk)
 
-}
+s1hyp_lowrisk <- subset(current_analysis$data,
+                        bp_cat == 'Stage 1 hypertension' & 
+                          pcr_gteq_10 == 'no')
+
+N_s1h_lowrisk_unwtd <- list(
+  ovrl         = nrow(s1hyp_lowrisk),
+  diab         = sum(s1hyp_lowrisk$diabetes == "yes"),
+  ckd          = sum(s1hyp_lowrisk$ckd == "yes"),
+  age_gt65     = sum(s1hyp_lowrisk$age_gt65 == "yes"),
+  any          = sum(s1hyp_lowrisk$any_ckd_diab_age65 == "yes")
+) %>%
+  map_chr(table_value)
 
@@
 # Reviewer 1
-
-<br>
 
@@
 
-__Response__:
+__Response__: We agree that this reference is not needed.
+In the updated manuscript, the text "written in Sections 9.3, 9.6, and 10.3 of the guideline" has been removed from the first paragraph of the Introduction.
 
@@
 
-__Response__:
+__Response__: We think this is a helpful clarification to include and have modified the first sentence of the Statistical Analysis section (see page 9) to read as follows: "Analyses were conducted for the overall population and among non-exclusive subgroups of participants with diabetes, CKD, ≥ 65 years of age, and with any of these three characteristics."
 
@@
 
-__Response__:
+__Response__: We agree and have taken three steps in response:
 
-Regarding the parenthetical mention of the ESC/ESH blood pressure guideline, we believe this guideline is highly relevant for clinical practice, but we are unable to determine precisely who would or would not be recommended to initiate treatment in the current study.
-The ESC/ESH guideline leverages the Systematic COronary Risk Evaluation (SCORE) algorithm to predict 10-year CVD risk.
+_Step 1_: We computed the percentage of US adults without high ASCVD risk and with stage 1 hypertension who would be assumed to have high ASCVD risk by the ACC/AHA guideline.
+In the revised manuscript, we have included this information.
+Specifically, on page 9-10, we write "The percentage of US adults with stage 1 hypertension incorrectly assumed to have high ASCVD risk by the ACC/AHA guideline due to diabetes, CKD, or age was also computed." On page 11, we write "Among those without high ASCVD risk and with stage 1 hypertension, `r table_value(perc_assumed_highrisk)`% were assumed to have high ASCVD risk by the ACC/AHA BP guideline."
+
+_Step 2_: We have computed the characteristics of US adults with stage 1 hypertension and 10-year predicted ASCVD risk < 10% (__Table__).
+Adults who would have been assumed to have high ASCVD risk by the ACC/AHA BP guideline are those with diabetes, CKD, or age ≥ 65 years in the far right column.
+While we believe these results are interesting, we have chosen not to include them in the revised manuscript as they are similar to results in supplemental table 1, which describes the characteristics of US adults with stage 1 hypertension.
+
+_Step 3_: We believe the 2018 ESC/ESH BP guideline is relevant to the current study, but we are unable to determine precisely who would or would not be recommended to initiate treatment by the ESC/ESH guideline in the current study.
+The ESC/ESH guideline leverages the Systematic COronary Risk Evaluation (SCORE) algorithm to predict 10-year CVD mortality risk.
 SCORE is derived from European cohort studies and includes risk charts for low and high risk countries.
-As the United States is not listed as a low or high risk country in the [online calculator for SCORE](https://www.escardio.org/Education/Practice-Tools/CVD-prevention-toolbox/SCORE-Risk-Charts), we do not feel that the SCORE algorithm could be properly applied to our cohort of US adults.
+Because the SCORE algorithm has not been validated in the United States and the United States is not listed as a low or high risk country in the [online calculator for SCORE](https://www.escardio.org/Education/Practice-Tools/CVD-prevention-toolbox/SCORE-Risk-Charts), the SCORE algorithm could not be properly applied to the current study's cohort of US adults.
 Therefore, we have not classified who would or would not be recommended to initiate treatment based on the ESC/ESH guideline in the revised manuscript.
@@
 __Comment 4__ Discussion, Along the lines, please discuss the ESH/ESC GL in this context and what the data adds for the recommendation provided herein.
+
+__Response__: We have added text that discusses components of the ESC/ESH guideline in the context of the current study. Specifically, on page 16, we write
+
+"For example, the 2018 European Society of Cardiology (ESC) and European Society of Hypertension (ESH) BP guideline recommends considering initiation of antihypertensive medication for adults at very high risk of CVD with untreated SBP between 130 and 139 mm Hg or untreated DBP between 85 and 89 mm Hg.
+Adults with predicted 10-year CVD mortality risk ≥ 10% according to the Systematic Coronary Risk Evaluation equations, severe CKD (eGFR < 30 mL/min/1.73 m^2^), or diabetes with target organ damage are included in the very high CVD risk group."
+
+We have also included text in the discussion describing how data from the current study inform future studies on the recommendations provided in the ESC/ESH guideline (see pages 16-17):
+
+"The current study found that many US adults with CKD (eGFR <60 mL/min/1.73 m^2^ or albuminuria) or diabetes did not have high ASCVD risk, defined as clinical CVD or 10-year ASCVD risk ≥ 10% according to the Pooled Cohort Risk equations.
+Future studies may assess generalization of the current study's findings to the ESC/ESH guideline by estimating the proportion of European adults with diabetes and target organ damage or severe CKD that have clinical CVD or 10-year CVD mortality risk ≥ 10% according to the Systematic Coronary Risk Evaluation equations."
+
+\newpage
+__Table__: Characteristics of US adults without high atherosclerotic cardiovascular disease risk and with stage 1 hypertension, overall and for subgroups defined by diabetes, chronic kidney disease, and ≥ 65 years of age.
+`r fp_par(line_spacing = 1)`
+
+```{r}
+
+col_labels <- function(N_vals){
+    tbl1_s1hyp_lowrisk$table %>%
+      select(-label, -level) %>%
+      names() %>%
+      paste('\nN =', N_vals) %>%
+      set_names(names(N_vals)) %>%
+      as.list()
+  }
+
+col_labels_s1h_lowrisk <- col_labels(N_s1h_lowrisk_unwtd)
+
+fts <- c(
+  '\u2A',
+  '\u2020',
+  '\u2021',
+  '\uA7',
+  '\u2016',
+  '\uB6',
+  '#',
+  '\u2a\u2a',
+  '\u2020\u2020',
+  '\u2021\u2021'
+)
+
+value_note <- as_paragraph("Table values are mean (standard error) or proportion.")
+
+ftr_ckd <- as_paragraph(glue('Chronic kidney disease is defined by an albumin-to-creatinine ratio \u2265 {acr_cutpoint} mg/g or an estimated glomerular filtration rate < {egfr_cutpoint} ml/min/1.73m\u00b2'))
+
+ftr_diab <- as_paragraph(glue('Diabetes was defined by fasting serum glucose \u2265 {gluc_cutpoint_fasted} mg/dL, non-fasting glucose \u2265 {gluc_cutpoint_fed} mg/dL, glycated hemoglobin (HbA1c) \u2265 {hba1c_cutpoint}%, or self-reported use of insulin or oral glucose lowering medication.'))
+
+ftr_cvdHx_defn <- as_paragraph('Clinical cardiovascular disease was defined by self-report of previous heart failure, coronary heart disease, stroke, or myocardial infarction')
+
+tbl1_s1hyp_lowrisk$table %>% 
+  as_grouped_data(groups = 'label') %>%
+  remove_empty('rows') %>%
+  as_flextable(hide_grouplabel = TRUE) %>%
+  add_header_row(values = c("", "Sub-groups"), colwidths = c(2, 4)) %>%
+  theme_box() %>%
+  set_header_labels(
+    'level' = 'Characteristic',
+    'Overall' = col_labels_s1h_lowrisk$ovrl,
+    'Diabetes' = col_labels_s1h_lowrisk$diab,
+    'CKD' = col_labels_s1h_lowrisk$ckd,
+    'Age 65+ years' = col_labels_s1h_lowrisk$age_gt65,
+    'Diabetes, CKD, or age 65+ years' = col_labels_s1h_lowrisk$any
+  ) %>%
+  padding(i = 4:8, j = 1, padding.left = 10, part = 'body') %>%
+  height(height = 1.5, part = 'header') %>%
+  width(width = 1.15) %>%
+  width(j = ~level, width = 1.75) %>%
+  align(align = 'center', part = 'all') %>%
+  align(j = 1, align = 'left', part = 'all') %>%
+  footnote(i=2, j=1, part='header', value=value_note, ref_symbols=fts[1]) %>%
+  footnote(i=2, j=3, part='header', value=ftr_diab, ref_symbols=fts[2]) %>%
+  footnote(i=2, j=4, part='header', value=ftr_ckd, ref_symbols=fts[3]) %>%
+  footnote(
+    i = ~ level == 'Clinical CVD',
+    j = 1,
+    part = 'body',
+    value = ftr_cvdHx_defn,
+    ref_symbols = fts[4]
+  ) %>%
+  footnote(
+    i = 1,
+    j = 1,
+    part = 'body',
+    value = as_paragraph("CKD = chronic kidney disease; CVD = cardiovascular disease; HDL = high density lipoprotein"),
+    ref_symbols = ''
+  )
+
+```
 
@@
 
+<br>
+
 __Comment 1__: Clinical CVD was self-reported, and the analysis did not take into account target organ damage, which is a strong predictor of cardiovascular risk.
@@
 
-__Comment 2__: Table 1 presents only total and HDL cholesterol values. However, cardiovascular risk is primarily driven by LDL cholesterol. How many patients were treated with statins ?
+__Response__: We agree and have added text in the Discussion section to clarify this limitation. Specifically, on page 17, we write
+
+"Clinical CVD status may also have been mis-classified as it was determined by self-report rather than diagnostic imaging.
+The current analysis also did not account for target organ damage, which is a strong predictor of CVD risk."
+
+<br>
+
+__Comment 2A__: Table 1 presents only total and HDL cholesterol values. However, cardiovascular risk is primarily driven by LDL cholesterol.
+
+__Response__: Thank you for this comment.
+In the current analysis, we studied predicted ASCVD risk according to the Pooled Cohort Risk prediction equations rather than observed CVD events.
+The Pooled Cohort Risk equations predict 10-year risk for ASCVD using multiple variables, including HDL and total cholesterol but not LDL cholesterol.
+Since LDL cholesterol does not influence 10-year risk for ASCVD according to the Pooled Cohort Risk equations, we did not include LDL as a study variable.
+
+<br>
+
+__Comment 2B__: How many patients were treated with statins?
+
+```{r}
+
+loadd(design_overall)
+
+statins <- svytable(~meds_statin, design_overall) %>% 
+  as.data.frame() %>% 
+  mutate(p = Freq/sum(Freq)) %>% 
+  select(-Freq) %>% 
+  filter(meds_statin == 'yes') %>% 
+  select(-meds_statin) %>% 
+  as.list() %>% 
+  map(~table_glue("{100*.x}%")) %>% 
+  unlist()
+
+statins_unweighted <- 
+  table(design_overall$variables$meds_statin) %>% 
+  as.data.frame() %>% 
+  rename(meds_statin = Var1) %>% 
+  mutate(Freq = as.integer(Freq)) %>% 
+  summarize(value = table_glue("{Freq[2]} of {sum(Freq)}")) %>% 
+  deframe() %>% 
+  glue_collapse(sep = ', ', last = ', and ')
+
+```
+
+__Response__: We are happy to answer this question.
+All NHANES participants were eligible to complete an interview with a trained survey interviewer involving dietary Supplements and prescription medications.
+The questions related to prescription medications cover the use of prescription medications during a one-month period prior to the survey date.
+During the interview, generic names and codes of prescriptions taken by the participant during the previous month were recorded.
+We linked these codes to statin medications (Atorvastatin, Atorvast, Fluvastatin, Lovastatin, Pitavastatin, Pravastatin, Rosuvastatin, and Simvastatin) to determine whether participants were taking a statin.
+Data from participants included in the current study indicate that `r statins` of US adults ages 40-79 years used a statin from 2013 to 2018.
+In case the reviewer would also like to assess the unweighted count, a total of `r statins_unweighted` participants had at least one prescription that was a statin in the current study.
+Statin usage clearly impacts CVD risk, but only plays a role in the Pooled Cohort risk equations for 10-year ASCVD risk if a statin user responds 'yes' to the question 'Are you receiving treatment for high blood pressure?' due to their statin use.
+Since we have already partitioned the sample based on self-reported usage of medication to lower blood pressure, we have not included additional data on statin use in the revised manuscript.
+
+<br>
 
@@
 
+__Response__: We think this is a good topic to include in the Discussion and have included an additional paragraph to address it: "The 2017 ACC/AHA BP guideline's definition of hypertension and recommendations for initiating antihypertensive medication differ from other guidelines published from 2015-2020.
+For example, the 2018 European Society of Cardiology (ESC) and European Society of Hypertension (ESH) BP guideline recommends considering initiation of antihypertensive medication for adults at very high risk of CVD with untreated SBP between 130 and 139 mm Hg or untreated DBP between 85 and 89 mm Hg.
+Adults with predicted 10-year CVD mortality risk ≥ 10% according to the Systematic Coronary Risk Evaluation equations, severe CKD (eGFR < 30 mL/min/1.73 m^2^), or diabetes with target organ damage are included in the very high CVD risk group.
+The current study found that many US adults with CKD (eGFR <60 mL/min/1.73 m^2^ or albuminuria) or diabetes did not have high ASCVD risk, defined as clinical CVD or 10-year ASCVD risk ≥ 10% according to the Pooled Cohort Risk equations.
+Future studies may assess generalization of the current study's findings to the ESC/ESH guideline by estimating the proportion of European adults with diabetes and target organ damage or severe CKD that have clinical CVD or 10-year CVD mortality risk ≥ 10% according to the Systematic Coronary Risk Evaluation equations."
+
+<br>
+
 __Comment 4__: Table 1: Presentation of heart rate might provide additional insights into differentiation between 4 subgroups.
 
-__Comment 5__: Can you provide the number of drugs in treated patients ?
+__Response__: We agree and have added heart rate in beats per minute to Table 1 and Table S1 of the revised manuscript.
+
+```{r}
+
+rx_stats_mean_se <- 
+  svymean(
+    ~meds_n_taken, 
+    subset(design_overall, meds_bp == 'yes'), 
+    na.rm = TRUE
+  ) %>% 
+  as.data.frame() %>% 
+  set_names(c("mean", "se"))
+
+rx_stats_quants <- 
+  svyquantile(
+    ~meds_n_taken, 
+    quantiles = c(0.25, 0.5, 0.75),
+    subset(design_overall, meds_bp == 'yes'), 
+    na.rm = TRUE
+  ) %>% 
+  as.data.frame() %>% 
+  set_names(c('q25', 'q50', 'q75')) %>% 
+  map(as.integer)
+
+rx_stats <- cbind(rx_stats_mean_se, rx_stats_quants) %>% 
+  as.list() %>% 
+  map(table_value)
+
+```
+
+<br>
+
+__Comment 5__: Can you provide the number of drugs in treated patients?
+
+__Response__: We are happy to provide these data for the reviewer.
+All NHANES participants were eligible to complete an interview with a trained survey interviewer involving dietary Supplements and prescription medications.
+The questions related to prescription medications cover the use of prescription medications during a one-month period prior to the survey date.
+During the interview, the number of prescription medications taken during the previous month was assessed.
+Data from participants taking antihypertensive medication in the current analysis indicate that the mean (standard error) number of prescription medications taken for US adults from 2013 through 2018 was `r rx_stats$mean` (`r rx_stats$se`), and the median (25^th^, 75^th^ percentile) was `r rx_stats$q50` (`r rx_stats$q25`, `r rx_stats$q75`).
+Since these medication data are not limited to prescriptions written for lowering blood pressure, we have not included these results in the updated manuscript.
+
+<br>
 
 __Comment 6__: Table S1. Please provide data regarding antihypertensive medication use.
+
+__Response__: Thank you for this comment.
+We grouped study participants into 4 non-overlapping groups based on blood pressure.
+A fifth group contained participants who were taking antihypertensive medications.
+Therefore, none of the participants with stage 1 hypertension were taking antihypertensive medications.
+We apologize for the lack of clarity and have added the following footnote to Table S1 to indicate that participants with stage 1 hypertension were not taking antihypertensive medication: "Stage 1 hypertension was defined as having untreated systolic blood pressure between 130 and 139 mm Hg with diastolic blood pressure < 90 mm Hg or diastolic blood pressure between 80 and 89 mm Hg with systolic blood pressure < 90 mm Hg"

### 2021-06-17 doc/ACCAHA_BP_groups.Rmd
r2r updated with PW feedback

@@
 
-# source("_drake.R")
+source("../packages.R")
+R.utils::sourceDirectory('../R')
+
+rspec <- round_spec() %>%
+  round_using_decimal(digits = 1)
+
+names(rspec) <- paste('table.glue', names(rspec), sep = '.')
+
+options(rspec)
 
@@
       acr_cutpoint,
-      fig_central_illustration)
+      fig_central_illustration,
+      perc_assumed_highrisk)
 
@@
   list2env(envir = globalenv())
+
+make_revision <- function(text,
+                          color = 'red', 
+                          font.size = 12, 
+                          font.family = 'Times New Roman'){
+
+  officer::ftext(text = text,
+                 prop = officer::fp_text(color = color, 
+                             font.size = font.size, 
+                             font.family = font.family))
+
+}
 
@@
 
-<!-- These are hard coded to discourage messing with guideline recs -->
+<!-- These are hard coded to discourage changing guideline recs -->
 
@@
 
-Analyses were conducted for the overall population and among participants with diabetes, CKD, ≥ 65 years of age, and for those with any of these three characteristics.
+Analyses were conducted for the overall population and among `r make_revision("non-exclusive subgroups of")` participants with diabetes, CKD, ≥ 65 years of age, and with any of these three characteristics.
 Participant characteristics were summarized as mean with its standard error for continuous variables and percentage for categorical variables.
 The percentage of US adults in each of the five categories based on BP and antihypertensive medication use was computed.
-The 25^th^, 50^th^, and 75^th^ percentile of 10-year predicted ASCVD risk and the proportion of participants with high ASCVD risk were estimated for the overall population and within each of the five categories based on BP and antihypertensive medication use.
+`r make_revision("The percentage of US adults with stage 1 hypertension incorrectly assumed to have high ASCVD risk by the ACC/AHA guideline due to diabetes, CKD, or age was also computed.")` The 25^th^, 50^th^, and 75^th^ percentile of 10-year predicted ASCVD risk and the percentage of participants with high ASCVD risk were estimated for the overall population and within each of the five categories based on BP and antihypertensive medication use.
 To assess the extent to which participants with a 10-year predicted ASCVD risk < 10% were close to the 10% threshold, we estimated the distribution of 10-year predicted ASCVD risk.
@@
 The estimated prevalence (95% CI) of stage 1 hypertension was `r inline$prevS1hOverall` overall and `r inline$prevS1hDiabetes`, `r inline$prevS1hCkd`, `r inline$prevS1hAge65`, and `r inline$prevS1hAny` among those with diabetes, CKD, age ≥ 65 years, and at least one of these conditions, respectively (`r refer_to('tab_bpdist')`).
-Characteristics of US adults 40 to 79 years of age with stage 1 hypertension, overall and for subgroups defined by diabetes, CKD and age ≥ 65 years, are presented in Table S1.
+`r make_revision(paste0("Among those without high ASCVD risk and with stage 1 hypertension, ", table_value(perc_assumed_highrisk), "% were assumed to have high ASCVD risk by the ACC/AHA BP guideline."))` Characteristics of US adults 40 to 79 years of age with stage 1 hypertension, overall and for subgroups defined by diabetes, CKD and age ≥ 65 years, are presented in Table S1.
 
@@
 
+`r make_revision("The 2017 ACC/AHA BP guideline's definition of hypertension and recommendations for initiating antihypertensive medication differ from other guidelines published from 2015-2020.
+For example, the 2018 European Society of Cardiology (ESC) and European Society of Hypertension (ESH) BP guideline recommends considering initiation of antihypertensive medication for adults at very high risk of CVD with untreated SBP between 130 and 139 mm Hg or untreated DBP between 85 and 89 mm Hg.
+Adults with predicted 10-year CVD mortality risk ≥ 10% according to the Systematic Coronary Risk Evaluation equations, severe CKD (eGFR < 30 mL/min/1.73 m^2^), or diabetes with target organ damage are included in the very high CVD risk group.
+The current study found that many US adults with CKD (eGFR <60 mL/min/1.73 m^2^ or albuminuria) or diabetes did not have high ASCVD risk, defined as clinical CVD or 10-year ASCVD risk ≥ 10% according to the Pooled Cohort Risk equations.
+Future studies may assess generalization of the current study's findings to the ESC/ESH guideline by estimating the proportion of European adults with diabetes and target organ damage or severe CKD that have clinical CVD or 10-year CVD mortality risk")` ≥ `r make_revision("10% according to the Systematic Coronary Risk Evaluation equations.")`
+
+<br>
+
 The current study has a number of strengths.
@@
 Additionally, since only one measurement of serum creatinine and urine albuminuria were available, CKD status may have been mis-classified in some adults.
-A total of `r table_value(sum(current_analysis$data$bp_cat == 'Stage 1 hypertension'))` participants had stage 1 hypertension, and some subgroups of this population based on diabetes, CKD, and ≥ 65 years of age were small.
+`r make_revision("Clinical CVD status may also have been mis-classified as it was determined by self-report rather than diagnostic imaging.
+The current analysis also did not account for target organ damage, which is a strong predictor of CVD risk.")` A total of `r table_value(sum(current_analysis$data$bp_cat == 'Stage 1 hypertension'))` participants had stage 1 hypertension, and some subgroups of this population based on diabetes, CKD, and ≥ 65 years of age were small.
 

### 2021-06-17 R/clean_exam_bp.R

@@ -19,6 +19,10 @@ clean_exam_bp <- function(
     .id = 'exam'
   )
 
+  # BP is measured on participants 8+ years; radial (brachial if necessary)
+  # pulse is measured on participants 8+ years;
+  # and heart rate is measured on children 0-7 years of age.
+
   # Variable description ----
 
   var_guide <- tibble(
@@ -26,19 +30,22 @@ clean_exam_bp <- function(
       'bp_sys_mmhg',
       'bp_dia_mmhg',
       'n_msr_sbp',
-      'n_msr_dbp'
+      'n_msr_dbp',
+      'pulse_60s'
     ),
     nhanes = c(
       'BPXSY1 - BPXSY4',
       'BPXDI1 - BPXDI4',
       'BPXSY1 - BPXSY4',
-      'BPXDI1 - BPXDI4'
+      'BPXDI1 - BPXDI4',
+      'BPXPLS'
     ),
     descr = c(
       'Systolic blood pressure, mm Hg',
       'Diastolic blood pressure, mm Hg',
       'Number of systolic blood pressure readings',
-      'Number of diastolic blood pressure readings'
+      'Number of diastolic blood pressure readings',
+      'Pulse; 60 seconds'
     )
   )
 
@@ -57,10 +64,12 @@ clean_exam_bp <- function(
   # Some participants have zero BP values. taking their mean results in
   # NaN (not a number). I set these NaN values to missing.
 
+
   data_cleaned_bp <- select(
     data_all,
     exam,
     seqn = SEQN,
+    pulse_60s = BPXPLS,
     sbp_1 = BPXSY1,
     sbp_2 = BPXSY2,
     sbp_3 = BPXSY3,
@@ -71,12 +80,14 @@ clean_exam_bp <- function(
     dbp_4 = BPXDI4
   ) %>%
     # reshape so I can do operations on all BP values by participant
-    pivot_longer(cols = -c(exam, seqn)) %>%
+    pivot_longer(cols = matches("^sbp|^dbp")) %>%
     separate(name, into = c('type', 'measure')) %>%
     pivot_wider(names_from = type, values_from = value) %>%
     mutate(dbp = replace(dbp, dbp == 0, NA_real_)) %>% # see note 1
     group_by(exam, seqn) %>%
     summarise(
+      # no need to summarize pulse, but do need to keep it
+      pulse_60s = pulse_60s[1],
[…]

### 2021-06-17 R/clean_rx_statin.R

@@ -1,0 +1,51 @@
+#' .. content for \description{} (no empty lines) ..
+#'
+#' .. content for \details{} ..
+#'
+#' @title
+#' @param exams
+#' @return
+#' @author bcjaeger
+#' @export
+clean_rx_statin <- function(exams) {
+
+  if(any(exams %in% c('1999', '2001', '2003')))
+    stop(
+      'cannot get statin usage for exams prior to 2005',
+      call. = FALSE
+    )
+
+  statins <- c("ATORVASTATIN",
+               "ATORVAST",
+               "FLUVASTATIN",
+               "LOVASTATIN",
+               "PITAVASTATIN",
+               "PRAVASTATIN",
+               "ROSUVASTATIN",
+               "SIMVASTATIN")
+
+  data_all <- map_dfr(
+    .x = make_exam_files(exams, data_label = 'RXQ_RX'),
+    .f = read_xpt,
+    .id = 'exam'
+  )
+
+  data_all %>%
+    select(
+      exam,
+      seqn = SEQN,
+      rx_used_30days = RXDUSE,
+      rx_name_generic = RXDDRUG,
+      rx_code_generic = RXDDRGID,
+      rx_seen_interview = RXQSEEN,
+      rx_days_taken = RXDDAYS,
+      rx_number_taken = RXDCOUNT
+    ) %>%
+    group_by(seqn) %>%
+    summarize(
+      exam = exam[1],
+      rx_number_taken = rx_number_taken[1],
+      statin = as.numeric(any(rx_name_generic %in% statins))
+    )
+
+}

### 2021-06-17 R/compile_report.R

@@ -407,6 +407,13 @@ compile_report <- function(exams,
       part = 'body',
       value = as_paragraph(write_abbrevs(abbrevs[c("CVD", "HDL", "CKD")])),
       ref_symbols = ''
+    ) %>%
+    footnote(
+      i = 1,
+      j = 1,
+      part = 'body',
+      value = as_paragraph("Stage 1 hypertension was defined as having untreated systolic blood pressure between 130 and 139 mm Hg with diastolic blood pressure < 90 mm Hg or diastolic blood pressure between 80 and 89 mm Hg with systolic blood pressure < 90 mm Hg"),
+      ref_symbols = ''
     )
 
   tbls_supp %<>% add_row(

### 2021-06-17 R/compute_perc_assumed_highrisk.R

@@ -1,0 +1,22 @@
+#' .. content for \description{} (no empty lines) ..
+#'
+#' .. content for \details{} ..
+#'
+#' @title
+
+#' @return
+#' @author bcjaeger
+#' @export
+compute_perc_assumed_highrisk <- function(design) {
+
+  lowcvdrisk_props <-
+    svytable(~any_ckd_diab_age65, design) %>%
+    as.data.frame() %>%
+    mutate(p = Freq / sum(Freq))
+
+  lowcvdrisk_props %>%
+    filter(any_ckd_diab_age65 == 'yes') %>%
+    mutate(perc = p * 100) %>%
+    pull(perc)
+
+}

### 2021-06-17 R/derive_others.R

@@ -87,7 +87,8 @@ derive_others <- function(data, exams,
       race_ethnicity = fct_recode(
         race_ethnicity,
         "Other Race/ethnicity - Including Multi-Racial" = "Other Race - Including Multi-Racial"
-      )
+      ),
+      statin = recode(statin, '0' = 'no', '1' = 'yes')
     ) %>%
     select(
       exam,
@@ -105,7 +106,10 @@ derive_others <- function(data, exams,
       n_msr_dbp,
       bp_sys_mmhg,
       bp_dia_mmhg,
+      pulse_60s,
       meds_bp,
+      meds_statin = statin,
+      meds_n_taken = rx_number_taken,
       smk_current,
       age_group,
       age_40to79,

### 2021-06-17 R/plan.R

@@ -41,6 +41,9 @@ the_plan <- drake_plan(
   qx_high_blood_pressure    = clean_qx_high_bp(exams),
   qx_healthcare_utilization = clean_qx_healthcare_utilization(exams),
 
+
+  statins = clean_rx_statin(exams),
+
   data_pooled = reduce(
     .x = list(
       demo,
@@ -56,11 +59,13 @@ the_plan <- drake_plan(
       qx_health_insurance,
       qx_diabetes,
       qx_high_blood_pressure,
-      qx_healthcare_utilization
+      qx_healthcare_utilization,
+      statins
     ),
     .f = left_join,
     by = c('exam', 'seqn')
   ),
+
 
   fasted_hrs_lower = 8,
   fasted_hrs_upper = 24,
@@ -107,6 +112,11 @@ the_plan <- drake_plan(
 
   design_s1hyp = subset(design_overall, bp_cat == 'Stage 1 hypertension'),
 
+  design_s1hyp_lowrisk = design_overall %>%
+    subset(bp_cat == 'Stage 1 hypertension' &
+             pcr_gteq_10 == 'no' &
+             ever_had_ascvd == 'no'),
+
   tbl1_variables = c(
     "Age, years" = "age",
     "Gender" = "sex",
@@ -114,6 +124,7 @@ the_plan <- drake_plan(
     "Current smoker" = "smk_current",
     "Total cholesterol, mg/dl" = "chol_total_mgdl",
     "HDL-cholesterol, mg/dl" = "chol_hdl_mgdl",
+    "Heart rate, beats per minute" = "pulse_60s",
     "Systolic blood pressure, mm Hg" = "bp_sys_mmhg",
     "Diastolic blood pressure, mm Hg" = "bp_dia_mmhg",
     "Antihypertensive medication use" = "meds_bp",
@@ -132,7 +143,12 @@ the_plan <- drake_plan(
   tbl1_s1hyp = tabulate_characteristics(design_s1hyp,
                                         tbl1_variables),
 
+  tbl1_s1hyp_lowrisk = tabulate_characteristics(design_s1hyp_lowrisk,
+                                                tbl1_variables),
+
   tbl_bpdist = tabulate_bpdist(design_overall),
+
+  perc_assumed_highrisk = compute_perc_assumed_highrisk(design_s1hyp_lowrisk),
 
   tbl_risk_overall = tabulate_risk_summary(design_overall),
   tbl_risk_overall_supp = tabulate_risk_summary(design_overall_supp),

### 2021-06-17 R/tabulate_characteristics.R

@@ -95,7 +95,9 @@ tb1_fun <- function(.x, by = NULL, design){
 
     } else {
 
-      svymean(x = formula, design = design) %>%
+      svymean(x = formula,
+              design = design,
+              na.rm = TRUE) %>%
         as_tibble() %>%
         rename_at(.vars = .x, .funs = ~ 'se') %>%
         mutate(level = .x) %>%

### 2021-06-24 doc/JoH submission/reviewer_response/reviewer_response.Rmd
adding LDL

@@
 
-__Summary__: Authors used the NHANES database to assess the prevalence of elevated 10-year predicted risk according to the ASCVD risk score in various groups of blood pressure.
+__Reviewer's Summary__: Authors used the NHANES database to assess the prevalence of elevated 10-year predicted risk according to the ASCVD risk score in various groups of blood pressure.
 The paper is well-written and provides data supporting the recommendations made by the AHA/ACC Guidelines when to initiate antihypertensive medication.
@@
 
-__Response__: We agree that this reference is not needed.
+__Response__: We agree that this information is not needed.
 In the updated manuscript, the text "written in Sections 9.3, 9.6, and 10.3 of the guideline" has been removed from the first paragraph of the Introduction.
@@
 
-_Step 1_: We computed the percentage of US adults without high ASCVD risk and with stage 1 hypertension who would be assumed to have high ASCVD risk by the ACC/AHA guideline.
+_Step 1_: We computed the percentage of US adults with 10-year predicted ASCVD risk < 10% and with stage 1 hypertension who would be assumed to have high ASCVD risk by the ACC/AHA guideline due to diabetes, CKD, or age ≥ 65 years.
 In the revised manuscript, we have included this information.
-Specifically, on page 9-10, we write "The percentage of US adults with stage 1 hypertension incorrectly assumed to have high ASCVD risk by the ACC/AHA guideline due to diabetes, CKD, or age was also computed." On page 11, we write "Among those without high ASCVD risk and with stage 1 hypertension, `r table_value(perc_assumed_highrisk)`% were assumed to have high ASCVD risk by the ACC/AHA BP guideline."
+Specifically, on page 9-10, we write "The percentage of US adults with stage 1 hypertension and 10-year predicted ASCVD risk < 10% assumed to have high ASCVD risk by the ACC/AHA guideline due to diabetes, CKD, or age was also computed." On page 11, we write "Overall, `r table_value(perc_assumed_highrisk)`% of those with stage 1 hypertension and without high ASCVD risk were assumed to have high ASCVD risk by the ACC/AHA BP guideline."
 
@@
 
-__Summary__: Jaeger et al.
+__Reviewer's Summary__: Jaeger et al.
 estimated the proportion of US adults with diabetes, chronic kidney disease,or ≥ 65 years of age that have high cardiovascular risk.
@@
 
-__Response__: We think this is a good topic to include in the Discussion and have included an additional paragraph to address it: "The 2017 ACC/AHA BP guideline's definition of hypertension and recommendations for initiating antihypertensive medication differ from other guidelines published from 2015-2020.
+__Response__: We think this is a good topic to include in the Discussion and have included an additional paragraph (see page 16) to address it: "The 2017 ACC/AHA BP guideline's definition of hypertension and recommendations for initiating antihypertensive medication differ from other guidelines published from 2015-2020.
 For example, the 2018 European Society of Cardiology (ESC) and European Society of Hypertension (ESH) BP guideline recommends considering initiation of antihypertensive medication for adults at very high risk of CVD with untreated SBP between 130 and 139 mm Hg or untreated DBP between 85 and 89 mm Hg.

### 2021-06-24 doc/ACCAHA_BP_groups.Rmd
adding LDL

@@
 
-__Word count (including references, but not tables and legends)__: 3837
+__Word count (including references, but not tables and legends)__: 4117
 
@@
 
-__number of figures__: 5 (2 main figures, 3, supplemental figues)
+__number of figures__: 5 (2 main figures, 3, supplemental figures)
 
@@
 The percentage of US adults in each of the five categories based on BP and antihypertensive medication use was computed.
-`r make_revision("The percentage of US adults with stage 1 hypertension incorrectly assumed to have high ASCVD risk by the ACC/AHA guideline due to diabetes, CKD, or age was also computed.")` The 25^th^, 50^th^, and 75^th^ percentile of 10-year predicted ASCVD risk and the percentage of participants with high ASCVD risk were estimated for the overall population and within each of the five categories based on BP and antihypertensive medication use.
+`r make_revision("The percentage of US adults with stage 1 hypertension and 10-year predicted ASCVD risk < 10% assumed to have high ASCVD risk by the ACC/AHA guideline due to diabetes, CKD, or age was also computed.")` The 25^th^, 50^th^, and 75^th^ percentile of 10-year predicted ASCVD risk and the percentage of participants with high ASCVD risk were estimated for the overall population and within each of the five categories based on BP and antihypertensive medication use.
 To assess the extent to which participants with a 10-year predicted ASCVD risk < 10% were close to the 10% threshold, we estimated the distribution of 10-year predicted ASCVD risk.
@@
 The estimated prevalence (95% CI) of stage 1 hypertension was `r inline$prevS1hOverall` overall and `r inline$prevS1hDiabetes`, `r inline$prevS1hCkd`, `r inline$prevS1hAge65`, and `r inline$prevS1hAny` among those with diabetes, CKD, age ≥ 65 years, and at least one of these conditions, respectively (`r refer_to('tab_bpdist')`).
-`r make_revision(paste0("Among those without high ASCVD risk and with stage 1 hypertension, ", table_value(perc_assumed_highrisk), "% were assumed to have high ASCVD risk by the ACC/AHA BP guideline."))` Characteristics of US adults 40 to 79 years of age with stage 1 hypertension, overall and for subgroups defined by diabetes, CKD and age ≥ 65 years, are presented in Table S1.
+`r make_revision(paste0("Overall, ", table_value(perc_assumed_highrisk), "% of those with stage 1 hypertension and without high ASCVD risk were assumed to have high ASCVD risk by the ACC/AHA BP guideline."))` Characteristics of US adults 40 to 79 years of age with stage 1 hypertension, overall and for subgroups defined by diabetes, CKD and age ≥ 65 years, are presented in Table S1.
 
@@
 
+\newpage
+
+`r rp$supplement.table$caption[2]` 
+`r fp_par(line_spacing = 1)`
+`r rp$supplement.table$object[[2]]`
+
 <!-- SUPPLEMENTAL FIGURES -->

### 2021-06-24 R/clean_labs_trig.R

@@ -1,0 +1,48 @@
+##' .. content for \description{} (no empty lines) ..
+##'
+##' .. content for \details{} ..
+##'
+##' @title
+##' @param exams
+clean_labs_trig <- function(
+  exams = c(1999, 2001, 2003, 2005, 2007, 2009, 2011, 2013, 2015, 2017),
+  include_variable_labels = TRUE
+) {
+
+  fnames <- make_exam_files(exams, data_label = 'TRIGLY')
+
+  if(1999 %in% exams)
+    fnames['1999-2000'] %<>% str_replace('TRIGLY', 'LAB13AM')
+  if(2001 %in% exams)
+    fnames['2001-2002'] %<>% str_replace('TRIGLY', 'L13AM')
+  if(2003 %in% exams)
+    fnames['2003-2004'] %<>% str_replace('TRIGLY', 'L13AM')
+
+  # 2017-2018 are not available yet
+  if(2017 %in% exams)
+    fnames <- fnames[-which(names(fnames) == '2017-2018')]
+
+  var_guide <- tibble(
+    term = c('chol_ldl_mgdl', 'triglycerides_mgdl'),
+    nhanes = c("LBDLDL", "LBXTR"),
+    descr = c("LDL-cholesterol, md/dL", "Triglyceride, mg/dL")
+  )
+
+  data_out <- map_dfr(
+    .x = fnames,
+    .f = read_xpt,
+    .id = 'exam'
+  ) %>%
+    select(exam,
+           seqn = SEQN,
+           wts_af_2yr = WTSAF2YR,
+           chol_ldl_mgdl = LBDLDL,
+           triglycerides_mgdl = LBXTR)
+
+  if(include_variable_labels){
+    add_labels(data_out, var_guide)
+  } else {
+    data_out
+  }
+
+}

### 2021-06-24 R/compile_report.R

@@ -30,6 +30,7 @@ compile_report <- function(exams,
                            design,
                            tbl1_overall,
                            tbl1_s1hyp,
+                           tbl1_s1hyp_lowrisk,
                            tbl_bpdist,
                            tbl_risk_overall,
                            tbl_risk_overall_supp,
@@ -140,6 +141,19 @@ compile_report <- function(exams,
   ) %>%
     map_chr(table_value)
 
+  s1hyp_lowrisk <- subset(current_analysis$data,
+                          bp_cat == 'Stage 1 hypertension' &
+                            pcr_gteq_10 == 'no')
+
+  N_s1h_lowrisk_unwtd <- list(
+    ovrl         = nrow(s1hyp_lowrisk),
+    diab         = sum(s1hyp_lowrisk$diabetes == "yes"),
+    ckd          = sum(s1hyp_lowrisk$ckd == "yes"),
+    age_gt65     = sum(s1hyp_lowrisk$age_gt65 == "yes"),
+    any          = sum(s1hyp_lowrisk$any_ckd_diab_age65 == "yes")
+  ) %>%
+    map_chr(table_value)
+
   get_wtd_N <- function(svyobj, label){
     as.matrix(svyobj)[label, , drop = TRUE] %>%
       set_names(NULL)
@@ -176,6 +190,7 @@ compile_report <- function(exams,
   col_labels_ovrl <- col_labels(N_vals = N_ovrl_unwtd)
   col_labels_s1h <- col_labels(N_vals = N_s1h_unwtd)
   col_labels_age40to79 <- col_labels(N_vals = N_age40to79_unwtd)
+  col_labels_s1h_lowrisk <- col_labels(N_s1h_lowrisk_unwtd)
 
   # table 1: characteristics ------------------------------------------------
 
@@ -420,6 +435,50 @@ compile_report <- function(exams,
     object = list(.tbl1_s1hyp),
     caption = "Characteristics of US adults with stage 1 hypertension, overall and for subgroups defined by diabetes, chronic kidney disease, and \u2265 65 years of age.",
     reference = 'tab_risk_stg1'
+  )
+
+  .tbl1_s1hyp_lowrisk <- tbl1_s1hyp_lowrisk %>%
+    as_grouped_data(groups = 'label') %>%
+    remove_empty('rows') %>%
+    as_flextable(hide_grouplabel = TRUE) %>%
[…]

### 2021-06-24 R/derive_others.R

@@ -102,6 +102,7 @@ derive_others <- function(data, exams,
       race,
       chol_total_mgdl,
       chol_hdl_mgdl,
+      chol_ldl_mgdl,
       n_msr_sbp,
       n_msr_dbp,
       bp_sys_mmhg,

### 2021-06-24 R/plan.R

@@ -32,6 +32,7 @@ the_plan <- drake_plan(
   labs_ghb     = clean_labs_ghb(exams),
   labs_hdl     = clean_labs_hdl(exams),
   labs_tchol   = clean_labs_tchol(exams),
+  labs_trig    = clean_labs_trig(exams),
 
   # Questionnaires ----
   qx_medical_status         = clean_qx_medical_status(exams),
@@ -54,6 +55,7 @@ the_plan <- drake_plan(
       labs_ghb,
       labs_hdl,
       labs_tchol,
+      labs_trig,
       qx_medical_status,
       qx_smoking_status,
       qx_health_insurance,
@@ -124,6 +126,7 @@ the_plan <- drake_plan(
     "Current smoker" = "smk_current",
     "Total cholesterol, mg/dl" = "chol_total_mgdl",
     "HDL-cholesterol, mg/dl" = "chol_hdl_mgdl",
+    "LDL-cholesterol, mg/dl" = "chol_ldl_mgdl",
     "Heart rate, beats per minute" = "pulse_60s",
     "Systolic blood pressure, mm Hg" = "bp_sys_mmhg",
     "Diastolic blood pressure, mm Hg" = "bp_dia_mmhg",
@@ -203,6 +206,7 @@ the_plan <- drake_plan(
     design_overall,
     tbl1_overall$table,
     tbl1_s1hyp$table,
+    tbl1_s1hyp_lowrisk$table,
     tbl_bpdist$table,
     tbl_risk_overall,
     tbl_risk_overall_supp,

### 2021-09-26 doc/JoH submission/reviewer_response/reviewer_response.Rmd
resubmitted to JoH

@@
 In the revised manuscript, we have included this information.
-Specifically, on page 9-10, we write "The percentage of US adults with stage 1 hypertension and 10-year predicted ASCVD risk < 10% assumed to have high ASCVD risk by the ACC/AHA guideline due to diabetes, CKD, or age was also computed." On page 11, we write "Overall, `r table_value(perc_assumed_highrisk)`% of those with stage 1 hypertension and without high ASCVD risk were assumed to have high ASCVD risk by the ACC/AHA BP guideline."
+Specifically, on page 10, we write "The percentage of US adults with stage 1 hypertension and 10-year predicted ASCVD risk < 10% assumed to have high ASCVD risk by the ACC/AHA guideline due to diabetes, CKD, or age was also computed." On page 11, we write
+"Among US adults with stage 1 hypertension and 10-year predicted ASCVD risk < 10%, 17.8% were assumed to have high ASCVD risk by the ACC/AHA BP guideline due to diabetes, CKD, or ≥ 65 years of age."
 
-_Step 2_: We have computed the characteristics of US adults with stage 1 hypertension and 10-year predicted ASCVD risk < 10% (__Table__).
+_Step 2_: We have computed the characteristics of US adults with stage 1 hypertension and 10-year predicted ASCVD risk < 10% (Table S2 in the revised manuscript; included below for convenience).
 Adults who would have been assumed to have high ASCVD risk by the ACC/AHA BP guideline are those with diabetes, CKD, or age ≥ 65 years in the far right column.
-While we believe these results are interesting, we have chosen not to include them in the revised manuscript as they are similar to results in supplemental table 1, which describes the characteristics of US adults with stage 1 hypertension.
+We have updated the Results section to highlight these characteristics.
+On page 11, we write "Among those with predicted ASCVD risk < 10% and assumed to have high ASCVD risk by the guideline, 69.6% were women (Table S3)."
 
@@
 
-We have also included text in the discussion describing how data from the current study inform future studies on the recommendations provided in the ESC/ESH guideline (see pages 16-17):
+We have also included text in the discussion describing how data from the current study inform future studies on the recommendations provided in the ESC/ESH guideline (see page 16):
 
@@
 \newpage
-__Table__: Characteristics of US adults without high atherosclerotic cardiovascular disease risk and with stage 1 hypertension, overall and for subgroups defined by diabetes, chronic kidney disease, and ≥ 65 years of age.
+__Table__: Characteristics of US adults with stage 1 hypertension and 10-year predicted atherosclerotic cardiovascular disease risk < 10%, overall and for subgroups defined by diabetes, chronic kidney disease, and ≥ 65 years of age.
 `r fp_par(line_spacing = 1)`
@@
 "Clinical CVD status may also have been mis-classified as it was determined by self-report rather than diagnostic imaging.
-The current analysis also did not account for target organ damage, which is a strong predictor of CVD risk."
+The current analysis also did not account for some forms of target organ damage, e.g.
+left-ventricular hypertrophy, that predict CVD risk."
 
@@
 The Pooled Cohort Risk equations predict 10-year risk for ASCVD using multiple variables, including HDL and total cholesterol but not LDL cholesterol.
-Since LDL cholesterol does not influence 10-year risk for ASCVD according to the Pooled Cohort Risk equations, we did not include LDL as a study variable.
+Thus, we did not originally include LDL as a study variable.
+In response to the reviewer's inquiry, we have included descriptive summaries of LDL cholesterol in Tables 1, S2, and S3 of the revised manuscript.
 
@@
 __Response__: We are happy to answer this question.
-All NHANES participants were eligible to complete an interview with a trained survey interviewer involving dietary Supplements and prescription medications.
-The questions related to prescription medications cover the use of prescription medications during a one-month period prior to the survey date.
-During the interview, generic names and codes of prescriptions taken by the participant during the previous month were recorded.
-We linked these codes to statin medications (Atorvastatin, Atorvast, Fluvastatin, Lovastatin, Pitavastatin, Pravastatin, Rosuvastatin, and Simvastatin) to determine whether participants were taking a statin.
+As part of the NHANES data collection, generic names and codes of prescriptions taken by the participant during the previous month were recorded.
 Data from participants included in the current study indicate that `r statins` of US adults ages 40-79 years used a statin from 2013 to 2018.
-In case the reviewer would also like to assess the unweighted count, a total of `r statins_unweighted` participants had at least one prescription that was a statin in the current study.
-Statin usage clearly impacts CVD risk, but only plays a role in the Pooled Cohort risk equations for 10-year ASCVD risk if a statin user responds 'yes' to the question 'Are you receiving treatment for high blood pressure?' due to their statin use.
-Since we have already partitioned the sample based on self-reported usage of medication to lower blood pressure, we have not included additional data on statin use in the revised manuscript.
+In the revised manuscript, we have included statin use as a descriptive variable in Tables 1, S2, and S3.
 
@@
 
-__Response__: We think this is a good topic to include in the Discussion and have included an additional paragraph (see page 16) to address it: "The 2017 ACC/AHA BP guideline's definition of hypertension and recommendations for initiating antihypertensive medication differ from other guidelines published from 2015-2020.
+__Response__: We think this is a good topic to include in the Discussion and have included an additional paragraph (see page 16) to address it: "The 2017 ACC/AHA BP guideline's definition of hypertension and recommendations for initiating antihypertensive medication differ from other guidelines published between 2015 and 2020.
 For example, the 2018 European Society of Cardiology (ESC) and European Society of Hypertension (ESH) BP guideline recommends considering initiation of antihypertensive medication for adults at very high risk of CVD with untreated SBP between 130 and 139 mm Hg or untreated DBP between 85 and 89 mm Hg.
 Adults with predicted 10-year CVD mortality risk ≥ 10% according to the Systematic Coronary Risk Evaluation equations, severe CKD (eGFR < 30 mL/min/1.73 m^2^), or diabetes with target organ damage are included in the very high CVD risk group.
-The current study found that many US adults with CKD (eGFR <60 mL/min/1.73 m^2^ or albuminuria) or diabetes did not have high ASCVD risk, defined as clinical CVD or 10-year ASCVD risk ≥ 10% according to the Pooled Cohort Risk equations.
+The current study found that a high percentage of US adults with CKD (eGFR <60 mL/min/1.73 m^2^ or albuminuria) or diabetes did not have high ASCVD risk, defined as clinical CVD or 10-year ASCVD risk ≥ 10% according to the Pooled Cohort Risk equations.
 Future studies may assess generalization of the current study's findings to the ESC/ESH guideline by estimating the proportion of European adults with diabetes and target organ damage or severe CKD that have clinical CVD or 10-year CVD mortality risk ≥ 10% according to the Systematic Coronary Risk Evaluation equations."
@@
 
-__Response__: We agree and have added heart rate in beats per minute to Table 1 and Table S1 of the revised manuscript.
+__Response__: We agree and have added heart rate in beats per minute to Table 1, Table S2, and Table S3 of the revised manuscript.
 
@@
 
-__Response__: We are happy to provide these data for the reviewer.
-All NHANES participants were eligible to complete an interview with a trained survey interviewer involving dietary Supplements and prescription medications.
-The questions related to prescription medications cover the use of prescription medications during a one-month period prior to the survey date.
-During the interview, the number of prescription medications taken during the previous month was assessed.
+__Response__: During the interview, the number of prescription medications taken during the previous month was assessed through a medication inventory.
 Data from participants taking antihypertensive medication in the current analysis indicate that the mean (standard error) number of prescription medications taken for US adults from 2013 through 2018 was `r rx_stats$mean` (`r rx_stats$se`), and the median (25^th^, 75^th^ percentile) was `r rx_stats$q50` (`r rx_stats$q25`, `r rx_stats$q75`).
 Since these medication data are not limited to prescriptions written for lowering blood pressure, we have not included these results in the updated manuscript.
+
+We also computed the number of antihypertensive medication classes used by participants who reported taking antihypertensive medications and had at least 1 antihypertensive medication class in their medication inventory.
+We have updated the manuscript with these results.
+On page 8, we write "Blood and urine samples were collected and a medication inventory was conducted during the medical examination.
+Antihypertensive medication classes were defined according to the 2017 ACC/AHA BP guideline." On page 9-10, we write "Among participants who reported taking antihypertensive medication and had at least 1 antihypertensive medication class in their medication inventory, the mean, median, and distribution of the number of classes of antihypertensive medication being used was estimated." On page 11, we write "Among US adults who reported using antihypertensive medication and had at least 1 antihypertensive medication class in their medication inventory, the median number of classes was 2 and 23.4% were taking 3 or more classes (Table S1)." We have also included a supplemental table showing the mean, median, and distribution of the number of antihypertensive medication classes used by US adults who reported using antihypertensive medication and had at least 1 antihypertensive medication class in their medication inventory (see Table S1 in revised manuscript).
 
@@
 We grouped study participants into 4 non-overlapping groups based on blood pressure.
-A fifth group contained participants who were taking antihypertensive medications.
-Therefore, none of the participants with stage 1 hypertension were taking antihypertensive medications.
-We apologize for the lack of clarity and have added the following footnote to Table S1 to indicate that participants with stage 1 hypertension were not taking antihypertensive medication: "Stage 1 hypertension was defined as having untreated systolic blood pressure between 130 and 139 mm Hg with diastolic blood pressure < 90 mm Hg or diastolic blood pressure between 80 and 89 mm Hg with systolic blood pressure < 90 mm Hg"
+A fifth group contained participants who reported taking antihypertensive medications.
+Therefore, none of the participants with stage 1 hypertension reported taking antihypertensive medications.
+We apologize for the lack of clarity and have added the following footnote to Table S1 (note: Table S1 is Table S2 in the revised manuscript) to indicate that participants with stage 1 hypertension did not report taking antihypertensive medication: "Stage 1 hypertension was defined as having untreated systolic blood pressure between 130 and 139 mm Hg with diastolic blood pressure < 90 mm Hg or diastolic blood pressure between 80 and 89 mm Hg with systolic blood pressure < 90 mm Hg"

### 2021-09-26 doc/ACCAHA_BP_groups.Rmd
resubmitted to JoH

@@
       fig_central_illustration,
-      perc_assumed_highrisk)
+      perc_assumed_highrisk,
+      tbl1_s1hyp,
+      tbl1_s1hyp_lowrisk)
 
@@
 
-Blood and urine samples were collected during the medical examination.
+Blood and urine samples were collected `r make_revision("and a medication inventory was conducted")` during the medical examination.
+`r make_revision(" Antihypertensive medication classes were defined according to the 2017 ACC/AHA BP guideline")` [@whelton20182017].
 Serum creatinine, serum glucose and glycated hemoglobin were measured using standard methods.
@@
 The percentage of US adults in each of the five categories based on BP and antihypertensive medication use was computed.
-`r make_revision("The percentage of US adults with stage 1 hypertension and 10-year predicted ASCVD risk < 10% assumed to have high ASCVD risk by the ACC/AHA guideline due to diabetes, CKD, or age was also computed.")` The 25^th^, 50^th^, and 75^th^ percentile of 10-year predicted ASCVD risk and the percentage of participants with high ASCVD risk were estimated for the overall population and within each of the five categories based on BP and antihypertensive medication use.
+`r make_revision("Among participants who reported taking antihypertensive medication and had at least 1 antihypertensive medication class in their medication inventory, the mean, median, and distribution of the number of classes of antihypertensive medication being used was estimated.")` `r make_revision("The percentage of US adults with stage 1 hypertension and 10-year predicted ASCVD risk < 10% assumed to have high ASCVD risk by the ACC/AHA guideline due to diabetes, CKD, or age was also estimated.")` The 25^th^, 50^th^, and 75^th^ percentile of 10-year predicted ASCVD risk and the percentage of participants with high ASCVD risk were estimated for the overall population and within each of the five categories based on BP and antihypertensive medication use.
 To assess the extent to which participants with a 10-year predicted ASCVD risk < 10% were close to the 10% threshold, we estimated the distribution of 10-year predicted ASCVD risk.
@@
 Data analysis was conducted using `r R_string_fancy` along with a collection of open-source software packages [@cite_R; @cite_drake; @cite_tidyverse; @cite_table.glue].
+The datasets generated during and/or analyzed during the current study are publicly available.
 The first author's GitHub repository (https://github.com/bcjaeger/ACC-AHA-BP-guideline-groups) provides code to reproduce the current study.
@@
 
+```{r}
+loadd(tbl_bpmeds)
+
+overall_3meds_or_more <- 
+  tbl_bpmeds$inline$overall[c('n_3', 'n_4', 'n_5', 'n_6')] %>% 
+  map_chr(str_remove, '%') %>% 
+  map_dbl(as.numeric) %>% 
+  sum()
+
+overall_meds_median <- tbl_bpmeds$inline$overall$median_iqr %>% 
+  bracket_drop()
+```
+
 Among US adults aged 40 to 79 years in `r min(exams)`-`r max(exams)+1`, the estimated prevalence (95% confidence interval [CI]) of diabetes and CKD was `r inline$prevDiabetesOverall` and `r inline$prevCkdOverall`, respectively, `r inline$prevAge65Overall` were estimated to be ≥ 65 years of age, and `r inline$prevAnyOverall` had diabetes, CKD, or ≥ 65 years of age (`r refer_to('tab_characteristics')`).
 The estimated prevalence (95% CI) of stage 1 hypertension was `r inline$prevS1hOverall` overall and `r inline$prevS1hDiabetes`, `r inline$prevS1hCkd`, `r inline$prevS1hAge65`, and `r inline$prevS1hAny` among those with diabetes, CKD, age ≥ 65 years, and at least one of these conditions, respectively (`r refer_to('tab_bpdist')`).
-`r make_revision(paste0("Overall, ", table_value(perc_assumed_highrisk), "% of those with stage 1 hypertension and without high ASCVD risk were assumed to have high ASCVD risk by the ACC/AHA BP guideline."))` Characteristics of US adults 40 to 79 years of age with stage 1 hypertension, overall and for subgroups defined by diabetes, CKD and age ≥ 65 years, are presented in Table S1.
+`r make_revision(text = paste0("Among US adults who reported using antihypertensive medication and had at least 1 antihypertensive medication class in their medication inventory, the median number of classes was ", overall_meds_median, " and ", overall_3meds_or_more,"% were taking 3 or more classes (", refer_to("tab_bpmeds"), ")") )`.
+Characteristics of US adults 40 to 79 years of age with stage 1 hypertension are presented in `r refer_to("tab_risk_stg1")`.
+`r make_revision(paste0("Among US adults with stage 1 hypertension and 10-year predicted ASCVD risk < 10%, ", table_value(perc_assumed_highrisk), "% were assumed to have high ASCVD risk by the ACC/AHA BP guideline due to diabetes, CKD, or \u2265 65 years of age.
+Among those with predicted ASCVD risk < 10% and assumed to have high ASCVD risk by the guideline, ", tbl1_s1hyp_lowrisk$inline$any$sex$Female,  "% were women (", refer_to("tab_lowrisk_stg1"), ")."))`
 
@@
 
-`r make_revision("The 2017 ACC/AHA BP guideline's definition of hypertension and recommendations for initiating antihypertensive medication differ from other guidelines published from 2015-2020.
+The 2017 ACC/AHA BP guideline's definition of hypertension and recommendations for initiating antihypertensive medication differ from other guidelines published between 2015 and 2020.
 For example, the 2018 European Society of Cardiology (ESC) and European Society of Hypertension (ESH) BP guideline recommends considering initiation of antihypertensive medication for adults at very high risk of CVD with untreated SBP between 130 and 139 mm Hg or untreated DBP between 85 and 89 mm Hg.
@@
 The current study found that many US adults with CKD (eGFR <60 mL/min/1.73 m^2^ or albuminuria) or diabetes did not have high ASCVD risk, defined as clinical CVD or 10-year ASCVD risk ≥ 10% according to the Pooled Cohort Risk equations.
-Future studies may assess generalization of the current study's findings to the ESC/ESH guideline by estimating the proportion of European adults with diabetes and target organ damage or severe CKD that have clinical CVD or 10-year CVD mortality risk")` ≥ `r make_revision("10% according to the Systematic Coronary Risk Evaluation equations.")`
+Future studies may assess generalization of the current study's findings to the ESC/ESH guideline by estimating the proportion of European adults with diabetes and target organ damage or severe CKD that have clinical CVD or 10-year CVD mortality risk ≥ 10% according to the Systematic Coronary Risk Evaluation equations.
 
@@
 `r make_revision("Clinical CVD status may also have been mis-classified as it was determined by self-report rather than diagnostic imaging.
-The current analysis also did not account for target organ damage, which is a strong predictor of CVD risk.")` A total of `r table_value(sum(current_analysis$data$bp_cat == 'Stage 1 hypertension'))` participants had stage 1 hypertension, and some subgroups of this population based on diabetes, CKD, and ≥ 65 years of age were small.
+The current analysis also did not account for target organ damage, e.g.
+left-ventricular hypertrophy, that predict CVD risk.")` A total of `r table_value(sum(current_analysis$data$bp_cat == 'Stage 1 hypertension'))` participants had stage 1 hypertension, and some subgroups of this population based on diabetes, CKD, and ≥ 65 years of age were small.
 
@@
 
+\newpage
+
+`r rp$supplement.table$caption[3]` 
+`r fp_par(line_spacing = 1)`
+`r rp$supplement.table$object[[3]]`
+
 <!-- SUPPLEMENTAL FIGURES -->

### 2021-09-26 R/clean_bp_meds.R

@@ -1,0 +1,28 @@
+#' .. content for \description{} (no empty lines) ..
+#'
+#' .. content for \details{} ..
+#'
+#' @title
+
+#' @return
+#' @author bcjaeger
+#' @export
+clean_bp_meds <- function() {
+
+  has_label <- function(x) !is.null(attr(x, 'label'))
+
+  list.files('data_htn_meds', full.names = TRUE) |>
+    set_names(c('2013-2014',
+                '2015-2016',
+                '2017-2017')) |>
+    map(read_sas) |>
+    map(select, where(has_label)) |>
+    bind_rows(.id = 'exam') |>
+    rowwise() |>
+    mutate(meds_n_bp_classes = sum(TD, ACEI, ARBs, CCB,
+                                   LOOP, KSPARING, ALDO,
+                                   BB, DRI, AB, CA, DV),
+           .before = TD) %>%
+    rename(seqn = SEQN)
+
+}

### 2021-09-26 R/compile_report.R

@@ -32,6 +32,7 @@ compile_report <- function(exams,
                            tbl1_s1hyp,
                            tbl1_s1hyp_lowrisk,
                            tbl_bpdist,
+                           tbl_bpmeds,
                            tbl_risk_overall,
                            tbl_risk_overall_supp,
                            tbl_exclusions,
@@ -119,6 +120,17 @@ compile_report <- function(exams,
   ) %>%
     map_chr(table_value)
 
+  analysis_bpmeds <- filter(analysis, meds_bp == 'yes' & meds_n_bp_classes > 0)
+
+  N_bpmeds_unwtd <- list(
+    ovrl         = nrow(analysis_bpmeds),
+    diab         = sum(analysis_bpmeds$diabetes == "yes"),
+    ckd          = sum(analysis_bpmeds$ckd == "yes"),
+    age_gt65     = sum(analysis_bpmeds$age_gt65 == "yes"),
+    any          = sum(analysis_bpmeds$any_ckd_diab_age65 == "yes")
+  ) %>%
+    map_chr(table_value)
+
   .s1h <- filter(analysis, bp_cat == 'Stage 1 hypertension')
 
   N_s1h_unwtd <- list(
@@ -188,6 +200,7 @@ compile_report <- function(exams,
   }
 
   col_labels_ovrl <- col_labels(N_vals = N_ovrl_unwtd)
+  col_labels_bpmeds <- col_labels(N_vals = N_bpmeds_unwtd)
   col_labels_s1h <- col_labels(N_vals = N_s1h_unwtd)
   col_labels_age40to79 <- col_labels(N_vals = N_age40to79_unwtd)
   col_labels_s1h_lowrisk <- col_labels(N_s1h_lowrisk_unwtd)
@@ -255,8 +268,8 @@ compile_report <- function(exams,
     add_header_row(values = c("", "Sub-groups"), colwidths = c(2, 4)) %>%
     theme_box() %>%
     height(height = 1.5, part = 'header') %>%
-    width(width = 1.15) %>%
-    width(j = ~bp_cat, width = 1.75) %>%
+    width(width = 1.1) %>%
+    width(j = ~bp_cat, width = 1.65) %>%
     align(align = 'center', part = 'all') %>%
     align(j = 1, align = 'left', part = 'all') %>%
     footnote(i=2, j=1, part='header', value=bp_cat_guide, ref_symbols=fts[1]) %>%
@@ -274,6 +287,74 @@ compile_report <- function(exams,
     object = list(.tbl_bpdist),
[…]

### 2021-09-26 R/derive_others.R

@@ -109,8 +109,21 @@ derive_others <- function(data, exams,
       bp_dia_mmhg,
       pulse_60s,
       meds_bp,
+      TD,
+      ACEI,
+      ARBs,
+      CCB,
+      LOOP,
+      KSPARING,
+      ALDO,
+      BB,
+      DRI,
+      AB,
+      CA,
+      DV,
       meds_statin = statin,
       meds_n_taken = rx_number_taken,
+      meds_n_bp_classes,
       smk_current,
       age_group,
       age_40to79,

### 2021-09-26 R/plan.R

@@ -42,6 +42,11 @@ the_plan <- drake_plan(
   qx_high_blood_pressure    = clean_qx_high_bp(exams),
   qx_healthcare_utilization = clean_qx_healthcare_utilization(exams),
 
+  # Anti-hypertensive medication classes
+  # These only work for 2013-2014, 2015-2016, and 2017-2018
+  # they were just added at the last minute before re-submission
+  # in response to a reviewer's request.
+  bp_meds = clean_bp_meds(),
 
   statins = clean_rx_statin(exams),
 
@@ -62,7 +67,8 @@ the_plan <- drake_plan(
       qx_diabetes,
       qx_high_blood_pressure,
       qx_healthcare_utilization,
-      statins
+      statins,
+      bp_meds
     ),
     .f = left_join,
     by = c('exam', 'seqn')
@@ -131,6 +137,7 @@ the_plan <- drake_plan(
     "Systolic blood pressure, mm Hg" = "bp_sys_mmhg",
     "Diastolic blood pressure, mm Hg" = "bp_dia_mmhg",
     "Antihypertensive medication use" = "meds_bp",
+    "Statin use" = "meds_statin",
     "Diabetes" = "diabetes",
     "CKD" = "ckd",
     "Aged 65+ years" = "age_gt65",
@@ -150,6 +157,7 @@ the_plan <- drake_plan(
                                                 tbl1_variables),
 
   tbl_bpdist = tabulate_bpdist(design_overall),
+  tbl_bpmeds = tabulate_bpmeds(design_overall),
 
   perc_assumed_highrisk = compute_perc_assumed_highrisk(design_s1hyp_lowrisk),
 
@@ -188,7 +196,9 @@ the_plan <- drake_plan(
                                            fig_text = fig_text),
 
 
-  inline = make_inline_results(design_overall, design_s1hyp, risk_models),
+  inline = make_inline_results(design_overall,
+                               design_s1hyp,
+                               risk_models),
 
   fig_central_illustration = visualize_central_illustration(tbl_bpdist$table,
                                                             inline),
@@ -208,6 +218,7 @@ the_plan <- drake_plan(
     tbl1_s1hyp$table,
     tbl1_s1hyp_lowrisk$table,
     tbl_bpdist$table,
+    tbl_bpmeds$table,
     tbl_risk_overall,
     tbl_risk_overall_supp,
     current_analysis$tbl,

### 2021-09-26 R/tabulate_bpmeds.R

@@ -1,0 +1,115 @@
+#' .. content for \description{} (no empty lines) ..
+#'
+#' .. content for \details{} ..
+#'
+#' @title
+#' @param design_overall
+#' @return
+#' @author bcjaeger
+#' @export
+tabulate_bpmeds <- function(design) {
+
+  fix_names <- function(.x, first_name = 'meds_n_bp_classes'){
+    if(ncol(.x) == 3){
+      set_names(.x, c(first_name, 'level', 'n'))
+    } else {
+      set_names(.x, c(first_name, 'n'))
+    }
+  }
+
+  formulae <- list(
+    overall = ~ meds_n_bp_classes,
+    diabetes = ~ meds_n_bp_classes + diabetes,
+    ckd = ~ meds_n_bp_classes + ckd,
+    # diabetes_and_ckd = ~ bp_cat + diabetes_and_ckd,
+    age_group = ~ meds_n_bp_classes + age_gt65,
+    any = ~ meds_n_bp_classes + any_ckd_diab_age65
+  )
+
+  # class_counts: determine the proportion of survey participants
+  # taking 0, 1, 2, ... 6 classes of medication overall and among
+  # study subgroups.
+
+  .design <- subset(design, meds_bp == 'yes' & meds_n_bp_classes > 0)
+
+  class_counts <- formulae %>%
+    map(svytable, design = .design) %>%
+    map(as_tibble) %>%
+    map_dfr(fix_names, .id = 'variable') %>%
+    filter(level == 'yes' | is.na(level)) %>%
+    select(-level) %>%
+    group_by(variable) %>%
+    mutate(tbl_val = table_glue("{100 * n / sum(n)}%")) %>%
+    select(variable, meds_n_bp_classes, tbl_val)
+
+  # mm_smry: Median/mode summary of the number of medications taken
+
+  rspec_2dig <- round_spec() %>%
+    round_using_decimal(digits = 2)
+
+  mm_design <- subset(design, meds_bp == 'yes'& meds_n_bp_classes > 0)
+
+  mm_designs <- list(
+    overall = mm_design,
+    diabetes = subset(mm_design, diabetes == 'yes'),
+    ckd = subset(mm_design, ckd == 'yes'),
+    age_group = subset(mm_design, age_gt65 == 'yes'),
+    any = subset(mm_design, any_ckd_diab_age65 == 'yes')
+  )
+
+  mean_smry <-
+    map(mm_designs,
+        .f = ~svymean(~meds_n_bp_classes,
[…]

### 2021-09-26 packages.R

@@ -48,4 +48,5 @@ conflicted::conflict_prefer('summarize', 'dplyr')
 conflicted::conflict_prefer("gather",    "tidyr")
 conflicted::conflict_prefer("set_names", "purrr")
 conflicted::conflict_prefer("make",      "drake")
-conflicted::conflict_prefer("expand", "tidyr")
+conflicted::conflict_prefer("expand",    "tidyr")
+conflicted::conflict_prefer("discard",   "purrr")

### 2021-09-26 R/make_inline_results.R
bug fix for survey package 4.1
an update to svyquantile broke existing code. The new svyquantile
object is different from the older versions of it and it also
does not have an as.data.frame message. So I had to get elements
from the new svyquantile object, move them around, and convert them
to a data frame.

@@ -105,8 +105,14 @@ make_inline_results <- function(design_overall,
     design = subset(design_overall, ever_had_ascvd == 'no'),
     quantiles = c(0.25, 0.50, 0.75)
   ) %>%
-    as_tibble() %>%
-    set_names(c('lwr', 'est', 'upr')) %>%
+    getElement('ascvd_risk_pcr') %>%
+    as_tibble(rownames = 'prob') %>%
+    mutate(prob = recode(prob,
+                         '0.25' = 'lwr',
+                         '0.5' = 'est',
+                         '0.75' = 'upr')) %>%
+    select(-ci.2.5, -ci.97.5, -se) %>%
+    pivot_wider(names_from = prob, values_from = quantile) %>%
     mutate_all(~.x * 100) %>%
     transmute(string = table_glue("{est}% ({lwr}%, {upr}%)")) %>%
     pull(string)
@@ -117,8 +123,14 @@ make_inline_results <- function(design_overall,
                     ever_had_ascvd == 'no'),
     quantiles = c(0.25, 0.50, 0.75)
   ) %>%
-    as_tibble() %>%
-    set_names(c('lwr', 'est', 'upr')) %>%
+    getElement('ascvd_risk_pcr') %>%
+    as_tibble(rownames = 'prob') %>%
+    mutate(prob = recode(prob,
+                         '0.25' = 'lwr',
+                         '0.5' = 'est',
+                         '0.75' = 'upr')) %>%
+    select(-ci.2.5, -ci.97.5, -se) %>%
+    pivot_wider(names_from = prob, values_from = quantile) %>%
     mutate_all(~.x * 100) %>%
     transmute(string = table_glue("{est}% ({lwr}%, {upr}%)")) %>%
     pull(string)
@@ -129,8 +141,14 @@ make_inline_results <- function(design_overall,
                     diabetes == 'yes' & ever_had_ascvd == 'no'),
     quantiles = c(0.25, 0.50, 0.75)
   ) %>%
-    as_tibble() %>%
-    set_names(c('lwr', 'est', 'upr')) %>%
+    getElement('ascvd_risk_pcr') %>%
+    as_tibble(rownames = 'prob') %>%
+    mutate(prob = recode(prob,
+                         '0.25' = 'lwr',
+                         '0.5' = 'est',
+                         '0.75' = 'upr')) %>%
+    select(-ci.2.5, -ci.97.5, -se) %>%
[…]

### 2021-09-26 R/plan.R

@@ -13,7 +13,7 @@
 
 the_plan <- drake_plan(
 
-  exams = c(2013, 2015, 2017),
+  exams = c(2011, 2013, 2015, 2017),
 
   # phrases to be used consistently throughout project
   risk_10yr = '10-year predicted risk for ASCVD',

### 2021-09-26 R/tabulate_bpmeds.R

@@ -76,10 +76,14 @@ tabulate_bpmeds <- function(design) {
                           quantiles = c(0.25, 0.50, 0.75),
                           na.rm = TRUE)
     ) %>%
-    map_dfr(as_tibble, .id = 'variable') %>%
-    rename(lwr = `0.25`,
-           est = `0.5`,
-           upr = `0.75`) %>%
+    map(getElement, 'meds_n_bp_classes') %>%
+    map_dfr(as_tibble, .id = 'variable', rownames = 'prob') %>%
+    mutate(prob = recode(prob,
+                         '0.25' = 'lwr',
+                         '0.5' = 'est',
+                         '0.75' = 'upr')) %>%
+    select(-ci.2.5, -ci.97.5, -se) %>%
+    pivot_wider(names_from = prob, values_from = quantile) %>%
     mutate(across(.cols = c(lwr, est, upr),
                   .fns = as.integer),
            tbl_val = table_glue("{est} ({lwr}, {upr})"),

### 2021-09-26 R/tabulate_risk_summary.R

@@ -86,9 +86,9 @@ tabulate_risk_summary <- function(design) {
 
   md_risk_ovrl_ovrl <-
     tibble(
-      est = as.numeric(md_risk_init)[2],
-      lwr = as.numeric(md_risk_init)[1],
-      upr = as.numeric(md_risk_init)[3],
+      est = as.numeric(md_risk_init$ascvd_risk_pcr[,'quantile'])[2],
+      lwr = as.numeric(md_risk_init$ascvd_risk_pcr[,'quantile'])[1],
+      upr = as.numeric(md_risk_init$ascvd_risk_pcr[,'quantile'])[3],
       variable = 'Overall',
       level = NA_character_
     )
@@ -111,8 +111,11 @@ tabulate_risk_summary <- function(design) {
       )
     ) %>%
     map(as_tibble) %>%
-    map(rename, lwr = `0.25`, est = `0.5`, upr = `0.75`) %>%
-    map(select, -starts_with('se.0')) %>%
+    map(rename,
+        lwr = `ascvd_risk_pcr.0.25`,
+        est = `ascvd_risk_pcr.0.5`,
+        upr = `ascvd_risk_pcr.0.75`) %>%
+    map(select, -starts_with('se.')) %>%
     map(mutate_if, is.factor, as.character) %>%
     map(standardize_names) %>%
     bind_rows(.id = 'variable') %>%
@@ -137,9 +140,11 @@ tabulate_risk_summary <- function(design) {
         ci = TRUE
       )
     ) %>%
-    map(as_tibble) %>%
-    map(rename, lwr = `0.25`, est = `0.5`, upr = `0.75`) %>%
-    map(select, -starts_with('se.0')) %>%
+    map(rename,
+        lwr = `ascvd_risk_pcr.0.25`,
+        est = `ascvd_risk_pcr.0.5`,
+        upr = `ascvd_risk_pcr.0.75`) %>%
+    map(select, -starts_with('se.')) %>%
     map(mutate_if, is.factor, as.character) %>%
     map(standardize_names) %>%
     bind_rows(.id = 'variable') %>%

### 2021-09-26 R/visualize_risk_bnry.R

@@ -31,8 +31,16 @@ visualize_risk_bnry <- function(risk_models,
     .f = ~ svyquantile(
       x = ~ age,
       design = .x,
-      quantiles = c(0.25, 0.50, 0.75)) %>%
-      as_tibble() %>%
+      quantiles = c(0.25, 0.50, 0.75)
+    ) %>%
+      getElement('age') %>%
+      as_tibble(rownames = 'prob') %>%
+      mutate(prob = recode(prob,
+                           '0.25' = 'lwr',
+                           '0.5' = 'est',
+                           '0.75' = 'upr')) %>%
+      select(-ci.2.5, -ci.97.5, -se) %>%
+      pivot_wider(names_from = prob, values_from = quantile) %>%
       pivot_longer(cols = everything())
   ) %>%
     bind_rows(.id = '.variable') %>%

### 2021-09-28 R/plan.R
go back to original years
Ran a test to make sure I could add an exam, now back to the main
analysis.

@@ -13,7 +13,7 @@
 
 the_plan <- drake_plan(
 
-  exams = c(2011, 2013, 2015, 2017),
+  exams = c(2013, 2015, 2017),
 
   # phrases to be used consistently throughout project
   risk_10yr = '10-year predicted risk for ASCVD',

### 2021-09-28 R/visualize_central_illustration.R

@@ -74,26 +74,16 @@ visualize_central_illustration <- function(tbl_bpdist, inline) {
     geom_text(aes(y=-6), size = 7.25, family = 'serif') +
     scale_y_continuous(limits = c(-8, 60)) +
     labs(x = '', y = '') +
-    scale_fill_manual(
-      values = c(
-        'purple',
-        brocolors('crayons')['Orange Red'],
-        brocolors('crayons')['Orange'],
-        brocolors('crayons')['Green Yellow'],
-        brocolors('crayons')['Green']
-      )
-    ) +
+    scale_fill_discrete()+
     geom_text(data = text,
               size = 5.5,
               family = 'serif',
               nudge_x = -.18,
-              color = brocolors('crayons')['Orange'],
               show.legend = FALSE) +
     geom_text(data = text_spanner,
               size = 5.5,
               family = 'serif',
-              nudge_x = .55,
-              color = brocolors('crayons')['Orange']) +
+              nudge_x = .55) +
     coord_flip() +
     ggtitle(label = 'US adults aged 40-79 years')
 
